### 2017-01-02 paper.Rmd
paper started

---
title: Silent pessimists - researchers' perceptions of malaria eradication and implications for health spending
author:
  - name: Joe Brew
    email: joebrew@economicsofmalaria.com
    affiliation: isglobal,cism
    footnote: Corresponding Author
  - name: Laia Cirera Crivillé
    email: laia.cirera@isglobal.org 
    affiliation: isglobal,cism
  - name: Elisa Sicuri
    email: elisa.sicuri@isglobal.org 
    affiliation: isglobal,icl,cism
address:
  - code: isglobal
    address: Barcelona Institute for Global Health, c/ Rosselló, 132, 5è 2a. 08036, Barcelona, Spain
  - code: icl
    address: Imperial College London, South Kensington Campus, London SW7 2AZ, U.K.
  - code: cism
    address: Centro de Investigação em Saúde de Manhiça, Vila da Manhiça, Bairro Cambeve, Rua 12, Distrito da Manhiça, CP 1929, Maputo, Mozambique
abstract: |
  Quantifying an event's probability and time frame is essential for calculating its expected value. In the case of global malaria eradication, uncertainty regarding feasibility makes it difficult for policymakers and public health practitioners to make fully informed decisions. The opportunity cost of investments in eradication-specific interventions can be high, particularly in contexts with other urgent health priorities. In a systematic survey of malaria researchers, we query perceptions regarding the likelihood and time frame of eradication, as well as the perceived chief areas needed for improvement in order for eradication to be achieved. We assess pessimism/optimism (via the proxy of years-to-eradication), broken down by area of expertise. Our results, which suggest a disconnect between public institutional discourse and private opinion, serve as a barometer of professional perspectives, and serve to highlight areas where attention is most needed for eradication to be achieved.

bibliography: library.bib
output: rticles::elsevier_article
---

```{r, echo = FALSE, warning = FALSE, message = FALSE, comment = NA, error= FALSE, cache = F}
# No scientific notation
options(scipen=999)

# Packages (load child-specific packages in their respective files)
library(knitr)
library(dplyr)
library(ggplot2)
library(DT)
library(tidyr)

# Basic knitr options
opts_chunk$set(comment = NA, 
               echo = FALSE, 
               warning = FALSE, 
               message = FALSE, 
               error = TRUE, 
               cache = FALSE)
```

```{r}
# Send emails
source('code/recruit.R', chdir = TRUE)

# Load data
file_name <- paste0('snapshot_', Sys.Date(), '.RData')
if(!file_name %in% dir('snapshots')){
  # Fetch data
  library(gsheet)
  url_responses<- 'https://docs.google.com/spreadsheets/d/1yeQ4TR73mdnDABPZ-ZEg3DAFu2Bko5NJ_nkMcNKr2lo/edit?usp=sharing'
  df <- gsheet2tbl(url_responses)

  # Manually rename variables
  names(df) <- tolower(gsub('.', '_', names(df), fixed = TRUE))
  names(df)[4:17] <-
    c('area',
      'years_10',
      'years_20',
      'years_30',
      'years_40',
      'years_50',
      'years',
      'governance',
      'health_workforce',
      'health_financing',
      'health_technologies',
      'health_information',
      'service_delivery',
      'comments')

  # Save a snapshot
  save(df, 
       file = paste0('snapshots/',
                     file_name))
} else {
  load(paste0('snapshots/',
              file_name))
}
```

```{r}
# Clean up survey responses
# Make NA all empty responses
df$comments[df$comments == ''] <- NA
df$email_address[df$email_address == ''] <- NA
# Flag duplicates
df$duplicate <- duplicated(df$email_address)
# Remove duplicates
df <- df[is.na(df$email_address) |
           !df$duplicate,]
# Create area dummies
df$area <- tolower(df$area)
df$area <- gsub('/', ', ', df$area)
df$area <- gsub('(', '', df$area, fixed = TRUE)
df$area <- gsub(')', '', df$area, fixed = TRUE)
areas <- tolower(paste0(sort(unique(df$area)), collapse = ', '))
areas <- sort(unique(unlist(strsplit(x = areas, split = ','))))
for (j in 1:length(areas)){
  df[,paste0(
    'area_',
    areas[j]
  )] <- NA
}
for (j in 1:length(areas)){
  df[,paste0(
    'area_',
    areas[j]
  )] <- grepl(areas[j], df$area)
}

# Make years numeric
df$years <- tolower(df$years)
# more needs to be done here

# Make comments standardized
df$comments <- tolower(df$comments)

df <- data.frame(df)

# Clean up missing responses
for (i in seq(10, 50, 10)){
  df[,paste0('years_', i)][df[,paste0('years_', i)] == ''] <- NA
  df[,paste0('years_', i)] <-
    factor(df[,paste0('years_', i)],
           levels = c('0%',
                      '1-20%',
                      '21-40%',
                      '41-60%',
                      '61-80%',
                      '81-99%',
                      '100%'))
}

years_data <- 
  gather(df, key,
         value, 
         years_10:years_50)

# plot
ggplot(data = years_data %>%
         filter(!is.na(value)),
       aes(x = value)) +
  geom_bar() +
  facet_wrap(~key) +
  theme_classic()

# library(wordcloud2)
# areas_df <- data.frame(word = areas)
# areas_df$freq <- NA
# for (i in 1:nrow(areas_df)){
#   areas_df$freq[i] <-
#     length(which(grepl(areas_df$word[i], df$area)))
# }
# areas_df <- areas_df %>% filter(word != '')
# wordcloud2(data = areas_df,
#            color = 'black', 
#            size = 2, minRotation = -pi/6, maxRotation = pi/6,
#   rotateRatio = 0.9)
```

```{r}
# Results cleanup
```

# Introduction

## Background

The scientific and public health communities have had eradication on their long-term agenda since the WHO established the Global Malaria Eradication Program in the 1950s [@Njera2011]. Following the failure of the WHO's first attempt, the focus shifted away from global eradication and towards local elimination and control strategies.

In recent years, much of the discourse regarding malaria has shifted back to global eradication [@Roberts2007], with funders, researchers, and public health practitioners rallying to the cause [@Tanner2015]. The Bill and Melinda Gates Foundation has begun actively promoting eradication as feasible "within a generation" [@Gates2014], and the leadership of the World Health Organization (WHO) has supported this goal. Even in areas of high endemicity, advances in immunology, parasitology, modeling and vaccinology, along with rapid economic development, have made eradication appear a more feasible goal, even if not possible in the short term [@Snow2015, @Eckhoff2014]. From both administrative [@Yamey2004] and scientific [@Alonso2011] points of view, eradication has never before received so much attention, nor appeared so within grasp.

Most of the current research on expert opinion regarding the feasibility of malaria eradication focuses on the \emph{how} rather than the \emph{if} and the \emph{when} [@Tanner2015]. The participants in the Malaria Eradication Research Agenda (MalERA) process, in particular, have positioned themselves as thought leaders in the field of guiding research goals and identifying gaps in order for elmination to occur [@Alonso2011]. Though the MalERA authors firmly state that eradication is \emph{not} feasible given the "current tools and state of knowledge", mentions to the time frame are vague ("within the lifetime of young scientists just embarking on their careers") and no mention is made of the perception of the probability of achieving eradication.

## The problem

The WHO Global Malaria Programme (GMP) has acknowledged that it "needs to take an official position on how and under what timeline malaria eradication could be achieved" [@WHO2015]. Such a position could inform policy, and plays a crucial role in the economic analysis of the expected value of malaria control inteventions.

However, no such position has been taken. This omission is likely intentional, and certainly understadable, given that MalERA's and the WHO GMP's goals are to guide research and technology in the direction of eradication, and not necessarily address the larger and much more subjective questions of \emph{if} and \emph{when}.

But just how close are we to eradication? The objective serves to inspire, rally funder support, motivate researchers, and focus the efforts of public health practitioners. Proponents of disease eradication point to the success of historical and current campaigns (smallpox and polio, respectively), and highlight the benefits in health and wealth to future generations. However, the opportunity cost of investments in eradication-specific interventions can be high. And the “expected value” of an investment in a binary scenario (eradication or not) is a function of the probability of the scenario’s occurrence, and the temporal lag of that occurrence. Therefore, knowing the likelihood and time frame of eradication of malaria is essential for making sound investments in health.

## The need for the wisdom of crowds

Patients often ask for a “second opinion”, a request which implicitly recognizes two important truths: (1) that an expert can sometimes be wrong and (2) that the combined opinions of multiple people can better approximate the truth than the opinion of only one. As Sir Francis Galton demonstrated in his famous ox-weight experiment [@Wallis2014], averaging the opinions of many can be more accurate than taking the opinion of any single expert, since the biases of diverse viewpoints can be complementary and symbiotic.

Additionally, one could argue that assessing likelihood and time frame of eradication is too important, subjective and complex a task to be left to only powerful individuals or small panels and committees. It requires the “wisdom of crowds.” Measuring consensus and discord among disease-specific researchers from a variety of disciplines can serve as a barometer of (informed) opinion, both guiding resources and identifying areas of concern [@Keenan2013].

## The justification

A great deal of previous research already covers the the cost per case prevented [@Sicuri2011, @Silumbe2015, @Btto2016, @IlungaIlunga2014, @Dalaba2015]. Likewise, a literature exists which could serve as a model for quantifying the location-specific opportunity costs associated with funneling funds towards malaria eradication [@Stuckey2014, @White2011, @Korenromp2012]. The correct discount rate for estimating the value of future lives saved is more of a philosphical question than an economic one. This leaves only the probability and time-frame to eradication, questions which have been addressed anecdotally, but never answered quantitatively.

The economic case for striving to achieve malaria eradication is compelling [@Barofsky2015]. Though the case-specific marginal cost of eradication can be expected to be high (relative to a simple control approach), successful eradication would mean massive recurring savings in the long-term [@Barrett2013]. However, to the extent that the case-specific marginal cost of prevention in an eradication campaign is high, estimating the likelihood of success is fundamental to the correct distribution of resources, particularly in low-income environments.

In other words, the rational assignment of resources for malaria eradication campaigns hinges on the expected value of those campaigns. We can describe this relationship formulaically below:

\begin{center}
$I_{T}$ = $P(x)_{}$ $\dfrac{B(m_{})}{m_{}}$(1 + $\delta$)$^{-T}$ -  $P(x)_{}$ $\dfrac{C(m_{})}{m_{}}$ (1 + $\delta$)$^{-T}$
\end{center}

\begin{itemize}
\item $ I $ is the return on investment
\item $ m $ is the number of malaria cases
\item $ x $ is the cut-off for a "successful campaign", ie the portion of eradication achieved
\item $ T $ is the time-frame (to both costs and benefits)
\item $ P $ is the probability of success
\item $ B $ is the benefit of preventing malaria
\item $ C $ is the cost of preventing malaria
\item $ \delta $ is the discount rate and opportunity cost
\end{itemize}

(I) is the return on investment at time (T) (the "end of malaria"). We take the present value of the benefits multiplied by the probability of succcess minus the value of costs times the probability of success, and multiplyboth terms by the discount rate traised to T to arrive at the return on investment.

## Objective

The objective of this study is simple: to help guide the optimal distribution of health resources by gauging (expert) opinion about, estimating the likelihood of, and quantifying the time frame to malaria eradication through a systematic survey of malaria research professionals from a wide array of academic disciplines.

# Methods

## Ethics

This research followed the principles of the Declaration of Helsinki. The study's protocol was approved by the Scientific Committee of the Barcelona Institute for Global Health.

## Participants

Our study population included all first authors (with available email addresses) returned in a PubMed search for the term "malaria" from January 1, 2010 through December 20, 2016. Personalized emails addressing the author by name and mentioning the relevant paper were sent to each of the `r nrow(email_df)` authors during the period from December 20, 2016 through January 2, 2017. Researchers were invited to participate by clicking a link to the survey form. Participants were informed directly on the survey form of the study's purpose, that responses were not guarnteed to be anonymous, and where to find further details on the study.

## Survey

The survey was simple, consisting of only name, email, and four content-related fields along with a "general comments" section. The survey was administered and data were collected through Google Drive. The original survey is viewable at [https://goo.gl/forms/IroAEooDuJ6KM5Ho2](https://goo.gl/forms/IroAEooDuJ6KM5Ho2).

Content-related survey fields consisted of:

1. Area of expertise.

2. Perceived probability (%) of malaria eradication in 10, 20, 30, 40, and 50 years.

3. Free choice perceived number of years until malaria eradication.

4. Ranking of the WHO's "health system building blocks" in regards to attention needed in order to achieve eradication.

## Analysis

Survey results were first analyzed descriptively. Following Francis Galton's example, we naively take the average of all responses as the likely point estimate for event probabilities, and the totality of the responses to each numeric question as the likely confidence interval of those likelihoods and time frames.

Ordinary least squares regression was employed to estimate the effect of area of expertise on the eradication pessimism-optimism (through the proxy of perceived years to eradication).

Content analysis of free text comments was carried out using frequency analyses. Comments were categorized and coded according to (more details needed here).

All analysis was carried out in R language [@R]. All analysis code, as well as the code used for the identification and contacting of participants, is publicly available at [https://github.com/joebrew/malaria_survey](https://github.com/joebrew/malaria_survey).

The searching and retrieval of information from the PubMed database was carried out using the RISmed package [@Kovalchik2015]. Qualitative analysis relied on the RQDA package (citation needed here).

# Results

A total of `r nrow(df)` researchers participated in the survey.

# Discussion

General note about pessimism.

General note about areas needing attention.

Difference between pessimism based on expertise.

## Limitations

No distinguishing of quality, experience, etc.

No inclusion of program workers

Potential bias due to non-anonymity

Flaws generally in wisdom of crowd approach

## Implications

References {#references .unnumbered}
==========

### 2017-01-02 code/recruit.R

@@ -305,15 +305,16 @@ sendify <- function(df){
     df$year,
     '.\n\n',
     'For my PhD research on the economics of malaria, I am conducting a ',
-    'survey of malaria research experts. The aim is to use a "wisdom of crowds" ',
-    'approach to gauge the likelihood and timeframe of eradication. I was hoping you would have two minutes or so ',
+    'survey of researchers. The aim is to use a "wisdom of crowds" ',
+    'approach to gauge the likelihood and timeframe of eradication. Given your research/publication history, ',
+    'I was hoping you would have two minutes or so ',
     'to answer a few questions. The survey is at ',
     'https://goo.gl/forms/IroAEooDuJ6KM5Ho2 .\n\n',
     'Thank you very much for your time. If you have any questions, please do not ',
     'hesitate to contact me.\n\n',
     'Best,\n\n',
     'Joe Brew\n',
-    'www.economicsofmalaria.com\n\n',
+    'Barcelona Institute for Global Health (www.isglobal.org)\n\n',
     '(P.S. If you want more details on the study I am doing, visit ',
     'https://github.com/joebrew/malaria_survey#can-we-do-it-a-survey-of-research-professionals-on-the-timeline-and-obstacles-to-eliminating-malaria .)'
     
@@ -354,12 +355,13 @@ sendify <- function(df){
             # attach.files = '../in_kind_proposal.pdf',
             send = TRUE)
 }
-
-for (i in 1417:nrow(email_df)){
-  message(paste0(i, ' of ', nrow(email_df)))
-  sendify(df = email_df[i,])
-  z <- data.frame(number = i)
-  write.csv(z, '~/Desktop/number.csv')
-  sleeper <- abs(sample(rnorm(mean = 30, n = 1000, sd = 10), 1))
-  Sys.sleep(sleeper)
-}
+# 
+# start_at <- read.csv('~/Desktop/number.csv')$number
+# for (i in start_at:nrow(email_df)){
+#   message(paste0(i, ' of ', nrow(email_df)))
+#   sendify(df = email_df[i,])
+#   z <- data.frame(number = i)
+#   write.csv(z, '~/Desktop/number.csv')
+#   sleeper <- abs(sample(rnorm(mean = 5, n = 1000, sd = 0), 1))
+#   Sys.sleep(sleeper)
+# }

### 2017-01-03 paper.Rmd
paper update

@@
     footnote: Corresponding Author
-  - name: Laia Cirera Crivillé
-    email: laia.cirera@isglobal.org 
-    affiliation: isglobal,cism
   - name: Elisa Sicuri
@@
 library(ggplot2)
-library(DT)
 library(tidyr)
+library(broom)
+library(RColorBrewer)
+# library(Hmisc)
+# library(Rmisc)
 
@@
                error = TRUE, 
-               cache = FALSE)
+               cache = FALSE,
+               fig.align = 'center')
 ```
@@
 ```{r}
+# Get publication theme for charts
+source('theme_publication.R')
+
 # Send emails
@@
 df$area <- gsub(')', '', df$area, fixed = TRUE)
+# Perform some replacements
+df$area[df$area == 'biochemistry'] <- 'chemistry'
+df$area[df$area == 'medical entomology'] <- 'entomology'
+df$area[df$area == 'vector biology'] <- 'biology'
+
 areas <- tolower(paste0(sort(unique(df$area)), collapse = ', '))
 areas <- sort(unique(unlist(strsplit(x = areas, split = ','))))
+areas <- trimws(areas, which = 'both')
+old_areas <- areas
+
+# Remove those areas for which there are fewer than 5 of a kind
+areas_df <- data.frame(area = areas)
+areas_df$count <- NA
+for (i in 1:nrow(areas_df)){
+  areas_df$count[i] <-
+    length(which(grepl(areas_df$area[i], 
+          df$area)))
+}
+areas_df <- areas_df %>%
+  filter(area != '',
+         count >= 5)
+areas <- areas[areas %in% areas_df$area]
+
 for (j in 1:length(areas)){
@@
 
+# Get number of areas
+# Average number of areas
+area_counter <- function(x){
+  result <- unlist(gregexpr(',', x))
+  if(result[1] == -1){
+    return(1)
+  } else {
+    return(length(result) + 1)
+  }
+}
+df$n_areas <- sapply(df$area, area_counter)
+
 # Make years numeric
@@
 df$comments <- tolower(df$comments)
+
+# Clean up names
+names(df) <- tolower(gsub('.', '_', names(df), fixed = TRUE))
+names(df) <- gsub(' ', '_', names(df))
+names(df) <- gsub('-', '_', names(df))
+names(df) <- gsub('&', 'and', names(df), fixed = TRUE)
+names(df) <- gsub('__', '_', names(df))
 
@@
 
-years_data <- 
-  gather(df, key,
-         value, 
-         years_10:years_50)
+# Clean up years
+df$years[df$years %in% c('', '10%',
+                         'cannot say',
+                         'depends on approach and commitment',
+                         "human species may be eradicated but zoonotic species may come up",
+                         "i don't know - too many unknown variables",
+                         "it depends...hard to predict.",
+                         "i think we have to be humble. malaria eradication was promised a long time ago...",
+                         "it is depend on global stability and climate change",
+                         "l don't know but it will remain big health problem",
+                         "not sure - depends on when the world begins to take the right steps towards eradication.",
+                         'not year but want to')] <- NA
+df$years[grepl('never|nevet|ever', df$years)] <- 50
+df$years <- gsub(' years| yrs|years|yrs| yeras|about ', '', df$years)
+df$years[df$years %in% c('100+',
+                         '≥100 to a global zero',
+                         '> 50',
+                         '50-100',
+                         '50 ish',
+                         '50yrs',
+                         '60 (one more generation)',
+                         '75a',
+                         'at least 400',
+                         "cannot be fully erdicated-some local eradication can be achieved within 50 ",
+                         'it will not be eradicated',
+                         'more than 50',
+                         'unlikely',
+                         'i doubt it can be eradicated at all')] <- 50
+df$years[df$years == '10-15'] <- 12.5
+df$years[df$years == '20-30'] <- 25
+df$years[df$years == '40-50'] <- 45
+df$years <- as.numeric(as.character(df$years))
+df$years[df$years > 50] <- 50
 
-# plot
-ggplot(data = years_data %>%
-         filter(!is.na(value)),
-       aes(x = value)) +
-  geom_bar() +
-  facet_wrap(~key) +
-  theme_classic()
+# Clean up the rankings
+bb <- c('governance', 'health_workforce',
+        'health_financing', 'health_technologies',
+        'health_information', 'service_delivery')
+for (i in 1:nrow(df)){
+  sub_df <- df[i,bb]
+  new_values <- sub_df / sum(sub_df, na.rm = TRUE) * 21
+  new_values[new_values > 6] <- 6
+  df[i,bb] <- new_values
+}
 
-# library(wordcloud2)
-# areas_df <- data.frame(word = areas)
-# areas_df$freq <- NA
-# for (i in 1:nrow(areas_df)){
-#   areas_df$freq[i] <-
-#     length(which(grepl(areas_df$word[i], df$area)))
-# }
-# areas_df <- areas_df %>% filter(word != '')
-# wordcloud2(data = areas_df,
-#            color = 'black', 
-#            size = 2, minRotation = -pi/6, maxRotation = pi/6,
-#   rotateRatio = 0.9)
 ```
@@
 
-## The justification
+## Rationale
 
@@
 
+## Expertise profile
+
+```{r}
+x <- df %>%
+  group_by(n_areas) %>%
+  tally %>%
+  mutate(p = n / sum(n) * 100)
+```
+
+Areas of expertise were non-exclusive and self-described, with participants having the option to choose from up to 3 of 10 checkboxes\footnote{Checkbox categories were anthropology, biology, clinical medicine, economics, epidemiology, immunology, parasitology, political science, statistics, and virology.}, or to write in one or more "other" areas of expertise.
+`r x$n[1]` participants (`r round(x$p[1], digits = 1)`%) declared only one area of expertise, with `r sum(x$n[1:3])` (`r round(sum(x$p[1:3]), digits = 1)`%) declaring three or fewer.
+
+Participants had a total of `r length(old_areas)` unique (self-described) areas of expertise, of which `r length(areas)` areas of expertise had 5 or more participants.
+
+```{r}
+temp <- areas_df %>%
+  arrange(desc(count))
+temp$area <- trimws(temp$area, which = 'both')
+names(temp) <- c('Area', 'Researchers')
+temp$Area <- as.character(temp$Area)
+temp$Area <- Hmisc::capitalize(temp$Area)
+kable(temp)
+```
+
+## Likelihood of eradication
+
+Participants were asked to quantify (as a percentage) the likelihood of eradication in the next 10, 20, 30, 40, and 50 years.
+Most participants saw eradication as extremely unlikely in the next 10-30 years, but increasingly likely thereafter.
+The following figure shows the distribution of year-specific likelihood perceptions (panels A-E), as well as an illustration of how both likelihood and uncertainty grow over time (panel F).
+
+```{r}
+# Define function for analyzing the years_n columns
+years_n <- function(n){
+  x <- df %>%
+    dplyr::select_(paste0('years_', n)) 
+  names(x) <- 'likelihood'
+  result <- x %>%
+    group_by(likelihood) %>%
+    tally %>%
+    mutate(p = n / sum(n) * 100) %>%
+    filter(!is.na(likelihood))
+
+  out <- list()
+  out[[1]] <- result
+  out[[2]] <-
+    ggplot(data = result,
+           aes(x = likelihood,
+               y = p)) +
+    geom_bar(stat = 'identity',
+             fill = 'darkorange',
+             alpha = 0.6) +
+    labs(title = paste0(toupper(letters[n/10]),'. ', n, ' years'),
+         subtitle = 'Perceived likelihood of eradication',
+         x = 'Likelihood',
+         y = '%') +
+    theme_publication(base_size = 10) +
+    theme(axis.text.x = element_text(angle = 90))
+  return(out)
+}
+```
+
+```{r, fig.height = 7}
+# Make plots of all
+years <- seq(10, 50, 10)
+for (i in 1:length(years)){
+  assign(paste0('g',i ),
+         years_n(n = years[i])[[2]])
+  x <- years_n(n = years[i])[[1]]
+  x$year <- years[i]
+  assign(paste0('x', i),
+         x)
+
+}
+# Combine all data
+x <- bind_rows(x1, x2, x3, x4, x5)
+
+# Make an aggregated version
+x$val <- ifelse(x$likelihood == '0%', 0,
+                ifelse(x$likelihood == '1-20%', 10,
+                       ifelse(x$likelihood == '21-40%', 30,
+                              ifelse(x$likelihood == '41-60%', 50,
+                                     ifelse(x$likelihood == '61-80%', 70,
+                                            ifelse(x$likelihood == '81-99%', 90,
+                                                   ifelse(x$likelihood == '100%', 100, NA)))))))
+xa <- x %>%
+  dplyr::group_by(year) %>%
+  dplyr::summarise(avg = weighted.mean(x = val, w = n, na.rm = TRUE),
+            q3 = Hmisc::wtd.quantile(val, weights = n, 0.75, na.rm = TRUE),
+            q1 = Hmisc::wtd.quantile(val, weights = n, 0.25, na.rm = TRUE))
+
+g6 <- 
+  ggplot(data = xa,
+         aes(x = year,
+             y = avg)) +
+  geom_ribbon(aes(ymin = q1,
+                  ymax = q3),
+              fill = 'orange',
+              alpha = 0.6) +
+  geom_line(color = 'darkorange') +
+  theme_publication(base_size = 10) +
+  xlab('Years') +
+  ylab('Average likelihood') +
+  ggtitle('G. Aggregated perceptions',
+          'Shaded area = inter-quartile range')
+
+Rmisc::multiplot(g1, g3, g5,
+                 g2, g4, g6,
+                 cols = 2)
+```
+
+## Time frame to eradication
+
+Participants were asked to provide the number of years they believe it will take until eradication can be achieved.
+`r length(which(is.na(df$years)))` (`r round(length(which(is.na(df$years))) / nrow(df) * 100, digits = 1)`%) were either blank or uninteligible, whereas `r length(which(!is.na(df$years)))` participants responded.
+Among respondants, `r length(which(df$years >= 50))` (`r round(length(which(df$years >= 50)) / length(which(!is.na(df$years))) * 100, digits = 1)` %) estimated that it would be 50 or more years until eradication.
+The below histogram shows the distribution of responses, appended at 50.
+
+```{r, fig.height = 3.5, fig.width = 4}
+ggplot(data = df,
+       aes(x = years)) +
+  geom_histogram(fill = 'darkorange',
+                 alpha = 0.6) +
+  theme_publication(base_size = 10) +
+  labs(x = 'Years',
+       y = 'Responses',
+       title = 'Perceived years until eradication',
+       subtitle = '(Estimates of greater than 50 years reduced to 50)')
+```
+
+## Difference in perceptions by expertise
+
+Participants were heterogenous in their perceptions, with all of the 5 pre-determined cut-offs containing the whole range of likelihoods (0-100%), and the free-form time frame responses suggesting that eradication would be achieved in as little as `r min(df$years, na.rm = TRUE)` to as many as "never".
+Heterogeneity can be partly explained by area of expertise, as evidenced by significant differences in the perceived years to eradication by area of expertise.
+
+```{r, fig.height = 4.5, fig.width = 4.5}
+# Get averages per area
+results_list <- list()
+dist_list <- list()
+year_list <- list()
+
+small_areas <- areas_df$area[areas_df$count >= 15]
+small_areas <- areas[1:12]
+for (i in 1:length(small_areas)){
+  this_area <- small_areas[i]
+  sub_data <- df[df[,paste0('area_', gsub(' ', '_', this_area))],]
+  this_df <- data_frame(area = this_area,
+                        avg = mean(sub_data$years, na.rm = TRUE),
+                        med = median(sub_data$years, na.rm = TRUE))
+  dist_df <- data_frame(area = this_area,
+                        val = sub_data$years)
+  numberfy <- function(x){
+    ifelse(x == '0%', 0,
+                ifelse(x == '1-20%', 10,
+                       ifelse(x == '21-40%', 30,
+                              ifelse(x == '41-60%', 50,
+                                     ifelse(x == '61-80%', 70,
+                                            ifelse(x == '81-99%', 90,
+                                                   ifelse(x == '100%', 100, NA)))))))
+
+  }
+  year_df <- data.frame(area = this_area,
+                        year = seq(10, 50, 10),
+                        val = c(mean(numberfy(sub_data$years_10), na.rm = TRUE),
+                                mean(numberfy(sub_data$years_20), na.rm = TRUE),
+                                mean(numberfy(sub_data$years_30), na.rm = TRUE),
+                                mean(numberfy(sub_data$years_40), na.rm = TRUE),
+                                mean(numberfy(sub_data$years_50), na.rm = TRUE)))
+  for (q in seq(0, 100, 10)){
+    this_df[,paste0('q_', q)] <- 
+      quantile(sub_data$years, q / 100, na.rm = TRUE)
+  }
+  results_list[[i]] <- this_df
+  dist_list[[i]] <- dist_df
+  year_list[[i]] <- year_df
+}
+results <- bind_rows(results_list)
+dist_results <- bind_rows(dist_list)
+year_results <- bind_rows(year_list)
+dist_results$the_area <- dist_results$area
+
+ggplot(data = dist_results,
+       aes(#group = area,
+           #fill = area,
+           x = val)) +
+  geom_density(fill = 'darkorange',
+               alpha = 0.6) +
+  theme_publication(base_size = 10) +
+  labs(x = 'Years',
+       y = 'Density',
+       title = 'Perceived years to eradication',
+       subtitle = '12 most popular areas of expertise only') +
+  facet_wrap(~the_area) 
+```
+
+```{r, fig.height = 3.5, fig.width = 4}
+model_formula <- paste0('years ~ ',
+                        paste0(paste0('area_', gsub(' ', '_', small_areas)), collapse = ' + '))
+model_formula <- as.formula(model_formula)
+fit <- lm(model_formula, data = df)
+# Get confidence intervals too
+ci <- tidy(confint(fit))
+x <- cbind(tidy(fit), ci)
+names(x) <- c('term', 'estimate', 'se', 'stat', 'p', 'rownames', 'lwr', 'upr')
+x <- x %>%
+  dplyr::select(term, estimate,
+                p, lwr, upr)
+the_intercept <- x$estimate[1]
+x <- x[-1,]
+for (the_column in c('estimate', 'lwr', 'upr')){
+  x[,the_column] <- x[,the_column] + the_intercept
+}
+x$term <- gsub('area_|TRUE', '', x$term)
+x <- x %>%
+  dplyr::arrange(estimate)
+x$term <- gsub('_', '\n', x$term)
+x$term <- factor(x$term, levels = x$term)
+ggplot(data = x,
+       aes(x = term,
+           y = estimate)) +
+  geom_bar(stat = 'identity',
+           fill = 'darkorange',
+           alpha = 0.6) +
+  geom_errorbar(aes(ymin = lwr,
+                    ymax = upr),
+                alpha = 0.6,
+                width = 0.8) +
+  theme_publication(base_size = 10) +
+  labs(x = 'Area',
+       y = 'Years',
+       title = 'Perceived years to eradication',
+       subtitle = 'By expertise, adjusted for multiple areas of expertise') +
+  theme(axis.text.x = element_text(angle = 90))
+
+```
+
+Heterogeneity by area of expertise is also apparent in perceived likelihood of eradication over the pre-defined five time-points, as seen below.
+
+```{r, fig.height = 4, fig.width = 4.5}
+cols <- colorRampPalette(brewer.pal(9, 'Spectral'))(length(unique(year_results$area)))
+ggplot(data = year_results,
+       aes(x = year,
+           y = val)) +
+  geom_line(aes(group = area,
+           color = area,
+           lty = area)) +
+  theme_publication(base_size = 10) +
+  scale_color_manual(name = '',
+                     values = cols,
+                     labels = unique(year_results$area)) +
+  scale_linetype_manual(name="", 
+                        values = rep(1:6, 100)[1:length(unique(year_results$area))],
+                     labels = unique(year_results$area)) +
+  xlab('Years until eradication') +
+  ylab('Likelihood') +
+  ggtitle('Likelihood trajectories',
+          'By area of expertise')
+```
+
+## Health system building blocks
+
+Finally, researchers were asked to rank the WHO's 6 health system building blocks as needing the most to least attention (6-1 scale) in order for eradication to be achieved.
+Disagreement was high, as evidenced by the variance in responses in the below point and violin chart.
+However, the general tendency was that governance was recognized as the most important area requiring attention, with health information thought to be the area least requiring attention.
+
+```{r}
+bb <- c('governance', 'health_workforce',
+        'health_financing', 'health_technologies',
+        'health_information', 'service_delivery')
+results_list <- list()
+for (i in 1:length(bb)){
+  this_df <- data.frame(bb = bb[i],
+                        ranking = as.numeric(df[,bb[i]]))
+  results_list[[i]] <- this_df
+}
+results <- bind_rows(results_list)
+results$bb <- gsub('_', '\n', results$bb)
+
+results_agg <-
+  results %>%
+  dplyr::group_by(bb) %>%
+  dplyr::summarise(avg = mean(ranking, na.rm = TRUE)) %>%
+  arrange(avg)
+results_agg$bb <- factor(results_agg$bb,
+                         levels = results_agg$bb)
+results$bb <- factor(results$bb, 
+                     levels = levels(results_agg$bb))
+
+ggplot(data = results) + 
+  geom_violin(aes(x = bb,
+           y = ranking),
+           fill = 'orange',
+              alpha = 0.6) +
+  geom_jitter(aes(x = bb,
+           y = ranking),
+           color = 'black',
+           with = 0.4,
+           height = 0.4,
+              alpha = 0.3,
+              size = 1) +
+  theme_publication(base_size = 10) +
+  labs(x = 'WHO Building block',
+       y = 'Ranking',
+       title = 'Perceived areas needing attention',
+       subtitle = 'Small points: jittered individual responses; large triangles: averages') +
+  geom_point(data = results_agg,
+             aes(x = bb,
+                 y = avg),
+             size = 5,
+             pch = 17,
+             color = 'black',
+             alpha = 0.8)
+```
+
 # Discussion
 
-General note about pessimism.
+## Collective pessimism
 
-General note about areas needing attention.
+Our study reveals a striking gap between the public discourse on malaria eradication, and those views held (largely privately) by malaria researchers.
+Approximately three-quarters of respondents believe that malaria will not be eradicated in the next 50 years; in other words, assuming our pool of respondents is of typical post-PhD age, most believe they will not live to see eradication.
 
-Difference between pessimism based on expertise.
+If we take the pooled opinions of researchers, as revealed through this survey, as the best approximation of truth available, then the disconnect between public discourse on malaria eradication and private opinion is troubling.
+It suggests that the goals set by the Bill and Melinda Gates Foundation (eradication "within a generation") and the WHO GMP (eradication "within the lifetime of young scientists just embarking on their careers") are unrealistic at best, and misleading at worst.
+This has important implications for spending in public health, since the attention and resources of funders, researchers and government agencies are directed to those areas where a result is expected.
+
+On the other hand, there are many reasons to be skeptical that the combined "wisdom of crowds" of malaria researchers is a reliable indicator of truth.
+First, academic researchers are specialists - their narrow, field-specific view of eradication's feasibility is arguably less reliable than the more "global" views of the WHO, or Bill Gates.
+Second, a number of biases may come in to play in this study.
+
+Among these biases, 4 are worth mentioning specifically.
+(1) "Conjunction fallacy" suggests that the general goal of eradication may seem less likely than the sum of the goals of country-specific elimination.
+(2) A (reverse) variant of the "hot hand fallacy", in which researchers may mistakenly base their assessment of current chances of eradication on previous failures.
+(3) Parkinson's law of triviality suggests that researchers may disproportionately see the challenges of their own research (antimalarial drug resistance, etc.) as larger or more relevant to the global eradication campaign than they really are.
+(4) Finally, and ironically, "optimism bias" may play a perverse role in researchers' responses; though eradication is certainly a goal desired by all, one could argue that malaria research specialists subconciously realize that they actually stand to lose out profesionally in the case of eradication.
+
+Whether the collective "wisdom" of researchers is worth adhering to or not is arguable.
+That said, to the extent that researchers' private opinions differ so greatly from those of global health leaders is itself a noteworthy result.
+If leaders' high levels of optimism are well-placed, this suggests that researchers are unduly pessimistic, and efforts should be made to convince them that eradication is more feasible than they realize.
+If, on the other hand, collective wisdom is a better forecasting agent than the proclamations and objectives of global health leaders, then it is important to recognize the sad truth that we are likely further from eradication than we would like to be.
+In this case, though the discourse on eradication can be motivating and inspiring, resources should be directed in a manner that reflects an intended outcome's likelihood of occurrence.
+
+## Building blocks to eradication
+
+It is noteworthy that there was so much discord among researchers in regards to which WHO building blocks required the most attention in order for eradication to be achieved.
+All six possible categories received votes for both the lowest and highest levels of importance, as well as every level in between.
+And the difference between "health information" (the building block deemed as least important) and "governance" (the most important) was less than 0.5 on a 1-6 scale.
+
+This discord suggests that the path to implementing strategies for eradication is not clear, at least from the perspective of this study's participants.
+This could mean that further work is needed in order to prioritize which areas require the most investment and attention in order for eradication to occur.
+On the other hand, one could interpret this result as reflecting the fact that previous work on priorities (ie, MalERA) has not been fully accessed or understood by the larger malaria research community.
+
+## Areas of expertise
+
+It is noteworthy that among the most "optimistic" experts were from the field of bioinformatics.
+This could be explained by the fact that, relative to other more "traditional" areas of science, informatics regularly sees paradigm shifts, and changes in technology and breakthroughs occur at a more rapid rate.
+That said, the high degree of optimism among chemists would seem to contradict this hypothesis.
+At any rate...
+(more details will go here).
 
@@
 
-No distinguishing of quality, experience, etc.
+In addition to the biases mentioned above, this study has many limitations.
+First, though results are not disclosed at the individual level, this survey was not entirely anonymous, suggesting that social desirability bias may have influenced responses, and that selection bias likely meant our pool of participants were substantially different from those who choose not to participate.
 
-No inclusion of program workers
+Second, we made no distinguishment between quality of research, years of experience, academic achievements, geographical area, etc.
+Our inclusion criteria were simple and rudimentary, allowing us to access many diverse viewpoints, but (perhaps inappropriately) weighting all viewpoints as equal.
 
-Potential bias due to non-anonymity
-
-Flaws generally in wisdom of crowd approach
+Third, this study included the corresponding authors of indexed journals.
+Though certainly a group with important knowledge related to malaria, this misses malaria control program employees, health agency workers, and other stakeholders.
+Their experiences and viewpoints are most likely vastly different from those of academecians.
 
@@
 
+Our survey attempted to quantify the likelihood of and time frame to malaria eradication by gauging the collective opinion of malaria researchers.
+Our results suggest that eradication is unlikely in the short and medium terms, and that there exists a great deal of disagreement among researchers in regards to which areas require the most attention in order for eradication to occur.
+The implication of these results are three-fold: (1) that those working or investing in eradication-specific campaigns should factor in the low likelihood and long time frame when calculating those campaigns' expected value; (2) that champions of near-term eradication need to make a more compelling case to malaria researchers of eradication's feasibility, in order to better focus and inspire the latter; and (3) that discord among malaria researchers as to which areas need the most attention in order for eradication to occur suggests a need for open discussion and concensus-making, so that resources and focus are directed appropriately.
+
 References {#references .unnumbered}

### 2017-01-03 theme_publication.R

@@ -1,0 +1,45 @@
+# https://rpubs.com/Koundy/71792
+
+theme_publication <- function(base_size=14) {
+  library(grid)
+  library(ggthemes)
+  (theme_foundation(base_size=base_size)
+    + theme(plot.title = element_text(#face = "bold",
+                                      size = rel(1.2), hjust = 0.5),
+            text = element_text(),
+            panel.background = element_rect(colour = NA),
+            plot.background = element_rect(colour = NA),
+            panel.border = element_rect(colour = NA),
+            axis.title = element_text(#face = "bold",
+                                      size = rel(1)),
+            axis.title.y = element_text(angle=90,vjust =2),
+            axis.title.x = element_text(vjust = -0.2),
+            axis.text = element_text(), 
+            axis.line = element_line(colour="black"),
+            axis.ticks = element_line(),
+            panel.grid.major = element_line(colour="#f0f0f0"),
+            panel.grid.minor = element_blank(),
+            legend.key = element_rect(colour = NA),
+            legend.position = "bottom",
+            legend.direction = "horizontal",
+            legend.key.size= unit(0.2, "cm"),
+            # legend.margin = unit(0, "cm"),
+            legend.title = element_text(face="italic"),
+            plot.margin=unit(c(10,5,5,5),"mm"),
+            strip.background=element_rect(colour="#f0f0f0",fill="#f0f0f0"),
+            strip.text = element_text(face="bold")
+    ))
+  
+}
+
+scale_fill_publication <- function(...){
+  library(scales)
+  discrete_scale("fill","publication",manual_pal(values = c("#386cb0","#fdb462","#7fc97f","#ef3b2c","#662506","#a6cee3","#fb9a99","#984ea3","#ffff33")), ...)
+  
+}
+
+scale_colour_publication <- function(...){
+  library(scales)
+  discrete_scale("colour","publication",manual_pal(values = c("#386cb0","#fdb462","#7fc97f","#ef3b2c","#662506","#a6cee3","#fb9a99","#984ea3","#ffff33")), ...)
+  
+}

### 2017-01-10 paper.Rmd
adding menno

@@
     footnote: Corresponding Author
+  - name: Menno Pradhan
+    email: m.p.pradhan@vu.nl
+    affiliation: vu,uva
   - name: Elisa Sicuri
@@
     address: Centro de Investigação em Saúde de Manhiça, Vila da Manhiça, Bairro Cambeve, Rua 12, Distrito da Manhiça, CP 1929, Maputo, Mozambique
+  - code: vu
+    address: Faculty of Economics and Business Administration, VU University Amsterdam, De Boelelaan 1105, 1081 HV Amsterdam, Netherlands
+  - code: uva
+    address: Faculty of Economics and Business, Section Microeconomics, University of Amsterdam, REC E, Roetersstraat 11, Amsterdam, Netherlands
 abstract: |

### 2017-07-25 paper.Rmd
big update

@@
 bibliography: library.bib
+params:
+  get_new_data: False
 output: rticles::elsevier_article
@@
 # library(Rmisc)
+# install.packages(c("gender", "genderdata"),
+#                  repos = "http://packages.ropensci.org",
+#                  type = "source")
+library(gender)
+library(wru)
+library(sampleSelection)
+library(stargazer)
 
@@
 # Load data
+get_new_data <- params$get_new_data
+if(get_new_data){
   file_name <- paste0('snapshot_', Sys.Date(), '.RData')
+} else {
+  snaps <- dir('snapshots')
+  dates <- as.Date(substr(snaps, 10, 19))
+  file_name <- snaps[which.max(dates)]
+}
 if(!file_name %in% dir('snapshots')){
@@
   names(df) <- tolower(gsub('.', '_', names(df), fixed = TRUE))
+  names(df) <- gsub(' ', '_', names(df))
   names(df)[4:17] <-
@@
 }
-```
 
-```{r}
 # Clean up survey responses
 # Make NA all empty responses
-df$comments[df$comments == ''] <- NA
-df$email_address[df$email_address == ''] <- NA
+df$comments <- ifelse(df$comments == '', 
+                      NA,
+                      df$comments)
+df$email_address <- ifelse(df$email_address == '',
+                           NA,
+                           df$email_address)
 # Flag duplicates
@@
   result <- unlist(gregexpr(',', x))
-  if(result[1] == -1){
+  if(is.na(result)){
+    return(0)
+  } else if(result[1] == -1){
     return(1)
@@
 }
-
 ```
@@
 ```{r}
-# Results cleanup
+# Get the non-respondents into the same data
+df$responded <- TRUE
+non_respondents <- email_df %>%
+  mutate(surname = `first _author_last_name`,
+         first_name = `first _author_first_name`,
+         name = author) %>%
+  dplyr::select(name, surname, first_name, email) %>%
+  filter(!email %in% df$email)
+
+# Add to one dataframe
+df <- bind_rows(df, non_respondents)
+```
+
+```{r}
+# Predict the gender based on first name ####
+
+# Extract first/last names
+df$first_name <- tolower(unlist(lapply(strsplit(df$name, ' '), function(x){x[1]})))
+df$last_name <- tolower(unlist(lapply(strsplit(df$name, ' '), function(x){x[length(x)]})))
+df$surname <- df$last_name
+
+if(get_new_data){
+  # Get gender based on name
+  names_df <- df %>%
+    group_by(first_name) %>%
+    tally %>%
+    ungroup %>%
+    dplyr::select(-n)
+  # Get ethnicity based on last name
+  surnames_df <- df %>%
+    group_by(surname) %>% 
+    tally %>%
+    ungroup %>%
+    dplyr::select(-n)
+  gender_scores <- gender(names = names_df$first_name,
+              years = c(1940, 1990),
+              method = 'ssa') %>%
+    rename(first_name = name) %>%
+    dplyr::select(first_name,
+                  proportion_male,
+                  proportion_female,
+                  gender)
+  surname_scores <- 
+    predict_race(voter.file = surnames_df,
+                 surname.only = TRUE)
+  save(surname_scores,
+       gender_scores,
+       file = 'data/name_scores.RData')
+} else {
+  load('data/name_scores.RData')
+}
+
+# Get most likely ethnicity
+ethnicities <- c('white', 'black', 'hispanic',
+                 'asian', 'other')
+surname_scores$ethnicity <- ethnicities[apply(surname_scores[,2:6], 1, function(x){which.max(x)[1]})]
+
+# Join surname scores to df
+df <-
+  left_join(x = df,
+            y = surname_scores,
+            by = 'surname')
+df <-
+  left_join(x = df,
+            y = gender_scores,
+            by = 'first_name')
+
+# Flag non respondents as such
+df$responded[is.na(df$responded)] <- FALSE
+```
+
+```{r}
+# sentiment score of contents
+library(databrew)
+df$sentiment <- databrew::score_sentiment(df$comments)
+```
+
+```{r}
+# Heckman selection
+# We're estimating years as a function of sex and ethnicity
+ols1 = lm(years ~ sentiment  + area_epidemiology + area_anthropology, data = df[df$responded,])
+
+# Estimate likelihood of response
+# it is very desirable to have at least one variable in the selection equation that acts like an instrument:
+# (https://rpubs.com/wsundstrom/t_selection)
+# for us, this is ethnicity - it should affect response (due to language)
+# but not likely to affect optimism
+
+# Heckman 2 step
+heck1 <- heckit(responded ~ gender + ethnicity,
+                years ~ sentiment + area_epidemiology + area_anthropology, data = df)
+
+# Maximum likelihood (like heckman 2 step, but slightly different)
+# ML estimation of selection model
+ml1 = selection(responded ~ gender + ethnicity,
+                years ~ sentiment + area_epidemiology + area_anthropology, data = df)
+
+# # Look at results
+# stargazer(ols1, heck1, ml1,    
+#           # se=list(cse(ols1),NULL,NULL), 
+#           title="Regression on years until eradication", type="latex", 
+#           df=FALSE, digits=4)
 ```
@@
 
+## Data generation
+
+The survey was intentionally as short as possible, so as to appeal to time-pressed participants.
+However, supplementary data on researchers' demographics is of value.
+Accordingly, we estimated the likelihood of a participant being of one of two genders (male or female) based on first name, and the likelihood of a participant being of one of five ethnicities (White, Black, Hispanic, Asian, Other) based on the provided last name.
+
 ## Analysis
@@
 
+The estimation of gender and ethnicity likelihoods for each participant relied on Mullen's implementation of US Social Security Administration names' analysis [@gender2015] and Khanna et al's bayesian prediction algorithm for the estimation of racial categories [@wru2015].
+
+De-biasing of sample selection was carried out using Heckman's 2 step approach (citation needed), as implemented by Toomet [@toomet2008].
+
 # Results
@@
 A total of `r nrow(df)` researchers participated in the survey.
+
+## Sample selection and de-biasing of results
+
+This section is unfinished. Below are regression outputs for both OLS and Heckman's 2 step model. I will update this soon.
+
+```{r}
+# stargazer(ols1, heck1, ml1,    
+#           # se=list(cse(ols1),NULL,NULL), 
+#           title="Regression on years until eradication", type="html",
+#           df=FALSE, digits=4)
+summary(ols1)
+summary(heck1)
+
+```
 
@@
 
+## Sentiment analysis of free-text commentary
+
+This section is unfinished.
+Below is the distribution of "sentiment" among the responses (0 is neutral, below 0 is negative, above 0 is positive), but this is preliminary.
+The chart is colored by ethnicity, and faceted by gender.
+
+```{r}
+ggplot(data = df %>%
+         filter(responded) %>%
+         # mutate(n_areas = factor(n_areas)) %>%
+         filter(!is.na(ethnicity),
+                !is.na(gender)),
+       aes(x = sentiment,
+           group = ethnicity)) +
+  geom_density(aes(fill = ethnicity),
+               alpha = 0.6,
+               n = 10) +
+  theme_publication() +
+  facet_wrap(~gender)
+
+```
+
 ## Health system building blocks

### 2017-09-12 paper.Rmd
better sample selection, now getting full citations data

--- 2017-01-10 paper.Rmd
@@
     affiliation: vu,uva
+  - name: Jacqueline Broerse
+    email: j.e.w.broerse@vu.nl
+    affiliation: vu
   - name: Elisa Sicuri
@@
 library(knitr)
-library(dplyr)
-library(ggplot2)
-library(tidyr)
-library(broom)
-library(RColorBrewer)
-# library(Hmisc)
-# library(Rmisc)
+library(xtable)
 
@@
                fig.align = 'center')
-```
+options(xtable.comment = FALSE)
 
-```{r}
-# Get publication theme for charts
-source('theme_publication.R')
-
-# Send emails
-source('code/recruit.R', chdir = TRUE)
-
-# Load data
-file_name <- paste0('snapshot_', Sys.Date(), '.RData')
-if(!file_name %in% dir('snapshots')){
-  # Fetch data
-  library(gsheet)
-  url_responses<- 'https://docs.google.com/spreadsheets/d/1yeQ4TR73mdnDABPZ-ZEg3DAFu2Bko5NJ_nkMcNKr2lo/edit?usp=sharing'
-  df <- gsheet2tbl(url_responses)
-
-  # Manually rename variables
-  names(df) <- tolower(gsub('.', '_', names(df), fixed = TRUE))
-  names(df)[4:17] <-
-    c('area',
-      'years_10',
-      'years_20',
-      'years_30',
-      'years_40',
-      'years_50',
-      'years',
-      'governance',
-      'health_workforce',
-      'health_financing',
-      'health_technologies',
-      'health_information',
-      'service_delivery',
-      'comments')
-
-  # Save a snapshot
-  save(df, 
-       file = paste0('snapshots/',
-                     file_name))
-} else {
-  load(paste0('snapshots/',
-              file_name))
-}
-```
-
-```{r}
-# Clean up survey responses
-# Make NA all empty responses
-df$comments[df$comments == ''] <- NA
-df$email_address[df$email_address == ''] <- NA
-# Flag duplicates
-df$duplicate <- duplicated(df$email_address)
-# Remove duplicates
-df <- df[is.na(df$email_address) |
-           !df$duplicate,]
-# Create area dummies
-df$area <- tolower(df$area)
-df$area <- gsub('/', ', ', df$area)
-df$area <- gsub('(', '', df$area, fixed = TRUE)
-df$area <- gsub(')', '', df$area, fixed = TRUE)
-# Perform some replacements
-df$area[df$area == 'biochemistry'] <- 'chemistry'
-df$area[df$area == 'medical entomology'] <- 'entomology'
-df$area[df$area == 'vector biology'] <- 'biology'
-
-areas <- tolower(paste0(sort(unique(df$area)), collapse = ', '))
-areas <- sort(unique(unlist(strsplit(x = areas, split = ','))))
-areas <- trimws(areas, which = 'both')
-old_areas <- areas
-
-# Remove those areas for which there are fewer than 5 of a kind
-areas_df <- data.frame(area = areas)
-areas_df$count <- NA
-for (i in 1:nrow(areas_df)){
-  areas_df$count[i] <-
-    length(which(grepl(areas_df$area[i], 
-          df$area)))
-}
-areas_df <- areas_df %>%
-  filter(area != '',
-         count >= 5)
-areas <- areas[areas %in% areas_df$area]
-
-for (j in 1:length(areas)){
-  df[,paste0(
-    'area_',
-    areas[j]
-  )] <- NA
-}
-for (j in 1:length(areas)){
-  df[,paste0(
-    'area_',
-    areas[j]
-  )] <- grepl(areas[j], df$area)
-}
-
-# Get number of areas
-# Average number of areas
-area_counter <- function(x){
-  result <- unlist(gregexpr(',', x))
-  if(result[1] == -1){
-    return(1)
-  } else {
-    return(length(result) + 1)
-  }
-}
-df$n_areas <- sapply(df$area, area_counter)
-
-# Make years numeric
-df$years <- tolower(df$years)
-# more needs to be done here
-
-# Make comments standardized
-df$comments <- tolower(df$comments)
-
-# Clean up names
-names(df) <- tolower(gsub('.', '_', names(df), fixed = TRUE))
-names(df) <- gsub(' ', '_', names(df))
-names(df) <- gsub('-', '_', names(df))
-names(df) <- gsub('&', 'and', names(df), fixed = TRUE)
-names(df) <- gsub('__', '_', names(df))
-
-df <- data.frame(df)
-
-# Clean up missing responses
-for (i in seq(10, 50, 10)){
-  df[,paste0('years_', i)][df[,paste0('years_', i)] == ''] <- NA
-  df[,paste0('years_', i)] <-
-    factor(df[,paste0('years_', i)],
-           levels = c('0%',
-                      '1-20%',
-                      '21-40%',
-                      '41-60%',
-                      '61-80%',
-                      '81-99%',
-                      '100%'))
-}
-
-# Clean up years
-df$years[df$years %in% c('', '10%',
-                         'cannot say',
-                         'depends on approach and commitment',
-                         "human species may be eradicated but zoonotic species may come up",
-                         "i don't know - too many unknown variables",
-                         "it depends...hard to predict.",
-                         "i think we have to be humble. malaria eradication was promised a long time ago...",
-                         "it is depend on global stability and climate change",
-                         "l don't know but it will remain big health problem",
-                         "not sure - depends on when the world begins to take the right steps towards eradication.",
-                         'not year but want to')] <- NA
-df$years[grepl('never|nevet|ever', df$years)] <- 50
-df$years <- gsub(' years| yrs|years|yrs| yeras|about ', '', df$years)
-df$years[df$years %in% c('100+',
-                         '≥100 to a global zero',
-                         '> 50',
-                         '50-100',
-                         '50 ish',
-                         '50yrs',
-                         '60 (one more generation)',
-                         '75a',
-                         'at least 400',
-                         "cannot be fully erdicated-some local eradication can be achieved within 50 ",
-                         'it will not be eradicated',
-                         'more than 50',
-                         'unlikely',
-                         'i doubt it can be eradicated at all')] <- 50
-df$years[df$years == '10-15'] <- 12.5
-df$years[df$years == '20-30'] <- 25
-df$years[df$years == '40-50'] <- 45
-df$years <- as.numeric(as.character(df$years))
-df$years[df$years > 50] <- 50
-
-# Clean up the rankings
-bb <- c('governance', 'health_workforce',
-        'health_financing', 'health_technologies',
-        'health_information', 'service_delivery')
-for (i in 1:nrow(df)){
-  sub_df <- df[i,bb]
-  new_values <- sub_df / sum(sub_df, na.rm = TRUE) * 21
-  new_values[new_values > 6] <- 6
-  df[i,bb] <- new_values
-}
-
-```
-
-```{r}
-# Results cleanup
+# Get data
+source('prepare_data.R')
 ```
@@
 A total of `r nrow(df)` researchers participated in the survey.
+
+## Sample selection and de-biasing of results
+
+This section is unfinished. Below are regression outputs for both OLS and Heckman's 2 step model. I will update this soon.
+
+```{r, results = 'asis'}
+stargazer(ols1, heck1, ml1,
+          header = FALSE,
+          # se=list(cse(ols1),NULL,NULL),
+          title="Regression on years until eradication", 
+          type="latex",
+          df=FALSE, digits=4)
+# summary(ols1)
+# summary(heck1)
+
+```
 

### 2017-09-12 code/recruit.R

@@ -174,6 +174,9 @@ if('pubmed_results.RData' %in% dir('../data')){
        file = '../data/pubmed_results.RData')
 }
 
+# Save the pubmed raw results for later
+pubmed_raw <- x$results
+
 if('final_authors.RData' %in% dir('../data')){
   load('../data/final_authors.RData')
 } else {

### 2017-09-12 prepare_data.R

@@ -1,0 +1,490 @@
+library(dplyr)
+library(ggplot2)
+library(tidyr)
+library(broom)
+library(RColorBrewer)
+# library(Hmisc)
+# library(Rmisc)
+# install.packages(c("gender", "genderdata"),
+#                  repos = "http://packages.ropensci.org",
+#                  type = "source")
+library(gender)
+library(wru)
+library(sampleSelection)
+library(stargazer)
+
+# Get publication theme for charts
+source('theme_publication.R')
+
+# Send emails
+source('code/recruit.R', chdir = TRUE)
+
+# Get number of citations of each article (sept 2017)
+citations_df <- data_frame(id = as.character(sort(unique(final_authors$id))),
+                           n_citations = NA)
+if(!'citations.RData' %in% dir('data')){
+  for (i in 1:nrow(citations_df)){
+    message(paste0(i, ' of ', nrow(citations_df)))
+    try({
+      res <- EUtilsSummary(paste0(citations_df$id[i],
+                                  '[uid]'))
+      citations_df$n_citations[i] <- Cited(res)
+    })
+  }
+  
+  citations_df <- 
+    citations_df %>%
+    arrange(desc(n_citations))
+  save(citations_df, 
+       file = 'data/citations.RData')
+} else {
+  load('data/citations.RData')
+}
+
+
+# Get average and total number of citations per author
+citations_metrics <-
+  final_authors %>%
+  left_join(citations_df) %>%
+  group_by(author) %>%
+  summarise(n_citations_total = sum(n_citations, na.rm = TRUE),
+            n_citations_average = mean(n_citations, na.rm = TRUE))
+
+# Join that data to our author data
+final_authors_aggregated <-
+  left_join(final_authors_aggregated,
+            citations_metrics,
+            by = 'author')
+
+# Load survey data
+if(exists('params')){
+  get_new_data <- params$get_new_data
+} else {
+  get_new_data <- FALSE
+}
+
+if(get_new_data){
+  file_name <- paste0('snapshot_', Sys.Date(), '.RData')
+} else {
+  snaps <- dir('snapshots')
+  dates <- as.Date(substr(snaps, 10, 19))
+  file_name <- snaps[which.max(dates)]
+}
+if(!file_name %in% dir('snapshots')){
+  # Fetch data
+  library(gsheet)
[…]

### 2017-10-05 paper.Rmd
update

@@
 # No scientific notation
-options(scipen=999)
+# options(scipen=999)
 
@@
 All analysis code, as well as the code used for the identification and contacting of participants, is publicly available at [https://github.com/joebrew/malaria_survey](https://github.com/joebrew/malaria_survey).
-
-The searching and retrieval of information from the PubMed database was carried out using the RISmed package [@Kovalchik2015]. Qualitative analysis relied on the RQDA package (citation needed here).
+The searching and retrieval of information from the PubMed database was carried out using the RISmed package [@Kovalchik2015].
 
@@
 
-De-biasing of sample selection was carried out using Heckman's 2 step approach (citation needed), as implemented by Toomet [@toomet2008].
+De-biasing of sample selection was carried out using Heckman's 2 step approach as implemented by Toomet [@toomet2008].
 
@@
 
-A total of `r nrow(df)` researchers participated in the survey.
+A total of `r length(which(df$responded))` researchers participated in the survey from the `r nrow(df)` invitations sent (participation rate of `r round(length(which(df$responded)) / nrow(df) * 100, 2)`%).
 
-## Sample selection and de-biasing of results
+## Sample selection
 
-This section is unfinished. Below are regression outputs for both OLS and Heckman's 2 step model. I will update this soon.
+Respondents were qualitatively different from non-respondents.
+Importantly, the average number of total author-specific citations was `r round(mean(df$n_citations_total[df$responded]), digits = 2)` among respondents, but `r round(mean(df$n_citations_total[!df$responded]), digits = 2)` among non-respondents.
+This suggests either a tendency for more senior or more cited researchers to not respond.
+The distribution of author-specific total citations is shown below (a).
+
+```{r}
+g1 <- ggplot(data = df %>%
+         mutate(responded = ifelse(responded, 'Respondents', 'Non-respondents')), 
+       aes(x = n_citations_total)) +
+  geom_density(aes(group = responded,
+                   fill = responded),
+               alpha = 0.6) +
+  scale_x_log10() +
+  theme_publication() +
+  scale_fill_manual(name = '',
+                    values = c('darkorange', 'lightblue')) +
+  labs(x = 'Citations (log scale)',
+       y = 'Density',
+       title = 'Total lifetime citations')
+```
+
+When examining the number of average citations per article, the difference between respondents was slightly less: `r round(median(df$n_citations_total[df$responded]), digits = 2)` among respondents, and `r round(median(df$n_citations_total[!df$responded]), digits = 2)` among non-respondents.
+Again, the distribution is shown below (b).
+
+```{r}
+g2 <- ggplot(data = df %>%
+         mutate(responded = ifelse(responded, 'Respondents', 'Non-respondents')), 
+       aes(x = n_citations_average)) +
+  geom_density(aes(group = responded,
+                   fill = responded),
+               alpha = 0.6,
+               n = 10) +
+  scale_x_log10() +
+  theme_publication() +
+  scale_fill_manual(name = '',
+                    values = c('darkorange', 'lightblue')) +
+  labs(x = 'Citations (log scale)',
+       y = 'Density',
+       title = 'Average citations per article')
+Rmisc::multiplot(g1, g2, cols = 2)
+```
+
+The below table shows the response rate by different demographic groups of interest.
+
+```{r}
+# function to get response rate per categorical variable
+response_rate <- function(variable = 'sex'){
+  df$x <- df[,variable]
+  out <- df %>%
+    group_by(x) %>%
+    summarise(responded = length(which(responded)),
+              n = n()) %>%
+    ungroup %>%
+    mutate(p = responded / n * 100)
+  return(out)
+}
+out_list <- list()
+vars <- c('sex',
+            'ethnicity',
+            'bin_citations')
+for (i in 1:length(vars)){
+  this_var <- vars[i]
+  x <- response_rate(variable = this_var)
+  x$variable <- this_var
+  out_list[[i]] <- x
+}
+out <- bind_rows(out_list) %>%
+  dplyr::select(variable, 
+                x,
+                responded,
+                n, 
+                p) %>%
+  rename(Variable = variable,
+         Characteristic = x,
+         Responded = responded,
+         Invited = n,
+         `Response rate` = p)
+kable(out, format = 'latex', caption = 'Response rate by author characteristics')
+```
+
+The below chart shows response rate by number of citations.
+
+```{r}
+x <- out %>%
+  filter(Variable == 'bin_citations') 
+ggplot(data = x,
+       aes(x = Characteristic,
+           y = `Response rate`)) +
+  geom_bar(stat = 'identity',
+           fill = 'lightblue',
+           alpha = 0.8) +
+  theme_publication() +
+  labs(x = 'Number of total citations',
+       y = 'Response rate',
+       title = 'Response rate by citations') +
+  geom_label(aes(label = paste0(round(`Response rate`, digits = 2), '%')))
+```
+
+## De-biasing of results
 
@@
           title="Regression on years until eradication", 
-          type="latex",
+          type="text",
           df=FALSE, digits=4)
@@
 
-## Expertise profile
+## Expertise profile among respondents
 
@@
 x <- df %>%
+  filter(responded) %>%
   group_by(n_areas) %>%
   tally %>%
-  mutate(p = n / sum(n) * 100)
+  mutate(p = n / sum(n, na.rm = TRUE) * 100)
 ```
@@
 
-Participants had a total of `r length(old_areas)` unique (self-described) areas of expertise, of which `r length(areas)` areas of expertise had 5 or more participants.
+Participants had a total of `r length(old_areas)` unique (self-described) areas of expertise, of which `r length(areas)` areas of expertise had 5 or more participants (see table 1).
 
@@
 temp$Area <- Hmisc::capitalize(temp$Area)
-kable(temp)
+kable(temp[1:10,], format = "latex", caption = 'Top 10 areas') %>%
+  kableExtra::kable_styling(#position = "float_right",
+                            font_size = 7)
 ```
@@
 
+## Qualitative analysis of results
+
+Participants were invited to provide "any general comments on the timeline and likelihood of global eradication".
+Of the `r length(which(df$responded))` who responded to the survey, `r length(which(!is.na(df$comments)))` (`r round(length(which(!is.na(df$comments))) / length(which(df$responded)) * 100, digits = 2)`%) provided a comment.
+
 # Discussion

### 2017-10-05 prepare_data.R

@@ -430,11 +430,13 @@ df$sex <- ifelse(df$proportion_female >= 0.5,
                         NA))
 
 # Bin the number of citations variable
+# options(scipen = '999')
 df$bin_citations <- 
   cut(x = df$n_citations_total,
       breaks = quantile(df$n_citations_total,
                na.rm = TRUE),
-      include.lowest = TRUE)
+      include.lowest = TRUE,
+      dig.lab = 10)
 
 # Remove the 1 "other" ethnicity since it screws up all our matrices
 df <- df %>%
@@ -458,7 +460,7 @@ ols1 = lm(years ~ sentiment  +
 # first equation is likelihood of response
 # second equation is impact on response
 formula_response <- as.formula("responded ~ sex + ethnicity + bin_citations")
-formula_years <- as.formula("years ~ #sentiment  + 
+formula_years <- as.formula("years ~  
                   ethnicity +
                   sex +
                   area_clinical_medicine +
@@ -480,7 +482,11 @@ heck1 <- heckit(formula_response,
 # ML estimation of selection model
 ml1 = selection(formula_response,
                 formula_years,
-                data = df)
+                data = df,
+                method = 'ml') # 2step or ml
+
+# Make tidy
+heckman <- summary(ml1)
 
 # # Look at results
 # stargazer(ols1, heck1, ml1,

### 2017-10-10 paper.Rmd
finished heckman

@@
 
-## The need for the wisdom of crowds
+## The need for a broad concensus
 
@@
 Additionally, one could argue that assessing likelihood and time frame of eradication is too important, subjective and complex a task to be left to only powerful individuals or small panels and committees.
-It requires the “wisdom of crowds.” Measuring consensus and discord among disease-specific researchers from a variety of disciplines can serve as a barometer of (informed) opinion, both guiding resources and identifying areas of concern [@Keenan2013].
+It requires the aggregation of multiple points of view.
+Measuring consensus and discord among disease-specific researchers from a variety of disciplines can serve as a barometer of (informed) opinion, both guiding resources and identifying areas of concern [@Keenan2013].
 
@@
 
-```{r, results = 'asis'}
-stargazer(ols1, heck1, ml1,
-          header = FALSE,
-          # se=list(cse(ols1),NULL,NULL),
-          title="Regression on years until eradication", 
-          type="text",
-          df=FALSE, digits=4)
-# summary(ols1)
-# summary(heck1)
+```{r, results = 'markup'}
+# stargazer(ols1, heck1, ml1,
+#           header = FALSE,
+#           # se=list(cse(ols1),NULL,NULL),
+#           title="Regression on years until eradication", 
+#           type="text",
+#           df=FALSE, digits=4)
+# # summary(ols1)
+# # summary(heck1)
 
@@
   x <- df %>%
+    filter(responded) %>%
     dplyr::select_(paste0('years_', n)) 
@@
 year_list <- list()
-
-small_areas <- areas_df$area[areas_df$count >= 15]
-small_areas <- areas[1:12]
+areas_df <- areas_df %>% arrange(desc(count))
+small_areas <- areas_df$area[1:12]
 for (i in 1:length(small_areas)){
@@
              color = 'black',
-             alpha = 0.8)
+             alpha = 0.8) +
+  ylim(0, 6)
+ggsave('~/Desktop/figure2.png', height = 4, width = 5.5)
 ```

### 2017-10-10 prepare_data.R

@@ -130,6 +130,7 @@ df$area[df$area == 'vector biology'] <- 'biology'
 areas <- tolower(paste0(sort(unique(df$area)), collapse = ', '))
 areas <- sort(unique(unlist(strsplit(x = areas, split = ','))))
 areas <- trimws(areas, which = 'both')
+areas <- sort(unique(areas))
 old_areas <- areas
 
 # Remove those areas for which there are fewer than 5 of a kind
@@ -271,7 +272,26 @@ df <-
          n_citations_average = ifelse(is.na(n_citations_average), 0, 
                                       n_citations_average))
 
-# Predict the gender based on first name ####
+# Make a numeric version of the probabilities
+prob_cols <- paste0('years_', seq(10, 50, 10))
+for (j in 1:length(prob_cols)){
+  old_name <- prob_cols[j]
+  new_name <- paste0(old_name, '_numeric')
+  var <- df[,old_name]
+  converted <- ifelse(var == '0%', 0,
+                      ifelse(var == '1-20%',
+                             10,
+                             ifelse(var == '21-40%',
+                                    30,
+                                    ifelse(var == '41-60%', 
+                                           50,
+                                           ifelse(var == '61-80%',
+                                                  70,
+                                                  ifelse(var == '81-99%',
+                                                         90,
+                                                         ifelse(var == '100%', 100, NA)))))))
+  df[,new_name] <- converted
+}
 
 # Extract first/last names
 df$first_name <- tolower(unlist(lapply(strsplit(df$name, ' '), function(x){x[1]})))
@@ -444,8 +464,7 @@ df <- df %>%
 
 # Heckman selection
 # We're estimating years as a function of sex and ethnicity
-ols1 = lm(years ~ sentiment  + 
-            ethnicity +
+ols1 = lm(years ~ ethnicity +
             sex +
             # area_anthropology +
             bin_citations, data = df[df$responded,])
@@ -459,18 +478,27 @@ ols1 = lm(years ~ sentiment  +
 # Heckman 2 step
 # first equation is likelihood of response
 # second equation is impact on response
-formula_response <- as.formula("responded ~ sex + ethnicity + bin_citations")
-formula_years <- as.formula("years ~  
+formula_response <- as.formula('responded ~ bin_citations')
+formula_years <- as.formula("years ~
                   ethnicity +
                   sex +
[…]

### 2017-10-11 abstract.Rmd
big update

--- 2017-09-12 paper.Rmd
@@
 title: Silent pessimists - researchers' perceptions of malaria eradication and implications for health spending
+subtitle: Abstract
 author:
@@
 ---
-
-```{r, echo = FALSE, warning = FALSE, message = FALSE, comment = NA, error= FALSE, cache = F}
-# No scientific notation
-options(scipen=999)
-
-# Packages (load child-specific packages in their respective files)
-library(knitr)
-library(xtable)
-
-# Basic knitr options
-opts_chunk$set(comment = NA, 
-               echo = FALSE, 
-               warning = FALSE, 
-               message = FALSE, 
-               error = TRUE, 
-               cache = FALSE,
-               fig.align = 'center')
-options(xtable.comment = FALSE)
-
-# Get data
-source('prepare_data.R')
-```
-
-# Introduction
-
-## Background
-
-The scientific and public health communities have had eradication on their long-term agenda since the WHO established the Global Malaria Eradication Program in the 1950s [@Njera2011].
-Following the failure of the WHO's first attempt, the focus shifted away from global eradication and towards local elimination and control strategies.
-
-In recent years, much of the discourse regarding malaria has shifted back to global eradication [@Roberts2007], with funders, researchers, and public health practitioners rallying to the cause [@Tanner2015].
-The Bill and Melinda Gates Foundation has begun actively promoting eradication as feasible "within a generation" [@Gates2014], and the leadership of the World Health Organization (WHO) has supported this goal.
-Even in areas of high endemicity, advances in immunology, parasitology, modeling and vaccinology, along with rapid economic development, have made eradication appear a more feasible goal, even if not possible in the short term [@Snow2015, @Eckhoff2014].
-From both administrative [@Yamey2004] and scientific [@Alonso2011] points of view, eradication has never before received so much attention, nor appeared so within grasp.
-
-Most of the current research on expert opinion regarding the feasibility of malaria eradication focuses on the \emph{how} rather than the \emph{if} and the \emph{when} [@Tanner2015].
-The participants in the Malaria Eradication Research Agenda (MalERA) process, in particular, have positioned themselves as thought leaders in the field of guiding research goals and identifying gaps in order for elmination to occur [@Alonso2011].
-Though the MalERA authors firmly state that eradication is \emph{not} feasible given the "current tools and state of knowledge", mentions to the time frame are vague ("within the lifetime of young scientists just embarking on their careers") and no mention is made of the perception of the probability of achieving eradication.
-
-## The problem
-
-The WHO Global Malaria Programme (GMP) has acknowledged that it "needs to take an official position on how and under what timeline malaria eradication could be achieved" [@WHO2015].
-Such a position could inform policy, and plays a crucial role in the economic analysis of the expected value of malaria control inteventions.
-
-However, no such position has been taken.
-This omission is likely intentional, and certainly understadable, given that MalERA's and the WHO GMP's goals are to guide research and technology in the direction of eradication, and not necessarily address the larger and much more subjective questions of \emph{if} and \emph{when}.
-
-But just how close are we to eradication?
-The objective serves to inspire, rally funder support, motivate researchers, and focus the efforts of public health practitioners.
-Proponents of disease eradication point to the success of historical and current campaigns (smallpox and polio, respectively), and highlight the benefits in health and wealth to future generations.
-However, the opportunity cost of investments in eradication-specific interventions can be high.
-And the “expected value” of an investment in a binary scenario (eradication or not) is a function of the probability of the scenario’s occurrence, and the temporal lag of that occurrence.
-Therefore, knowing the likelihood and time frame of eradication of malaria is essential for making sound investments in health.
-
-## The need for the wisdom of crowds
-
-Patients often ask for a “second opinion”, a request which implicitly recognizes two important truths: (1) that an expert can sometimes be wrong and (2) that the combined opinions of multiple people can better approximate the truth than the opinion of only one.
-As Sir Francis Galton demonstrated in his famous ox-weight experiment [@Wallis2014], averaging the opinions of many can be more accurate than taking the opinion of any single expert, since the biases of diverse viewpoints can be complementary and symbiotic.
-
-Additionally, one could argue that assessing likelihood and time frame of eradication is too important, subjective and complex a task to be left to only powerful individuals or small panels and committees.
-It requires the “wisdom of crowds.” Measuring consensus and discord among disease-specific researchers from a variety of disciplines can serve as a barometer of (informed) opinion, both guiding resources and identifying areas of concern [@Keenan2013].
-
-## Rationale
-
-A great deal of previous research already covers the the cost per case prevented [@Sicuri2011, @Silumbe2015, @Btto2016, @IlungaIlunga2014, @Dalaba2015].
-Likewise, a literature exists which could serve as a model for quantifying the location-specific opportunity costs associated with funneling funds towards malaria eradication [@Stuckey2014, @White2011, @Korenromp2012].
-The correct discount rate for estimating the value of future lives saved is more of a philosphical question than an economic one.
-This leaves only the probability and time-frame to eradication, questions which have been addressed anecdotally, but never answered quantitatively.
-
-The economic case for striving to achieve malaria eradication is compelling [@Barofsky2015].
-Though the case-specific marginal cost of eradication can be expected to be high (relative to a simple control approach), successful eradication would mean massive recurring savings in the long-term [@Barrett2013].
-However, to the extent that the case-specific marginal cost of prevention in an eradication campaign is high, estimating the likelihood of success is fundamental to the correct distribution of resources, particularly in low-income environments.
-
-In other words, the rational assignment of resources for malaria eradication campaigns hinges on the expected value of those campaigns. We can describe this relationship formulaically below:
-
-\begin{center}
-$I_{T}$ = $P(x)_{}$ $\dfrac{B(m_{})}{m_{}}$(1 + $\delta$)$^{-T}$ -  $P(x)_{}$ $\dfrac{C(m_{})}{m_{}}$ (1 + $\delta$)$^{-T}$
-\end{center}
-
-\begin{itemize}
-\item $ I $ is the return on investment
-\item $ m $ is the number of malaria cases
-\item $ x $ is the cut-off for a "successful campaign", ie the portion of eradication achieved
-\item $ T $ is the time-frame (to both costs and benefits)
-\item $ P $ is the probability of success
-\item $ B $ is the benefit of preventing malaria
-\item $ C $ is the cost of preventing malaria
-\item $ \delta $ is the discount rate and opportunity cost
-\end{itemize}
-
-(I) is the return on investment at time (T) (the "end of malaria").
-We take the present value of the benefits multiplied by the probability of succcess minus the value of costs times the probability of success, and multiplyboth terms by the discount rate traised to T to arrive at the return on investment.
-
-## Objective
-
-The objective of this study is simple: to help guide the optimal distribution of health resources by gauging (expert) opinion about, estimating the likelihood of, and quantifying the time frame to malaria eradication through a systematic survey of malaria research professionals from a wide array of academic disciplines.
-
-# Methods
-
-## Ethics
-
-This research followed the principles of the Declaration of Helsinki. The study's protocol was approved by the Scientific Committee of the Barcelona Institute for Global Health.
-
-## Participants
-
-Our study population included all first authors (with available email addresses) returned in a PubMed search for the term "malaria" from January 1, 2010 through December 20, 2016.
-Personalized emails addressing the author by name and mentioning the relevant paper were sent to each of the `r nrow(email_df)` authors during the period from December 20, 2016 through January 2, 2017.
-Researchers were invited to participate by clicking a link to the survey form.
-Participants were informed directly on the survey form of the study's purpose, that responses were not guarnteed to be anonymous, and where to find further details on the study.
-
-## Survey
-
-The survey was simple, consisting of only name, email, and four content-related fields along with a "general comments" section.
-The survey was administered and data were collected through Google Drive.
-The original survey is viewable at [https://goo.gl/forms/IroAEooDuJ6KM5Ho2](https://goo.gl/forms/IroAEooDuJ6KM5Ho2).
-
-Content-related survey fields consisted of:
-
-1. Area of expertise.
-
-2. Perceived probability (%) of malaria eradication in 10, 20, 30, 40, and 50 years.
-
-3. Free choice perceived number of years until malaria eradication.
-
-4. Ranking of the WHO's "health system building blocks" in regards to attention needed in order to achieve eradication.
-
-## Data generation
-
-The survey was intentionally as short as possible, so as to appeal to time-pressed participants.
-However, supplementary data on researchers' demographics is of value.
-Accordingly, we estimated the likelihood of a participant being of one of two genders (male or female) based on first name, and the likelihood of a participant being of one of five ethnicities (White, Black, Hispanic, Asian, Other) based on the provided last name.
-
-## Analysis
-
-Survey results were first analyzed descriptively.
-Following Francis Galton's example, we naively take the average of all responses as the likely point estimate for event probabilities, and the totality of the responses to each numeric question as the likely confidence interval of those likelihoods and time frames.
-
-Ordinary least squares regression was employed to estimate the effect of area of expertise on the eradication pessimism-optimism (through the proxy of perceived years to eradication).
-
-Content analysis of free text comments was carried out using frequency analyses. Comments were categorized and coded according to (more details needed here).
-
-All analysis was carried out in R language [@R].
-All analysis code, as well as the code used for the identification and contacting of participants, is publicly available at [https://github.com/joebrew/malaria_survey](https://github.com/joebrew/malaria_survey).
-
-The searching and retrieval of information from the PubMed database was carried out using the RISmed package [@Kovalchik2015]. Qualitative analysis relied on the RQDA package (citation needed here).
-
-The estimation of gender and ethnicity likelihoods for each participant relied on Mullen's implementation of US Social Security Administration names' analysis [@gender2015] and Khanna et al's bayesian prediction algorithm for the estimation of racial categories [@wru2015].
-
-De-biasing of sample selection was carried out using Heckman's 2 step approach (citation needed), as implemented by Toomet [@toomet2008].
-
-# Results
-
-A total of `r nrow(df)` researchers participated in the survey.
-
-## Sample selection and de-biasing of results
-
-This section is unfinished. Below are regression outputs for both OLS and Heckman's 2 step model. I will update this soon.
-
-```{r, results = 'asis'}
-stargazer(ols1, heck1, ml1,
-          header = FALSE,
-          # se=list(cse(ols1),NULL,NULL),
-          title="Regression on years until eradication", 
-          type="latex",
-          df=FALSE, digits=4)
-# summary(ols1)
-# summary(heck1)
-
-```
-
-## Expertise profile
-
-```{r}
-x <- df %>%
-  group_by(n_areas) %>%
-  tally %>%
-  mutate(p = n / sum(n) * 100)
-```
-
-Areas of expertise were non-exclusive and self-described, with participants having the option to choose from up to 3 of 10 checkboxes\footnote{Checkbox categories were anthropology, biology, clinical medicine, economics, epidemiology, immunology, parasitology, political science, statistics, and virology.}, or to write in one or more "other" areas of expertise.
-`r x$n[1]` participants (`r round(x$p[1], digits = 1)`%) declared only one area of expertise, with `r sum(x$n[1:3])` (`r round(sum(x$p[1:3]), digits = 1)`%) declaring three or fewer.
-
-Participants had a total of `r length(old_areas)` unique (self-described) areas of expertise, of which `r length(areas)` areas of expertise had 5 or more participants.
-
-```{r}
-temp <- areas_df %>%
-  arrange(desc(count))
-temp$area <- trimws(temp$area, which = 'both')
-names(temp) <- c('Area', 'Researchers')
-temp$Area <- as.character(temp$Area)
-temp$Area <- Hmisc::capitalize(temp$Area)
-kable(temp)
-```
-
-## Likelihood of eradication
-
-Participants were asked to quantify (as a percentage) the likelihood of eradication in the next 10, 20, 30, 40, and 50 years.
-Most participants saw eradication as extremely unlikely in the next 10-30 years, but increasingly likely thereafter.
-The following figure shows the distribution of year-specific likelihood perceptions (panels A-E), as well as an illustration of how both likelihood and uncertainty grow over time (panel F).
-
-```{r}
-# Define function for analyzing the years_n columns
-years_n <- function(n){
-  x <- df %>%
-    dplyr::select_(paste0('years_', n)) 
-  names(x) <- 'likelihood'
-  result <- x %>%
-    group_by(likelihood) %>%
-    tally %>%
-    mutate(p = n / sum(n) * 100) %>%
-    filter(!is.na(likelihood))
-
-  out <- list()
-  out[[1]] <- result
-  out[[2]] <-
-    ggplot(data = result,
-           aes(x = likelihood,
-               y = p)) +
-    geom_bar(stat = 'identity',
-             fill = 'darkorange',
-             alpha = 0.6) +
-    labs(title = paste0(toupper(letters[n/10]),'. ', n, ' years'),
-         subtitle = 'Perceived likelihood of eradication',
-         x = 'Likelihood',
-         y = '%') +
-    theme_publication(base_size = 10) +
-    theme(axis.text.x = element_text(angle = 90))
-  return(out)
-}
-```
-
-```{r, fig.height = 7}
-# Make plots of all
-years <- seq(10, 50, 10)
-for (i in 1:length(years)){
-  assign(paste0('g',i ),
-         years_n(n = years[i])[[2]])
-  x <- years_n(n = years[i])[[1]]
-  x$year <- years[i]
-  assign(paste0('x', i),
-         x)
-
-}
-# Combine all data
-x <- bind_rows(x1, x2, x3, x4, x5)
-
-# Make an aggregated version
-x$val <- ifelse(x$likelihood == '0%', 0,
-                ifelse(x$likelihood == '1-20%', 10,
-                       ifelse(x$likelihood == '21-40%', 30,
-                              ifelse(x$likelihood == '41-60%', 50,
-                                     ifelse(x$likelihood == '61-80%', 70,
-                                            ifelse(x$likelihood == '81-99%', 90,
-                                                   ifelse(x$likelihood == '100%', 100, NA)))))))
-xa <- x %>%
-  dplyr::group_by(year) %>%
-  dplyr::summarise(avg = weighted.mean(x = val, w = n, na.rm = TRUE),
-            q3 = Hmisc::wtd.quantile(val, weights = n, 0.75, na.rm = TRUE),
-            q1 = Hmisc::wtd.quantile(val, weights = n, 0.25, na.rm = TRUE))
-
-g6 <- 
-  ggplot(data = xa,
-         aes(x = year,
-             y = avg)) +
-  geom_ribbon(aes(ymin = q1,
-                  ymax = q3),
-              fill = 'orange',
-              alpha = 0.6) +
-  geom_line(color = 'darkorange') +
-  theme_publication(base_size = 10) +
-  xlab('Years') +
-  ylab('Average likelihood') +
-  ggtitle('G. Aggregated perceptions',
-          'Shaded area = inter-quartile range')
-
-Rmisc::multiplot(g1, g3, g5,
-                 g2, g4, g6,
-                 cols = 2)
-```
-
-## Time frame to eradication
-
-Participants were asked to provide the number of years they believe it will take until eradication can be achieved.
-`r length(which(is.na(df$years)))` (`r round(length(which(is.na(df$years))) / nrow(df) * 100, digits = 1)`%) were either blank or uninteligible, whereas `r length(which(!is.na(df$years)))` participants responded.
-Among respondants, `r length(which(df$years >= 50))` (`r round(length(which(df$years >= 50)) / length(which(!is.na(df$years))) * 100, digits = 1)` %) estimated that it would be 50 or more years until eradication.
-The below histogram shows the distribution of responses, appended at 50.
-
-```{r, fig.height = 3.5, fig.width = 4}
-ggplot(data = df,
-       aes(x = years)) +
-  geom_histogram(fill = 'darkorange',
-                 alpha = 0.6) +
-  theme_publication(base_size = 10) +
-  labs(x = 'Years',
-       y = 'Responses',
-       title = 'Perceived years until eradication',
-       subtitle = '(Estimates of greater than 50 years reduced to 50)')
-```
-
-## Difference in perceptions by expertise
-
-Participants were heterogenous in their perceptions, with all of the 5 pre-determined cut-offs containing the whole range of likelihoods (0-100%), and the free-form time frame responses suggesting that eradication would be achieved in as little as `r min(df$years, na.rm = TRUE)` to as many as "never".
-Heterogeneity can be partly explained by area of expertise, as evidenced by significant differences in the perceived years to eradication by area of expertise.
-
-```{r, fig.height = 4.5, fig.width = 4.5}
-# Get averages per area
-results_list <- list()
-dist_list <- list()
-year_list <- list()
-
-small_areas <- areas_df$area[areas_df$count >= 15]
-small_areas <- areas[1:12]
-for (i in 1:length(small_areas)){
-  this_area <- small_areas[i]
-  sub_data <- df[df[,paste0('area_', gsub(' ', '_', this_area))],]
-  this_df <- data_frame(area = this_area,
-                        avg = mean(sub_data$years, na.rm = TRUE),
-                        med = median(sub_data$years, na.rm = TRUE))
-  dist_df <- data_frame(area = this_area,
-                        val = sub_data$years)
-  numberfy <- function(x){
-    ifelse(x == '0%', 0,
-                ifelse(x == '1-20%', 10,
-                       ifelse(x == '21-40%', 30,
-                              ifelse(x == '41-60%', 50,
-                                     ifelse(x == '61-80%', 70,
-                                            ifelse(x == '81-99%', 90,
-                                                   ifelse(x == '100%', 100, NA)))))))
-
-  }
-  year_df <- data.frame(area = this_area,
-                        year = seq(10, 50, 10),
-                        val = c(mean(numberfy(sub_data$years_10), na.rm = TRUE),
-                                mean(numberfy(sub_data$years_20), na.rm = TRUE),
-                                mean(numberfy(sub_data$years_30), na.rm = TRUE),
-                                mean(numberfy(sub_data$years_40), na.rm = TRUE),
-                                mean(numberfy(sub_data$years_50), na.rm = TRUE)))
-  for (q in seq(0, 100, 10)){
-    this_df[,paste0('q_', q)] <- 
-      quantile(sub_data$years, q / 100, na.rm = TRUE)
-  }
-  results_list[[i]] <- this_df
-  dist_list[[i]] <- dist_df
-  year_list[[i]] <- year_df
-}
-results <- bind_rows(results_list)
-dist_results <- bind_rows(dist_list)
-year_results <- bind_rows(year_list)
-dist_results$the_area <- dist_results$area
-
-ggplot(data = dist_results,
-       aes(#group = area,
-           #fill = area,
-           x = val)) +
-  geom_density(fill = 'darkorange',
-               alpha = 0.6) +
-  theme_publication(base_size = 10) +
-  labs(x = 'Years',
-       y = 'Density',
-       title = 'Perceived years to eradication',
-       subtitle = '12 most popular areas of expertise only') +
-  facet_wrap(~the_area) 
-```
-
-```{r, fig.height = 3.5, fig.width = 4}
-model_formula <- paste0('years ~ ',
-                        paste0(paste0('area_', gsub(' ', '_', small_areas)), collapse = ' + '))
-model_formula <- as.formula(model_formula)
-fit <- lm(model_formula, data = df)
-# Get confidence intervals too
-ci <- tidy(confint(fit))
-x <- cbind(tidy(fit), ci)
-names(x) <- c('term', 'estimate', 'se', 'stat', 'p', 'rownames', 'lwr', 'upr')
-x <- x %>%
-  dplyr::select(term, estimate,
-                p, lwr, upr)
-the_intercept <- x$estimate[1]
-x <- x[-1,]
-for (the_column in c('estimate', 'lwr', 'upr')){
-  x[,the_column] <- x[,the_column] + the_intercept
-}
-x$term <- gsub('area_|TRUE', '', x$term)
-x <- x %>%
-  dplyr::arrange(estimate)
-x$term <- gsub('_', '\n', x$term)
-x$term <- factor(x$term, levels = x$term)
-ggplot(data = x,
-       aes(x = term,
-           y = estimate)) +
-  geom_bar(stat = 'identity',
-           fill = 'darkorange',
-           alpha = 0.6) +
-  geom_errorbar(aes(ymin = lwr,
-                    ymax = upr),
-                alpha = 0.6,
-                width = 0.8) +
-  theme_publication(base_size = 10) +
-  labs(x = 'Area',
-       y = 'Years',
-       title = 'Perceived years to eradication',
-       subtitle = 'By expertise, adjusted for multiple areas of expertise') +
-  theme(axis.text.x = element_text(angle = 90))
-
-```
-
-Heterogeneity by area of expertise is also apparent in perceived likelihood of eradication over the pre-defined five time-points, as seen below.
-
-```{r, fig.height = 4, fig.width = 4.5}
-cols <- colorRampPalette(brewer.pal(9, 'Spectral'))(length(unique(year_results$area)))
-ggplot(data = year_results,
-       aes(x = year,
-           y = val)) +
-  geom_line(aes(group = area,
-           color = area,
-           lty = area)) +
-  theme_publication(base_size = 10) +
-  scale_color_manual(name = '',
-                     values = cols,
-                     labels = unique(year_results$area)) +
-  scale_linetype_manual(name="", 
-                        values = rep(1:6, 100)[1:length(unique(year_results$area))],
-                     labels = unique(year_results$area)) +
-  xlab('Years until eradication') +
-  ylab('Likelihood') +
-  ggtitle('Likelihood trajectories',
-          'By area of expertise')
-```
-
-## Sentiment analysis of free-text commentary
-
-This section is unfinished.
-Below is the distribution of "sentiment" among the responses (0 is neutral, below 0 is negative, above 0 is positive), but this is preliminary.
-The chart is colored by ethnicity, and faceted by gender.
-
-```{r}
-ggplot(data = df %>%
-         filter(responded) %>%
-         # mutate(n_areas = factor(n_areas)) %>%
-         filter(!is.na(ethnicity),
-                !is.na(gender)),
-       aes(x = sentiment,
-           group = ethnicity)) +
-  geom_density(aes(fill = ethnicity),
-               alpha = 0.6,
-               n = 10) +
-  theme_publication() +
-  facet_wrap(~gender)
-
-```
-
-## Health system building blocks
-
-Finally, researchers were asked to rank the WHO's 6 health system building blocks as needing the most to least attention (6-1 scale) in order for eradication to be achieved.
-Disagreement was high, as evidenced by the variance in responses in the below point and violin chart.
-However, the general tendency was that governance was recognized as the most important area requiring attention, with health information thought to be the area least requiring attention.
-
-```{r}
-bb <- c('governance', 'health_workforce',
-        'health_financing', 'health_technologies',
-        'health_information', 'service_delivery')
-results_list <- list()
-for (i in 1:length(bb)){
-  this_df <- data.frame(bb = bb[i],
-                        ranking = as.numeric(df[,bb[i]]))
-  results_list[[i]] <- this_df
-}
-results <- bind_rows(results_list)
-results$bb <- gsub('_', '\n', results$bb)
-
-results_agg <-
-  results %>%
-  dplyr::group_by(bb) %>%
-  dplyr::summarise(avg = mean(ranking, na.rm = TRUE)) %>%
-  arrange(avg)
-results_agg$bb <- factor(results_agg$bb,
-                         levels = results_agg$bb)
-results$bb <- factor(results$bb, 
-                     levels = levels(results_agg$bb))
-
-ggplot(data = results) + 
-  geom_violin(aes(x = bb,
-           y = ranking),
-           fill = 'orange',
-              alpha = 0.6) +
-  geom_jitter(aes(x = bb,
-           y = ranking),
-           color = 'black',
-           with = 0.4,
-           height = 0.4,
-              alpha = 0.3,
-              size = 1) +
-  theme_publication(base_size = 10) +
-  labs(x = 'WHO Building block',
-       y = 'Ranking',
-       title = 'Perceived areas needing attention',
-       subtitle = 'Small points: jittered individual responses; large triangles: averages') +
-  geom_point(data = results_agg,
-             aes(x = bb,
-                 y = avg),
-             size = 5,
-             pch = 17,
-             color = 'black',
-             alpha = 0.8)
-```
-
-# Discussion
-
-## Collective pessimism
-
-Our study reveals a striking gap between the public discourse on malaria eradication, and those views held (largely privately) by malaria researchers.
-Approximately three-quarters of respondents believe that malaria will not be eradicated in the next 50 years; in other words, assuming our pool of respondents is of typical post-PhD age, most believe they will not live to see eradication.
-
-If we take the pooled opinions of researchers, as revealed through this survey, as the best approximation of truth available, then the disconnect between public discourse on malaria eradication and private opinion is troubling.
-It suggests that the goals set by the Bill and Melinda Gates Foundation (eradication "within a generation") and the WHO GMP (eradication "within the lifetime of young scientists just embarking on their careers") are unrealistic at best, and misleading at worst.
-This has important implications for spending in public health, since the attention and resources of funders, researchers and government agencies are directed to those areas where a result is expected.
-
-On the other hand, there are many reasons to be skeptical that the combined "wisdom of crowds" of malaria researchers is a reliable indicator of truth.
-First, academic researchers are specialists - their narrow, field-specific view of eradication's feasibility is arguably less reliable than the more "global" views of the WHO, or Bill Gates.
-Second, a number of biases may come in to play in this study.
-
-Among these biases, 4 are worth mentioning specifically.
-(1) "Conjunction fallacy" suggests that the general goal of eradication may seem less likely than the sum of the goals of country-specific elimination.
-(2) A (reverse) variant of the "hot hand fallacy", in which researchers may mistakenly base their assessment of current chances of eradication on previous failures.
-(3) Parkinson's law of triviality suggests that researchers may disproportionately see the challenges of their own research (antimalarial drug resistance, etc.) as larger or more relevant to the global eradication campaign than they really are.
-(4) Finally, and ironically, "optimism bias" may play a perverse role in researchers' responses; though eradication is certainly a goal desired by all, one could argue that malaria research specialists subconciously realize that they actually stand to lose out profesionally in the case of eradication.
-
-Whether the collective "wisdom" of researchers is worth adhering to or not is arguable.
-That said, to the extent that researchers' private opinions differ so greatly from those of global health leaders is itself a noteworthy result.
-If leaders' high levels of optimism are well-placed, this suggests that researchers are unduly pessimistic, and efforts should be made to convince them that eradication is more feasible than they realize.
-If, on the other hand, collective wisdom is a better forecasting agent than the proclamations and objectives of global health leaders, then it is important to recognize the sad truth that we are likely further from eradication than we would like to be.
-In this case, though the discourse on eradication can be motivating and inspiring, resources should be directed in a manner that reflects an intended outcome's likelihood of occurrence.
-
-## Building blocks to eradication
-
-It is noteworthy that there was so much discord among researchers in regards to which WHO building blocks required the most attention in order for eradication to be achieved.
-All six possible categories received votes for both the lowest and highest levels of importance, as well as every level in between.
-And the difference between "health information" (the building block deemed as least important) and "governance" (the most important) was less than 0.5 on a 1-6 scale.
-
-This discord suggests that the path to implementing strategies for eradication is not clear, at least from the perspective of this study's participants.
-This could mean that further work is needed in order to prioritize which areas require the most investment and attention in order for eradication to occur.
-On the other hand, one could interpret this result as reflecting the fact that previous work on priorities (ie, MalERA) has not been fully accessed or understood by the larger malaria research community.
-
-## Areas of expertise
-
-It is noteworthy that among the most "optimistic" experts were from the field of bioinformatics.
-This could be explained by the fact that, relative to other more "traditional" areas of science, informatics regularly sees paradigm shifts, and changes in technology and breakthroughs occur at a more rapid rate.
-That said, the high degree of optimism among chemists would seem to contradict this hypothesis.
-At any rate...
-(more details will go here).
-
-## Limitations
-
-In addition to the biases mentioned above, this study has many limitations.
-First, though results are not disclosed at the individual level, this survey was not entirely anonymous, suggesting that social desirability bias may have influenced responses, and that selection bias likely meant our pool of participants were substantially different from those who choose not to participate.
-
-Second, we made no distinguishment between quality of research, years of experience, academic achievements, geographical area, etc.
-Our inclusion criteria were simple and rudimentary, allowing us to access many diverse viewpoints, but (perhaps inappropriately) weighting all viewpoints as equal.
-
-Third, this study included the corresponding authors of indexed journals.
-Though certainly a group with important knowledge related to malaria, this misses malaria control program employees, health agency workers, and other stakeholders.
-Their experiences and viewpoints are most likely vastly different from those of academecians.
-
-## Implications
-
-Our survey attempted to quantify the likelihood of and time frame to malaria eradication by gauging the collective opinion of malaria researchers.
-Our results suggest that eradication is unlikely in the short and medium terms, and that there exists a great deal of disagreement among researchers in regards to which areas require the most attention in order for eradication to occur.
-The implication of these results are three-fold: (1) that those working or investing in eradication-specific campaigns should factor in the low likelihood and long time frame when calculating those campaigns' expected value; (2) that champions of near-term eradication need to make a more compelling case to malaria researchers of eradication's feasibility, in order to better focus and inspire the latter; and (3) that discord among malaria researchers as to which areas need the most attention in order for eradication to occur suggests a need for open discussion and concensus-making, so that resources and focus are directed appropriately.
-
-References {#references .unnumbered}
-==========

### 2017-10-11 paper.Rmd
big update

@@
 output: rticles::elsevier_article
+preprint: false
 ---
@@
 # Get data
-source('prepare_data.R')
+source('prepare_data.R', echo = FALSE)
 ```
@@
 ```{r, results = 'markup'}
-# stargazer(ols1, heck1, ml1,
-#           header = FALSE,
-#           # se=list(cse(ols1),NULL,NULL),
-#           title="Regression on years until eradication", 
-#           type="text",
-#           df=FALSE, digits=4)
-# # summary(ols1)
-# # summary(heck1)
+
+ggplot(data = heckman,
+       aes(x = years,
+           y = value,
+           color = key,
+           lty = key)) +
+  geom_line(alpha = 0.8) +
+  geom_point(alpha = 0.6) +
+  theme_black() +
+  labs(x = 'Years',
+       y = 'Likelihood of eradication') +
+  scale_linetype_manual(name = '', values = 1:2) +
+  scale_color_manual(name = '', values = c('white', 'darkorange')) +
+  labs(title = 'Heckman selection adjustment')
 
@@
 
-ggplot(data = results) + 
-  geom_violin(aes(x = bb,
-           y = ranking),
-           fill = 'orange',
-              alpha = 0.6) +
-  geom_jitter(aes(x = bb,
-           y = ranking),
-           color = 'black',
-           with = 0.4,
-           height = 0.4,
-              alpha = 0.3,
-              size = 1) +
-  theme_publication(base_size = 10) +
-  labs(x = 'WHO Building block',
-       y = 'Ranking',
-       title = 'Perceived areas needing attention',
-       subtitle = 'Small points: jittered individual responses; large triangles: averages') +
-  geom_point(data = results_agg,
-             aes(x = bb,
-                 y = avg),
-             size = 5,
-             pch = 17,
-             color = 'black',
-             alpha = 0.8) +
-  ylim(0, 6)
-ggsave('~/Desktop/figure2.png', height = 4, width = 5.5)
+library(ggridges)
+ggplot(data = results %>% filter(!is.na(ranking)),
+       aes(x = ranking,
+           y = bb,
+           fill = bb)) +
+  geom_density_ridges(#fill = 'darkorange',
+                      alpha = 0.6,
+                      scale = 1.5) +
+  theme_black() +
+  xlim(0,30) +
+  labs(x = 'Perceived importance',
+       y = 'WHO Building Block') +
+ scale_fill_cyclical(values = c("darkorange", "yellow"))
+
+# ggplot(data = results) + 
+#   geom_violin(aes(x = bb,
+#            y = ranking),
+#            fill = 'orange',
+#               alpha = 0.6) +
+#   geom_jitter(aes(x = bb,
+#            y = ranking),
+#            color = 'black',
+#            with = 0.4,
+#            height = 0.4,
+#               alpha = 0.3,
+#               size = 1) +
+#   theme_publication(base_size = 10) +
+#   labs(x = 'WHO Building block',
+#        y = 'Ranking',
+#        title = 'Perceived areas needing attention',
+#        subtitle = 'Small points: jittered individual responses; large triangles: averages') +
+#   geom_point(data = results_agg,
+#              aes(x = bb,
+#                  y = avg),
+#              size = 5,
+#              pch = 17,
+#              color = 'black',
+#              alpha = 0.8) +
+#   ylim(0, 6)
 ```

### 2017-10-11 prepare_data.R

@@ -12,6 +12,7 @@ library(gender)
 library(wru)
 library(sampleSelection)
 library(stargazer)
+library(nnet)
 
 # Get publication theme for charts
 source('theme_publication.R')
@@ -243,8 +244,8 @@ bb <- c('governance', 'health_workforce',
         'health_information', 'service_delivery')
 for (i in 1:nrow(df)){
   sub_df <- df[i,bb]
-  new_values <- sub_df / sum(sub_df, na.rm = TRUE) * 21
-  new_values[new_values > 6] <- 6
+  new_values <- sub_df / sum(sub_df, na.rm = TRUE) * 100
+  # new_values[new_values > 6] <- 6
   df[i,bb] <- new_values
 }
 
@@ -462,23 +463,46 @@ df$bin_citations <-
 df <- df %>%
   filter(ethnicity != 'other')
 
+# See if men and women have different pessimism scores
+
+sig <- data.frame(expand.grid(years = rep(seq(10, 50, 10), each = 6),
+                              p = NA))
+for (i in seq(10, 50, 10)){
+  suppressMessages(test <- multinom(as.formula(paste0('years_', i, ' ~ sex')), data = df))
+  z <- summary(test)$coefficients/summary(test)$standard.errors
+  p <- (1 - pnorm(abs(z), 0, 1))*2
+  p <- p[,2]
+  sig$p[sig$years == i] <- p
+}
+if(all(sig$p > 0.05)){
+  message('No significant difference between men and womens optimism')
+} else {
+  message('Men and women are significantly different re: optimism')
+}
+sig_respond <- glm(responded ~ sex, data = df, family = binomial('logit'))
+summary(sig_respond)
+if(broom::tidy(sig_respond)$p.value[2] <= 0.05){
+  message('Men and women have different response rates')
+} else {
+  message('Men and women have similar response rates')
+}
 # Heckman selection
-# We're estimating years as a function of sex and ethnicity
-ols1 = lm(years ~ ethnicity +
-            sex +
-            # area_anthropology +
-            bin_citations, data = df[df$responded,])
+# # We're estimating years as a function of sex and ethnicity
+# ols1 = lm(years ~ ethnicity +
+#             sex +
+#             # area_anthropology +
+#             bin_citations, data = df[df$responded,])
 
 # Estimate likelihood of response
 # it is very desirable to have at least one variable in the selection equation that acts like an instrument:
 # (https://rpubs.com/wsundstrom/t_selection)
[…]

### 2017-10-11 shiny/global.R

@@ -1,0 +1,160 @@
+library(shinydashboard)
+library(googlesheets)
+library(ggplot2)
+library(dplyr)
+library(Hmisc)
+library(ggridges)
+
+
+# Define plotting theme
+theme_databrew <- function (base_size = 15, base_family = "Sawasdee", y_comma = TRUE, 
+                            subtitle_family = "Sawasdee", axis_family = "Sawasdee") 
+{
+  color_background = "#F8F5E1"
+  color_grid_major = "grey"
+  color_axis_text = "#0d63c4"
+  color_axis_title = color_axis_text
+  color = "darkgrey"
+  color_title = color_axis_text
+  color_subtitle = grey(0.1)
+  base_size1 = base_size
+  out <- theme_bw(base_size = base_size1) + theme(panel.background = element_rect(fill = color_background, 
+                                                                                  color = color_background)) + theme(plot.background = element_rect(fill = color_background, 
+                                                                                                                                                    color = color_background)) + theme(panel.border = element_rect(color = color_background)) + 
+    theme(panel.grid.major = element_line(color = adjustcolor(color_grid_major, 
+                                                              alpha.f = 0.25), size = 0.25)) + theme(panel.grid.major = element_line(color = adjustcolor(color_grid_major, 
+                                                                                                                                                         alpha.f = 0.4), size = 0.4)) + theme(panel.grid.minor = element_blank()) + 
+    theme(axis.ticks = element_blank()) + theme(legend.background = element_rect(fill = color_background)) + 
+    theme(legend.text = element_text(family = base_family, 
+                                     size = base_size * 0.7, color = color_axis_title)) + 
+    theme(plot.title = element_text(family = base_family, 
+                                    color = color_title, size = base_size * 1.2, vjust = 1.25)) + 
+    theme(plot.subtitle = element_text(family = subtitle_family, 
+                                       color = color_subtitle, size = base_size * 0.8, vjust = 1.25)) + 
+    theme(axis.text.x = element_text(family = axis_family, 
+                                     size = base_size * 0.7, color = color_axis_text)) + 
+    theme(axis.text.y = element_text(family = axis_family, 
+                                     size = base_size * 0.7, color = color_axis_text)) + 
+    theme(axis.title.x = element_text(family = axis_family, 
[…]

### 2017-10-11 shiny/server.R

@@ -1,0 +1,47 @@
+#
+# This is the server logic of a Shiny web application. You can run the 
+# application by clicking 'Run App' above.
+#
+# Find out more about building applications with Shiny here:
+# 
+#    http://shiny.rstudio.com/
+#
+
+library(shiny)
+library(googlesheets)
+library(ggplot2)
+library(dplyr)
+
+# Define server logic required to draw a histogram
+shinyServer(function(input, output) {
+   
+  
+  
+  output$p1 <- renderPlot({
+    plot_variable(input$variable)
+  })
+  
+  output$p2 <- renderPlot({
+    plot_variable_by(input$variable,
+                     input$by_variable)
+  })
+  output$v1 <- renderValueBox({
+    valueBox(value = nrow(df),
+             subtitle = 'Participants',
+             icon = icon("cog", lib = "glyphicon"),
+             color = 'light-blue')
+  })
+  output$v2 <- renderValueBox({
+    valueBox(value = round(mean(df$years, na.rm = TRUE), digits = 1),
+             subtitle = 'Average age of participants',
+             icon = icon('table'),
+             color = 'red')
+  })
+  output$v3 <- renderValueBox({
+    valueBox(value = round(length(which(df$sex == 'Female')) / nrow(df) * 100, digits = 1),
+             subtitle = '% female',
+             icon = icon('calendar'),
+             color = 'orange')
+  })
+  
+})

### 2017-10-11 shiny/ui.R

@@ -1,0 +1,53 @@
+dashboardPage(
+  dashboardHeader(title = "Survey results"),
+  dashboardSidebar(
+    selectInput("variable",
+                "Variable",
+                c("Joe's height" = 'height',
+                  "Joe's sleep last night" = 'sleep',
+                  "Joe's age" = 'age')),
+    selectInput('by_variable',
+                'Examine results by:',
+                c('', "Participant age" = 'years',
+                  "Participant sex" = 'sex', "Nothing" = 'nothing'))
+  ),
+  dashboardBody(
+    # Boxes need to be put in a row (or column)
+    fluidRow(
+      box(plotOutput("p1", height = 250)),
+      box(plotOutput("p2", height = 250)),
+      valueBoxOutput('v1'),
+      valueBoxOutput('v2'),
+      valueBoxOutput('v3')
+    )
+  )
+)
+
+# library(shiny)
+# 
+# # Define UI for application that draws a histogram
+# shinyUI(fluidPage(
+#   
+#   # Application title
+#   titlePanel("Survey results: was the crowd wise?"),
+#   
+#   # Sidebar with a slider input for number of bins 
+#   sidebarLayout(
+#     sidebarPanel(
+#        selectInput("variable",
+#                    "Variable",
+#                    c('height',
+#                      'sleep',
+#                      'age')),
+#        selectInput('by_variable',
+#                    'Examine results by:',
+#                    c('', 'years', 'sex'))
+#     ),
+#     
+#     # Show a plot of the generated distribution
+#     mainPanel(
+#        plotOutput("p1"),
+#        plotOutput("p2")
+#     )
+#   )
+# ))

### 2017-10-11 theme_publication.R

@@ -43,3 +43,52 @@ scale_colour_publication <- function(...){
   discrete_scale("colour","publication",manual_pal(values = c("#386cb0","#fdb462","#7fc97f","#ef3b2c","#662506","#a6cee3","#fb9a99","#984ea3","#ffff33")), ...)
   
 }
+
+library(ggplot2)
+library(gridExtra)
+
+theme_black = function(base_size = 12, base_family = "") {
+  
+  theme_grey(base_size = base_size, base_family = base_family) %+replace%
+    
+    theme(
+      # Specify axis options
+      axis.line = element_blank(),  
+      axis.text.x = element_text(size = base_size*0.8, color = "white", lineheight = 0.9),  
+      axis.text.y = element_text(size = base_size*0.8, color = "white", lineheight = 0.9),  
+      axis.ticks = element_line(color = "white", size  =  0.2),  
+      axis.title.x = element_text(size = base_size, color = "white", margin = margin(0, 10, 0, 0)),  
+      axis.title.y = element_text(size = base_size, color = "white", angle = 90, margin = margin(0, 10, 0, 0)),  
+      axis.ticks.length = unit(0.3, "lines"),   
+      # Specify legend options
+      legend.background = element_rect(color = NA, fill = "black"),  
+      legend.key = element_rect(color = "white",  fill = "black"),  
+      legend.key.size = unit(1.2, "lines"),  
+      legend.key.height = NULL,  
+      legend.key.width = NULL,      
+      legend.text = element_text(size = base_size*0.8, color = "white"),  
+      legend.title = element_text(size = base_size*0.8, face = "bold", hjust = 0, color = "white"),  
+      legend.position = "right",  
+      legend.text.align = NULL,  
+      legend.title.align = NULL,  
+      legend.direction = "vertical",  
+      legend.box = NULL, 
+      # Specify panel options
+      panel.background = element_rect(fill = "black", color  =  NA),  
+      panel.border = element_rect(fill = NA, color = "white"),  
+      panel.grid.major = element_line(color = "grey35"),  
+      panel.grid.minor = element_line(color = "grey20"),  
+      panel.margin = unit(0.5, "lines"),   
+      # Specify facetting options
+      strip.background = element_rect(fill = "grey30", color = "grey10"),  
+      strip.text.x = element_text(size = base_size*0.8, color = "white"),  
+      strip.text.y = element_text(size = base_size*0.8, color = "white",angle = -90),  
[…]

### 2017-10-12 paper.Rmd
major update

--- 2017-10-10 paper.Rmd
@@
 title: Silent pessimists - researchers' perceptions of malaria eradication and implications for health spending
-author:
-  - name: Joe Brew
-    email: joebrew@economicsofmalaria.com
-    affiliation: isglobal,cism
-    footnote: Corresponding Author
-  - name: Menno Pradhan
-    email: m.p.pradhan@vu.nl
-    affiliation: vu,uva
-  - name: Jacqueline Broerse
-    email: j.e.w.broerse@vu.nl
-    affiliation: vu
-  - name: Elisa Sicuri
-    email: elisa.sicuri@isglobal.org 
-    affiliation: isglobal,icl,cism
-address:
-  - code: isglobal
-    address: Barcelona Institute for Global Health, c/ Rosselló, 132, 5è 2a. 08036, Barcelona, Spain
-  - code: icl
-    address: Imperial College London, South Kensington Campus, London SW7 2AZ, U.K.
-  - code: cism
-    address: Centro de Investigação em Saúde de Manhiça, Vila da Manhiça, Bairro Cambeve, Rua 12, Distrito da Manhiça, CP 1929, Maputo, Mozambique
-  - code: vu
-    address: Faculty of Economics and Business Administration, VU University Amsterdam, De Boelelaan 1105, 1081 HV Amsterdam, Netherlands
-  - code: uva
-    address: Faculty of Economics and Business, Section Microeconomics, University of Amsterdam, REC E, Roetersstraat 11, Amsterdam, Netherlands
-abstract: |
-  Quantifying an event's probability and time frame is essential for calculating its expected value.
-In the case of global malaria eradication, uncertainty regarding feasibility makes it difficult for policymakers and public health practitioners to make fully informed decisions.
-The opportunity cost of investments in eradication-specific interventions can be high, particularly in contexts with other urgent health priorities.
-In a systematic survey of malaria researchers, we query perceptions regarding the likelihood and time frame of eradication, as well as the perceived chief areas needed for improvement in order for eradication to be achieved.
-We assess pessimism/optimism (via the proxy of years-to-eradication), broken down by area of expertise.
-Our results, which suggest a disconnect between public institutional discourse and private opinion, serve as a barometer of professional perspectives, and serve to highlight areas where attention is most needed for eradication to be achieved.
-
 bibliography: library.bib
-params:
-  get_new_data: False
-output: rticles::elsevier_article
+output: 
+  pdf_document:
+    includes:
+      in_header: preamble.sty
 ---
@@
 # Get data
-source('prepare_data.R')
+source('prepare_data.R', echo = FALSE)
+
+theme_paper <- theme_publication
 ```
+
+```{r}
+authors <- data.frame(name = c('Joe Brew',
+                               'Menno Pradhan',
+                               'Jacqueline Broerse',
+                               'Elisa Sicuri'),
+                      email = c('joe@databrew.cc',
+                                'm.p.pradhan@vu.nl',
+                                'j.e.w.broerse@vu.nl',
+                                'elisa.sicuri@isglobal.org'),
+                      affilitation = c("isglobal,cism,vu",
+                                       "vu,uva",
+                                       "vu",
+                                       "isglobal,icl,cism"),
+                      footnote = c("Corresponding Author",
+                                   rep('', 3)),
+                      stringsAsFactors = FALSE)
+institutions <- data.frame(code = c('isglobal',
+                                    'icl',
+                                    'cism',
+                                    'vu',
+                                    'uva'),
+                           institution = c('Barcelona Institute for Global Health',
+                                           'Imperial College London',
+                                           'Centro de Investigação em Saúde de Manhiça',
+                                           'VU University Amsterdam',
+                                           'University of Amsterdam'),
+                           address = c('c/ Rosselló, 132, 5è 2a. 08036, Barcelona, Spain',
+                                       'South Kensington Campus, London SW7 2AZ, U.K.',
+                                       'Vila da Manhiça, Bairro Cambeve, Rua 12, Distrito da Manhiça, CP 1929, Maputo, Mozambique',
+                                       'De Boelelaan 1105, 1081 HV Amsterdam, Netherlands',
+                                       'REC E, Roetersstraat 11, Amsterdam, Netherlands'),
+                      stringsAsFactors = FALSE)
+
+make_author <- function(authors,
+                        institutions){
+
+  out <- c()
+  for (i in 1:nrow(authors)){
+    this_author <- authors$name[i]
+    these_institutions <- authors$affilitation[i]
+    these_institutions <- unlist(strsplit(these_institutions, ','))
+    author_text <- paste0(this_author)
+    for (j in 1:length(these_institutions)){
+      this_institution <- these_institutions[j]
+      if(any(grepl(this_institution, out))){
+        author_text <- paste0(author_text,
+                              '\\footrecall{',
+                              this_institution,
+                              '}'
+                              )
+      } else {
+        # new institution, get full name
+        full_name <- institutions$institution[institutions$code == this_institution]
+        address <- institutions$address[institutions$code == this_institution]
+        author_text <- paste0(author_text,
+                              '\\footremember{',
+                              this_institution,
+                              '}{',
+                              full_name,
+                              ': ',
+                              address,
+                              '}')
+      }
+    }
+    out[i] <- author_text
+  }
+  out <- paste0(out, collapse = ', ')
+  cat(out)
+}
+```
+
+\begin{center}
+\begin{large}
+
+```{r, results = 'asis', eval = TRUE}
+make_author(authors = authors,
+            institutions = institutions)
+```
+
+\end{large}
+\end{center}
+
+\vspace{5mm}
+
+\begin{center}
+\textbf{Abstract}  
+\end{center}
+
+\vspace{5mm}
+\begin{center}
+\begin{changemargin}{3cm}{3cm}
+
+Quantifying an event's probability and time frame is essential for calculating its expected value.
+In the case of global malaria eradication, uncertainty regarding feasibility makes it difficult for policymakers and public health practitioners to make fully informed decisions.
+The opportunity cost of investments in eradication-specific interventions can be high, particularly in contexts with other urgent health priorities.
+In a systematic survey of malaria researchers, we query perceptions regarding the likelihood and time frame of eradication, as well as the perceived chief areas needed for improvement in order for eradication to be achieved.
+We assess pessimism/optimism (via the proxy of years-to-eradication), broken down by area of expertise, and adjust for selection bias.
+Our results show a disconnect between optimistic public institutional discourse and pessimistic private opinion, suggesting either (a) the necessity of a realistic accounting of eradication's low short-term likelihood in health planning and financing, or (b) the need for a more compelling case regarding eradication's feasibility to be made to the research community.
+\end{changemargin}
+\end{center}
 
@@
 
-## Data generation
+## Supplementary data generation
 
 The survey was intentionally as short as possible, so as to appeal to time-pressed participants.
-However, supplementary data on researchers' demographics is of value.
+However, supplementary data on researchers is of value for the assessing of selection bias and determinants of perception.
 Accordingly, we estimated the likelihood of a participant being of one of two genders (male or female) based on first name, and the likelihood of a participant being of one of five ethnicities (White, Black, Hispanic, Asian, Other) based on the provided last name.
+For gender estimations we used data from the North Atlantic Population Project, and U.S.
+government [@Lincoln]; for ethnicity, Khanna et al's bayesian prediction algorithm for the estimation of racial categories [@wru2015, @Imai_2016] was employed.
 
 ## Analysis
+
+The searching and retrieval of information from the PubMed database was carried out using the RISmed package [@Kovalchik2015].
 
@@
 Ordinary least squares regression was employed to estimate the effect of area of expertise on the eradication pessimism-optimism (through the proxy of perceived years to eradication).
+De-biasing of sample selection was carried out using Heckman's 2 step approach as implemented by Toomet [@toomet2008].
 
-Content analysis of free text comments was carried out using frequency analyses. Comments were categorized and coded according to (more details needed here).
+Qualitative analysis of free text comments was carried out using thematic content analysis.
 
-All analysis was carried out in R language [@R].
+Quantitative analysis was carried out in R language [@R].
 All analysis code, as well as the code used for the identification and contacting of participants, is publicly available at [https://github.com/joebrew/malaria_survey](https://github.com/joebrew/malaria_survey).
-The searching and retrieval of information from the PubMed database was carried out using the RISmed package [@Kovalchik2015].
-
-The estimation of gender and ethnicity likelihoods for each participant relied on Mullen's implementation of US Social Security Administration names' analysis [@gender2015] and Khanna et al's bayesian prediction algorithm for the estimation of racial categories [@wru2015].
-
-De-biasing of sample selection was carried out using Heckman's 2 step approach as implemented by Toomet [@toomet2008].
 
@@
 A total of `r length(which(df$responded))` researchers participated in the survey from the `r nrow(df)` invitations sent (participation rate of `r round(length(which(df$responded)) / nrow(df) * 100, 2)`%).
-
-## Sample selection
-
-Respondents were qualitatively different from non-respondents.
-Importantly, the average number of total author-specific citations was `r round(mean(df$n_citations_total[df$responded]), digits = 2)` among respondents, but `r round(mean(df$n_citations_total[!df$responded]), digits = 2)` among non-respondents.
-This suggests either a tendency for more senior or more cited researchers to not respond.
-The distribution of author-specific total citations is shown below (a).
-
-```{r}
-g1 <- ggplot(data = df %>%
-         mutate(responded = ifelse(responded, 'Respondents', 'Non-respondents')), 
-       aes(x = n_citations_total)) +
-  geom_density(aes(group = responded,
-                   fill = responded),
-               alpha = 0.6) +
-  scale_x_log10() +
-  theme_publication() +
-  scale_fill_manual(name = '',
-                    values = c('darkorange', 'lightblue')) +
-  labs(x = 'Citations (log scale)',
-       y = 'Density',
-       title = 'Total lifetime citations')
-```
-
-When examining the number of average citations per article, the difference between respondents was slightly less: `r round(median(df$n_citations_total[df$responded]), digits = 2)` among respondents, and `r round(median(df$n_citations_total[!df$responded]), digits = 2)` among non-respondents.
-Again, the distribution is shown below (b).
-
-```{r}
-g2 <- ggplot(data = df %>%
-         mutate(responded = ifelse(responded, 'Respondents', 'Non-respondents')), 
-       aes(x = n_citations_average)) +
-  geom_density(aes(group = responded,
-                   fill = responded),
-               alpha = 0.6,
-               n = 10) +
-  scale_x_log10() +
-  theme_publication() +
-  scale_fill_manual(name = '',
-                    values = c('darkorange', 'lightblue')) +
-  labs(x = 'Citations (log scale)',
-       y = 'Density',
-       title = 'Average citations per article')
-Rmisc::multiplot(g1, g2, cols = 2)
-```
-
-The below table shows the response rate by different demographic groups of interest.
-
-```{r}
-# function to get response rate per categorical variable
-response_rate <- function(variable = 'sex'){
-  df$x <- df[,variable]
-  out <- df %>%
-    group_by(x) %>%
-    summarise(responded = length(which(responded)),
-              n = n()) %>%
-    ungroup %>%
-    mutate(p = responded / n * 100)
-  return(out)
-}
-out_list <- list()
-vars <- c('sex',
-            'ethnicity',
-            'bin_citations')
-for (i in 1:length(vars)){
-  this_var <- vars[i]
-  x <- response_rate(variable = this_var)
-  x$variable <- this_var
-  out_list[[i]] <- x
-}
-out <- bind_rows(out_list) %>%
-  dplyr::select(variable, 
-                x,
-                responded,
-                n, 
-                p) %>%
-  rename(Variable = variable,
-         Characteristic = x,
-         Responded = responded,
-         Invited = n,
-         `Response rate` = p)
-kable(out, format = 'latex', caption = 'Response rate by author characteristics')
-```
-
-The below chart shows response rate by number of citations.
-
-```{r}
-x <- out %>%
-  filter(Variable == 'bin_citations') 
-ggplot(data = x,
-       aes(x = Characteristic,
-           y = `Response rate`)) +
-  geom_bar(stat = 'identity',
-           fill = 'lightblue',
-           alpha = 0.8) +
-  theme_publication() +
-  labs(x = 'Number of total citations',
-       y = 'Response rate',
-       title = 'Response rate by citations') +
-  geom_label(aes(label = paste0(round(`Response rate`, digits = 2), '%')))
-```
-
-## De-biasing of results
-
-```{r, results = 'markup'}
-# stargazer(ols1, heck1, ml1,
-#           header = FALSE,
-#           # se=list(cse(ols1),NULL,NULL),
-#           title="Regression on years until eradication", 
-#           type="text",
-#           df=FALSE, digits=4)
-# # summary(ols1)
-# # summary(heck1)
-
-```
 
@@
 
-```{r}
+```{r, fig.cap='Perceptions of likelihood of eradication', fig.height = 6.2}
 # Define function for analyzing the years_n columns
@@
          y = '%') +
-    theme_publication(base_size = 10) +
+    theme_paper(base_size = 10) +
     theme(axis.text.x = element_text(angle = 90))
@@
 }
-```
 
-```{r, fig.height = 7}
 # Make plots of all
@@
   geom_line(color = 'darkorange') +
-  theme_publication(base_size = 10) +
+  theme_paper(base_size = 10) +
   xlab('Years') +
@@
 Participants were asked to provide the number of years they believe it will take until eradication can be achieved.
-`r length(which(is.na(df$years)))` (`r round(length(which(is.na(df$years))) / nrow(df) * 100, digits = 1)`%) were either blank or uninteligible, whereas `r length(which(!is.na(df$years)))` participants responded.
+`r length(which(is.na(df$years[df$responded])))` (`r round(length(which(is.na(df$years[df$responded]))) / nrow(df) * 100, digits = 1)`%) were either blank or uninteligible, whereas `r length(which(!is.na(df$years)))` participants responded.
 Among respondants, `r length(which(df$years >= 50))` (`r round(length(which(df$years >= 50)) / length(which(!is.na(df$years))) * 100, digits = 1)` %) estimated that it would be 50 or more years until eradication.
-The below histogram shows the distribution of responses, appended at 50.
+The below histogram shows the distribution of responses, truncated at 50.
 
@@
                  alpha = 0.6) +
-  theme_publication(base_size = 10) +
+  theme_paper(base_size = 10) +
   labs(x = 'Years',
@@
 
+## Sample selection
+
+Respondents were qualitatively different from non-respondents.
+Importantly, the average number of total author-specific citations was `r round(mean(df$n_citations_total[df$responded]), digits = 2)` among respondents, but `r round(mean(df$n_citations_total[!df$responded]), digits = 2)` among non-respondents.
+This suggests either a tendency for more senior or more cited researchers not to respond.
+When examining the number of average citations per article, the difference between respondents and non-respondents was slightly less: `r round(median(df$n_citations_total[df$responded]), digits = 2)` among respondents, and `r round(median(df$n_citations_total[!df$responded]), digits = 2)` among non-respondents.
+Males responded at a greater rate (`r round(mean(df$responded[df$sex == 'male'], na.rm = T) * 100, digits = 2)`) than females (`r round(mean(df$responded[df$sex == 'female'], na.rm = T) * 100, digits = 2)`) and those with Hispanic last names responded at a greater rate than those with last names of other ethnicities (see table).
+
+```{r}
+# function to get response rate per categorical variable
+response_rate <- function(variable = 'sex'){
+  df$x <- df[,variable]
+  out <- df %>%
+    group_by(x) %>%
+    summarise(responded = length(which(responded)),
+              n = n()) %>%
+    ungroup %>%
+    mutate(p = responded / n * 100)
+  return(out)
+}
+out_list <- list()
+vars <- c('sex',
+            'ethnicity',
+            'bin_citations')
+for (i in 1:length(vars)){
+  this_var <- vars[i]
+  x <- response_rate(variable = this_var)
+  x$variable <- this_var
+  out_list[[i]] <- x
+}
+out <- bind_rows(out_list) %>%
+  dplyr::select(variable, 
+                x,
+                responded,
+                n, 
+                p) %>%
+  rename(Variable = variable,
+         Characteristic = x,
+         Responded = responded,
+         Invited = n,
+         `Response rate` = p)
+knitr::kable(out, format = 'latex', caption = 'Response rate by author characteristics')
+```
+
+Selection bias is not of concern in the case of differential response if the groups for whom there are differences are not different in terms of the outcome variable.
+This was the case for sex: males responded at a significantly greater rate than females (p < 0.001), but were not statistically significantly different in regards to pessimism/optimism (ie, time frame or likelihood of eradication).
+In the case of researcher impact (as measured by the total number of citations), selection bias plays an important role: being highly-cited was associated both with eradication "pessimism" as well as likelihood of non-response.
+In other words, our pool of respondents was less highly-cited than our pool of invitees, and among respondents, those who were highly-cited tended to be more pessimistic (see below figure).
+
+```{r}
+# df$bin_citations <- factor(df$bin_citations,
+#                            labels = c('0',
+#                                       '1-9',
+#                                       '10-51',
+#                                       '52+'))
+x <- df %>%
+  group_by(citations = bin_citations) %>%
+  summarise(years_10 = mean(years_10_numeric, na.rm = TRUE),
+            years_20 = mean(years_20_numeric, na.rm = TRUE),
+            years_30 = mean(years_30_numeric, na.rm = TRUE),
+            years_40 = mean(years_40_numeric, na.rm = TRUE),
+            years_50 = mean(years_50_numeric, na.rm = TRUE),
+            n = length(unique(email))) %>%
+  ungroup %>%
+  gather(key, value, years_10:years_50) %>%
+  filter(!is.na(citations))
+
+cols <- colorRampPalette(c('red', 'orange', 'blue') #brewer.pal(n = 9, 'Spectral')
+                         )(length(unique(x$citations)))
+ggplot(data = x %>% filter(!is.na(citations)),
+       aes(x = as.numeric(gsub('years_', '', key)),
+           y = value,
+           color = citations,
+           group = citations)) +
+  geom_point(alpha = 0.7) +
+  geom_line(alpha = 0.6) +
+  theme_paper() +
+  scale_color_manual(name = 'Number of citations',
+                     values = cols) +
+  labs(x = 'Years',
+       y = '% likelihood',
+       title = 'Difference in perceived likelihood of eradication by citations',
+       subtitle = 'More citations = more pessimistic')
+```
+
+## De-biasing of results
+
+We used Heckman's 2-step correction method [@Heckman_1979].
+Given that sex affected response rate but not response itself, we were able to use sex as an instrumental variable, introducing it in both the selection and response models.
+Our selection model, which estimated the likelihood of survey response as a probit function of sex allowed us to estimate (via the Inverse Mills ratio) an expected error term for our outcome models, in which we quantify the effect of the number of citations on the perceived average likelihood of eradication at 10, 20, 30, 40, and 50 years.
+The below chart shows the difference in the aggregate perceived likelihood of eradication before and after implementing Heckman's 2-step model.
+
+```{r, results = 'markup'}
+ggplot(data = heckman,
+       aes(x = years,
+           y = value,
+           color = key,
+           lty = key)) +
+  geom_line(alpha = 0.8) +
+  geom_point(alpha = 0.6) +
+  theme_paper() +
+  labs(x = 'Years',
+       y = 'Likelihood of eradication') +
+  scale_linetype_manual(name = '', values = 1:2) +
+  scale_color_manual(name = '', values = c('blue', 'darkorange')) +
+  labs(title = 'Heckman selection adjustment')
+```
+
+The below table shows the Heckman model Heckman model estimates for all five models.
+
+```{r}
+rn <- names(heck_10$coefficients)
+heck <- data_frame(Coefficient = rn,
+                   `Model 10` = heck_10$coefficients,
+                   `Model 20` = heck_20$coefficients,
+                   `Model 30` = heck_30$coefficients,
+                   `Model 40` = heck_40$coefficients,
+                   `Model 50` = heck_50$coefficients)
+knitr::kable(heck)
+```
+
 ## Difference in perceptions by expertise
@@
 Heterogeneity can be partly explained by area of expertise, as evidenced by significant differences in the perceived years to eradication by area of expertise.
+
+```{r, fig.height = 3.5, fig.width = 4}
+areas_df <- areas_df %>% arrange(desc(count))
+small_areas <- areas_df$area[1:12]
+model_formula <- paste0('years ~ ',
+                        paste0(paste0('area_', gsub(' ', '_', small_areas)), collapse = ' + '))
+model_formula <- as.formula(model_formula)
+fit <- lm(model_formula, data = df)
+# Get confidence intervals too
+ci <- tidy(confint(fit))
+x <- cbind(tidy(fit), ci)
+names(x) <- c('term', 'estimate', 'se', 'stat', 'p', 'rownames', 'lwr', 'upr')
+x <- x %>%
+  dplyr::select(term, estimate,
+                p, lwr, upr)
+the_intercept <- x$estimate[1]
+x <- x[-1,]
+for (the_column in c('estimate', 'lwr', 'upr')){
+  x[,the_column] <- x[,the_column] + the_intercept
+}
+x$term <- gsub('area_|TRUE', '', x$term)
+x <- x %>%
+  dplyr::arrange(estimate)
+x$term <- gsub('_', '\n', x$term)
+x$term <- factor(x$term, levels = x$term)
+ggplot(data = x,
+       aes(x = term,
+           y = estimate)) +
+  geom_bar(stat = 'identity',
+           fill = 'darkorange',
+           alpha = 0.6) +
+  geom_errorbar(aes(ymin = lwr,
+                    ymax = upr),
+                alpha = 0.6,
+                width = 0.8,
+                color = 'red') +
+  theme_paper(base_size = 10) +
+  labs(x = 'Area',
+       y = 'Years',
+       title = 'Perceived years to eradication',
+       subtitle = 'By expertise, adjusted for multiple areas of expertise') +
+  theme(axis.text.x = element_text(angle = 90))
+
+```
+
+## Health system building blocks
+
+Finally, researchers were asked to rank the WHO's 6 health system building blocks as needing the most to least attention (6-1 scale) in order for eradication to be achieved.
+Disagreement was high, as evidenced by the variance in responses in the below point and violin chart.
+However, the general tendency was that governance was recognized as the most important area requiring attention, with health information thought to be the area least requiring attention.
+
+```{r}
+bb <- c('governance', 'health_workforce',
+        'health_financing', 'health_technologies',
+        'health_information', 'service_delivery')
+results_list <- list()
+for (i in 1:length(bb)){
+  this_df <- data.frame(bb = bb[i],
+                        ranking = as.numeric(df[,bb[i]]))
+  results_list[[i]] <- this_df
+}
+results <- bind_rows(results_list)
+results$bb <- gsub('_', '\n', results$bb)
+
+results_agg <-
+  results %>%
+  dplyr::group_by(bb) %>%
+  dplyr::summarise(avg = mean(ranking, na.rm = TRUE)) %>%
+  arrange(avg)
+results_agg$bb <- factor(results_agg$bb,
+                         levels = results_agg$bb)
+results$bb <- factor(results$bb, 
+                     levels = levels(results_agg$bb))
+
+library(ggridges)
+ggplot(data = results %>% filter(!is.na(ranking)),
+       aes(x = ranking,
+           y = bb,
+           fill = bb)) +
+  geom_density_ridges(#fill = 'darkorange',
+                      alpha = 0.6,
+                      scale = 1.5) +
+  theme_paper() +
+  xlim(0,30) +
+  labs(x = 'Perceived importance',
+       y = 'WHO Building Block') +
+ scale_fill_cyclical(values = c("darkorange", "yellow"))
+
+# ggplot(data = results) + 
+#   geom_violin(aes(x = bb,
+#            y = ranking),
+#            fill = 'orange',
+#               alpha = 0.6) +
+#   geom_jitter(aes(x = bb,
+#            y = ranking),
+#            color = 'black',
+#            with = 0.4,
+#            height = 0.4,
+#               alpha = 0.3,
+#               size = 1) +
+#   theme_paper(base_size = 10) +
+#   labs(x = 'WHO Building block',
+#        y = 'Ranking',
+#        title = 'Perceived areas needing attention',
+#        subtitle = 'Small points: jittered individual responses; large triangles: averages') +
+#   geom_point(data = results_agg,
+#              aes(x = bb,
+#                  y = avg),
+#              size = 5,
+#              pch = 17,
+#              color = 'black',
+#              alpha = 0.8) +
+#   ylim(0, 6)
+```
+
+## Qualitative analysis of results
+
+Participants were invited to provide "any general comments on the timeline and likelihood of global eradication".
+Of the `r length(which(df$responded))` who responded to the survey, `r length(which(!is.na(df$comments)))` (`r round(length(which(!is.na(df$comments))) / length(which(df$responded)) * 100, digits = 2)`%) provided a comment.
+Thematic content analysis [@Vaismoradi_2016] was employed to code responses into four subject themes as well as binary categorization of descriptive vs.
+presciptive.
+
+The four subject themes, identified and refined through iterative analysis, were:
+
+1. Innovation
+2. Systematic challenges  
+3. Poverty
+4. Meta: challenging the question, re-framing the goal, insisting on other priorities, etc.
+
+# Discussion
+
+## General pessimism
+
+Our study reveals a striking gap between the public discourse on malaria eradication, and those views held (largely privately) by malaria researchers.
+Approximately three-quarters of respondents believe that malaria will not be eradicated in the next 50 years; in other words, assuming our pool of respondents is of typical post-PhD age, most believe they will not live to see eradication.
+
+If we take the pooled opinions of researchers, as revealed through this survey, as the best approximation of truth available, then the disconnect between public discourse on malaria eradication and private opinion is troubling.
+It suggests that the goals set by the Bill and Melinda Gates Foundation (eradication "within a generation") and the WHO GMP (eradication "within the lifetime of young scientists just embarking on their careers") are unrealistic at best, and misleading at worst.
+This has important implications for spending in public health, since the attention and resources of funders, researchers and government agencies are directed to those areas where a result is expected.
+
+On the other hand, there are many reasons to be skeptical that the combined "wisdom of crowds" of malaria researchers is a reliable indicator of truth.
+First, academic researchers are specialists - their narrow, field-specific view of eradication's feasibility is arguably less reliable than the more "global" views of the WHO, or Bill Gates.
+Second, a number of biases may come in to play in this study.
+
+Among these biases, 4 are worth mentioning specifically.
+(1) "Conjunction fallacy" suggests that the general goal of eradication may seem less likely than the sum of the goals of country-specific elimination.
+(2) A (reverse) variant of the "hot hand fallacy", in which researchers may mistakenly base their assessment of current chances of eradication on previous failures.
+(3) Parkinson's law of triviality suggests that researchers may disproportionately see the challenges of their own research (antimalarial drug resistance, etc.) as larger or more relevant to the global eradication campaign than they really are.
+(4) Finally, and ironically, "optimism bias" may play a perverse role in researchers' responses; though eradication is certainly a goal desired by all, one could argue that malaria research specialists subconciously realize that they actually stand to lose out profesionally in the case of eradication.
+
+Whether the collective "wisdom" of researchers is worth adhering to or not is arguable.
+That said, to the extent that researchers' private opinions differ so greatly from those of global health leaders is itself a noteworthy result.
+If leaders' high levels of optimism are well-placed, this suggests that researchers are unduly pessimistic, and efforts should be made to convince them that eradication is more feasible than they realize.
+If, on the other hand, collective wisdom is a better forecasting agent than the proclamations and objectives of global health leaders, then it is important to recognize the sad truth that we are likely further from eradication than we would like to be.
+In this case, though the discourse on eradication can be motivating and inspiring, resources should be directed in a manner that reflects an intended outcome's likelihood of occurrence.
+
+## Discord over building blocks to eradication
+
+It is noteworthy that there was so much discord among researchers in regards to which WHO building blocks required the most attention in order for eradication to be achieved.
+All six possible categories received votes for both the lowest and highest levels of importance, as well as every level in between.
+And the difference between "health information" (the building block deemed as least important) and "governance" (the most important) was less than 0.5 on a 1-6 scale.
+
+This discord suggests that the path to implementing strategies for eradication is not clear, at least from the perspective of this study's participants.
+This could mean that further work is needed in order to prioritize which areas require the most investment and attention in order for eradication to occur.
+On the other hand, one could interpret this result as reflecting the fact that previous work on priorities (ie, MalERA) has not been fully accessed or understood by the larger malaria research community.
+
+## Few differences by area of expertise
+
+It is noteworthy that among the most "optimistic" experts were from the field of bioinformatics.
+This could be explained by the fact that, relative to other more "traditional" areas of science, informatics regularly sees paradigm shifts, and changes in technology and breakthroughs occur at a more rapid rate.
+That said, the high degree of optimism among chemists would seem to contradict this hypothesis.
+At any rate...
+(more details will go here).
+
+## Limitations
+
+In addition to the biases mentioned above, this study has many limitations.
+First, though results are not disclosed at the individual level, this survey was not entirely anonymous, suggesting that social desirability bias may have influenced responses, and that selection bias likely meant our pool of participants were substantially different from those who choose not to participate.
+
+Second, we made no distinguishment between quality of research, years of experience, academic achievements, geographical area, etc.
+Our inclusion criteria were simple and rudimentary, allowing us to access many diverse viewpoints, but (perhaps inappropriately) weighting all viewpoints as equal.
+
+Third, this study included the corresponding authors of indexed journals.
+Though certainly a group with important knowledge related to malaria, this misses malaria control program employees, health agency workers, and other stakeholders.
+Their experiences and viewpoints are most likely vastly different from those of academecians.
+
+## Implications
+
+Our survey attempted to quantify the likelihood of and time frame to malaria eradication by gauging the collective opinion of malaria researchers.
+Our results suggest that eradication is unlikely in the short and medium terms, and that there exists a great deal of disagreement among researchers in regards to which areas require the most attention in order for eradication to occur.
+The implication of these results are three-fold: (1) that those working or investing in eradication-specific campaigns should factor in the low likelihood and long time frame when calculating those campaigns' expected value; (2) that champions of near-term eradication need to make a more compelling case to malaria researchers of eradication's feasibility, in order to better focus and inspire the latter; and (3) that discord among malaria researchers as to which areas need the most attention in order for eradication to occur suggests a need for open discussion and concensus-making, so that resources and focus are directed appropriately.
+
+References {#references .unnumbered}
+==========
+
+# Appendix
+
+The distribution of author-specific total citations is shown below (a).
+
+```{r}
+g1 <- ggplot(data = df %>%
+         mutate(responded = ifelse(responded, 'Respondents', 'Non-respondents')), 
+       aes(x = n_citations_total)) +
+  geom_density(aes(group = responded,
+                   fill = responded),
+               alpha = 0.6) +
+  scale_x_log10() +
+  theme_paper() +
+  scale_fill_manual(name = '',
+                    values = c('darkorange', 'lightblue')) +
+  labs(x = 'Citations (log scale)',
+       y = 'Density',
+       title = 'Total lifetime citations')
+```
+
+Again, the distribution is shown below (b).
+
+```{r}
+g2 <- ggplot(data = df %>%
+         mutate(responded = ifelse(responded, 'Respondents', 'Non-respondents')), 
+       aes(x = n_citations_average)) +
+  geom_density(aes(group = responded,
+                   fill = responded),
+               alpha = 0.6,
+               n = 10) +
+  scale_x_log10() +
+  theme_paper() +
+  scale_fill_manual(name = '',
+                    values = c('darkorange', 'lightblue')) +
+  labs(x = 'Citations (log scale)',
+       y = 'Density',
+       title = 'Average citations per article')
+# Rmisc::multiplot(g1, g2, cols = 2)
+g1
+g2
+```
 
@@
                alpha = 0.6) +
-  theme_publication(base_size = 10) +
+  theme_paper(base_size = 10) +
   labs(x = 'Years',
@@
   facet_wrap(~the_area) 
-```
-
-```{r, fig.height = 3.5, fig.width = 4}
-model_formula <- paste0('years ~ ',
-                        paste0(paste0('area_', gsub(' ', '_', small_areas)), collapse = ' + '))
-model_formula <- as.formula(model_formula)
-fit <- lm(model_formula, data = df)
-# Get confidence intervals too
-ci <- tidy(confint(fit))
-x <- cbind(tidy(fit), ci)
-names(x) <- c('term', 'estimate', 'se', 'stat', 'p', 'rownames', 'lwr', 'upr')
-x <- x %>%
-  dplyr::select(term, estimate,
-                p, lwr, upr)
-the_intercept <- x$estimate[1]
-x <- x[-1,]
-for (the_column in c('estimate', 'lwr', 'upr')){
-  x[,the_column] <- x[,the_column] + the_intercept
-}
-x$term <- gsub('area_|TRUE', '', x$term)
-x <- x %>%
-  dplyr::arrange(estimate)
-x$term <- gsub('_', '\n', x$term)
-x$term <- factor(x$term, levels = x$term)
-ggplot(data = x,
-       aes(x = term,
-           y = estimate)) +
-  geom_bar(stat = 'identity',
-           fill = 'darkorange',
-           alpha = 0.6) +
-  geom_errorbar(aes(ymin = lwr,
-                    ymax = upr),
-                alpha = 0.6,
-                width = 0.8) +
-  theme_publication(base_size = 10) +
-  labs(x = 'Area',
-       y = 'Years',
-       title = 'Perceived years to eradication',
-       subtitle = 'By expertise, adjusted for multiple areas of expertise') +
-  theme(axis.text.x = element_text(angle = 90))
-
 ```
@@
            lty = area)) +
-  theme_publication(base_size = 10) +
+  theme_paper(base_size = 10) +
   scale_color_manual(name = '',
@@
 
-## Sentiment analysis of free-text commentary
-
-This section is unfinished.
-Below is the distribution of "sentiment" among the responses (0 is neutral, below 0 is negative, above 0 is positive), but this is preliminary.
-The chart is colored by ethnicity, and faceted by gender.
-
 ```{r}
@@
                n = 10) +
-  theme_publication() +
+  theme_paper() +
   facet_wrap(~gender)
@@
 ```
-
-## Health system building blocks
-
-Finally, researchers were asked to rank the WHO's 6 health system building blocks as needing the most to least attention (6-1 scale) in order for eradication to be achieved.
-Disagreement was high, as evidenced by the variance in responses in the below point and violin chart.
-However, the general tendency was that governance was recognized as the most important area requiring attention, with health information thought to be the area least requiring attention.
-
-```{r}
-bb <- c('governance', 'health_workforce',
-        'health_financing', 'health_technologies',
-        'health_information', 'service_delivery')
-results_list <- list()
-for (i in 1:length(bb)){
-  this_df <- data.frame(bb = bb[i],
-                        ranking = as.numeric(df[,bb[i]]))
-  results_list[[i]] <- this_df
-}
-results <- bind_rows(results_list)
-results$bb <- gsub('_', '\n', results$bb)
-
-results_agg <-
-  results %>%
-  dplyr::group_by(bb) %>%
-  dplyr::summarise(avg = mean(ranking, na.rm = TRUE)) %>%
-  arrange(avg)
-results_agg$bb <- factor(results_agg$bb,
-                         levels = results_agg$bb)
-results$bb <- factor(results$bb, 
-                     levels = levels(results_agg$bb))
-
-ggplot(data = results) + 
-  geom_violin(aes(x = bb,
-           y = ranking),
-           fill = 'orange',
-              alpha = 0.6) +
-  geom_jitter(aes(x = bb,
-           y = ranking),
-           color = 'black',
-           with = 0.4,
-           height = 0.4,
-              alpha = 0.3,
-              size = 1) +
-  theme_publication(base_size = 10) +
-  labs(x = 'WHO Building block',
-       y = 'Ranking',
-       title = 'Perceived areas needing attention',
-       subtitle = 'Small points: jittered individual responses; large triangles: averages') +
-  geom_point(data = results_agg,
-             aes(x = bb,
-                 y = avg),
-             size = 5,
-             pch = 17,
-             color = 'black',
-             alpha = 0.8) +
-  ylim(0, 6)
-ggsave('~/Desktop/figure2.png', height = 4, width = 5.5)
-```
-
-## Qualitative analysis of results
-
-Participants were invited to provide "any general comments on the timeline and likelihood of global eradication".
-Of the `r length(which(df$responded))` who responded to the survey, `r length(which(!is.na(df$comments)))` (`r round(length(which(!is.na(df$comments))) / length(which(df$responded)) * 100, digits = 2)`%) provided a comment.
-
-# Discussion
-
-## Collective pessimism
-
-Our study reveals a striking gap between the public discourse on malaria eradication, and those views held (largely privately) by malaria researchers.
-Approximately three-quarters of respondents believe that malaria will not be eradicated in the next 50 years; in other words, assuming our pool of respondents is of typical post-PhD age, most believe they will not live to see eradication.
-
-If we take the pooled opinions of researchers, as revealed through this survey, as the best approximation of truth available, then the disconnect between public discourse on malaria eradication and private opinion is troubling.
-It suggests that the goals set by the Bill and Melinda Gates Foundation (eradication "within a generation") and the WHO GMP (eradication "within the lifetime of young scientists just embarking on their careers") are unrealistic at best, and misleading at worst.
-This has important implications for spending in public health, since the attention and resources of funders, researchers and government agencies are directed to those areas where a result is expected.
-
-On the other hand, there are many reasons to be skeptical that the combined "wisdom of crowds" of malaria researchers is a reliable indicator of truth.
-First, academic researchers are specialists - their narrow, field-specific view of eradication's feasibility is arguably less reliable than the more "global" views of the WHO, or Bill Gates.
-Second, a number of biases may come in to play in this study.
-
-Among these biases, 4 are worth mentioning specifically.
-(1) "Conjunction fallacy" suggests that the general goal of eradication may seem less likely than the sum of the goals of country-specific elimination.
-(2) A (reverse) variant of the "hot hand fallacy", in which researchers may mistakenly base their assessment of current chances of eradication on previous failures.
-(3) Parkinson's law of triviality suggests that researchers may disproportionately see the challenges of their own research (antimalarial drug resistance, etc.) as larger or more relevant to the global eradication campaign than they really are.
-(4) Finally, and ironically, "optimism bias" may play a perverse role in researchers' responses; though eradication is certainly a goal desired by all, one could argue that malaria research specialists subconciously realize that they actually stand to lose out profesionally in the case of eradication.
-
-Whether the collective "wisdom" of researchers is worth adhering to or not is arguable.
-That said, to the extent that researchers' private opinions differ so greatly from those of global health leaders is itself a noteworthy result.
-If leaders' high levels of optimism are well-placed, this suggests that researchers are unduly pessimistic, and efforts should be made to convince them that eradication is more feasible than they realize.
-If, on the other hand, collective wisdom is a better forecasting agent than the proclamations and objectives of global health leaders, then it is important to recognize the sad truth that we are likely further from eradication than we would like to be.
-In this case, though the discourse on eradication can be motivating and inspiring, resources should be directed in a manner that reflects an intended outcome's likelihood of occurrence.
-
-## Building blocks to eradication
-
-It is noteworthy that there was so much discord among researchers in regards to which WHO building blocks required the most attention in order for eradication to be achieved.
-All six possible categories received votes for both the lowest and highest levels of importance, as well as every level in between.
-And the difference between "health information" (the building block deemed as least important) and "governance" (the most important) was less than 0.5 on a 1-6 scale.
-
-This discord suggests that the path to implementing strategies for eradication is not clear, at least from the perspective of this study's participants.
-This could mean that further work is needed in order to prioritize which areas require the most investment and attention in order for eradication to occur.
-On the other hand, one could interpret this result as reflecting the fact that previous work on priorities (ie, MalERA) has not been fully accessed or understood by the larger malaria research community.
-
-## Areas of expertise
-
-It is noteworthy that among the most "optimistic" experts were from the field of bioinformatics.
-This could be explained by the fact that, relative to other more "traditional" areas of science, informatics regularly sees paradigm shifts, and changes in technology and breakthroughs occur at a more rapid rate.
-That said, the high degree of optimism among chemists would seem to contradict this hypothesis.
-At any rate...
-(more details will go here).
-
-## Limitations
-
-In addition to the biases mentioned above, this study has many limitations.
-First, though results are not disclosed at the individual level, this survey was not entirely anonymous, suggesting that social desirability bias may have influenced responses, and that selection bias likely meant our pool of participants were substantially different from those who choose not to participate.
-
-Second, we made no distinguishment between quality of research, years of experience, academic achievements, geographical area, etc.
-Our inclusion criteria were simple and rudimentary, allowing us to access many diverse viewpoints, but (perhaps inappropriately) weighting all viewpoints as equal.
-
-Third, this study included the corresponding authors of indexed journals.
-Though certainly a group with important knowledge related to malaria, this misses malaria control program employees, health agency workers, and other stakeholders.
-Their experiences and viewpoints are most likely vastly different from those of academecians.
-
-## Implications
-
-Our survey attempted to quantify the likelihood of and time frame to malaria eradication by gauging the collective opinion of malaria researchers.
-Our results suggest that eradication is unlikely in the short and medium terms, and that there exists a great deal of disagreement among researchers in regards to which areas require the most attention in order for eradication to occur.
-The implication of these results are three-fold: (1) that those working or investing in eradication-specific campaigns should factor in the low likelihood and long time frame when calculating those campaigns' expected value; (2) that champions of near-term eradication need to make a more compelling case to malaria researchers of eradication's feasibility, in order to better focus and inspire the latter; and (3) that discord among malaria researchers as to which areas need the most attention in order for eradication to occur suggests a need for open discussion and concensus-making, so that resources and focus are directed appropriately.
-
-References {#references .unnumbered}
-==========

### 2017-10-12 prepare_data.R

@@ -1,3 +1,4 @@
+get_new_data <- FALSE
 library(dplyr)
 library(ggplot2)
 library(tidyr)
@@ -14,574 +15,577 @@ library(sampleSelection)
 library(stargazer)
 library(nnet)
 
-# Get publication theme for charts
-source('theme_publication.R')
-
-# Send emails
-source('code/recruit.R', chdir = TRUE)
-
-# Get number of citations of each article (sept 2017)
-citations_df <- data_frame(id = as.character(sort(unique(final_authors$id))),
-                           n_citations = NA)
-if(!'citations.RData' %in% dir('data')){
-  for (i in 1:nrow(citations_df)){
-    message(paste0(i, ' of ', nrow(citations_df)))
-    try({
-      res <- EUtilsSummary(paste0(citations_df$id[i],
-                                  '[uid]'))
-      citations_df$n_citations[i] <- Cited(res)
-    })
+if('prepared_data.RData' %in% dir()){
+  load('prepared_data.RData')
+} else {
+  
+  # Send emails
+  source('code/recruit.R', chdir = TRUE)
+  
+  # Get number of citations of each article (sept 2017)
+  citations_df <- data_frame(id = as.character(sort(unique(final_authors$id))),
+                             n_citations = NA)
+  if(!'citations.RData' %in% dir('data')){
+    for (i in 1:nrow(citations_df)){
+      message(paste0(i, ' of ', nrow(citations_df)))
+      try({
+        res <- EUtilsSummary(paste0(citations_df$id[i],
+                                    '[uid]'))
+        citations_df$n_citations[i] <- Cited(res)
+      })
+    }
+    
+    citations_df <- 
+      citations_df %>%
+      arrange(desc(n_citations))
+    save(citations_df, 
+         file = 'data/citations.RData')
+  } else {
+    load('data/citations.RData')
   }
   
-  citations_df <- 
-    citations_df %>%
-    arrange(desc(n_citations))
-  save(citations_df, 
-       file = 'data/citations.RData')
-} else {
-  load('data/citations.RData')
-}
-
-
-# Get average and total number of citations per author
-citations_metrics <-
-  final_authors %>%
-  left_join(citations_df) %>%
-  group_by(author) %>%
-  summarise(n_citations_total = sum(n_citations, na.rm = TRUE),
-            n_citations_average = mean(n_citations, na.rm = TRUE))
-
-# Join that data to our author data
-final_authors_aggregated <-
-  left_join(final_authors_aggregated,
[…]

### 2017-10-12 theme_publication.R

@@ -1,6 +1,6 @@
 # https://rpubs.com/Koundy/71792
 
-theme_publication <- function(base_size=14) {
+theme_publication <- function(base_size=9) {
   library(grid)
   library(ggthemes)
   (theme_foundation(base_size=base_size)
@@ -76,11 +76,11 @@ theme_black = function(base_size = 12, base_family = "") {
       # Specify panel options
       panel.background = element_rect(fill = "black", color  =  NA),  
       panel.border = element_rect(fill = NA, color = "white"),  
-      panel.grid.major = element_line(color = "grey35"),  
-      panel.grid.minor = element_line(color = "grey20"),  
+      panel.grid.major = element_line(color = "black"),  
+      panel.grid.minor = element_line(color = "black"),  
       panel.margin = unit(0.5, "lines"),   
       # Specify facetting options
-      strip.background = element_rect(fill = "grey30", color = "grey10"),  
+      strip.background = element_rect(fill = "black", color = "black"),  
       strip.text.x = element_text(size = base_size*0.8, color = "white"),  
       strip.text.y = element_text(size = base_size*0.8, color = "white",angle = -90),  
       # Specify plot options

### 2017-10-12 paper.Rmd
update

@@
 temp$Area <- Hmisc::capitalize(temp$Area)
-kable(temp[1:10,], format = "latex", caption = 'Top 10 areas') %>%
-  kableExtra::kable_styling(#position = "float_right",
-                            font_size = 7)
+kable(temp[1:10,], #format = "latex", 
+      caption = 'Top 10 areas') #%>%
+  # kableExtra::kable_styling(#position = "float_right",
+  #                           font_size = 7)
 ```
@@
          `Response rate` = p)
-knitr::kable(out, format = 'latex', caption = 'Response rate by author characteristics')
+knitr::kable(out, 
+             # format = 'latex', 
+             caption = 'Response rate by author characteristics')
 ```
@@
 Of the `r length(which(df$responded))` who responded to the survey, `r length(which(!is.na(df$comments)))` (`r round(length(which(!is.na(df$comments))) / length(which(df$responded)) * 100, digits = 2)`%) provided a comment.
-Thematic content analysis [@Vaismoradi_2016] was employed to code responses into four subject themes as well as binary categorization of descriptive vs.
+Thematic content analysis [@Vaismoradi_2016] was employed to code responses into four subject themes as well as the binary categorization of descriptive vs.
 presciptive.
@@
 
-1. Innovation
-2. Systematic challenges  
-3. Poverty
-4. Meta: challenging the question, re-framing the goal, insisting on other priorities, etc.
+1. Innovation: comments pertaining to new tools, drugs, methods, or strategies required to achieve eradication.
+2. Systematic challenges: comments pertaining to political, social, environmental or logistical issues related to eradication.  
+3. Poverty: comments specifically related to the economic and socieconomic components of malaria eradication.
+4. Meta: challenging the question of eradication itself, re-framing the goal, insisting on other priorities, etc.
+
+In regards to **innovation**, comments largely pertained to the necessity of further technological advances.
+One participant wrote that "currently available technology can't achieve [eradication], even if delivered optimally"; another argued that eradication could not be achieved without a "game-changing innovation", whereas two others referred to the need for "transformative" technologies.
+Many noted the need to "overcome the challenge of drug resistance" and develop better vaccines.
+Genetic engineering was mentioned by several commenters.
+Most comments coded as "innovatation" were presciptive in nature, often suggesting the nature of the needed innovation, with a heavy slant towards pharmaceutical options and vaccination.
+
+**Systematic challenges** to malaria eradication were noted by the majority of commenters.
+In direct contrast to the previous comments, one participant stated that "we already have the tools to achieve  eradication" and that the only piece lacking was "robust health systems".
+Others echoed the sentiment, with many comments focusing on the need of strong surveillance and treatment delivery systems.
+Many commenters focused on the reasons for stagnating progress, such as "weak or failing health systems...due to political unwillingness or conflict".
+Others highlighted the inherent challenges in the epidemiology of malaria, such as the changing dynamics of malaria transmission, the resilience of the parasite and vector, climate change, and the inability to aim interventions accurately with an "ever-moving target".
+Comments coded as "systematic" tended to be descriptive and slightly more pessimistic than others.
+
+**Poverty** was assigned its own category in the codification of free text responses because of its ubiquity as a theme in comments.
+Many noted that malaria is a "disease of poverty", with "social injustice" as the root cause.
+Some made the sequential argument that "eradication of poverty" must preceed disease eradication.
+Along the same lines, one commenter said that eradication requires "a full systems-wide approach, not a disease-specific approach.
+The eradication of smallpox was a triumph of management, not medicine or technology." Another noted that the survey "left off the list the most important factor - economic development".
+Many echoed the sentiment, stating that "with no economic development, you cannot have eradication" and that poverty is the "cause" of malaria.
+As with the "systematic challenges" of eradication, comments which were coded as poverty tended to be descriptive rather than prescriptive.
+
+**Meta** arguments were rarer than the other categories, but cohesive and consistent.
+One commenter wrote that eradication is a "postwar" idea that developed from the "abandonment of a broad sociopolitical understanding of the causes of disease, and the emphasis on technological solutions." Many stated that global malaria eradication was simply not possible, and 2 argued that it may not be desirable or ethical.
+One stated that the concept was "absurd" and that "I'm not even sure why people talk about it".
+Several pointed to the failure of the WHO GMP in the 1950s as evidence of the futile nature of eradication programs.
+Many highlighted that talking about "malaria" as one disease misses the mark, since the different species of parasite and contexts in which they live make elimination in each area very distinct from other areas.
+"Meta" comments tended to be skeptical of the feasibility of eradication, or to challenge the  notion that it is a meaningful or useful endeavor.
+Largely, they were prescriptive, advocating for a re-framing of the conversation so that the focus was not on an "arbitrary" goal like eradication, but rather on scaling up control and making region-specific progress.
 
@@
 ==========
-
-# Appendix
-
-The distribution of author-specific total citations is shown below (a).
-
-```{r}
-g1 <- ggplot(data = df %>%
-         mutate(responded = ifelse(responded, 'Respondents', 'Non-respondents')), 
-       aes(x = n_citations_total)) +
-  geom_density(aes(group = responded,
-                   fill = responded),
-               alpha = 0.6) +
-  scale_x_log10() +
-  theme_paper() +
-  scale_fill_manual(name = '',
-                    values = c('darkorange', 'lightblue')) +
-  labs(x = 'Citations (log scale)',
-       y = 'Density',
-       title = 'Total lifetime citations')
-```
-
-Again, the distribution is shown below (b).
-
-```{r}
-g2 <- ggplot(data = df %>%
-         mutate(responded = ifelse(responded, 'Respondents', 'Non-respondents')), 
-       aes(x = n_citations_average)) +
-  geom_density(aes(group = responded,
-                   fill = responded),
-               alpha = 0.6,
-               n = 10) +
-  scale_x_log10() +
-  theme_paper() +
-  scale_fill_manual(name = '',
-                    values = c('darkorange', 'lightblue')) +
-  labs(x = 'Citations (log scale)',
-       y = 'Density',
-       title = 'Average citations per article')
-# Rmisc::multiplot(g1, g2, cols = 2)
-g1
-g2
-```
-
-```{r, fig.height = 4.5, fig.width = 4.5}
-# Get averages per area
-results_list <- list()
-dist_list <- list()
-year_list <- list()
-areas_df <- areas_df %>% arrange(desc(count))
-small_areas <- areas_df$area[1:12]
-for (i in 1:length(small_areas)){
-  this_area <- small_areas[i]
-  sub_data <- df[df[,paste0('area_', gsub(' ', '_', this_area))],]
-  this_df <- data_frame(area = this_area,
-                        avg = mean(sub_data$years, na.rm = TRUE),
-                        med = median(sub_data$years, na.rm = TRUE))
-  dist_df <- data_frame(area = this_area,
-                        val = sub_data$years)
-  numberfy <- function(x){
-    ifelse(x == '0%', 0,
-                ifelse(x == '1-20%', 10,
-                       ifelse(x == '21-40%', 30,
-                              ifelse(x == '41-60%', 50,
-                                     ifelse(x == '61-80%', 70,
-                                            ifelse(x == '81-99%', 90,
-                                                   ifelse(x == '100%', 100, NA)))))))
-
-  }
-  year_df <- data.frame(area = this_area,
-                        year = seq(10, 50, 10),
-                        val = c(mean(numberfy(sub_data$years_10), na.rm = TRUE),
-                                mean(numberfy(sub_data$years_20), na.rm = TRUE),
-                                mean(numberfy(sub_data$years_30), na.rm = TRUE),
-                                mean(numberfy(sub_data$years_40), na.rm = TRUE),
-                                mean(numberfy(sub_data$years_50), na.rm = TRUE)))
-  for (q in seq(0, 100, 10)){
-    this_df[,paste0('q_', q)] <- 
-      quantile(sub_data$years, q / 100, na.rm = TRUE)
-  }
-  results_list[[i]] <- this_df
-  dist_list[[i]] <- dist_df
-  year_list[[i]] <- year_df
-}
-results <- bind_rows(results_list)
-dist_results <- bind_rows(dist_list)
-year_results <- bind_rows(year_list)
-dist_results$the_area <- dist_results$area
-
-ggplot(data = dist_results,
-       aes(#group = area,
-           #fill = area,
-           x = val)) +
-  geom_density(fill = 'darkorange',
-               alpha = 0.6) +
-  theme_paper(base_size = 10) +
-  labs(x = 'Years',
-       y = 'Density',
-       title = 'Perceived years to eradication',
-       subtitle = '12 most popular areas of expertise only') +
-  facet_wrap(~the_area) 
-```
-
-Heterogeneity by area of expertise is also apparent in perceived likelihood of eradication over the pre-defined five time-points, as seen below.
-
-```{r, fig.height = 4, fig.width = 4.5}
-cols <- colorRampPalette(brewer.pal(9, 'Spectral'))(length(unique(year_results$area)))
-ggplot(data = year_results,
-       aes(x = year,
-           y = val)) +
-  geom_line(aes(group = area,
-           color = area,
-           lty = area)) +
-  theme_paper(base_size = 10) +
-  scale_color_manual(name = '',
-                     values = cols,
-                     labels = unique(year_results$area)) +
-  scale_linetype_manual(name="", 
-                        values = rep(1:6, 100)[1:length(unique(year_results$area))],
-                     labels = unique(year_results$area)) +
-  xlab('Years until eradication') +
-  ylab('Likelihood') +
-  ggtitle('Likelihood trajectories',
-          'By area of expertise')
-```
-
-```{r}
-ggplot(data = df %>%
-         filter(responded) %>%
-         # mutate(n_areas = factor(n_areas)) %>%
-         filter(!is.na(ethnicity),
-                !is.na(gender)),
-       aes(x = sentiment,
-           group = ethnicity)) +
-  geom_density(aes(fill = ethnicity),
-               alpha = 0.6,
-               n = 10) +
-  theme_paper() +
-  facet_wrap(~gender)
-
-```

### 2017-10-12 shiny/global.R
shiny update

@@ -62,6 +62,17 @@ df <- gs_read_csv(sheet)
 names(df) <- c('timestamp', 'years', 'sex',
                'height', 'sleep', 'age')
 
+df$date <- as.Date(substr(df$timestamp, 1, 10), format = '%m/%d/%Y')
+if(max(df$date, na.rm = TRUE) == '2017-10-05'){
+  fake_data <- TRUE
+} else {
+  fake_data <- FALSE
+}
+
+if(!fake_data){
+  df <- df %>% filter(date > '2017-10-05')
+}
+
 # Make sure variables are classified as needed
 make_numeric <- function(x){as.numeric(as.character(x))}
 df <- 

### 2017-10-12 shiny/server.R

@@ -1,11 +1,3 @@
-#
-# This is the server logic of a Shiny web application. You can run the 
-# application by clicking 'Run App' above.
-#
-# Find out more about building applications with Shiny here:
-# 
-#    http://shiny.rstudio.com/
-#
 
 library(shiny)
 library(googlesheets)
@@ -15,7 +7,14 @@ library(dplyr)
 # Define server logic required to draw a histogram
 shinyServer(function(input, output) {
    
-  
+  output$t1 <- renderText({
+    if(fake_data){
+      return('Using fake data')
+    } else {
+      collect_date <- max(df$date, na.rm = TRUE)
+      return(paste0('Using data collected through ', dplyr::last(df$timestamp)))
+    }
+  })
   
   output$p1 <- renderPlot({
     plot_variable(input$variable)

### 2017-10-12 shiny/ui.R

@@ -18,7 +18,8 @@ dashboardPage(
       box(plotOutput("p2", height = 250)),
       valueBoxOutput('v1'),
       valueBoxOutput('v2'),
-      valueBoxOutput('v3')
+      valueBoxOutput('v3'),
+      textOutput('t1')
     )
   )
 )

### 2017-10-17 paper.Rmd
paper update

@@
 In recent years, much of the discourse regarding malaria has shifted back to global eradication [@Roberts2007], with funders, researchers, and public health practitioners rallying to the cause [@Tanner2015].
-The Bill and Melinda Gates Foundation has begun actively promoting eradication as feasible "within a generation" [@Gates2014], and the leadership of the World Health Organization (WHO) has supported this goal.
+The Bill and Melinda Gates Foundation has begun actively promoting eradication as feasible "within a generation" [@Gates2014], and the leadership of the World Health Organization (WHO) has supported this goal, stating the objective of eliminating malaria in 65 new countries from 2015 through 2030 (see below).
+
+```{r}
+# Read WHO data (compiled manually from WHO website)
+who <- readr::read_csv('who_elimination_data.csv')
+who$year <- as.numeric(substr(who$year, 6, 9))
+projection <- data.frame(year = seq(2030.2, 2035, length = 20),
+                         countries = seq(33, 0, length = 20))
+g <- ggplot(data = who %>% mutate(past = ifelse(past, 'Historical',
+                                           'WHO objective')) %>%
+         filter(!is.na(with_malaria)) ,
+       aes(x = year,
+           y = with_malaria,
+           color = past)) +
+  geom_line() +
+  geom_point() +
+  theme_paper() +
+  labs(x = '',
+       y = 'Countries',
+       title = 'Countries with malaria: Observed and WHO objectives',
+       subtitle = 'Data from http://www.who.int/malaria/areas/elimination/overview/en/') +
+  scale_color_manual(name = '',
+                     values = c('darkorange', 'blue')) +
+  ylim(0, 130) +
+  theme(axis.text.x = element_text(angle = 90)) +
+  geom_line(data = projection,
+            aes(x = year,
+                y = countries,
+                color = NA,
+                group = NA),
+            color = 'black',
+            lty = 2) +
+  geom_hline(yintercept = 0, col = 'red')
+g
+# #Make animation for presentation
+# make_animation <- function(){
+#   g <- 
+#     ggplot(data = who %>% mutate(past = ifelse(past, 'Historical',
+#                                            'WHO objective')) %>%
+#          filter(!is.na(with_malaria)) ,
+#        aes(x = year,
+#            y = with_malaria,
+#            color = past)) +
+#   geom_line() +
+#   geom_point() +
+#   theme_black() +
+#   labs(x = '',
+#        y = 'Countries',
+#        title = 'Countries with malaria: Observed and WHO objectives',
+#        subtitle = 'Data from http://www.who.int/malaria/areas/elimination/overview/en/') +
+#   scale_color_manual(name = '',
+#                      values = c('darkorange', 'blue')) +
+#   ylim(0, 130) +
+#   theme(axis.text.x = element_text(angle = 90)) +
+#   geom_hline(yintercept = 0, col = 'red') +
+#     xlim(1970, 2060)
+#   add_zero <- function (x, n) {
+#     x <- as.character(x)
+#     adders <- n - nchar(x)
+#     adders <- ifelse(adders < 0, 0, adders)
+#     for (i in 1:length(x)) {
+#         if (!is.na(x[i])) {
+#             x[i] <- paste0(paste0(rep("0", adders[i]), collapse = ""), 
+#                 x[i], collapse = "")
+#         }
+#     }
+#     return(x)
+# }
+#   counter <- 0
+#   a <- (seq(1,5, length = 15))^2.5
+#   a <- round(a)
+#   a <- c(a, rev(a) +2)
+#   for (i in a){
+#     message(counter)
+#     counter <- counter +1
+#     projection <- data.frame(year = seq(2017, 2035+i, length = 20),
+#                          countries = seq(100, 0, length = 20))
+#     g <- g + geom_line(data = projection,
+#             aes(x = year,
+#                 y = countries,
+#                 color = NA,
+#                 group = NA),
+#             color = 'grey',
+#             alpha = 0.1) 
+#     x <- g +
+#   geom_line(data = projection,
+#             aes(x = year,
+#                 y = countries,
+#                 color = NA,
+#                 group = NA),
+#             color = 'white',
+#             lty = 2) 
+#     print(x)
+#     ggsave(filename = paste0('animation/',
+#                              add_zero(counter, n = 3),
+#                              '.png'))
+#   }
+# }
+# make_animation()
+```
+
 Even in areas of high endemicity, advances in immunology, parasitology, modeling and vaccinology, along with rapid economic development, have made eradication appear a more feasible goal, even if not possible in the short term [@Snow2015, @Eckhoff2014].
@@
                  cols = 2)
+
+# z <- ggplot(data = who %>% mutate(past = ifelse(past, 'Historical',
+#                                            'WHO objective')) %>%
+#          filter(!is.na(with_malaria)) ,
+#        aes(x = year,
+#            y = with_malaria,
+#            color = past)) +
+#   geom_line() +
+#   geom_point() +
+#   theme_paper() +
+#   labs(x = '',
+#        y = 'Countries',
+#        title = 'Countries with malaria: Observed and WHO objectives',
+#        subtitle = 'Data from http://www.who.int/malaria/areas/elimination/overview/en/') +
+#   scale_color_manual(name = '',
+#                      values = c('darkorange', 'blue')) +
+#   ylim(0, 130) +
+#   theme(axis.text.x = element_text(angle = 90)) +
+#   geom_line(data = projection,
+#             aes(x = year,
+#                 y = countries,
+#                 color = NA,
+#                 group = NA),
+#             color = 'white',
+#             lty = 2) +
+#   geom_hline(yintercept = 0, col = 'red')
+# 
+# # xa_plot <- xa %>% mutate(year = year + 2016) %>% filter(year == 2066)
+# xa_plot <- data.frame(year = c(2015, 2066),
+#                       val = c(100, 0))
+#   
+# z + geom_line(data = xa_plot,
+#               aes(x = year,
+#                   y = val),
+#               color = 'white',
+#               alpha = 0.6,
+#               group = 1) +
+#   theme_black()
 ```

### 2017-10-18 shiny/global.R
app update

@@ -107,7 +107,8 @@ plot_variable <- function(variable = 'sleep',
     theme_databrew() +
     labs(x = Hmisc::capitalize(variable),
          y = 'Density',
-         title = paste0('Crowd perception of ', variable)) +
+         title = paste0("Joe's ", variable),
+         subtitle = paste0('Crowd perception')) +
     geom_vline(xintercept = avg,
                lty = 2,
                alpha = 0.8) +
@@ -144,7 +145,7 @@ plot_variable_by <- function(variable = 'sleep',
         theme_databrew() +
         labs(x = Hmisc::capitalize(variable),
              y = 'Density',
-             title = paste0("Crowd perception of Joe's ", variable)) +
+             title = paste0(variable)) +
         scale_fill_manual(name = '',
                           values = c('darkorange', 'blue'))
     } else {
@@ -155,7 +156,7 @@ plot_variable_by <- function(variable = 'sleep',
         theme_databrew() +
         labs(x = Hmisc::capitalize(variable_by),
              y = '',
-             title = paste0("Crowd perception of Joe's ", variable)) +
+             title = paste0(variable)) +
         stat_smooth (geom="line", alpha=0.3, size=1, #span=0.5,
                      color = 'blue') +
         geom_line(stat="smooth",method = "lm",

### 2017-10-18 shiny/server.R

@@ -17,11 +17,30 @@ shinyServer(function(input, output) {
   })
   
   output$p1 <- renderPlot({
-    plot_variable(input$variable)
+    # plot_variable(input$variable)
+    plot_variable('height')
   })
   
   output$p2 <- renderPlot({
-    plot_variable_by(input$variable,
+    # plot_variable_by(input$variable,
+    #                  input$by_variable)
+    plot_variable_by('height',
+                     input$by_variable)
+  })
+  output$p3 <- renderPlot({
+    plot_variable('sleep')
+  })
+  
+  output$p4 <- renderPlot({
+    plot_variable_by('sleep',
+                     input$by_variable)
+  })
+  output$p5 <- renderPlot({
+    plot_variable('age')
+  })
+  
+  output$p6 <- renderPlot({
+    plot_variable_by('age',
                      input$by_variable)
   })
   output$v1 <- renderValueBox({

### 2017-10-18 shiny/ui.R

@@ -1,54 +1,30 @@
 dashboardPage(
   dashboardHeader(title = "Survey results"),
   dashboardSidebar(
-    selectInput("variable",
-                "Variable",
-                c("Joe's height" = 'height',
-                  "Joe's sleep last night" = 'sleep',
-                  "Joe's age" = 'age')),
+    # selectInput("variable",
+    #             "Variable",
+    #             c("Joe's height" = 'height',
+    #               "Joe's sleep last night" = 'sleep',
+    #               "Joe's age" = 'age')),
     selectInput('by_variable',
                 'Examine results by:',
                 c('', "Participant age" = 'years',
                   "Participant sex" = 'sex', "Nothing" = 'nothing'))
   ),
   dashboardBody(
-    # Boxes need to be put in a row (or column)
     fluidRow(
-      box(plotOutput("p1", height = 250)),
-      box(plotOutput("p2", height = 250)),
       valueBoxOutput('v1'),
       valueBoxOutput('v2'),
-      valueBoxOutput('v3'),
-      textOutput('t1')
-    )
+      valueBoxOutput('v3')),
+    h3('Crowd perception:'),
+    fluidRow(box(plotOutput("p1", height = 250), width = 4),
+             box(plotOutput("p3", height = 250), width = 4),
+             box(plotOutput("p5", height = 250), width = 4)),
+    h3('Effect of confounders:'),
+    fluidRow(box(plotOutput("p2", height = 250), width = 4),
+             box(plotOutput("p4", height = 250), width = 4),
+             box(plotOutput("p6", height = 250), width = 4)),
+    fluidRow(textOutput('t1'))
   )
 )
 
-# library(shiny)
-# 
-# # Define UI for application that draws a histogram
-# shinyUI(fluidPage(
-#   
-#   # Application title
-#   titlePanel("Survey results: was the crowd wise?"),
-#   
-#   # Sidebar with a slider input for number of bins 
-#   sidebarLayout(
-#     sidebarPanel(
-#        selectInput("variable",
-#                    "Variable",
-#                    c('height',
-#                      'sleep',
-#                      'age')),
-#        selectInput('by_variable',
-#                    'Examine results by:',
-#                    c('', 'years', 'sex'))
-#     ),
-#     
-#     # Show a plot of the generated distribution
-#     mainPanel(
-#        plotOutput("p1"),
-#        plotOutput("p2")
-#     )
-#   )
-# ))

### 2017-11-24 paper.Rmd
major update

--- 2017-10-12 paper.Rmd
@@
   pdf_document:
+    latex_engine: xelatex
     includes:
@@
 
-The scientific and public health communities have had eradication on their long-term agenda since the WHO established the Global Malaria Eradication Program in the 1950s [@Njera2011].
-Following the failure of the WHO's first attempt, the focus shifted away from global eradication and towards local elimination and control strategies.
+The scientific and public health communities have had eradication on their policy agenda since the WHO established the Global Malaria Eradication Program in the 1950s [@Njera2011].
+Following the failure of the WHO's first attempt, the focus shifted away from global eradication towards local elimination and control strategies.
+In recent years, much of the discourse regarding malaria has shifted back to global eradication [@Roberts2007], with funders, researchers, and public health practitioners rallying to the cause [@Tanner2015].
+The Bill and Melinda Gates Foundation has begun actively promoting eradication as feasible "within a generation" [@Gates2014], and the leadership of the World Health Organization (WHO) has supported this goal, stating the objective of eliminating malaria in 65 new countries from 2015 through 2030 (Figure 1).
 
-In recent years, much of the discourse regarding malaria has shifted back to global eradication [@Roberts2007], with funders, researchers, and public health practitioners rallying to the cause [@Tanner2015].
-The Bill and Melinda Gates Foundation has begun actively promoting eradication as feasible "within a generation" [@Gates2014], and the leadership of the World Health Organization (WHO) has supported this goal.
-Even in areas of high endemicity, advances in immunology, parasitology, modeling and vaccinology, along with rapid economic development, have made eradication appear a more feasible goal, even if not possible in the short term [@Snow2015, @Eckhoff2014].
+```{r, fig.cap='Countries with malaria: Observed and WHO objectives', fig.height = 3, fig.width = 4}
+# Read WHO data (compiled manually from WHO website)
+# Data from http://www.who.int/malaria/areas/elimination/overview/en/'
+who <- readr::read_csv('who_elimination_data.csv')
+who$year <- as.numeric(substr(who$year, 6, 9))
+projection <- data.frame(year = seq(2030.2, 2035, length = 20),
+                         countries = seq(33, 0, length = 20))
+g <- ggplot(data = who %>% mutate(past = ifelse(past, 'Historical',
+                                           'WHO objective')) %>%
+         filter(!is.na(with_malaria)) ,
+       aes(x = year,
+           y = with_malaria,
+           color = past)) +
+  geom_line() +
+  geom_point() +
+  theme_paper() +
+  labs(x = '',
+       y = 'Countries') +
+  scale_color_manual(name = '',
+                     values = c('darkorange', 'blue')) +
+  ylim(0, 130) +
+  theme(axis.text.x = element_text(angle = 90)) #+
+  # geom_line(data = projection,
+  #           aes(x = year,
+  #               y = countries,
+  #               color = NA,
+  #               group = NA),
+  #           color = 'black',
+  #           lty = 2) +
+  # geom_hline(yintercept = 0, col = 'red') 
+g
+# #Make animation for presentation
+# make_animation <- function(){
+#   g <- 
+#     ggplot(data = who %>% mutate(past = ifelse(past, 'Historical',
+#                                            'WHO objective')) %>%
+#          filter(!is.na(with_malaria)) ,
+#        aes(x = year,
+#            y = with_malaria,
+#            color = past)) +
+#   geom_line() +
+#   geom_point() +
+#   theme_black() +
+#   labs(x = '',
+#        y = 'Countries',
+#        title = 'Countries with malaria: Observed and WHO objectives',
+#        subtitle = 'Data from http://www.who.int/malaria/areas/elimination/overview/en/') +
+#   scale_color_manual(name = '',
+#                      values = c('darkorange', 'blue')) +
+#   ylim(0, 130) +
+#   theme(axis.text.x = element_text(angle = 90)) +
+#   geom_hline(yintercept = 0, col = 'red') +
+#     xlim(1970, 2060)
+#   add_zero <- function (x, n) {
+#     x <- as.character(x)
+#     adders <- n - nchar(x)
+#     adders <- ifelse(adders < 0, 0, adders)
+#     for (i in 1:length(x)) {
+#         if (!is.na(x[i])) {
+#             x[i] <- paste0(paste0(rep("0", adders[i]), collapse = ""), 
+#                 x[i], collapse = "")
+#         }
+#     }
+#     return(x)
+# }
+#   counter <- 0
+#   a <- (seq(1,5, length = 15))^2.5
+#   a <- round(a)
+#   a <- c(a, rev(a) +2)
+#   for (i in a){
+#     message(counter)
+#     counter <- counter +1
+#     projection <- data.frame(year = seq(2017, 2035+i, length = 20),
+#                          countries = seq(100, 0, length = 20))
+#     g <- g + geom_line(data = projection,
+#             aes(x = year,
+#                 y = countries,
+#                 color = NA,
+#                 group = NA),
+#             color = 'grey',
+#             alpha = 0.1) 
+#     x <- g +
+#   geom_line(data = projection,
+#             aes(x = year,
+#                 y = countries,
+#                 color = NA,
+#                 group = NA),
+#             color = 'white',
+#             lty = 2) 
+#     print(x)
+#     ggsave(filename = paste0('animation/',
+#                              add_zero(counter, n = 3),
+#                              '.png'))
+#   }
+# }
+# make_animation()
+```
+
+Even in areas of high endemicity, advances in immunology, parasitology, modeling and vaccinology, along with rapid economic development, have made eradication appear a more feasible goal, even if not possible in the short term [@Snow2015] [@Eckhoff2014].
 From both administrative [@Yamey2004] and scientific [@Alonso2011] points of view, eradication has never before received so much attention, nor appeared so within grasp.
@@
 
-## The problem
-
 The WHO Global Malaria Programme (GMP) has acknowledged that it "needs to take an official position on how and under what timeline malaria eradication could be achieved" [@WHO2015].
-Such a position could inform policy, and plays a crucial role in the economic analysis of the expected value of malaria control inteventions.
+Such a position could inform policy, and plays a crucial role in the economic analysis of the expected value of malaria control interventions.
 
 However, no such position has been taken.
-This omission is likely intentional, and certainly understadable, given that MalERA's and the WHO GMP's goals are to guide research and technology in the direction of eradication, and not necessarily address the larger and much more subjective questions of \emph{if} and \emph{when}.
+This omission is likely intentional, and certainly understandable, given that MalERA's and the WHO GMP's goals are to guide research and technology in the direction of eradication, and not necessarily address the larger and much more subjective questions of \emph{if} and \emph{when}.
 
@@
 
-## Rationale
-
-A great deal of previous research already covers the the cost per case prevented [@Sicuri2011, @Silumbe2015, @Btto2016, @IlungaIlunga2014, @Dalaba2015].
-Likewise, a literature exists which could serve as a model for quantifying the location-specific opportunity costs associated with funneling funds towards malaria eradication [@Stuckey2014, @White2011, @Korenromp2012].
-The correct discount rate for estimating the value of future lives saved is more of a philosphical question than an economic one.
+A great deal of previous research already covers the the cost per case prevented [@Sicuri2011] [@Silumbe2015] [@Btto2016 [@IlungaIlunga2014] [@Dalaba2015].
+Likewise, literature exists which could serve as a model for quantifying the location-specific opportunity costs associated with funneling funds towards malaria eradication [@Stuckey2014] [@White2011] [@Korenromp2012].
+The correct discount rate for estimating the value of future lives saved is more of a philosophical question than an economic one.
 This leaves only the probability and time-frame to eradication, questions which have been addressed anecdotally, but never answered quantitatively.
@@
 
-## Objective
-
-The objective of this study is simple: to help guide the optimal distribution of health resources by gauging (expert) opinion about, estimating the likelihood of, and quantifying the time frame to malaria eradication through a systematic survey of malaria research professionals from a wide array of academic disciplines.
+The objective of this study is to help guide the optimal distribution of health resources by gauging (expert) opinion about, estimating the likelihood of, and quantifying the time frame to malaria eradication through a systematic survey of malaria research professionals from a wide array of academic disciplines.
 
 # Methods
-
-## Ethics
-
-This research followed the principles of the Declaration of Helsinki. The study's protocol was approved by the Scientific Committee of the Barcelona Institute for Global Health.
-
-## Participants
 
@@
 Participants were informed directly on the survey form of the study's purpose, that responses were not guarnteed to be anonymous, and where to find further details on the study.
-
-## Survey
 
@@
 1. Area of expertise.
+2. Perceived probability (%) of malaria eradication in 10, 20, 30, 40, and 50 years.
+3. Free choice perceived number of years until malaria eradication.
+4. Ranking of the WHO's "health system building blocks" [@manya2017] in regards to attention needed in order to achieve eradication.
 
-2. Perceived probability (%) of malaria eradication in 10, 20, 30, 40, and 50 years.
-
-3. Free choice perceived number of years until malaria eradication.
-
-4. Ranking of the WHO's "health system building blocks" in regards to attention needed in order to achieve eradication.
-
-## Supplementary data generation
+The purpose of final point was to introduce a prescriptive element to the researchers' responses (ie, identify potential areas of consensus in regards to the path towards eradication).
 
@@
 For gender estimations we used data from the North Atlantic Population Project, and U.S.
-government [@Lincoln]; for ethnicity, Khanna et al's bayesian prediction algorithm for the estimation of racial categories [@wru2015, @Imai_2016] was employed.
-
-## Analysis
+government [@Lincoln]; for ethnicity, Khanna et al's bayesian prediction algorithm for the estimation of racial categories [@wru2015] [@Imai_2016] was employed.
 
@@
 
+Qualitative analysis of free text comments was carried out using thematic content analysis, following a grounded theory approach [@Markey_2014].
+Participants were invited to provide "any general comments on the timeline and likelihood of global eradication".
+Thematic content analysis [@Vaismoradi_2016] was employed to code responses following the 6-phase approach laid out by Braun and Clarke [@Braun2006].
+The approach was inductive, used open-coding to identify latent themes, and underwent several iterations in which codes were modified, discarded and created.
+Using the RQDA software to assist in data management and theme coding [@Ronggui2017], four subject themes were identified.
+Comments were additionally coded as either descriptive (comments pertaining to the "problem" of malaria eradication) or presciptive (pertaining to potential "solutions" for eradicating malaria).
+Finally, free-text comments were scored for overall sentiment polarity [@sentimentr2017].
+
+Quantitative analysis was carried out in R language [@R].
 Ordinary least squares regression was employed to estimate the effect of area of expertise on the eradication pessimism-optimism (through the proxy of perceived years to eradication).
 De-biasing of sample selection was carried out using Heckman's 2 step approach as implemented by Toomet [@toomet2008].
-
-Qualitative analysis of free text comments was carried out using thematic content analysis.
-
-Quantitative analysis was carried out in R language [@R].
 All analysis code, as well as the code used for the identification and contacting of participants, is publicly available at [https://github.com/joebrew/malaria_survey](https://github.com/joebrew/malaria_survey).
 
+This research followed the principles of the Declaration of Helsinki. The study's protocol was approved by the Scientific Committee of the Barcelona Institute for Global Health.
+
 # Results
-
-A total of `r length(which(df$responded))` researchers participated in the survey from the `r nrow(df)` invitations sent (participation rate of `r round(length(which(df$responded)) / nrow(df) * 100, 2)`%).
-
-## Expertise profile among respondents
 
@@
 
-Areas of expertise were non-exclusive and self-described, with participants having the option to choose from up to 3 of 10 checkboxes\footnote{Checkbox categories were anthropology, biology, clinical medicine, economics, epidemiology, immunology, parasitology, political science, statistics, and virology.}, or to write in one or more "other" areas of expertise.
-`r x$n[1]` participants (`r round(x$p[1], digits = 1)`%) declared only one area of expertise, with `r sum(x$n[1:3])` (`r round(sum(x$p[1:3]), digits = 1)`%) declaring three or fewer.
-
-Participants had a total of `r length(old_areas)` unique (self-described) areas of expertise, of which `r length(areas)` areas of expertise had 5 or more participants (see table 1).
+A total of `r length(which(df$responded))` researchers participated in the survey from the `r nrow(df)` invitations sent (participation rate of `r round(length(which(df$responded)) / nrow(df) * 100, 2)`%).
+Areas of expertise were non-exclusive and self-described, with participants having the option to choose from up to 3 of 10 checkboxes\footnote{Responses categories were Anthropology, Biochemistry, Bioinformatics, Biology, Chemistry, Clinical medicine, Drug discovery, Ecology, Economics, Entomology, Epidemiology, Geography, GIS, History, Immunology, Infectious disease, IT, Malaria, Medical entomology, Medicinal chemistry, Microbiology, Parasitology, Pharmacology, Pharmacy, Political science, Public health, Statistics, Vector biology, Vector control, and Virology.}, or to write in one or more "other" areas of expertise.
+`r sum(x$n[1:3])` (`r round(sum(x$p[1:3]), digits = 1)`%) participants declared three or fewer areas of expertise.
 
@@
 temp$Area <- Hmisc::capitalize(temp$Area)
-kable(temp[1:10,], #format = "latex", 
-      caption = 'Top 10 areas') #%>%
+temp$Area[temp$Area == 'It'] <- 'Information Technology'
+# kable(temp[1:10,]) #%>%
   # kableExtra::kable_styling(#position = "float_right",
@@
 
-## Likelihood of eradication
+Participants had a total of `r length(old_areas)` unique (self-described) areas of expertise.
+The five most popular were `r paste0(paste0(temp$Area[1:5], ' (', temp$Researchers[1:5], ')'), collapse = ', ')`.
 
@@
 Most participants saw eradication as extremely unlikely in the next 10-30 years, but increasingly likely thereafter.
-The following figure shows the distribution of year-specific likelihood perceptions (panels A-E), as well as an illustration of how both likelihood and uncertainty grow over time (panel F).
+Figure 2 shows the distribution of year-specific likelihood perceptions (panels A-E), as well as an illustration of how both likelihood and uncertainty grow over time (panel F).
 
-```{r, fig.cap='Perceptions of likelihood of eradication', fig.height = 6.2}
+```{r, fig.cap='Perceptions of likelihood of eradication', fig.height = 4.5}
 # Define function for analyzing the years_n columns
@@
     labs(title = paste0(toupper(letters[n/10]),'. ', n, ' years'),
-         subtitle = 'Perceived likelihood of eradication',
+         # subtitle = 'Perceived likelihood of eradication',
          x = 'Likelihood',
@@
     theme_paper(base_size = 10) +
-    theme(axis.text.x = element_text(angle = 90))
+    theme(axis.text.x = element_text(angle = 90)) +
+  theme(plot.title = element_text(size=8))
   return(out)
@@
   ggtitle('G. Aggregated perceptions',
-          'Shaded area = inter-quartile range')
+          'Shaded area = inter-quartile range') +
+  theme(plot.title = element_text(size=8))
 
@@
                  g2, g4, g6,
-                 cols = 2)
+                 cols = 3)
+
+# z <- ggplot(data = who %>% mutate(past = ifelse(past, 'Historical',
+#                                            'WHO objective')) %>%
+#          filter(!is.na(with_malaria)) ,
+#        aes(x = year,
+#            y = with_malaria,
+#            color = past)) +
+#   geom_line() +
+#   geom_point() +
+#   theme_paper() +
+#   labs(x = '',
+#        y = 'Countries',
+#        title = 'Countries with malaria: Observed and WHO objectives',
+#        subtitle = 'Data from http://www.who.int/malaria/areas/elimination/overview/en/') +
+#   scale_color_manual(name = '',
+#                      values = c('darkorange', 'blue')) +
+#   ylim(0, 130) +
+#   theme(axis.text.x = element_text(angle = 90)) +
+#   geom_line(data = projection,
+#             aes(x = year,
+#                 y = countries,
+#                 color = NA,
+#                 group = NA),
+#             color = 'white',
+#             lty = 2) +
+#   geom_hline(yintercept = 0, col = 'red')
+# 
+# # xa_plot <- xa %>% mutate(year = year + 2016) %>% filter(year == 2066)
+# xa_plot <- data.frame(year = c(2015, 2066),
+#                       val = c(100, 0))
+#   
+# z + geom_line(data = xa_plot,
+#               aes(x = year,
+#                   y = val),
+#               color = 'white',
+#               alpha = 0.6,
+#               group = 1) +
+#   theme_black()
 ```
-
-## Time frame to eradication
 
@@
 Among respondants, `r length(which(df$years >= 50))` (`r round(length(which(df$years >= 50)) / length(which(!is.na(df$years))) * 100, digits = 1)` %) estimated that it would be 50 or more years until eradication.
-The below histogram shows the distribution of responses, truncated at 50.
 
-```{r, fig.height = 3.5, fig.width = 4}
+```{r, fig.height = 3.5, fig.width = 4, eval = FALSE}
 ggplot(data = df,
@@
 ```
-
-## Sample selection
 
@@
          `Response rate` = p)
+out$Variable <- Hmisc::capitalize(out$Variable)
+out$Variable[out$Variable == 'Bin_citations'] <- 'Citations'
+out$Characteristic <- Hmisc::capitalize(out$Characteristic)
+out$`Response rate` <- paste0(round(out$`Response rate`, digits = 2), ' %')
+
+for(i in nrow(out):2){
+  this_var <- out$Variable[i]
+  prev_var <- out$Variable[i-1]
+  if(this_var == prev_var){
+    out$Variable[i] <- ''
+  }
+}
 knitr::kable(out, 
@@
 In the case of researcher impact (as measured by the total number of citations), selection bias plays an important role: being highly-cited was associated both with eradication "pessimism" as well as likelihood of non-response.
-In other words, our pool of respondents was less highly-cited than our pool of invitees, and among respondents, those who were highly-cited tended to be more pessimistic (see below figure).
+In other words, our pool of respondents was less highly-cited than our pool of invitees, and among respondents, those who were highly-cited tended to be more pessimistic (see Figure 3, Panel A).
 
 ```{r}
-# df$bin_citations <- factor(df$bin_citations,
-#                            labels = c('0',
-#                                       '1-9',
-#                                       '10-51',
-#                                       '52+'))
 x <- df %>%
@@
                          )(length(unique(x$citations)))
-ggplot(data = x %>% filter(!is.na(citations)),
+x1 <- ggplot(data = x %>% filter(!is.na(citations)),
        aes(x = as.numeric(gsub('years_', '', key)),
@@
   labs(x = 'Years',
-       y = '% likelihood',
-       title = 'Difference in perceived likelihood of eradication by citations',
-       subtitle = 'More citations = more pessimistic')
+       y = 'Likelihood of eradication',
+       subtitle = 'A: Difference in perceived likelihood of eradication by citations')
 ```
 
-## De-biasing of results
-
-We used Heckman's 2-step correction method [@Heckman_1979].
-Given that sex affected response rate but not response itself, we were able to use sex as an instrumental variable, introducing it in both the selection and response models.
-Our selection model, which estimated the likelihood of survey response as a probit function of sex allowed us to estimate (via the Inverse Mills ratio) an expected error term for our outcome models, in which we quantify the effect of the number of citations on the perceived average likelihood of eradication at 10, 20, 30, 40, and 50 years.
-The below chart shows the difference in the aggregate perceived likelihood of eradication before and after implementing Heckman's 2-step model.
-
-```{r, results = 'markup'}
+```{r}
+x2 <- 
   ggplot(data = heckman,
@@
   labs(x = 'Years',
-       y = 'Likelihood of eradication') +
+       y = 'Likelihood of eradication',
+       subtitle = 'B: Perceived likelihood of eradication: Heckman method and unadjusted') +
   scale_linetype_manual(name = '', values = 1:2) +
-  scale_color_manual(name = '', values = c('blue', 'darkorange')) +
-  labs(title = 'Heckman selection adjustment')
+  scale_color_manual(name = '', values = c('blue', 'darkorange'))
 ```
 
-The below table shows the Heckman model Heckman model estimates for all five models.
+```{r, fig.cap = 'Sample selection bias and adjustment', fig.height = 3.5}
+Rmisc::multiplot(x1, x2, cols = 2)
+```
+
+In order to de-bias sample selection, we employed Heckman's two-step correction method [@Heckman_1979].
+Given that sex affected response rate but not response itself, we were able to use sex as an instrumental variable, introducing it in both the selection and response models.
+Our selection models, which estimated the likelihood of survey response as a probit function of sex allowed us to estimate (via the Inverse Mills ratio) an expected error term for our outcome models, in which we quantify the effect of the number of citations on the perceived average likelihood of eradication at 10, 20, 30, 40, and 50 years (employing a separate model for each time period).
+Figure 3 shows the difference in the aggregate perceived likelihood of eradication before and after implementing Heckman's two-step model.
+
+Table 2 shows the Heckman model Heckman estimates for all five models.
 
@@
                    `Model 50` = heck_50$coefficients)
-knitr::kable(heck)
+for (j in 2:ncol(heck)){
+  heck[,j] <- round(heck[,j], digits = 3)
+}
+heck$Coefficient <- gsub('bin_citations', 'Citations ', heck$Coefficient)
+heck$Coefficient <- gsub('invMillsRatio', 'Inverse Mills Ratio', heck$Coefficient)
+heck$Coefficient <- gsub('sigma', 'Sigma', heck$Coefficient)
+heck$Coefficient <- gsub('rho', 'Rho', heck$Coefficient)
+heck$Coefficient <- gsub('sexmale', 'Sex male', heck$Coefficient)
+heck$Coefficient <- paste0(c(rep('Selection ', 4), rep('Outcome ', 2), rep('', 3)), heck$Coefficient)
+knitr::kable(heck,
+             caption = 'Heckman selection model coefficients')
 ```
 
-## Difference in perceptions by expertise
+Participants were heterogenous in their perceptions, with all of the 5 pre-determined cut-offs containing the whole range of likelihoods (0-100%), and the free-form time frame responses suggesting that eradication would be achieved in a time-frame ranging from less than a decade to never.
+Heterogeneity can only be partly explained by area of expertise, as the differences in perception between disciplines were minor and insignificant (see Figure 4).
 
-Participants were heterogenous in their perceptions, with all of the 5 pre-determined cut-offs containing the whole range of likelihoods (0-100%), and the free-form time frame responses suggesting that eradication would be achieved in as little as `r min(df$years, na.rm = TRUE)` to as many as "never".
-Heterogeneity can be partly explained by area of expertise, as evidenced by significant differences in the perceived years to eradication by area of expertise.
-
-```{r, fig.height = 3.5, fig.width = 4}
+```{r, fig.height = 3, fig.width = 4, fig.cap = 'Average perceived years to aggregation by discipline'}
 areas_df <- areas_df %>% arrange(desc(count))
@@
 x$term <- gsub('_', '\n', x$term)
+x$term <- Hmisc::capitalize(x$term)
+x$term[x$term == 'It'] <- 'Information\ntechnology'
+
 x$term <- factor(x$term, levels = x$term)
@@
   labs(x = 'Area',
-       y = 'Years',
-       title = 'Perceived years to eradication',
-       subtitle = 'By expertise, adjusted for multiple areas of expertise') +
+       y = 'Years') +
   theme(axis.text.x = element_text(angle = 90))
@@
 ```
-
-## Health system building blocks
-
-Finally, researchers were asked to rank the WHO's 6 health system building blocks as needing the most to least attention (6-1 scale) in order for eradication to be achieved.
-Disagreement was high, as evidenced by the variance in responses in the below point and violin chart.
-However, the general tendency was that governance was recognized as the most important area requiring attention, with health information thought to be the area least requiring attention.
 
@@
 
-library(ggridges)
-ggplot(data = results %>% filter(!is.na(ranking)),
-       aes(x = ranking,
-           y = bb,
-           fill = bb)) +
-  geom_density_ridges(#fill = 'darkorange',
-                      alpha = 0.6,
-                      scale = 1.5) +
-  theme_paper() +
-  xlim(0,30) +
-  labs(x = 'Perceived importance',
-       y = 'WHO Building Block') +
- scale_fill_cyclical(values = c("darkorange", "yellow"))
+# library(ggridges)
+# ggplot(data = results %>% filter(!is.na(ranking)),
+#        aes(x = ranking,
+#            y = bb,
+#            fill = bb)) +
+#   geom_density_ridges(#fill = 'darkorange',
+#                       alpha = 0.6,
+#                       scale = 1.5) +
+#   theme_paper() +
+#   xlim(0,30) +
+#   labs(x = 'Perceived importance',
+#        y = 'WHO Building Block') +
+#  scale_fill_cyclical(values = c("darkorange", "yellow"))
 
@@
 
-## Qualitative analysis of results
+## Qualitative analysis of comments
 
-Participants were invited to provide "any general comments on the timeline and likelihood of global eradication".
 Of the `r length(which(df$responded))` who responded to the survey, `r length(which(!is.na(df$comments)))` (`r round(length(which(!is.na(df$comments))) / length(which(df$responded)) * 100, digits = 2)`%) provided a comment.
-Thematic content analysis [@Vaismoradi_2016] was employed to code responses into four subject themes as well as the binary categorization of descriptive vs.
-presciptive.
+Relative to non-commenters, commenters were slightly more optimistic on average, but also slightly more polarized in opinion.
+The four subject themes identified through iterative, open coding were:
 
-The four subject themes, identified and refined through iterative analysis, were:
+1. *Innovation*: comments pertaining to new tools, drugs, methods, or strategies required to achieve eradication.
+2. *Systematic challenges*: comments pertaining to political, social, environmental or logistical issues related to eradication.
+3. *Poverty*: comments specifically related to the economic and socieconomic components of malaria eradication.
+4. *Meta*: challenging the question of eradication itself, re-framing the goal, insisting on other priorities, etc.
 
-1. Innovation: comments pertaining to new tools, drugs, methods, or strategies required to achieve eradication.
-2. Systematic challenges: comments pertaining to political, social, environmental or logistical issues related to eradication.  
-3. Poverty: comments specifically related to the economic and socieconomic components of malaria eradication.
-4. Meta: challenging the question of eradication itself, re-framing the goal, insisting on other priorities, etc.
+Comments were also classified as descriptive or prescriptive.
+A slight majority (`r round(320 / 540 * 100, digits = 2)`%) were descriptive.
+Descriptive commenters were slightly more pessimistic (in regards to perceived years until eradication) than prescriptive commenters, though this difference did not reach the level of statistical significance (p = 0.21).
+Descriptive comments also received sentiment polarity scores which were slightly more negative than prescriptive comments, although again this difference did not reach the level of statistical significance (p = 0.18).
 
 In regards to **innovation**, comments largely pertained to the necessity of further technological advances.
-One participant wrote that "currently available technology can't achieve [eradication], even if delivered optimally"; another argued that eradication could not be achieved without a "game-changing innovation", whereas two others referred to the need for "transformative" technologies.
-Many noted the need to "overcome the challenge of drug resistance" and develop better vaccines.
-Genetic engineering was mentioned by several commenters.
+One participant wrote that "currently available technology can't achieve [eradication], even if delivered optimally"; another argued that eradication could not be achieved without a "game-changing innovation", whereas multiple others referred to the need for "transformative" technologies:
+
+\begin{quote}
+We can't achieve eradication with our current tools. We'd need new medicines, a better vaccine, and maybe other vector control tools.
+\end{quote}
+
+Many noted the need to "overcome the challenge of drug resistance".
+More than 10% of commenters noted the need for an effective vaccine.
+Genetic engineering was mentioned by several commenters as a promising means to achieve eradication quickly.
 Most comments coded as "innovatation" were presciptive in nature, often suggesting the nature of the needed innovation, with a heavy slant towards pharmaceutical options and vaccination.
@@
 **Systematic challenges** to malaria eradication were noted by the majority of commenters.
-In direct contrast to the previous comments, one participant stated that "we already have the tools to achieve  eradication" and that the only piece lacking was "robust health systems".
+In direct contrast to the previous comments, many emphasized that "we already have the tools to achieve  eradication" and that the only piece lacking was "robust health systems".
+Many commenters noted problems of coordination:
+
+\begin{quote}
+It will be very difficult to eradicate malaria...
+not because we don't have the technologies, which we already have...
+the problem is politics.
+Malaria doesn't stop in borders of a country and it would take a joint effort of a lot of political leaders to get programs in place to fight malaria.
+Unfortunately I don't see this happening anytime soon.
+\end{quote}
+
 Others echoed the sentiment, with many comments focusing on the need of strong surveillance and treatment delivery systems.
@@
 
-**Poverty** was assigned its own category in the codification of free text responses because of its ubiquity as a theme in comments.
+**Poverty** was assigned its own category in the codification of free text responses - although it is best understood as a sub-category of "systemtatic challenges" - because of its ubiquity as a theme in comments.
 Many noted that malaria is a "disease of poverty", with "social injustice" as the root cause.
 Some made the sequential argument that "eradication of poverty" must preceed disease eradication.
-Along the same lines, one commenter said that eradication requires "a full systems-wide approach, not a disease-specific approach.
-The eradication of smallpox was a triumph of management, not medicine or technology." Another noted that the survey "left off the list the most important factor - economic development".
+Along the same lines, one commenter wrote:
+
+\begin{quote}
+Eradication requires a full systems-wide approach, not a disease-specific approach. The eradication of smallpox was a triumph of management, not medicine or technology.
+\end{quote}
+
+Another noted that the survey "left off the list the most important factor - economic development".
 Many echoed the sentiment, stating that "with no economic development, you cannot have eradication" and that poverty is the "cause" of malaria.
@@
 One stated that the concept was "absurd" and that "I'm not even sure why people talk about it".
-Several pointed to the failure of the WHO GMP in the 1950s as evidence of the futile nature of eradication programs.
+Another questioned the utility of discussing "eradiction" as a concept:
+
+\begin{quote}
+Eradication is a different objective than elimination.
+Elimination means that the disease is not endemic but could reappear even in a country like Norway if infrastructure breaks down.
+Elimination may be possible in poor endemic countries, following socioeconomic development.
+Eradication means that the parasite disapears from the planet, which is not realistic...
+\end{quote}
+
+Many pointed to the failure of the WHO GMP in the 1950s as evidence of the futile nature of eradication programs.
 Many highlighted that talking about "malaria" as one disease misses the mark, since the different species of parasite and contexts in which they live make elimination in each area very distinct from other areas.
@@
 
-## General pessimism
-
-Our study reveals a striking gap between the public discourse on malaria eradication, and those views held (largely privately) by malaria researchers.
+Our survey reveals a notable gap between the public discourse on malaria eradication, and those views held (largely privately) by malaria researchers.
 Approximately three-quarters of respondents believe that malaria will not be eradicated in the next 50 years; in other words, assuming our pool of respondents is of typical post-PhD age, most believe they will not live to see eradication.
@@
 
-On the other hand, there are many reasons to be skeptical that the combined "wisdom of crowds" of malaria researchers is a reliable indicator of truth.
+## Limitations
+
+There are many reasons to be skeptical that the combined "wisdom of crowds" of malaria researchers is a reliable indicator of truth.
 First, academic researchers are specialists - their narrow, field-specific view of eradication's feasibility is arguably less reliable than the more "global" views of the WHO, or Bill Gates.
-Second, a number of biases may come in to play in this study.
+Second, a number of biases may come into play in this study.
 
-Among these biases, 4 are worth mentioning specifically.
+Among these biases, four are worth mentioning specifically.
 (1) "Conjunction fallacy" suggests that the general goal of eradication may seem less likely than the sum of the goals of country-specific elimination.
@@
 (4) Finally, and ironically, "optimism bias" may play a perverse role in researchers' responses; though eradication is certainly a goal desired by all, one could argue that malaria research specialists subconciously realize that they actually stand to lose out profesionally in the case of eradication.
+
+Though results are not disclosed at the individual level, this survey was not entirely anonymous, suggesting that social desirability bias may have influenced responses, and that selection bias likely meant our pool of participants were substantially different from those who choose not to participate.
+
+We made no distinguishment between quality of research, years of experience, academic achievements, geographical area, etc.
+Our inclusion criteria were simple and rudimentary, allowing us to access many diverse viewpoints, but (perhaps inappropriately) weighting all viewpoints as equal.
+
+This study included the corresponding authors of indexed journals.
+Though certainly a group with important knowledge related to malaria, this misses malaria control program employees, health agency workers, and other stakeholders.
+Their experiences and viewpoints may be different from those of academicians, and arguably more relevant.
+
+## Conclusion
 
@@
 
-## Discord over building blocks to eradication
-
-It is noteworthy that there was so much discord among researchers in regards to which WHO building blocks required the most attention in order for eradication to be achieved.
-All six possible categories received votes for both the lowest and highest levels of importance, as well as every level in between.
-And the difference between "health information" (the building block deemed as least important) and "governance" (the most important) was less than 0.5 on a 1-6 scale.
-
-This discord suggests that the path to implementing strategies for eradication is not clear, at least from the perspective of this study's participants.
-This could mean that further work is needed in order to prioritize which areas require the most investment and attention in order for eradication to occur.
-On the other hand, one could interpret this result as reflecting the fact that previous work on priorities (ie, MalERA) has not been fully accessed or understood by the larger malaria research community.
-
-## Few differences by area of expertise
-
-It is noteworthy that among the most "optimistic" experts were from the field of bioinformatics.
-This could be explained by the fact that, relative to other more "traditional" areas of science, informatics regularly sees paradigm shifts, and changes in technology and breakthroughs occur at a more rapid rate.
-That said, the high degree of optimism among chemists would seem to contradict this hypothesis.
-At any rate...
-(more details will go here).
-
-## Limitations
-
-In addition to the biases mentioned above, this study has many limitations.
-First, though results are not disclosed at the individual level, this survey was not entirely anonymous, suggesting that social desirability bias may have influenced responses, and that selection bias likely meant our pool of participants were substantially different from those who choose not to participate.
-
-Second, we made no distinguishment between quality of research, years of experience, academic achievements, geographical area, etc.
-Our inclusion criteria were simple and rudimentary, allowing us to access many diverse viewpoints, but (perhaps inappropriately) weighting all viewpoints as equal.
-
-Third, this study included the corresponding authors of indexed journals.
-Though certainly a group with important knowledge related to malaria, this misses malaria control program employees, health agency workers, and other stakeholders.
-Their experiences and viewpoints are most likely vastly different from those of academecians.
-
-## Implications
-
 Our survey attempted to quantify the likelihood of and time frame to malaria eradication by gauging the collective opinion of malaria researchers.
 Our results suggest that eradication is unlikely in the short and medium terms, and that there exists a great deal of disagreement among researchers in regards to which areas require the most attention in order for eradication to occur.
-The implication of these results are three-fold: (1) that those working or investing in eradication-specific campaigns should factor in the low likelihood and long time frame when calculating those campaigns' expected value; (2) that champions of near-term eradication need to make a more compelling case to malaria researchers of eradication's feasibility, in order to better focus and inspire the latter; and (3) that discord among malaria researchers as to which areas need the most attention in order for eradication to occur suggests a need for open discussion and concensus-making, so that resources and focus are directed appropriately.
+The implication of these results are three-fold: (1) that those working or investing in eradication-specific campaigns should factor in the low likelihood and long time frame when calculating those campaigns' expected value; (2) that champions of near-term eradication need to make a more compelling case to malaria researchers of eradication's feasibility, in order to better focus and inspire the latter; and (3) that discord among malaria researchers as to which areas need the most attention in order for eradication to occur, suggests a need for open discussion and concensus-making, so that resources and focus are directed appropriately.
 

### 2017-11-24 prepare_data.R

@@ -451,6 +451,7 @@ if('prepared_data.RData' %in% dir()){
     ifelse(df$n_citations_total <= 5, '0-5',
            ifelse(df$n_citations_total < 99, '6-99',
                   ifelse(df$n_citations_total >= 100, '> 99', NA)))
+  df$bin_citations[is.na(df$bin_citations)] <- '0-5'
     # cut(x = df$n_citations_total,
     #     breaks = quantile(df$n_citations_total,
     #                       na.rm = TRUE),

### 2017-12-27 paper.Rmd
update

@@
 ---
-title: Silent pessimists - researchers' perceptions of malaria eradication and implications for health spending
+title: "Silent pessimists: researchers' perceptions of malaria eradication and implications for health spending"
 bibliography: library.bib
@@
 The opportunity cost of investments in eradication-specific interventions can be high, particularly in contexts with other urgent health priorities.
-In a systematic survey of malaria researchers, we query perceptions regarding the likelihood and time frame of eradication, as well as the perceived chief areas needed for improvement in order for eradication to be achieved.
+In a systemic survey of malaria researchers, we query perceptions regarding the likelihood and time frame of eradication, as well as the perceived chief areas needed for improvement in order for eradication to be achieved.
 We assess pessimism/optimism (via the proxy of years-to-eradication), broken down by area of expertise, and adjust for selection bias.
@@
 
-The WHO Global Malaria Programme (GMP) has acknowledged that it "needs to take an official position on how and under what timeline malaria eradication could be achieved" [@WHO2015].
-Such a position could inform policy, and plays a crucial role in the economic analysis of the expected value of malaria control interventions.
+International programes, such as the WHO Global Malaria Programme (GMP), have acknowledged the need "to take an official position on how and under what timeline malaria eradication could be achieved" [@WHO2015].
+Such a position could inform policy, and plays a crucial role in the economic analysis of the expected value of malaria elimination initiatives.
 
@@
 
-A great deal of previous research already covers the the cost per case prevented [@Sicuri2011] [@Silumbe2015] [@Btto2016 [@IlungaIlunga2014] [@Dalaba2015].
+A great deal of previous research already covers the cost per case prevented [@Sicuri2011] [@Silumbe2015] [@Btto2016 [@IlungaIlunga2014] [@Dalaba2015].
 Likewise, literature exists which could serve as a model for quantifying the location-specific opportunity costs associated with funneling funds towards malaria eradication [@Stuckey2014] [@White2011] [@Korenromp2012].
@@
 
-The objective of this study is to help guide the optimal distribution of health resources by gauging (expert) opinion about, estimating the likelihood of, and quantifying the time frame to malaria eradication through a systematic survey of malaria research professionals from a wide array of academic disciplines.
+The objective of this study is to help guide the optimal distribution of health resources by gauging (expert) opinion about, estimating the likelihood of, and quantifying the time frame to malaria eradication through a systemic survey of malaria research professionals from a wide array of academic disciplines.
 
@@
 Researchers were invited to participate by clicking a link to the survey form.
-Participants were informed directly on the survey form of the study's purpose, that responses were not guarnteed to be anonymous, and where to find further details on the study.
-
 The survey was simple, consisting of only name, email, and four content-related fields along with a "general comments" section.
@@
 
-Qualitative analysis of free text comments was carried out using thematic content analysis, following a grounded theory approach [@Markey_2014].
+Quantitative analysis was carried out in R language [@R].
+Ordinary least squares regression was employed to estimate the effect of area of expertise on the eradication pessimism-optimism (through the proxy of perceived years to eradication).
+De-biasing of sample selection was carried out using Heckman's 2 step approach as implemented by Toomet [@toomet2008].
+All analysis code, as well as the code used for the identification and contacting of participants, is publicly available at [https://github.com/joebrew/malaria_survey](https://github.com/joebrew/malaria_survey).
+
+Qualitative analysis of free text comments was carried out using thematic content analysis, with inductive open coding [@Markey_2014].
 Participants were invited to provide "any general comments on the timeline and likelihood of global eradication".
@@
 Finally, free-text comments were scored for overall sentiment polarity [@sentimentr2017].
-
-Quantitative analysis was carried out in R language [@R].
-Ordinary least squares regression was employed to estimate the effect of area of expertise on the eradication pessimism-optimism (through the proxy of perceived years to eradication).
-De-biasing of sample selection was carried out using Heckman's 2 step approach as implemented by Toomet [@toomet2008].
-All analysis code, as well as the code used for the identification and contacting of participants, is publicly available at [https://github.com/joebrew/malaria_survey](https://github.com/joebrew/malaria_survey).
 
@@
 A total of `r length(which(df$responded))` researchers participated in the survey from the `r nrow(df)` invitations sent (participation rate of `r round(length(which(df$responded)) / nrow(df) * 100, 2)`%).
-Areas of expertise were non-exclusive and self-described, with participants having the option to choose from up to 3 of 10 checkboxes\footnote{Responses categories were Anthropology, Biochemistry, Bioinformatics, Biology, Chemistry, Clinical medicine, Drug discovery, Ecology, Economics, Entomology, Epidemiology, Geography, GIS, History, Immunology, Infectious disease, IT, Malaria, Medical entomology, Medicinal chemistry, Microbiology, Parasitology, Pharmacology, Pharmacy, Political science, Public health, Statistics, Vector biology, Vector control, and Virology.}, or to write in one or more "other" areas of expertise.
-`r sum(x$n[1:3])` (`r round(sum(x$p[1:3]), digits = 1)`%) participants declared three or fewer areas of expertise.
+Areas of expertise were non-exclusive and self-described, with participants having the option to choose from up to 3 of 10 checkboxes, or to write in one or more "other" areas of expertise.\footnote{Response categories were Anthropology, Biochemistry, Bioinformatics, Biology, Chemistry, Clinical medicine, Drug discovery, Ecology, Economics, Entomology, Epidemiology, Geography, GIS, History, Immunology, Infectious disease, IT, Malaria, Medical entomology, Medicinal chemistry, Microbiology, Parasitology, Pharmacology, Pharmacy, Political science, Public health, Statistics, Vector biology, Vector control, and Virology.} `r sum(x$n[1:3])` (`r round(sum(x$p[1:3]), digits = 1)`%) participants declared three or fewer areas of expertise.
 
@@
 Importantly, the average number of total author-specific citations was `r round(mean(df$n_citations_total[df$responded]), digits = 2)` among respondents, but `r round(mean(df$n_citations_total[!df$responded]), digits = 2)` among non-respondents.
-This suggests either a tendency for more senior or more cited researchers not to respond.
-When examining the number of average citations per article, the difference between respondents and non-respondents was slightly less: `r round(median(df$n_citations_total[df$responded]), digits = 2)` among respondents, and `r round(median(df$n_citations_total[!df$responded]), digits = 2)` among non-respondents.
+This suggests either a tendency for more senior or impactful researchers not to respond.
+When examining the number of average citations per article, the difference between respondents remained: `r round(mean(df$n_citations_average[df$responded]), digits = 2)` among respondents, and `r round(mean(df$n_citations_average[!df$responded]), digits = 2)` among non-respondents, highlighting the greater impact of non-respondents relative to respondents.
 Males responded at a greater rate (`r round(mean(df$responded[df$sex == 'male'], na.rm = T) * 100, digits = 2)`) than females (`r round(mean(df$responded[df$sex == 'female'], na.rm = T) * 100, digits = 2)`) and those with Hispanic last names responded at a greater rate than those with last names of other ethnicities (see table).
@@
 ```
+
+Of the below two sections only one will remain in the paper: either (i) de-biasing using weighted binomial regression or (ii) de-biasing using Heckman.
+
+## De-biasing using weighted binomial regression
+
+```{r}
+# Estimate model for de-biasing sample selection without Heckman.
+response_model <- glm(responded ~ bin_citations + sex, data = df, family = binomial('logit'))
+# Use model to predict likelihood of response
+df$likelihood_of_response <- predict(response_model, df, type = 'response')
+# Use inverse of likelihood of response to assign weight for model
+df$weight <- 1 - df$likelihood_of_response
+```
+
+## De-biasing using Heckman
 
@@
 #   ylim(0, 6)
+
+# a <- data_frame(category = rep(c("Innovation",
+#                                                    "Systemic Challenges",
+#                                                    "Poverty",
+#                                                    "Meta"),2),
+#                 type = rep(c('Prescriptive', 'Descriptive'), each = 4),
+#                 val = c(213,
+#                         25,
+#                         85,
+#                         32,22,
+#                         112,
+#                         70,
+#                         142))
+# a$val <- ifelse(a$type == 'Prescriptive', a$val * -1, a$val)
+# ggplot(data = a,
+#        aes(x = category,
+#            y = val)) +
+#   geom_bar(alpha = 0.5,stat = 'identity', aes(fill = type)) +
+#   coord_flip() +
+#   geom_label(aes(label = abs(val))) +
+#   theme(legend.position = 'bottom') +
+#   scale_fill_manual(name = '',
+#                     values = c('lightblue', 'darkorange')) +
+#   theme_fivethirtyeight() +
+#   ylim(-220, 150) +
+#   labs(title = 'Classification of survey free responses',
+#        subtitle = 'By thematic categorization and diagnostic')
 ```
@@
 1. *Innovation*: comments pertaining to new tools, drugs, methods, or strategies required to achieve eradication.
-2. *Systematic challenges*: comments pertaining to political, social, environmental or logistical issues related to eradication.
-3. *Poverty*: comments specifically related to the economic and socieconomic components of malaria eradication.
-4. *Meta*: challenging the question of eradication itself, re-framing the goal, insisting on other priorities, etc.
+2. *Systemic challenges*: comments pertaining to political, social, environmental or logistical issues related to eradication.
+3. *Complexity*: comments which of focus on the multi-dimensional components of eradication.
+4. *Tackling the fundamentals*: challenging the question of eradication itself, re-framing the goal, insisting on other priorities, etc.
 
@@
 Genetic engineering was mentioned by several commenters as a promising means to achieve eradication quickly.
-Most comments coded as "innovatation" were presciptive in nature, often suggesting the nature of the needed innovation, with a heavy slant towards pharmaceutical options and vaccination.
+Most comments coded as "innovation" were presciptive in nature, often suggesting the nature of the needed innovation, with a heavy slant towards pharmaceutical options and vaccination.
 
-**Systematic challenges** to malaria eradication were noted by the majority of commenters.
+**Systemic challenges** to malaria eradication were noted by the majority of commenters.
+Comments in this category can be divided into roughly four sub-themes: (i) lack of coordination, (ii) lack of good surveillance and health services delivery, (iii) lack of political will and (iv) poverty.
 In direct contrast to the previous comments, many emphasized that "we already have the tools to achieve  eradication" and that the only piece lacking was "robust health systems".
-Many commenters noted problems of coordination:
+Many commenters noted problems of coordination, as illustrated in the below quote.
 
@@
 the problem is politics.
-Malaria doesn't stop in borders of a country and it would take a joint effort of a lot of political leaders to get programs in place to fight malaria.
+Malaria doesn't stop in (sic) borders of a country and it would take a joint effort of a lot of political leaders to get programs in place to fight malaria.
 Unfortunately I don't see this happening anytime soon.
@@
 Others echoed the sentiment, with many comments focusing on the need of strong surveillance and treatment delivery systems.
-Many commenters focused on the reasons for stagnating progress, such as "weak or failing health systems...due to political unwillingness or conflict".
-Others highlighted the inherent challenges in the epidemiology of malaria, such as the changing dynamics of malaria transmission, the resilience of the parasite and vector, climate change, and the inability to aim interventions accurately with an "ever-moving target".
-Comments coded as "systematic" tended to be descriptive and slightly more pessimistic than others.
-
-**Poverty** was assigned its own category in the codification of free text responses - although it is best understood as a sub-category of "systemtatic challenges" - because of its ubiquity as a theme in comments.
+Many commenters focused on other reasons for stagnating progress, such as "weak or failing health systems...due to political unwillingness or conflict".
+Comments coded as "systemic" tended to be descriptive and slightly more pessimistic than others.
 Many noted that malaria is a "disease of poverty", with "social injustice" as the root cause.
@@
 Many echoed the sentiment, stating that "with no economic development, you cannot have eradication" and that poverty is the "cause" of malaria.
-As with the "systematic challenges" of eradication, comments which were coded as poverty tended to be descriptive rather than prescriptive.
+As with the "systemic challenges" of eradication, comments which were coded as poverty tended to be descriptive rather than prescriptive.
 
-**Meta** arguments were rarer than the other categories, but cohesive and consistent.
-One commenter wrote that eradication is a "postwar" idea that developed from the "abandonment of a broad sociopolitical understanding of the causes of disease, and the emphasis on technological solutions." Many stated that global malaria eradication was simply not possible, and 2 argued that it may not be desirable or ethical.
+**Complexity** was a relatively rare category (<20\% of all comments), those whose comments were coded as the "complexity" category were slightly more pessimistic than average in regards to the timeline and likelihood of eradication.
+Many commenters highlighted the inherent challenges in the epidemiology of malaria, such as the changing dynamics of malaria transmission, the resilience of the parasite and vector, climate change, and the inability to aim interventions accurately with an "ever-moving target".
+The potential for adaptation was highlighted in reference both to the mosquito as well as the parasite itself.
+Many comments addressed the fact that the conversation on eradication is largely taking place within the public health community, whereas the causes of malaria endemicity are largely orthogonal to public health interventions, "going beyond the health sector".
+Several commenters pointed out the multitude of prerequisite conditions for eradication to even be considered feasible:
+
+\begin{quote}
+To my mind, this question is highly dependent on background context, e.g.
+global political and economic dynamics, as well as international conflict.
+Complete global eradication is an extremely singular goal that requires a vast array of necessary conditions - if any of these fail, eradication will not be achieved.
+\end{quote}
+
+**Tackling the fundamentals** was rarer than the other categories, but cohesive and consistent.
+One commenter wrote that eradication is a "postwar" idea that developed from the "abandonment of a broad sociopolitical understanding of the causes of disease, and the emphasis on technological solutions." Many stated that global malaria eradication was simply not possible, and two argued that it may not be desirable or ethical.
 One stated that the concept was "absurd" and that "I'm not even sure why people talk about it".
@@
 
-Though results are not disclosed at the individual level, this survey was not entirely anonymous, suggesting that social desirability bias may have influenced responses, and that selection bias likely meant our pool of participants were substantially different from those who choose not to participate.
-
 We made no distinguishment between quality of research, years of experience, academic achievements, geographical area, etc.
@@
 Though certainly a group with important knowledge related to malaria, this misses malaria control program employees, health agency workers, and other stakeholders.
-Their experiences and viewpoints may be different from those of academicians, and arguably more relevant.
+Their experiences and viewpoints may be different from those of academics, and arguably more relevant.
 
@@
 That said, to the extent that researchers' private opinions differ so greatly from those of global health leaders is itself a noteworthy result.
-If leaders' high levels of optimism are well-placed, this suggests that researchers are unduly pessimistic, and efforts should be made to convince them that eradication is more feasible than they realize.
-If, on the other hand, collective wisdom is a better forecasting agent than the proclamations and objectives of global health leaders, then it is important to recognize the sad truth that we are likely further from eradication than we would like to be.
+If leaders' high levels of optimism are well-placed, this suggests that researchers are unduly pessimistic, and efforts should be made to convince them that eradication is more feasible than they realize (so that efforts are directed accordingly).
+If, on the other hand, collective wisdom is a better forecasting agent than the states objectives of global health leaders, then it is important to recognize the sad truth that we are likely further from eradication than we would like to be.
 In this case, though the discourse on eradication can be motivating and inspiring, resources should be directed in a manner that reflects an intended outcome's likelihood of occurrence.
@@
 Our results suggest that eradication is unlikely in the short and medium terms, and that there exists a great deal of disagreement among researchers in regards to which areas require the most attention in order for eradication to occur.
+The causes for pessimism are diverse, but common themes were the need for innovation, systemic challenges, and the complexity of the disease and its transmission, along with a notable share of researchers who question the utility of the eradication concept itself.
 The implication of these results are three-fold: (1) that those working or investing in eradication-specific campaigns should factor in the low likelihood and long time frame when calculating those campaigns' expected value; (2) that champions of near-term eradication need to make a more compelling case to malaria researchers of eradication's feasibility, in order to better focus and inspire the latter; and (3) that discord among malaria researchers as to which areas need the most attention in order for eradication to occur, suggests a need for open discussion and concensus-making, so that resources and focus are directed appropriately.

### 2017-12-27 paper.Rmd
update

@@
 ---
-title: "Silent pessimists: researchers' perceptions of malaria eradication and implications for health spending"
+title: "Silent pessimists: researchers' perceptions of malaria eradication"
 bibliography: library.bib
@@
 
+\newpage
+
+\noindent\fbox{%
+    \parbox{\textwidth}{%
+        Of the below two columns only one will remain in the paper: either (i) de-biasing using weighted binomial regression or (ii) de-biasing using Heckman.
+    }%
+}
+
+\begin{multicols}{2}
+
+\subsection*{De-biasing using weighted binomial regression}
+
+In order to de-bias sample selection, we estimated a binomial logistic regression model for the likelihood of response as a function of sex and (binned) number of citations, and then used the inverse of the selection model's predictions as weights in a simple linear model to adjust our estimates.
+We run weighted model to estimate the likelihood of eradication at 10, 20, 30, 40, and 50 years (employing a separate model for each time period).
+Figure 3 shows the difference in the aggregate perceived likelihood of eradication before and after adjusting for sample selection.
+
+```{r}
+# Estimate model for de-biasing sample selection without Heckman.
+response_model <- glm(responded ~ bin_citations + sex, data = df, family = binomial('logit'))
+# Use model to predict likelihood of response
+df$likelihood_of_response <- predict(response_model, df, type = 'response')
+# Use inverse of likelihood of response to assign weight for model
+df$weight <- 1 - df$likelihood_of_response
+# Run likelihood of eradication models
+for (i in seq(10, 50, 10)){
+  assign(paste0('formula_simple_years_', i),
+         as.formula(paste0('years_',
+                           i,
+                           '_numeric ~ sex + bin_citations')))
+  assign(paste0('simple_', i),
+         lm(get(paste0('formula_simple_years_', i)), data = df))
+  assign(paste0('simple_', i, '_weighted'),
+         lm(get(paste0('formula_simple_years_', i)), data = df,
+            weights = df$weight))
+
+}
+
+# Get aggregate adjusted vs unadjusted likelihoods of eradications
+simple <- data_frame(years = seq(10, 50, 10),
+                     adjusted = NA,
+                     unadjusted = NA)
+for (i in seq(10, 50, 10)){
+   simple$unadjusted[simple$years == i] <- mean(df[,paste0('years_', i, '_numeric')], na.rm = TRUE)
+   simple$adjusted[simple$years == i] <- weighted.mean(x = df[,paste0('years_', i, '_numeric')],
+                                                       w = ifelse(is.na(df$weight), 0,
+                                                                  df$weight), na.rm = TRUE)
+  # simple_model <- get(paste0('simple_', i))
+  # weighted_model <- get(paste0('simple_', i, '_weighted'))
+
+}
+simple <- gather(simple, key, value, adjusted:unadjusted)
+g2 <- ggplot(data = simple,
+       aes(x = years,
+           y = value,
+           color = key,
+           lty = key)) +
+    geom_line(alpha = 0.8) +
+  geom_point(alpha = 0.6) +
+  theme_paper() +
+  labs(x = 'Years',
+       y = 'Likelihood of eradication',
+       subtitle = 'B: Perceived likelihood of eradication: Adjusted and unadjusted') +
+  scale_linetype_manual(name = '', values = 1:2) +
+  scale_color_manual(name = '', values = c('blue', 'darkorange'))
+x <- df %>%
+  group_by(citations = bin_citations) %>%
+  summarise(years_10 = mean(years_10_numeric, na.rm = TRUE),
+            years_20 = mean(years_20_numeric, na.rm = TRUE),
+            years_30 = mean(years_30_numeric, na.rm = TRUE),
+            years_40 = mean(years_40_numeric, na.rm = TRUE),
+            years_50 = mean(years_50_numeric, na.rm = TRUE),
+            n = length(unique(email))) %>%
+  ungroup %>%
+  gather(key, value, years_10:years_50) %>%
+  filter(!is.na(citations))
+
+cols <- colorRampPalette(c('red', 'orange', 'blue') #brewer.pal(n = 9, 'Spectral')
+                         )(length(unique(x$citations)))
+g1 <- ggplot(data = x %>% filter(!is.na(citations)),
+       aes(x = as.numeric(gsub('years_', '', key)),
+           y = value,
+           color = citations,
+           group = citations)) +
+  geom_point(alpha = 0.7) +
+  geom_line(alpha = 0.6) +
+  theme_paper() +
+  scale_color_manual(name = 'Number of citations',
+                     values = cols) +
+  labs(x = 'Years',
+       y = 'Likelihood of eradication',
+       subtitle = 'A: Difference in perceived likelihood of eradication by citations')
+```
+
+```{r, fig.height = 7.5}
+
+Rmisc::multiplot(g1, g2, cols = 1)
+
+# # Combine into a dataframe
+# simple_df <- expand.grid(bin_citations = sort(unique(df$bin_citations)),
+#                          sex = sort(unique(df$sex))) %>%
+#   mutate(simple = NA,
+#          weighted = NA)
+# out_list <- list()
+# counter <- 0
+# for(i in seq(10, 50, 10)){
+#   counter <- counter + 1
+#   this_df <- simple_df %>%
+#     mutate(years = i)
+#   simple_model <- get(paste0('simple_', i))
+#   weighted_model <- get(paste0('simple_', i, '_weighted'))
+#   this_df$simple <- predict(simple_model, this_df)
+#   this_df$weighted <- predict(weighted_model, this_df)
+#   out_list[[counter]] <- this_df
+# }
+# simple_df <- bind_rows(out_list)
+# simple_df <- simple_df %>%
+#   gather(key, value, simple:weighted)
+# # Just aggregate sexes
+# simple_df <- simple_df %>%
+#   group_by(bin_citations, years, key) %>%
+#   summarise(value = mean(value)) %>%
+#   ungroup
+# 
+# ggplot(data = simple_df,
+#        aes(x = years,
+#            y = value,
+#            color = bin_citations)) +
+#   geom_line()
+```
+
+\vfill\null
+\columnbreak
+
+\subsection*{De-biasing using Heckman}
+
+In order to de-bias sample selection, we employed Heckman's two-step correction method.
+Given that sex affected response rate but not response itself, we were able to use sex as an instrumental variable, introducing it in both the selection and response models.
+Our selection models, which estimated the likelihood of survey response as a probit function of sex allowed us to estimate (via the Inverse Mills ratio) an expected error term for our outcome models, in which we quantify the effect of the number of citations on the perceived average likelihood of eradication at 10, 20, 30, 40, and 50 years (employing a separate model for each time period).
+Figure 3 shows the difference in the aggregate perceived likelihood of eradication before and after implementing Heckman's two-step model.
+
 ```{r}
@@
        subtitle = 'A: Difference in perceived likelihood of eradication by citations')
-```
 
-```{r}
 x2 <- 
@@
 
-```{r, fig.cap = 'Sample selection bias and adjustment', fig.height = 3.5}
-Rmisc::multiplot(x1, x2, cols = 2)
+```{r fig.height = 7.5}
+Rmisc::multiplot(x1, x2, cols = 1)
 ```
 
-Of the below two sections only one will remain in the paper: either (i) de-biasing using weighted binomial regression or (ii) de-biasing using Heckman.
+```{r, eval = FALSE}
+# Table 2 shows the Heckman model Heckman estimates for all five models.
 
-## De-biasing using weighted binomial regression
-
-```{r}
-# Estimate model for de-biasing sample selection without Heckman.
-response_model <- glm(responded ~ bin_citations + sex, data = df, family = binomial('logit'))
-# Use model to predict likelihood of response
-df$likelihood_of_response <- predict(response_model, df, type = 'response')
-# Use inverse of likelihood of response to assign weight for model
-df$weight <- 1 - df$likelihood_of_response
-```
-
-## De-biasing using Heckman
-
-In order to de-bias sample selection, we employed Heckman's two-step correction method [@Heckman_1979].
-Given that sex affected response rate but not response itself, we were able to use sex as an instrumental variable, introducing it in both the selection and response models.
-Our selection models, which estimated the likelihood of survey response as a probit function of sex allowed us to estimate (via the Inverse Mills ratio) an expected error term for our outcome models, in which we quantify the effect of the number of citations on the perceived average likelihood of eradication at 10, 20, 30, 40, and 50 years (employing a separate model for each time period).
-Figure 3 shows the difference in the aggregate perceived likelihood of eradication before and after implementing Heckman's two-step model.
-
-Table 2 shows the Heckman model Heckman estimates for all five models.
-
-```{r}
 rn <- names(heck_10$coefficients)
@@
 ```
+
+\end{multicols}
+
+\newpage
 

### 2017-12-28 paper.Rmd
big paper update

@@
 
+Malaria is a parasitic disease transmitted to humans by mosquitoes.
+The _Plasmodium falciparum_ species, transmitted by the female _Anopheles_ mosquito, accounts for a large majority of the 200 million annual cases as well as the half million annual deaths [@White2014] [@World2016].
+Malaria "elimination", the "interruption of all local transmission of the infection in a country or region" [@Tanner2015] is actively being pursued by dozens of countries around the world, leading to a renewed push for "eradication" (the global elmination of malaria) [@Rabinovich_2017].
+
+This is not the first time that eradication has been in the international spotlight.
 The scientific and public health communities have had eradication on their policy agenda since the WHO established the Global Malaria Eradication Program in the 1950s [@Njera2011].
+In 1957, U.S.
+President Dwight Eisenhower told Congress that malaria could be expected to be eradicated in five years.
 Following the failure of the WHO's first attempt, the focus shifted away from global eradication towards local elimination and control strategies.
 In recent years, much of the discourse regarding malaria has shifted back to global eradication [@Roberts2007], with funders, researchers, and public health practitioners rallying to the cause [@Tanner2015].
-The Bill and Melinda Gates Foundation has begun actively promoting eradication as feasible "within a generation" [@Gates2014], and the leadership of the World Health Organization (WHO) has supported this goal, stating the objective of eliminating malaria in 65 new countries from 2015 through 2030 (Figure 1).
+The Bill and Melinda Gates Foundation has begun actively promoting eradication as feasible "within a generation" [@Gates2014], and the leadership of the World Health Organization (WHO) has set similarly ambitious goals, stating the objective of eliminating malaria in 65 new countries from 2015 through 2030 (Figure 1).
 
@@
 
-Even in areas of high endemicity, advances in immunology, parasitology, modeling and vaccinology, along with rapid economic development, have made eradication appear a more feasible goal, even if not possible in the short term [@Snow2015] [@Eckhoff2014].
+Even in areas of high endemicity, advances in immunology, parasitology, modeling and vaccinology, along with rapid economic development, have made eradication appear a more feasible goal, though not possible in the short term [@Snow2015] [@Eckhoff2014].
 From both administrative [@Yamey2004] and scientific [@Alonso2011] points of view, eradication has never before received so much attention, nor appeared so within grasp.
@@
 Most of the current research on expert opinion regarding the feasibility of malaria eradication focuses on the \emph{how} rather than the \emph{if} and the \emph{when} [@Tanner2015].
-The participants in the Malaria Eradication Research Agenda (MalERA) process, in particular, have positioned themselves as thought leaders in the field of guiding research goals and identifying gaps in order for elmination to occur [@Alonso2011].
-Though the MalERA authors firmly state that eradication is \emph{not} feasible given the "current tools and state of knowledge", mentions to the time frame are vague ("within the lifetime of young scientists just embarking on their careers") and no mention is made of the perception of the probability of achieving eradication.
-
-International programes, such as the WHO Global Malaria Programme (GMP), have acknowledged the need "to take an official position on how and under what timeline malaria eradication could be achieved" [@WHO2015].
-Such a position could inform policy, and plays a crucial role in the economic analysis of the expected value of malaria elimination initiatives.
-
-However, no such position has been taken.
-This omission is likely intentional, and certainly understandable, given that MalERA's and the WHO GMP's goals are to guide research and technology in the direction of eradication, and not necessarily address the larger and much more subjective questions of \emph{if} and \emph{when}.
-
-But just how close are we to eradication?
-The objective serves to inspire, rally funder support, motivate researchers, and focus the efforts of public health practitioners.
+The participants in the Malaria Eradication Research Agenda (MalERA) process, in particular, have guided research goals and identified gaps in order for elmination to occur [@Alonso2011].
+Though the MalERA authors firmly state that eradication is \emph{not} feasible given the "current tools and state of knowledge", mentions to the time frame are vague ("within the lifetime of young scientists just embarking on their careers") and no mention is made of the perception of the overall probability of achieving eradication.
+Similarly, international programmes, such as the WHO Global Malaria Programme (GMP), have acknowledged the need "to take an official position on how and under what timeline malaria eradication could be achieved" [@WHO2015].
+Clarity on timeline and likelihood of eradication could inform policy, and plays a crucial role in the economic analysis of the expected value of malaria elimination initiatives.
+But achieving clarity is difficult, given the many complex and interacting variables which affect malaria transmission, research funding, and technological development.
+The question of \emph{how} is complex enough, rendering questions of \emph{if} and \emph{when} even more difficult to answer.
+
+The general objective of eradication serves to inspire, rally funder support, motivate researchers, and focus the efforts of public health practitioners.
 Proponents of disease eradication point to the success of historical and current campaigns (smallpox and polio, respectively), and highlight the benefits in health and wealth to future generations.
@@
 And the “expected value” of an investment in a binary scenario (eradication or not) is a function of the probability of the scenario’s occurrence, and the temporal lag of that occurrence.
-Therefore, knowing the likelihood and time frame of eradication of malaria is essential for making sound investments in health.
-
-## The need for a broad concensus
-
-Patients often ask for a “second opinion”, a request which implicitly recognizes two important truths: (1) that an expert can sometimes be wrong and (2) that the combined opinions of multiple people can better approximate the truth than the opinion of only one.
-As Sir Francis Galton demonstrated in his famous ox-weight experiment [@Wallis2014], averaging the opinions of many can be more accurate than taking the opinion of any single expert, since the biases of diverse viewpoints can be complementary and symbiotic.
-
-Additionally, one could argue that assessing likelihood and time frame of eradication is too important, subjective and complex a task to be left to only powerful individuals or small panels and committees.
-It requires the aggregation of multiple points of view.
+Therefore, estimating the likelihood and time frame of eradication of malaria is essential for making sound investments in health.
+But how can we quantify these values given the great deal of uncertainty surrounding eradication?
+
+Many studies have shown value in expert elicitation as a means to reduce uncertainty and inform decision making [@Morgan_2014].
+But experts can sometimes be mistaken, a fact implicitly recognized when patients request a "second opinion" from another doctor when facing uncertainty.
+Additionally, relying on only a small panel of experts for a problem as complex as malaria exposes one to more bias, just as an overly concentrated investment portfolio exposes one to more risk.
+As Sir Francis Galton demonstrated in his famous study in which he showed that the crowds' aggregated estimates of cow's weight formed a quasi-normal distribution centered around the true weight [@Wallis2014] [@Galton1907Voxpopuli], averaging the perceptions of many can be more accurate than taking the opinion of any single expert, since the biases of diverse viewpoints can be complementary and symbiotic.
+
+Assessing the likelihood and time frame of eradication, therefore, requires the combination of multiple points of view.
 Measuring consensus and discord among disease-specific researchers from a variety of disciplines can serve as a barometer of (informed) opinion, both guiding resources and identifying areas of concern [@Keenan2013].
-
-A great deal of previous research already covers the cost per case prevented [@Sicuri2011] [@Silumbe2015] [@Btto2016 [@IlungaIlunga2014] [@Dalaba2015].
+We propose that the aggregation of malaria researchers' perceptions regarding the time frame andlikelihood of eradication forms a probability distribution which can be used to estimate the expected value of eradication-specific investments.
+
+A great deal of previous research already covers the cost per case prevented [@Sicuri2011] [@Silumbe2015] [@Btto2016] [@IlungaIlunga2014] [@Dalaba2015].
 Likewise, literature exists which could serve as a model for quantifying the location-specific opportunity costs associated with funneling funds towards malaria eradication [@Stuckey2014] [@White2011] [@Korenromp2012].
@@
 
-In other words, the rational assignment of resources for malaria eradication campaigns hinges on the expected value of those campaigns. We can describe this relationship formulaically below:
+In other words, the rational assignment of resources for malaria eradication campaigns hinges on the expected value of those campaigns. We can describe this relationship below:
 
@@
 \item $ m $ is the number of malaria cases
-\item $ x $ is the cut-off for a "successful campaign", ie the portion of eradication achieved
+\item $ x $ is whether eradication has been achievied
 \item $ T $ is the time-frame (to both costs and benefits)
-\item $ P $ is the probability of success
+\item $ P $ is the probability (of eradication)
 \item $ B $ is the benefit of preventing malaria
@@
 
-This study included the corresponding authors of indexed journals.
+This study included the first authors of indexed journals.
 Though certainly a group with important knowledge related to malaria, this misses malaria control program employees, health agency workers, and other stakeholders.
 Their experiences and viewpoints may be different from those of academics, and arguably more relevant.
+Additionally, in public health journals, first authors are often more junior than their collaborators.
+By focusing solely on first authors, we may have unintentionally created a sample which is qualitatively different than the true universe of malaria researchers.
 

### 2017-12-28 paper.Rmd
update

@@
 Many pointed to the failure of the WHO GMP in the 1950s as evidence of the futile nature of eradication programs.
-Many highlighted that talking about "malaria" as one disease misses the mark, since the different species of parasite and contexts in which they live make elimination in each area very distinct from other areas.
-"Meta" comments tended to be skeptical of the feasibility of eradication, or to challenge the  notion that it is a meaningful or useful endeavor.
+Some highlighted that talking about "malaria" as one disease misses the mark, since the different species of parasite and contexts in which they live make elimination in each area very distinct from other areas.
+Comments which "tackled the fundamentals" tended to be skeptical of the feasibility of eradication, or to challenge the  notion that it is a meaningful or useful endeavor.
 Largely, they were prescriptive, advocating for a re-framing of the conversation so that the focus was not on an "arbitrary" goal like eradication, but rather on scaling up control and making region-specific progress.

### 2018-01-02 paper.Rmd
fixed heckman errors

@@
                            i,
-                           '_numeric ~ sex + bin_citations')))
-  assign(paste0('simple_', i),
-         lm(get(paste0('formula_simple_years_', i)), data = df))
+                           '_numeric ~ sex')))
+
+                           # '_numeric ~ sex + bin_citations')))
+  # assign(paste0('simple_', i),
+  #        lm(get(paste0('formula_simple_years_', i)), data = df))
   assign(paste0('simple_', i, '_weighted'),
@@
                      unadjusted = NA)
+simple$unadjusted <- heckman$value[heckman$key == 'Unadjusted']
 for (i in seq(10, 50, 10)){
-   simple$unadjusted[simple$years == i] <- mean(df[,paste0('years_', i, '_numeric')], na.rm = TRUE)
+   # simple$unadjusted[simple$years == i] <- mean(df[,paste0('years_', i, '_numeric')], na.rm = TRUE)
    simple$adjusted[simple$years == i] <- weighted.mean(x = df[,paste0('years_', i, '_numeric')],
@@
   geom_point(alpha = 0.6) +
-  theme_paper() +
+  theme_paper(base_size = 13) +
   labs(x = 'Years',
@@
   geom_line(alpha = 0.6) +
-  theme_paper() +
+  theme_paper(base_size = 13) +
   scale_color_manual(name = 'Number of citations',
@@
 ```
+
+\vfill\null
 
@@
 
-\vfill\null
 \columnbreak

### 2018-01-02 paper.Rmd
done with elisa revisions

@@
 ---
-title: "Silent pessimists: researchers' perceptions of malaria eradication"
+title: "Researchers' perceptions of malaria eradication: findings from a mixed-methods analysis of a large survey"
 bibliography: library.bib
@@
 The opportunity cost of investments in eradication-specific interventions can be high, particularly in contexts with other urgent health priorities.
-In a systemic survey of malaria researchers, we query perceptions regarding the likelihood and time frame of eradication, as well as the perceived chief areas needed for improvement in order for eradication to be achieved.
+In a large survey of malaria researchers (n = 844), we query perceptions regarding the likelihood and time frame of eradication, as well as the perceived chief areas needed for improvement in order for eradication to be achieved.
 We assess pessimism/optimism (via the proxy of years-to-eradication), broken down by area of expertise, and adjust for selection bias.
+We also carry out a qualitative analysis of free-form comments provided by 61\% of respondents.
 Our results show a disconnect between optimistic public institutional discourse and pessimistic private opinion, suggesting either (a) the necessity of a realistic accounting of eradication's low short-term likelihood in health planning and financing, or (b) the need for a more compelling case regarding eradication's feasibility to be made to the research community.
@@
 \end{center}
+
+\noindent\fbox{%
+    \parbox{\textwidth}{%
+        \subsection*{Research Highlights}
+        \begin{itemize}
+          \item Makes novel use of a "wisdom of crowds" approach
+          \item Assesses perceived time frame and likelihood of global malaria eradication among researchers
+          \item Identifies challenges pertaining to eradication through qualitative analysis
+          \item Highlights the gap between researchers' collective pessimism and institutional optimism
+        \end{itemize}
+      \subsection*{Keywords}
+        Malaria, eradication, elimination, mixed methods, survey, crowdsourcing 
+    }%
+}
 
@@
 In recent years, much of the discourse regarding malaria has shifted back to global eradication [@Roberts2007], with funders, researchers, and public health practitioners rallying to the cause [@Tanner2015].
-The Bill and Melinda Gates Foundation has begun actively promoting eradication as feasible "within a generation" [@Gates2014], and the leadership of the World Health Organization (WHO) has set similarly ambitious goals, stating the objective of eliminating malaria in 65 new countries from 2015 through 2030 (Figure 1).
+The Bill and Melinda Gates Foundation has begun actively promoting eradication as feasible "within a generation" [@Gates2014], and the World Health Organization (WHO) has set ambitious goals, stating the objective of eliminating malaria in 65 new endemic countries from 2015 through 2030 (Figure 1).
 
@@
 Most of the current research on expert opinion regarding the feasibility of malaria eradication focuses on the \emph{how} rather than the \emph{if} and the \emph{when} [@Tanner2015].
-The participants in the Malaria Eradication Research Agenda (MalERA) process, in particular, have guided research goals and identified gaps in order for elmination to occur [@Alonso2011].
-Though the MalERA authors firmly state that eradication is \emph{not} feasible given the "current tools and state of knowledge", mentions to the time frame are vague ("within the lifetime of young scientists just embarking on their careers") and no mention is made of the perception of the overall probability of achieving eradication.
-Similarly, international programmes, such as the WHO Global Malaria Programme (GMP), have acknowledged the need "to take an official position on how and under what timeline malaria eradication could be achieved" [@WHO2015].
+The participants in the Malaria Eradication Research Agenda (MalERA) process, in particular, have guided research goals and identified gaps in order for elmination to occur [@Alonso2011] [@Rabinovich_2017].
+Though the MalERA authors firmly state that eradication is \emph{not} feasible given the "current tools and state of knowledge", mentions to the time frame are vague ("within the lifetime of young scientists just embarking on their careers" [@Alonso2011] and "in the longer term" [@Rabinovich_2017]) and no mention is made of the perception of the overall probability of achieving eradication.
+International programmes, such as the WHO Global Malaria Programme (GMP), have acknowledged the need "to take an official position on how and under what timeline malaria eradication could be achieved" [@WHO2015].
 Clarity on timeline and likelihood of eradication could inform policy, and plays a crucial role in the economic analysis of the expected value of malaria elimination initiatives.
@@
 
-```{r}
-x <- df %>%
-  filter(responded) %>%
-  group_by(n_areas) %>%
-  tally %>%
-  mutate(p = n / sum(n, na.rm = TRUE) * 100)
-```
-
-A total of `r length(which(df$responded))` researchers participated in the survey from the `r nrow(df)` invitations sent (participation rate of `r round(length(which(df$responded)) / nrow(df) * 100, 2)`%).
-Areas of expertise were non-exclusive and self-described, with participants having the option to choose from up to 3 of 10 checkboxes, or to write in one or more "other" areas of expertise.\footnote{Response categories were Anthropology, Biochemistry, Bioinformatics, Biology, Chemistry, Clinical medicine, Drug discovery, Ecology, Economics, Entomology, Epidemiology, Geography, GIS, History, Immunology, Infectious disease, IT, Malaria, Medical entomology, Medicinal chemistry, Microbiology, Parasitology, Pharmacology, Pharmacy, Political science, Public health, Statistics, Vector biology, Vector control, and Virology.} `r sum(x$n[1:3])` (`r round(sum(x$p[1:3]), digits = 1)`%) participants declared three or fewer areas of expertise.
-
-```{r}
-temp <- areas_df %>%
-  arrange(desc(count))
-temp$area <- trimws(temp$area, which = 'both')
-names(temp) <- c('Area', 'Researchers')
-temp$Area <- as.character(temp$Area)
-temp$Area <- Hmisc::capitalize(temp$Area)
-temp$Area[temp$Area == 'It'] <- 'Information Technology'
-# kable(temp[1:10,]) #%>%
-  # kableExtra::kable_styling(#position = "float_right",
-  #                           font_size = 7)
-```
-
-Participants had a total of `r length(old_areas)` unique (self-described) areas of expertise.
-The five most popular were `r paste0(paste0(temp$Area[1:5], ' (', temp$Researchers[1:5], ')'), collapse = ', ')`.
-
-Participants were asked to quantify (as a percentage) the likelihood of eradication in the next 10, 20, 30, 40, and 50 years.
-Most participants saw eradication as extremely unlikely in the next 10-30 years, but increasingly likely thereafter.
-Figure 2 shows the distribution of year-specific likelihood perceptions (panels A-E), as well as an illustration of how both likelihood and uncertainty grow over time (panel F).
-
-```{r, fig.cap='Perceptions of likelihood of eradication', fig.height = 4.5}
+```{r, fig.cap='Perceptions of likelihood of eradication', fig.height = 4}
 # Define function for analyzing the years_n columns
@@
 
+```{r}
+x <- df %>%
+  filter(responded) %>%
+  group_by(n_areas) %>%
+  tally %>%
+  mutate(p = n / sum(n, na.rm = TRUE) * 100)
+```
+
+A total of `r length(which(df$responded))` researchers participated in the survey from the `r nrow(df)` invitations sent (participation rate of `r round(length(which(df$responded)) / nrow(df) * 100, 2)`%).
+Areas of expertise were non-exclusive and self-described, with participants having the option to choose from up to 3 of 10 checkboxes, or to write in one or more "other" areas of expertise.\footnote{Response categories were Anthropology, Biochemistry, Bioinformatics, Biology, Chemistry, Clinical medicine, Drug discovery, Ecology, Economics, Entomology, Epidemiology, Geography, GIS, History, Immunology, Infectious disease, IT, Malaria, Medical entomology, Medicinal chemistry, Microbiology, Parasitology, Pharmacology, Pharmacy, Political science, Public health, Statistics, Vector biology, Vector control, and Virology.} `r sum(x$n[1:3])` (`r round(sum(x$p[1:3]), digits = 1)`%) participants declared three or fewer areas of expertise.
+
+```{r}
+temp <- areas_df %>%
+  arrange(desc(count))
+temp$area <- trimws(temp$area, which = 'both')
+names(temp) <- c('Area', 'Researchers')
+temp$Area <- as.character(temp$Area)
+temp$Area <- Hmisc::capitalize(temp$Area)
+temp$Area[temp$Area == 'It'] <- 'Information Technology'
+# kable(temp[1:10,]) #%>%
+  # kableExtra::kable_styling(#position = "float_right",
+  #                           font_size = 7)
+```
+
+Participants had a total of `r length(old_areas)` unique (self-described) areas of expertise.
+The five most popular were `r paste0(paste0(temp$Area[1:5], ' (', temp$Researchers[1:5], ')'), collapse = ', ')`.
+
+Participants were asked to quantify (as a percentage) the likelihood of eradication in the next 10, 20, 30, 40, and 50 years.
+Most participants saw eradication as extremely unlikely in the next 10-30 years, but increasingly likely thereafter.
+Figure 2 shows the distribution of year-specific likelihood perceptions (panels A-E), as well as an illustration of how both likelihood and uncertainty grow over time (panel F).
+
 Participants were asked to provide the number of years they believe it will take until eradication can be achieved.
@@
        y = 'Likelihood of eradication',
-       subtitle = 'A: Difference in perceived likelihood of eradication by citations')
+       subtitle = 'A: Perceived likelihood of eradication by citations')
 ```
@@
        y = 'Likelihood of eradication',
-       subtitle = 'A: Difference in perceived likelihood of eradication by citations')
+       subtitle = 'A: Perceived likelihood of eradication by citations')
 
@@
 
+# # Alternative - median instead of mean
+# alt <- data.frame(area = small_areas,
+#                   med = NA,
+#                   lwr = NA,
+#                   upr = NA)
+# for(i in 1:nrow(alt)){
+#   message(i)
+#   the_area <- alt$area[i]
+#   the_area <- gsub(' ', '_', the_area)
+#   the_column <- df[,paste0('area_', the_area)] * 100
+#   alt$med[i] <- median(the_column, na.rm = TRUE)
+#   alt$lwr[i] <- quantile(the_column, 0.25, na.rm = TRUE)
+#   alt$upr[i] <- median(the_column, 0.75, na.rm = TRUE)
+# }
+# ggplot(data = alt,
+#        aes(x = area,
+#            y = med)) +
+#   geom_bar(stat = 'identity', fill = 'darkorange') +
+#   geom_linerange(aes(ymin = lwr,
+#                      ymax = upr)) +
+#   theme_paper()
 ```
@@
 Of the `r length(which(df$responded))` who responded to the survey, `r length(which(!is.na(df$comments)))` (`r round(length(which(!is.na(df$comments))) / length(which(df$responded)) * 100, digits = 2)`%) provided a comment.
-Relative to non-commenters, commenters were slightly more optimistic on average, but also slightly more polarized in opinion.
+Relative to non-commenters, commenters were more optimistic on average, but also more polarized in opinion.
 The four subject themes identified through iterative, open coding were:
@@
 Comments were also classified as descriptive or prescriptive.
-A slight majority (`r round(320 / 540 * 100, digits = 2)`%) were descriptive.
-Descriptive commenters were slightly more pessimistic (in regards to perceived years until eradication) than prescriptive commenters, though this difference did not reach the level of statistical significance (p = 0.21).
-Descriptive comments also received sentiment polarity scores which were slightly more negative than prescriptive comments, although again this difference did not reach the level of statistical significance (p = 0.18).
+A majority (`r round(320 / 540 * 100, digits = 2)`%) were descriptive.
+Descriptive commenters were more pessimistic (in regards to perceived years until eradication) than prescriptive commenters, though this difference did not reach the level of statistical significance (p = 0.21).
+Descriptive comments also received sentiment polarity scores which were more negative than prescriptive comments, although again this difference did not reach the level of statistical significance (p = 0.18).
 
@@
 Many commenters focused on other reasons for stagnating progress, such as "weak or failing health systems...due to political unwillingness or conflict".
-Comments coded as "systemic" tended to be descriptive and slightly more pessimistic than others.
+Comments coded as "systemic" tended to be descriptive and more pessimistic than others.
 Many noted that malaria is a "disease of poverty", with "social injustice" as the root cause.
@@
 
-**Complexity** was a relatively rare category (<20\% of all comments), those whose comments were coded as the "complexity" category were slightly more pessimistic than average in regards to the timeline and likelihood of eradication.
+**Complexity** was a relatively rare category (<20\% of all comments), those whose comments were coded as the "complexity" category were more pessimistic than average in regards to the timeline and likelihood of eradication.
 Many commenters highlighted the inherent challenges in the epidemiology of malaria, such as the changing dynamics of malaria transmission, the resilience of the parasite and vector, climate change, and the inability to aim interventions accurately with an "ever-moving target".
@@
 Approximately three-quarters of respondents believe that malaria will not be eradicated in the next 50 years; in other words, assuming our pool of respondents is of typical post-PhD age, most believe they will not live to see eradication.
+When adjusted for selection bias, the perceived likelihood of eradication 50 years from now remains similarly low, but estimates for shorter-term eradication are even lower.
 
 If we take the pooled opinions of researchers, as revealed through this survey, as the best approximation of truth available, then the disconnect between public discourse on malaria eradication and private opinion is troubling.
-It suggests that the goals set by the Bill and Melinda Gates Foundation (eradication "within a generation") and the WHO GMP (eradication "within the lifetime of young scientists just embarking on their careers") are unrealistic at best, and misleading at worst.
 This has important implications for spending in public health, since the attention and resources of funders, researchers and government agencies are directed to those areas where a result is expected.
 
+In regards to differences by academic discipline, it is important to note that diversity within disciplines was greater than diversity between them.
+That said, one might surmise as to why disciplines at the extremes differed.
+Chemists, on average, reported that eradication will be achieved in less than 40 years, whereas economists thought it would take a full ten years more.
+The collective optimism in the field of chemistry may be attributable to recent advances in drug development and insecticides, whereas economists may be more pessimistic due to concerns such as free-riding when it comes to global public goods [@barrett] [@Bodansky_2012].
+This study was not designed to generate inference regarding reasons why disciplines might differ in perception, but it does suggest further lines of research.
+
 ## Limitations
@@
 There are many reasons to be skeptical that the combined "wisdom of crowds" of malaria researchers is a reliable indicator of truth.
-First, academic researchers are specialists - their narrow, field-specific view of eradication's feasibility is arguably less reliable than the more "global" views of the WHO, or Bill Gates.
-Second, a number of biases may come into play in this study.
+First, academic researchers are specialists - their narrow, field-specific view of eradication's feasibility is arguably less reliable than the more "global" views of large institutions.
+Though crowds have been found to be more "wise" than individuals in many cases, the application of a wisdom of crowds approach is not suitable to all classes of problems [@Mannes_2014].
+Crowds can be susceptible to social biases [@Lorenz_2011] (although this survey's anonimity largely protects against this issue), and other biases may come in to play, especially given that our study was of a crowd of "specialists", rather than the population as a whole.
 

### 2018-01-30 paper.Rmd
removing heckman, paper about ready to submit

@@
 Ordinary least squares regression was employed to estimate the effect of area of expertise on the eradication pessimism-optimism (through the proxy of perceived years to eradication).
-De-biasing of sample selection was carried out using Heckman's 2 step approach as implemented by Toomet [@toomet2008].
 All analysis code, as well as the code used for the identification and contacting of participants, is publicly available at [https://github.com/joebrew/malaria_survey](https://github.com/joebrew/malaria_survey).
@@
 
-\newpage
-
-\noindent\fbox{%
-    \parbox{\textwidth}{%
-        Of the below two columns only one will remain in the paper: either (i) de-biasing using weighted binomial regression or (ii) de-biasing using Heckman.
-    }%
-}
-
-\begin{multicols}{2}
-
-\subsection*{De-biasing using weighted binomial regression}
-
-In order to de-bias sample selection, we estimated a binomial logistic regression model for the likelihood of response as a function of sex and (binned) number of citations, and then used the inverse of the selection model's predictions as weights in a simple linear model to adjust our estimates.
+\subsection*{De-biasing sample selection}
+
+In order to de-bias sample selection, we employed Heckman's two-step correction method as well a more simple binomial logistic regression model to estimate the likelihood of response as a function of sex and (binned) number of citations.
+To the extent that the two methods presented nearly identical value, we present here the results of latter.
+Having estimated the odds of survey participation, we then used the inverse of the selection model's predictions as weights in a simple linear model to adjust our estimates.
 We run weighted model to estimate the likelihood of eradication at 10, 20, 30, 40, and 50 years (employing a separate model for each time period).
-Figure 3 shows the difference in the aggregate perceived likelihood of eradication before and after adjusting for sample selection.
+Figure 3 shows both the aggregated perceived likelihood of eradication over time by number of publications (panel A) as well as the difference in the aggregate perceived likelihood of eradication for the entire sample before and after adjusting for sample selection (panel B).
 
@@
   labs(x = 'Years',
-       y = 'Likelihood of eradication',
-       subtitle = 'B: Perceived likelihood of eradication: Adjusted and unadjusted') +
+       y = 'Likelihood',
+       subtitle = 'Panel B') +
   scale_linetype_manual(name = '', values = 1:2) +
@@
   theme_paper(base_size = 13) +
-  scale_color_manual(name = 'Number of citations',
+  scale_color_manual(name = 'N° citations',
                      values = cols) +
   labs(x = 'Years',
-       y = 'Likelihood of eradication',
-       subtitle = 'A: Perceived likelihood of eradication by citations')
-```
-
-\vfill\null
-
-```{r, fig.height = 7.5}
-
-Rmisc::multiplot(g1, g2, cols = 1)
-
-# # Combine into a dataframe
-# simple_df <- expand.grid(bin_citations = sort(unique(df$bin_citations)),
-#                          sex = sort(unique(df$sex))) %>%
-#   mutate(simple = NA,
-#          weighted = NA)
-# out_list <- list()
-# counter <- 0
-# for(i in seq(10, 50, 10)){
-#   counter <- counter + 1
-#   this_df <- simple_df %>%
-#     mutate(years = i)
-#   simple_model <- get(paste0('simple_', i))
-#   weighted_model <- get(paste0('simple_', i, '_weighted'))
-#   this_df$simple <- predict(simple_model, this_df)
-#   this_df$weighted <- predict(weighted_model, this_df)
-#   out_list[[counter]] <- this_df
-# }
-# simple_df <- bind_rows(out_list)
-# simple_df <- simple_df %>%
-#   gather(key, value, simple:weighted)
-# # Just aggregate sexes
-# simple_df <- simple_df %>%
-#   group_by(bin_citations, years, key) %>%
-#   summarise(value = mean(value)) %>%
-#   ungroup
-# 
-# ggplot(data = simple_df,
-#        aes(x = years,
-#            y = value,
-#            color = bin_citations)) +
-#   geom_line()
-```
-
-\columnbreak
-
-\subsection*{De-biasing using Heckman}
-
-In order to de-bias sample selection, we employed Heckman's two-step correction method.
-Given that sex affected response rate but not response itself, we were able to use sex as an instrumental variable, introducing it in both the selection and response models.
-Our selection models, which estimated the likelihood of survey response as a probit function of sex allowed us to estimate (via the Inverse Mills ratio) an expected error term for our outcome models, in which we quantify the effect of the number of citations on the perceived average likelihood of eradication at 10, 20, 30, 40, and 50 years (employing a separate model for each time period).
-Figure 3 shows the difference in the aggregate perceived likelihood of eradication before and after implementing Heckman's two-step model.
-
-```{r}
-x <- df %>%
-  group_by(citations = bin_citations) %>%
-  summarise(years_10 = mean(years_10_numeric, na.rm = TRUE),
-            years_20 = mean(years_20_numeric, na.rm = TRUE),
-            years_30 = mean(years_30_numeric, na.rm = TRUE),
-            years_40 = mean(years_40_numeric, na.rm = TRUE),
-            years_50 = mean(years_50_numeric, na.rm = TRUE),
-            n = length(unique(email))) %>%
-  ungroup %>%
-  gather(key, value, years_10:years_50) %>%
-  filter(!is.na(citations))
-
-cols <- colorRampPalette(c('red', 'orange', 'blue') #brewer.pal(n = 9, 'Spectral')
-                         )(length(unique(x$citations)))
-x1 <- ggplot(data = x %>% filter(!is.na(citations)),
-       aes(x = as.numeric(gsub('years_', '', key)),
-           y = value,
-           color = citations,
-           group = citations)) +
-  geom_point(alpha = 0.7) +
-  geom_line(alpha = 0.6) +
-  theme_paper(base_size = 13) +
-  scale_color_manual(name = 'Number of citations',
-                     values = cols) +
-  labs(x = 'Years',
-       y = 'Likelihood of eradication',
-       subtitle = 'A: Perceived likelihood of eradication by citations')
-
-x2 <- 
-  ggplot(data = heckman,
-       aes(x = years,
-           y = value,
-           color = key,
-           lty = key)) +
-  geom_line(alpha = 0.8) +
-  geom_point(alpha = 0.6) +
-  theme_paper(base_size = 13) +
-  labs(x = 'Years',
-       y = 'Likelihood of eradication',
-       subtitle = 'B: Perceived likelihood of eradication: Heckman method and unadjusted') +
-  scale_linetype_manual(name = '', values = 1:2) +
-  scale_color_manual(name = '', values = c('blue', 'darkorange'))
-```
-
-\vfill\null
-
-```{r fig.height = 7.5}
-Rmisc::multiplot(x1, x2, cols = 1)
-```
-
-```{r, eval = FALSE}
-# Table 2 shows the Heckman model Heckman estimates for all five models.
-
-rn <- names(heck_10$coefficients)
-heck <- data_frame(Coefficient = rn,
-                   `Model 10` = heck_10$coefficients,
-                   `Model 20` = heck_20$coefficients,
-                   `Model 30` = heck_30$coefficients,
-                   `Model 40` = heck_40$coefficients,
-                   `Model 50` = heck_50$coefficients)
-for (j in 2:ncol(heck)){
-  heck[,j] <- round(heck[,j], digits = 3)
-}
-heck$Coefficient <- gsub('bin_citations', 'Citations ', heck$Coefficient)
-heck$Coefficient <- gsub('invMillsRatio', 'Inverse Mills Ratio', heck$Coefficient)
-heck$Coefficient <- gsub('sigma', 'Sigma', heck$Coefficient)
-heck$Coefficient <- gsub('rho', 'Rho', heck$Coefficient)
-heck$Coefficient <- gsub('sexmale', 'Sex male', heck$Coefficient)
-heck$Coefficient <- paste0(c(rep('Selection ', 4), rep('Outcome ', 2), rep('', 3)), heck$Coefficient)
-knitr::kable(heck,
-             caption = 'Heckman selection model coefficients')
-```
-
-\end{multicols}
-
-\newpage
+       y = 'Likelihood',
+       subtitle = 'Panel A')
+```
+
+```{r, fig.height = 3.5, fig.cap = '(A) Average perceived likelihood of eradication over time by number of author publications; (B) Aggregated perceived likelihood of eradication over time, adjusted for sample selection and unadjusted.'}
+Rmisc::multiplot(g1, g2, cols = 2)
+```
 
@@
 Relative to non-commenters, commenters were more optimistic on average, but also more polarized in opinion.
-The four subject themes identified through iterative, open coding were:
-
-1. *Innovation*: comments pertaining to new tools, drugs, methods, or strategies required to achieve eradication.
-2. *Systemic challenges*: comments pertaining to political, social, environmental or logistical issues related to eradication.
+The three subject themes identified through iterative, open coding were:
+
+1. *Solutions*: Comments pertaining to the innovations required to achieve eradication, priorities, and the desirability of certain approaches.
+
+2. *Systematic challenges*: comments pertaining to political, social, environmental or logistical issues related to eradication.
+
 3. *Complexity*: comments which of focus on the multi-dimensional components of eradication.
-4. *Tackling the fundamentals*: challenging the question of eradication itself, re-framing the goal, insisting on other priorities, etc.
 
@@
 
-In regards to **innovation**, comments largely pertained to the necessity of further technological advances.
+In regards to **solutions**, comments largely pertained to the necessity of further technological advances and innovations.
 One participant wrote that "currently available technology can't achieve [eradication], even if delivered optimally"; another argued that eradication could not be achieved without a "game-changing innovation", whereas multiple others referred to the need for "transformative" technologies:
@@
 Genetic engineering was mentioned by several commenters as a promising means to achieve eradication quickly.
-Most comments coded as "innovation" were presciptive in nature, often suggesting the nature of the needed innovation, with a heavy slant towards pharmaceutical options and vaccination.
+Most comments coded as "solutions" were presciptive in nature, often suggesting the nature of the needed innovation, with a heavy slant towards pharmaceutical options and vaccination.
 
@@
 
-**Tackling the fundamentals** was rarer than the other categories, but cohesive and consistent.
+Many commenters thought that the terms "eradication" and "malaria" were so complex and nebulous that the public health practitioners should avoid the them all together, so as to not repeat the mistakes of the WHO GMP in the 1950s.
+For example, some highlighted that talking about "malaria" as one disease misses the mark, since the different species of parasite and contexts in which they live make elimination in each area very distinct from other areas.
 One commenter wrote that eradication is a "postwar" idea that developed from the "abandonment of a broad sociopolitical understanding of the causes of disease, and the emphasis on technological solutions." Many stated that global malaria eradication was simply not possible, and two argued that it may not be desirable or ethical.
@@
 
-Many pointed to the failure of the WHO GMP in the 1950s as evidence of the futile nature of eradication programs.
-Some highlighted that talking about "malaria" as one disease misses the mark, since the different species of parasite and contexts in which they live make elimination in each area very distinct from other areas.
-Comments which "tackled the fundamentals" tended to be skeptical of the feasibility of eradication, or to challenge the  notion that it is a meaningful or useful endeavor.
+Comments questioning the utility of eradication as a concept or goal tended to be skeptical of the its feasibility.
 Largely, they were prescriptive, advocating for a re-framing of the conversation so that the focus was not on an "arbitrary" goal like eradication, but rather on scaling up control and making region-specific progress.
@@
 
-There are many reasons to be skeptical that the combined "wisdom of crowds" of malaria researchers is a reliable indicator of truth.
+There are several reasons to be skeptical that the combined "wisdom of crowds" of malaria researchers is a reliable indicator of truth.
 First, academic researchers are specialists - their narrow, field-specific view of eradication's feasibility is arguably less reliable than the more "global" views of large institutions.
@@
 
-We made no distinguishment between quality of research, years of experience, academic achievements, geographical area, etc.
+We made no distinction between quality of research, years of experience, academic achievements, geographical area, etc.
 Our inclusion criteria were simple and rudimentary, allowing us to access many diverse viewpoints, but (perhaps inappropriately) weighting all viewpoints as equal.
@@
 Additionally, in public health journals, first authors are often more junior than their collaborators.
-By focusing solely on first authors, we may have unintentionally created a sample which is qualitatively different than the true universe of malaria researchers.
+By focusing solely on first authors, we may have unintentionally created a sample which is qualitatively different than the true universe of malaria researchers; to the extent that in our result pool researchers with less experience (as represented through publications) tended to be more "optimistic" regarding eradication, it is reasonable to assume that the restriction of first authors may have lead to an overly optimistic sample, making the results of the survey even more striking.
 
@@
 
-Whether the collective "wisdom" of researchers is worth adhering to or not is arguable.
-That said, to the extent that researchers' private opinions differ so greatly from those of global health leaders is itself a noteworthy result.
-If leaders' high levels of optimism are well-placed, this suggests that researchers are unduly pessimistic, and efforts should be made to convince them that eradication is more feasible than they realize (so that efforts are directed accordingly).
-If, on the other hand, collective wisdom is a better forecasting agent than the states objectives of global health leaders, then it is important to recognize the sad truth that we are likely further from eradication than we would like to be.
+Our survey attempted to quantify the likelihood of and time frame to malaria eradication by gauging the collective opinion of malaria researchers.
+Our survey shows that the opinions of malaria researchers appear to diverge from those of malaria programme financiers in regards to the feasibility and timeframe of eradication, with researchers expressing more pessism than the institutions and individuals which finance and oversee global eradication efforts.
+The causes for pessimism are diverse, but common themes were the need for innovation, systemic challenges, and the complexity of the disease and its transmissio.
+
+The implication of these results are three-fold: (1) that those working or investing in eradication-specific campaigns should factor in researchers' perceived low likelihood and long time frame when calculating those campaigns' expected value; (2) that champions of near-term eradication may need to make a more compelling case to malaria researchers of eradication's feasibility, in order to better focus and inspire the latter; and (3) that discord between malaria researchers and institutions regarding eradication suggests a need for open discussion and concensus-making, so that efforts and focus are directed appropriately.
+
+We have strived to present the results of our study without insinuation regarding the "true" feasibility and timeframe of eradication, and only time will tell whether the collective "wisdom" of researchers was worth adhering to or not.
+If the research community is unduly pessimistic, efforts should be made to convince them that eradication is more feasible than they realize (so that resources are directed accordingly).
+If, on the other hand, collective wisdom is a better forecasting agent than the stated objectives of global health leaders and institutions, then it is important to recognize the sad truth that we are likely further from eradication than we would like to be.
 In this case, though the discourse on eradication can be motivating and inspiring, resources should be directed in a manner that reflects an intended outcome's likelihood of occurrence.
-
-Our survey attempted to quantify the likelihood of and time frame to malaria eradication by gauging the collective opinion of malaria researchers.
-Our results suggest that eradication is unlikely in the short and medium terms, and that there exists a great deal of disagreement among researchers in regards to which areas require the most attention in order for eradication to occur.
-The causes for pessimism are diverse, but common themes were the need for innovation, systemic challenges, and the complexity of the disease and its transmission, along with a notable share of researchers who question the utility of the eradication concept itself.
-The implication of these results are three-fold: (1) that those working or investing in eradication-specific campaigns should factor in the low likelihood and long time frame when calculating those campaigns' expected value; (2) that champions of near-term eradication need to make a more compelling case to malaria researchers of eradication's feasibility, in order to better focus and inspire the latter; and (3) that discord among malaria researchers as to which areas need the most attention in order for eradication to occur, suggests a need for open discussion and concensus-making, so that resources and focus are directed appropriately.
 

### 2018-02-13 paper.Rmd
adjusting to jacqulines comments

@@
       in_header: preamble.sty
+csl: elsevier-with-titles.csl
 ---
@@
                cache = FALSE,
-               fig.align = 'center')
+               fig.align = 'center',
+               fig.pos = 'h')
 options(xtable.comment = FALSE)
@@
 But experts can sometimes be mistaken, a fact implicitly recognized when patients request a "second opinion" from another doctor when facing uncertainty.
-Additionally, relying on only a small panel of experts for a problem as complex as malaria exposes one to more bias, just as an overly concentrated investment portfolio exposes one to more risk.
+Additionally, relying on only a small panel of experts for a problem as complex as malaria exposes one to bias, just as an overly concentrated investment portfolio exposes one to more risk.
 As Sir Francis Galton demonstrated in his famous study in which he showed that the crowds' aggregated estimates of cow's weight formed a quasi-normal distribution centered around the true weight [@Wallis2014] [@Galton1907Voxpopuli], averaging the perceptions of many can be more accurate than taking the opinion of any single expert, since the biases of diverse viewpoints can be complementary and symbiotic.
@@
 
-The objective of this study is to help guide the optimal distribution of health resources by gauging (expert) opinion about, estimating the likelihood of, and quantifying the time frame to malaria eradication through a systemic survey of malaria research professionals from a wide array of academic disciplines.
+The objective of this study is to gauge (expert) opinion about, estimate the likelihood of, and quantify the potential time frame to malaria eradication through a systemic survey of malaria research professionals from a wide array of academic disciplines.
+In doing so, we aim to help guide the optimal distribution of health resources by informing estimations of the expected value of malaria eradication efforts.
 
@@
 3. Free choice perceived number of years until malaria eradication.
-4. Ranking of the WHO's "health system building blocks" [@manya2017] in regards to attention needed in order to achieve eradication.
-
-The purpose of final point was to introduce a prescriptive element to the researchers' responses (ie, identify potential areas of consensus in regards to the path towards eradication).
+4.
+Ranking of the WHO's "health system building blocks" [@manya2017] in regards to attention needed in order to achieve eradication (the purpose of final point was to introduce a prescriptive element to the researchers' responses, ie, identify potential areas of consensus in regards to the path towards eradication).
 
@@
 government [@Lincoln]; for ethnicity, Khanna et al's bayesian prediction algorithm for the estimation of racial categories [@wru2015] [@Imai_2016] was employed.
-
 The searching and retrieval of information from the PubMed database was carried out using the RISmed package [@Kovalchik2015].
@@
 Finally, free-text comments were scored for overall sentiment polarity [@sentimentr2017].
-
-This research followed the principles of the Declaration of Helsinki. The study's protocol was approved by the Scientific Committee of the Barcelona Institute for Global Health.
 
@@
 
+\subsection*{Quantitative results}
+
 Participants were asked to quantify (as a percentage) the likelihood of eradication in the next 10, 20, 30, 40, and 50 years.
@@
 Importantly, the average number of total author-specific citations was `r round(mean(df$n_citations_total[df$responded]), digits = 2)` among respondents, but `r round(mean(df$n_citations_total[!df$responded]), digits = 2)` among non-respondents.
-This suggests either a tendency for more senior or impactful researchers not to respond.
+This suggests a tendency for more senior or impactful researchers not to respond.
 When examining the number of average citations per article, the difference between respondents remained: `r round(mean(df$n_citations_average[df$responded]), digits = 2)` among respondents, and `r round(mean(df$n_citations_average[!df$responded]), digits = 2)` among non-respondents, highlighting the greater impact of non-respondents relative to respondents.
-Males responded at a greater rate (`r round(mean(df$responded[df$sex == 'male'], na.rm = T) * 100, digits = 2)`) than females (`r round(mean(df$responded[df$sex == 'female'], na.rm = T) * 100, digits = 2)`) and those with Hispanic last names responded at a greater rate than those with last names of other ethnicities (see table).
+Males responded at a greater rate (`r round(mean(df$responded[df$sex == 'male'], na.rm = T) * 100, digits = 2)`) than females (`r round(mean(df$responded[df$sex == 'female'], na.rm = T) * 100, digits = 2)`) and those with Hispanic last names responded at a greater rate than those with last names of other ethnicities (table 1).
 
@@
 
-\subsection*{De-biasing sample selection}
-
-In order to de-bias sample selection, we employed Heckman's two-step correction method as well a more simple binomial logistic regression model to estimate the likelihood of response as a function of sex and (binned) number of citations.
-To the extent that the two methods presented nearly identical value, we present here the results of latter.
+In order to de-bias sample selection, we employed Heckman's two-step correction method as well as simple binomial logistic regression model to estimate the likelihood of response as a function of sex and (binned) number of citations.
+To the extent that the two methods presented nearly identical value, we present here the results of the latter.
 Having estimated the odds of survey participation, we then used the inverse of the selection model's predictions as weights in a simple linear model to adjust our estimates.
-We run weighted model to estimate the likelihood of eradication at 10, 20, 30, 40, and 50 years (employing a separate model for each time period).
+We run a separate weighted model to estimate the likelihood of eradication at 10, 20, 30, 40, and 50 years.
 Figure 3 shows both the aggregated perceived likelihood of eradication over time by number of publications (panel A) as well as the difference in the aggregate perceived likelihood of eradication for the entire sample before and after adjusting for sample selection (panel B).
@@
        y = 'Likelihood',
-       subtitle = 'Panel B') +
+       subtitle = 'B') +
   scale_linetype_manual(name = '', values = 1:2) +
@@
        y = 'Likelihood',
-       subtitle = 'Panel A')
+       subtitle = 'A')
 ```
@@
 
-2. *Systematic challenges*: comments pertaining to political, social, environmental or logistical issues related to eradication.
+2. *Systemic challenges*: comments pertaining to political, social, environmental or logistical issues related to eradication.
 
-3. *Complexity*: comments which of focus on the multi-dimensional components of eradication.
+3. *Complexity*: comments which focus on the multi-dimensional components of eradication.
 
@@
 Many commenters focused on other reasons for stagnating progress, such as "weak or failing health systems...due to political unwillingness or conflict".
-Comments coded as "systemic" tended to be descriptive and more pessimistic than others.
 Many noted that malaria is a "disease of poverty", with "social injustice" as the root cause.
@@
 Many echoed the sentiment, stating that "with no economic development, you cannot have eradication" and that poverty is the "cause" of malaria.
-As with the "systemic challenges" of eradication, comments which were coded as poverty tended to be descriptive rather than prescriptive.
+Comments coded as "systemic" tended to be descriptive and more pessimistic than others.
 
@@
 
-Comments questioning the utility of eradication as a concept or goal tended to be skeptical of the its feasibility.
+Comments questioning the utility of eradication as a concept or goal tended to be skeptical of its feasibility.
 Largely, they were prescriptive, advocating for a re-framing of the conversation so that the focus was not on an "arbitrary" goal like eradication, but rather on scaling up control and making region-specific progress.
@@
 
-Our survey reveals a notable gap between the public discourse on malaria eradication, and those views held (largely privately) by malaria researchers.
 Approximately three-quarters of respondents believe that malaria will not be eradicated in the next 50 years; in other words, assuming our pool of respondents is of typical post-PhD age, most believe they will not live to see eradication.
@@
 
-If we take the pooled opinions of researchers, as revealed through this survey, as the best approximation of truth available, then the disconnect between public discourse on malaria eradication and private opinion is troubling.
-This has important implications for spending in public health, since the attention and resources of funders, researchers and government agencies are directed to those areas where a result is expected.
+If we take the pooled opinions of researchers, as revealed through this survey, as the best approximation of truth available, then the disconnect between public discourse on malaria eradication and private opinion is noteworthy This has important implications for spending in public health, since the attention and resources of funders, researchers and government agencies are directed to those areas where a result is expected.
 
@@
 
-There are several reasons to be skeptical that the combined "wisdom of crowds" of malaria researchers is a reliable indicator of truth.
+There are several reasons to be skeptical that the combined opinions of malaria researchers is a reliable indicator of truth.
 First, academic researchers are specialists - their narrow, field-specific view of eradication's feasibility is arguably less reliable than the more "global" views of large institutions.
@@
 
-Our survey attempted to quantify the likelihood of and time frame to malaria eradication by gauging the collective opinion of malaria researchers.
-Our survey shows that the opinions of malaria researchers appear to diverge from those of malaria programme financiers in regards to the feasibility and timeframe of eradication, with researchers expressing more pessism than the institutions and individuals which finance and oversee global eradication efforts.
-The causes for pessimism are diverse, but common themes were the need for innovation, systemic challenges, and the complexity of the disease and its transmissio.
+Our survey attempted to quantify the likelihood of, and time frame to, malaria eradication by gauging the collective opinion of malaria researchers.
+Our survey shows that the opinions of malaria researchers appear to diverge from those of malaria programme financiers in regards to the feasibility and timeframe of eradication, with researchers expressing more scepticism than the institutions and individuals which finance and oversee global eradication efforts.
+The causes for scepticism are diverse, but common themes were the need for innovation, systemic challenges, and the complexity of the disease and its transmission.
 
@@
 
-We have strived to present the results of our study without insinuation regarding the "true" feasibility and timeframe of eradication, and only time will tell whether the collective "wisdom" of researchers was worth adhering to or not.
-If the research community is unduly pessimistic, efforts should be made to convince them that eradication is more feasible than they realize (so that resources are directed accordingly).
-If, on the other hand, collective wisdom is a better forecasting agent than the stated objectives of global health leaders and institutions, then it is important to recognize the sad truth that we are likely further from eradication than we would like to be.
-In this case, though the discourse on eradication can be motivating and inspiring, resources should be directed in a manner that reflects an intended outcome's likelihood of occurrence.
+We have strived to present the results of our study without insinuation regarding the "true" feasibility and timeframe of eradication, as only time will tell whether the collective "wisdom" of researchers was worth adhering to or not.
+If the research community is unduly sceptical, efforts should be made to convince them that eradication is more feasible than they realize (so that resources are directed accordingly).
+If, on the other hand, collective wisdom of specialists is a better forecasting agent than the stated objectives of global health leaders and institutions, then it is important to recognize the sad truth that we are likely further from eradication than we would like to be.
+In this case, though the discourse on eradication can be motivating and inspiring, resources should be directed in a manner that reflects the intended outcome's likelihood of occurrence.
 

### 2018-03-22 paper.Rmd
checkpoint thursday morning

@@
   pdf_document:
+    keep_tex: true
     latex_engine: xelatex
@@
 The opportunity cost of investments in eradication-specific interventions can be high, particularly in contexts with other urgent health priorities.
-In a large survey of malaria researchers (n = 844), we query perceptions regarding the likelihood and time frame of eradication, as well as the perceived chief areas needed for improvement in order for eradication to be achieved.
+In a large survey of malaria researchers (n = 844), we query perceptions regarding the likelihood and time frame of eradication.
 We assess pessimism/optimism (via the proxy of years-to-eradication), broken down by area of expertise, and adjust for selection bias.
@@
 The general objective of eradication serves to inspire, rally funder support, motivate researchers, and focus the efforts of public health practitioners.
-Proponents of disease eradication point to the success of historical and current campaigns (smallpox and polio, respectively), and highlight the benefits in health and wealth to future generations.
-However, the opportunity cost of investments in eradication-specific interventions can be high.
-And the “expected value” of an investment in a binary scenario (eradication or not) is a function of the probability of the scenario’s occurrence, and the temporal lag of that occurrence.
+Proponents of disease eradication point to the success of historical and current campaigns (smallpox and polio, respectively), and highlight the benefits in health and wealth to future generations (one often cited figure for smallpox was a cost-benefit ratio of more than 400 to 1 [@Barrett_2006]).
+However, the opportunity cost of investments in eradication-specific interventions can be high, and cost savings from malaria elimination have historically been less than those from smallpox [@Cutler_2010].
+Additionally, the “expected value” of an investment in a binary scenario (eradication or not) is a function of the probability of the scenario’s occurrence, and the temporal lag of that occurrence.
 Therefore, estimating the likelihood and time frame of eradication of malaria is essential for making sound investments in health.
@@
 3. Free choice perceived number of years until malaria eradication.
-4.
-Ranking of the WHO's "health system building blocks" [@manya2017] in regards to attention needed in order to achieve eradication (the purpose of final point was to introduce a prescriptive element to the researchers' responses, ie, identify potential areas of consensus in regards to the path towards eradication).
 
@@
 There are several reasons to be skeptical that the combined opinions of malaria researchers is a reliable indicator of truth.
-First, academic researchers are specialists - their narrow, field-specific view of eradication's feasibility is arguably less reliable than the more "global" views of large institutions.
-Though crowds have been found to be more "wise" than individuals in many cases, the application of a wisdom of crowds approach is not suitable to all classes of problems [@Mannes_2014].
+First, academic researchers are specialists - their narrow, field-specific view of eradication's feasibility is of arguable reliability.
+Though crowds have been found to be more "wise" than individuals in many cases, the application of an approach similar to the "wisdom of crowds" is not suitable to all classes of problems [@Mannes_2014].
 Crowds can be susceptible to social biases [@Lorenz_2011] (although this survey's anonimity largely protects against this issue), and other biases may come in to play, especially given that our study was of a crowd of "specialists", rather than the population as a whole.
@@
 (4) Finally, and ironically, "optimism bias" may play a perverse role in researchers' responses; though eradication is certainly a goal desired by all, one could argue that malaria research specialists subconciously realize that they actually stand to lose out profesionally in the case of eradication.
-
-We made no distinction between quality of research, years of experience, academic achievements, geographical area, etc.
-Our inclusion criteria were simple and rudimentary, allowing us to access many diverse viewpoints, but (perhaps inappropriately) weighting all viewpoints as equal.
 
@@
 Our survey attempted to quantify the likelihood of, and time frame to, malaria eradication by gauging the collective opinion of malaria researchers.
-Our survey shows that the opinions of malaria researchers appear to diverge from those of malaria programme financiers in regards to the feasibility and timeframe of eradication, with researchers expressing more scepticism than the institutions and individuals which finance and oversee global eradication efforts.
+Our survey shows that the opinions of malaria researchers appear to diverge from public goals, with researchers expressing hesitance about the likelihood of eradication and suggesting a long time frame.
 The causes for scepticism are diverse, but common themes were the need for innovation, systemic challenges, and the complexity of the disease and its transmission.
@@
 If the research community is unduly sceptical, efforts should be made to convince them that eradication is more feasible than they realize (so that resources are directed accordingly).
-If, on the other hand, collective wisdom of specialists is a better forecasting agent than the stated objectives of global health leaders and institutions, then it is important to recognize the sad truth that we are likely further from eradication than we would like to be.
+If, on the other hand, collective wisdom of specialists is a useful forecasting agent, then it is important to recognize the sad truth that we are likely further from eradication than we would like to be.
 In this case, though the discourse on eradication can be motivating and inspiring, resources should be directed in a manner that reflects the intended outcome's likelihood of occurrence.

### 2018-03-22 paper.Rmd
major update

@@
 ---
-title: "Researchers' perceptions of malaria eradication: findings from a mixed-methods analysis of a large survey"
+title: "Researchers' perceptions of malaria eradication: findings from a mixed-methods analysis of a large online survey"
 bibliography: library.bib
@@
 The opportunity cost of investments in eradication-specific interventions can be high, particularly in contexts with other urgent health priorities.
-In a large survey of malaria researchers (n = 844), we query perceptions regarding the likelihood and time frame of eradication.
+In a large online survey of malaria researchers (n = 844), we query perceptions regarding the likelihood and time frame of eradication.
 We assess pessimism/optimism (via the proxy of years-to-eradication), broken down by area of expertise, and adjust for selection bias.
 We also carry out a qualitative analysis of free-form comments provided by 61\% of respondents.
-Our results show a disconnect between optimistic public institutional discourse and pessimistic private opinion, suggesting either (a) the necessity of a realistic accounting of eradication's low short-term likelihood in health planning and financing, or (b) the need for a more compelling case regarding eradication's feasibility to be made to the research community.
+Our results show that researchers are largely sceptical of the feasibility of near-term malaria eradication, with most believing that eradication will not be achieved for 50 years or more.
 \end{changemargin}
@@
 }
+m
 
@@
 
-Malaria is a parasitic disease transmitted to humans by mosquitoes.
-The _Plasmodium falciparum_ species, transmitted by the female _Anopheles_ mosquito, accounts for a large majority of the 200 million annual cases as well as the half million annual deaths [@White2014] [@World2016].
+Malaria is a parasitic disease transmitted among humans by mosquitoes.
+The _Plasmodium falciparum_ species accounts for a large majority of the 200 million annual cases as well as the half million annual deaths worldwide [@White2014] [@World2016].
 Malaria "elimination", the "interruption of all local transmission of the infection in a country or region" [@Tanner2015] is actively being pursued by dozens of countries around the world, leading to a renewed push for "eradication" (the global elmination of malaria) [@Rabinovich_2017].
@@
 Even in areas of high endemicity, advances in immunology, parasitology, modeling and vaccinology, along with rapid economic development, have made eradication appear a more feasible goal, though not possible in the short term [@Snow2015] [@Eckhoff2014].
-From both administrative [@Yamey2004] and scientific [@Alonso2011] points of view, eradication has never before received so much attention, nor appeared so within grasp.
+From both administrative [@Yamey2004] and scientific [@Alonso2011] points of view, eradication has never before received so much attention.
 
@@
 The general objective of eradication serves to inspire, rally funder support, motivate researchers, and focus the efforts of public health practitioners.
-Proponents of disease eradication point to the success of historical and current campaigns (smallpox and polio, respectively), and highlight the benefits in health and wealth to future generations (one often cited figure for smallpox was a cost-benefit ratio of more than 400 to 1 [@Barrett_2006]).
-However, the opportunity cost of investments in eradication-specific interventions can be high, and cost savings from malaria elimination have historically been less than those from smallpox [@Cutler_2010].
-Additionally, the “expected value” of an investment in a binary scenario (eradication or not) is a function of the probability of the scenario’s occurrence, and the temporal lag of that occurrence.
+Proponents of disease eradication point to the success of historical and current campaigns (smallpox and polio, respectively), and highlight the long term benefits in health and wealth to future generations (one often cited figure for smallpox was a cost-benefit ratio of more than 400 to 1 [@Barrett_2006]).
+However, the opportunity cost of investments in eradication-specific interventions is likely to be high, particularly in contexts of very low resources and many competing health problems.
+Additionally the impact of malaria on economic indicators is heterogeneous, with singificant impact in areas of Sub-Saharan Africa - where the endemicity is high - and little to no impact in areas of low endemicity [@Cutler_2010] [@Barofsky2015].
+Additionally, the “expected value” of an investment in a binary scenario (eradication or not) is a function of the probability of the scenario’s occurrence, the temporal lag of that occurrence, and the uncertainy around both probability of occurrence and temporal lag.
+This uncertainty makes the "risk" of investing in malaria elimination and eradication high.
 Therefore, estimating the likelihood and time frame of eradication of malaria is essential for making sound investments in health.
@@
 
-A great deal of previous research already covers the cost per case prevented [@Sicuri2011] [@Silumbe2015] [@Btto2016] [@IlungaIlunga2014] [@Dalaba2015].
+A great deal of previous research from serveral endemic areas already covers the cost per case prevented [@Sicuri2011] [@Silumbe2015] [@Btto2016] [@IlungaIlunga2014] [@Dalaba2015].
 Likewise, literature exists which could serve as a model for quantifying the location-specific opportunity costs associated with funneling funds towards malaria eradication [@Stuckey2014] [@White2011] [@Korenromp2012].
@@
 
-The economic case for striving to achieve malaria eradication is compelling [@Barofsky2015].
 Though the case-specific marginal cost of eradication can be expected to be high (relative to a simple control approach), successful eradication would mean massive recurring savings in the long-term [@Barrett2013].
@@
 \begin{center}
-$I_{T}$ = $P(x)_{}$ $\dfrac{B(m_{})}{m_{}}$(1 + $\delta$)$^{-T}$ -  $P(x)_{}$ $\dfrac{C(m_{})}{m_{}}$ (1 + $\delta$)$^{-T}$
+$I_{T}$ = $P(x)_{}$ $\dfrac{B(m_{}*p)}{m_{}*p}$(1 + $\delta$)$^{-T}$ -  $P(x)_{}$ $\dfrac{C(m_{}*p)}{m_{}*p}$ (1 + $\delta$)$^{-T}$
 \end{center}
@@
 \item $ I $ is the return on investment
-\item $ m $ is the number of malaria cases
+\item $ m $ is the prevalence of malaria
+\item $ p $ is the population size
 \item $ x $ is whether eradication has been achievied
@@
 \item $ C $ is the cost of preventing malaria
-\item $ \delta $ is the discount rate and opportunity cost
+\item $ \delta $ represents both the discount rate and opportunity cost
 \end{itemize}
@@
 
-The objective of this study is to gauge (expert) opinion about, estimate the likelihood of, and quantify the potential time frame to malaria eradication through a systemic survey of malaria research professionals from a wide array of academic disciplines.
+The objective of this study is to gauge (expert) opinion about, estimate the likelihood of, and quantify the potential time frame to malaria eradication through a systematic online survey of malaria research professionals from a wide array of academic disciplines.
 In doing so, we aim to help guide the optimal distribution of health resources by informing estimations of the expected value of malaria eradication efforts.
@@
 Our study population included all first authors (with available email addresses) returned in a PubMed search for the term "malaria" from January 1, 2010 through December 20, 2016.
+We used PubMed because it was the most comprehensive publication database for malaria-releated research, and also exposed enough metadata about articles and authors so as to allow for relevant analysis.
 Personalized emails addressing the author by name and mentioning the relevant paper were sent to each of the `r nrow(email_df)` authors during the period from December 20, 2016 through January 2, 2017.
@@
 However, supplementary data on researchers is of value for the assessing of selection bias and determinants of perception.
-Accordingly, we estimated the likelihood of a participant being of one of two genders (male or female) based on first name, and the likelihood of a participant being of one of five ethnicities (White, Black, Hispanic, Asian, Other) based on the provided last name.
-For gender estimations we used data from the North Atlantic Population Project, and U.S.
-government [@Lincoln]; for ethnicity, Khanna et al's bayesian prediction algorithm for the estimation of racial categories [@wru2015] [@Imai_2016] was employed.
-The searching and retrieval of information from the PubMed database was carried out using the RISmed package [@Kovalchik2015].
+Accordingly, we estimated the likelihood of a participant being of one of two genders (male or female) based on first name.
+In order to do this, we used data from the North Atlantic Population Project, and U.S.
+government [@Lincoln].
+We also calculated the total number of citations which each author had received, as well as the total number of articles authored.
+We binned total citations into three categories: 0-5 (junior-level researchers, PhD students, etc.); 6-99 (most professional academics); and >99 (the most prolific researchers).
+The searching and retrieval of information pertaining to articles and citations from the PubMed database was carried out using the RISmed package [@Kovalchik2015].
 
@@
 Quantitative analysis was carried out in R language [@R].
-Ordinary least squares regression was employed to estimate the effect of area of expertise on the eradication pessimism-optimism (through the proxy of perceived years to eradication).
+Ordinary least squares regression was employed to estimate the effect of area of expertise on perceived years to eradication.
 All analysis code, as well as the code used for the identification and contacting of participants, is publicly available at [https://github.com/joebrew/malaria_survey](https://github.com/joebrew/malaria_survey).
@@
     theme(axis.text.x = element_text(angle = 90)) +
-  theme(plot.title = element_text(size=8))
+  theme(plot.title = element_text(size=8)) +
+    ylim(0, 60)
   return(out)
@@
 
-Rmisc::multiplot(g1, g3, g5,
-                 g2, g4, g6,
+Rmisc::multiplot(g1, g4, g2,
+                 g5, g3, g6,
                  cols = 3)
@@
 When examining the number of average citations per article, the difference between respondents remained: `r round(mean(df$n_citations_average[df$responded]), digits = 2)` among respondents, and `r round(mean(df$n_citations_average[!df$responded]), digits = 2)` among non-respondents, highlighting the greater impact of non-respondents relative to respondents.
-Males responded at a greater rate (`r round(mean(df$responded[df$sex == 'male'], na.rm = T) * 100, digits = 2)`) than females (`r round(mean(df$responded[df$sex == 'female'], na.rm = T) * 100, digits = 2)`) and those with Hispanic last names responded at a greater rate than those with last names of other ethnicities (table 1).
+Males responded at a greater rate (`r round(mean(df$responded[df$sex == 'male'], na.rm = T) * 100, digits = 2)`) than females (`r round(mean(df$responded[df$sex == 'female'], na.rm = T) * 100, digits = 2)`).
 
@@
 vars <- c('sex',
-            'ethnicity',
+            # 'ethnicity',
             'bin_citations')
@@
 In the case of researcher impact (as measured by the total number of citations), selection bias plays an important role: being highly-cited was associated both with eradication "pessimism" as well as likelihood of non-response.
-In other words, our pool of respondents was less highly-cited than our pool of invitees, and among respondents, those who were highly-cited tended to be more pessimistic (see Figure 3, Panel A).
+In other words, our pool of respondents was less highly-cited than our pool of invitees, and among respondents, those who were highly-cited tended to be more pessimistic.
 
@@
 We run a separate weighted model to estimate the likelihood of eradication at 10, 20, 30, 40, and 50 years.
-Figure 3 shows both the aggregated perceived likelihood of eradication over time by number of publications (panel A) as well as the difference in the aggregate perceived likelihood of eradication for the entire sample before and after adjusting for sample selection (panel B).
+Figure 3 shows both the aggregated perceived likelihood of eradication over time before and after adjusting for sample selection based on binned number of publications.
+Our adjusted and unadjusted estimates coincide in the long-term, but diverge sharply in the near-term.
 
@@
 # Use inverse of likelihood of response to assign weight for model
-df$weight <- 1 - df$likelihood_of_response
+df$weight <- 1 / df$likelihood_of_response
 # Run likelihood of eradication models
@@
 
-```{r, fig.height = 3.5, fig.cap = '(A) Average perceived likelihood of eradication over time by number of author publications; (B) Aggregated perceived likelihood of eradication over time, adjusted for sample selection and unadjusted.'}
-Rmisc::multiplot(g1, g2, cols = 2)
+```{r, fig.height = 3.5, fig.cap = 'Aggregated perceived likelihood of eradication over time, adjusted for sample selection and unadjusted.'}
+# Rmisc::multiplot(g1, g2, cols = 2)
+g2
 ```
@@
 **Systemic challenges** to malaria eradication were noted by the majority of commenters.
-Comments in this category can be divided into roughly four sub-themes: (i) lack of coordination, (ii) lack of good surveillance and health services delivery, (iii) lack of political will and (iv) poverty.
+Comments in this category can be divided into four sub-themes: (i) lack of coordination, (ii) lack of good surveillance and health services delivery, (iii) lack of political will and (iv) poverty.
 In direct contrast to the previous comments, many emphasized that "we already have the tools to achieve  eradication" and that the only piece lacking was "robust health systems".
@@
 
-Approximately three-quarters of respondents believe that malaria will not be eradicated in the next 50 years; in other words, assuming our pool of respondents is of typical post-PhD age, most believe they will not live to see eradication.
+Approximately three-quarters of respondents believe that malaria will not be eradicated in the next 50 years; in other words, given that our pool of respondents is of typical post-PhD age, most believe they will not live to see eradication.
 When adjusted for selection bias, the perceived likelihood of eradication 50 years from now remains similarly low, but estimates for shorter-term eradication are even lower.
-
-If we take the pooled opinions of researchers, as revealed through this survey, as the best approximation of truth available, then the disconnect between public discourse on malaria eradication and private opinion is noteworthy This has important implications for spending in public health, since the attention and resources of funders, researchers and government agencies are directed to those areas where a result is expected.
 
@@
 Chemists, on average, reported that eradication will be achieved in less than 40 years, whereas economists thought it would take a full ten years more.
-The collective optimism in the field of chemistry may be attributable to recent advances in drug development and insecticides, whereas economists may be more pessimistic due to concerns such as free-riding when it comes to global public goods [@barrett] [@Bodansky_2012].
+Speculatively, the collective optimism in the field of chemistry may be attributable to recent advances in drug development and insecticides, whereas economists may be more pessimistic due to concerns such as free-riding when it comes to global public goods [@barrett] [@Bodansky_2012].
 This study was not designed to generate inference regarding reasons why disciplines might differ in perception, but it does suggest further lines of research.
+
+Eradication of a disease is a "high stakes game", exposed to multiple competing - and at times contradictory - incentives from multiple stakeholders [@barrett].
+Understanding these incentives, and the factors which can alter them, is vital to understanding how eradication can succeed, and where it is most vulnerable to failure.
+The return on investment of eradication-specific interventions is affected by the fact that most researchers agree that eradication will take a long time to achieve.
+This, in turn, reduces the expected value of future benefits, disincentivizing eradication-specific investment.
+Given this, it is important to quantify the positive externalities of "failed" eradication; in areas of high endemicity, even if the goal of elimination is not achieved, the reduction in burden or disease can still make interventions cost-effective.
+
+However, areas of high malaria endemicity are often also those with high competing health costs.
+When estimating the return on investment of malaria elimination initiatives, not only must one take into account the potential benefits (even in the case of failure), but also the opportunity costs (even in the case of success).
+After all, elimination is not a binary success/failure proposition - an initiative should be judged both on its epidemiological circumstances [@Churcher_2014] as well as the counterfactual improvements in health which could have been achieved via other paths.
 
@@
 
-There are several reasons to be skeptical that the combined opinions of malaria researchers is a reliable indicator of truth.
-First, academic researchers are specialists - their narrow, field-specific view of eradication's feasibility is of arguable reliability.
+There are several reasons to be skeptical that the combined opinions of malaria researchers is a reliable indicator.
+First, academic researchers are specialists - their narrow, field-specific view of eradication's feasibility is of arguable reliability, given that they may be unfamiliar with the operational, cultural and "real-world" challenges of malaria eradication.
 Though crowds have been found to be more "wise" than individuals in many cases, the application of an approach similar to the "wisdom of crowds" is not suitable to all classes of problems [@Mannes_2014].
@@
 
-Among these biases, four are worth mentioning specifically.
+Four potential biases are worth mentioning specifically.
 (1) "Conjunction fallacy" suggests that the general goal of eradication may seem less likely than the sum of the goals of country-specific elimination.
@@
 (4) Finally, and ironically, "optimism bias" may play a perverse role in researchers' responses; though eradication is certainly a goal desired by all, one could argue that malaria research specialists subconciously realize that they actually stand to lose out profesionally in the case of eradication.
+
+As with Keenan et al's survey of experts regarding the feasibility of eradication of neglected tropical diseases [@Keenan2013], our survey did not delve into whether researchers had clinical or operational experience, nor did it assess opinions of program workers, nor did it explore complexities pertaining to different types of or forms of existence of malaria.
 
@@
 Our survey attempted to quantify the likelihood of, and time frame to, malaria eradication by gauging the collective opinion of malaria researchers.
-Our survey shows that the opinions of malaria researchers appear to diverge from public goals, with researchers expressing hesitance about the likelihood of eradication and suggesting a long time frame.
+The findings of our survey show researchers expressing hesitance about the likelihood of eradication and suggesting a long time frame.
 The causes for scepticism are diverse, but common themes were the need for innovation, systemic challenges, and the complexity of the disease and its transmission.
 
-The implication of these results are three-fold: (1) that those working or investing in eradication-specific campaigns should factor in researchers' perceived low likelihood and long time frame when calculating those campaigns' expected value; (2) that champions of near-term eradication may need to make a more compelling case to malaria researchers of eradication's feasibility, in order to better focus and inspire the latter; and (3) that discord between malaria researchers and institutions regarding eradication suggests a need for open discussion and concensus-making, so that efforts and focus are directed appropriately.
+The implication of these results are two-fold: (1) that those working or investing in eradication-specific campaigns, as well as those modelling these campaigns' hypothetical cost-effectiveness, should factor in researchers' perceived low likelihood and long time frame when calculating those campaigns' expected value; (2) that champions of near-term eradication may need to make a more compelling case to malaria researchers of eradication's feasibility, in order to better focus and inspire the latter.
 
 We have strived to present the results of our study without insinuation regarding the "true" feasibility and timeframe of eradication, as only time will tell whether the collective "wisdom" of researchers was worth adhering to or not.
-If the research community is unduly sceptical, efforts should be made to convince them that eradication is more feasible than they realize (so that resources are directed accordingly).
-If, on the other hand, collective wisdom of specialists is a useful forecasting agent, then it is important to recognize the sad truth that we are likely further from eradication than we would like to be.
-In this case, though the discourse on eradication can be motivating and inspiring, resources should be directed in a manner that reflects the intended outcome's likelihood of occurrence.
+The actual cost-effectiveness of eradication interventions is not only a function of eradication's success, but also of a number of other factors which are only knowable retrospectively.
+This study's primary contribution is the provision of a snapshot of perceptions of malaria researchers, whose opinions may be of value not only to other researchers, but also to the malaria and public health communities at large.
 

### 2018-04-07 paper.Rmd
removing formula

@@
 
-In other words, the rational assignment of resources for malaria eradication campaigns hinges on the expected value of those campaigns. We can describe this relationship below:
-
-\begin{center}
-$I_{T}$ = $P(x)_{}$ $\dfrac{B(m_{}*p)}{m_{}*p}$(1 + $\delta$)$^{-T}$ -  $P(x)_{}$ $\dfrac{C(m_{}*p)}{m_{}*p}$ (1 + $\delta$)$^{-T}$
-\end{center}
-
-\begin{itemize}
-\item $ I $ is the return on investment
-\item $ m $ is the prevalence of malaria
-\item $ p $ is the population size
-\item $ x $ is whether eradication has been achievied
-\item $ T $ is the time-frame (to both costs and benefits)
-\item $ P $ is the probability (of eradication)
-\item $ B $ is the benefit of preventing malaria
-\item $ C $ is the cost of preventing malaria
-\item $ \delta $ represents both the discount rate and opportunity cost
-\end{itemize}
-
-(I) is the return on investment at time (T) (the "end of malaria").
-We take the present value of the benefits multiplied by the probability of succcess minus the value of costs times the probability of success, and multiplyboth terms by the discount rate traised to T to arrive at the return on investment.
+In other words, the rational assignment of resources for malaria eradication campaigns hinges on the expected value of those campaigns, the latter being a direct function of the discount rate applied to future benefits (which this study does not aspire to assess) and the probability of "success" (ie, eradication).
+Holding constant factors such as the cost of eradication and the benefits of achieving it, the return on investment is a linear function of eradication's probability.
+Given this, estimating probability is crucial to evaluating if and when attempts at eradication should be undertaken.
 

### 2018-04-07 paper.Rmd
major changes

@@
 Quantifying an event's probability and time frame is essential for calculating its expected value.
-In the case of global malaria eradication, uncertainty regarding feasibility makes it difficult for policymakers and public health practitioners to make fully informed decisions.
+In the case of global malaria eradication, uncertainty regarding feasibility makes it difficult for policymakers and public health practitioners to forecast the expected value of future benefits.
 The opportunity cost of investments in eradication-specific interventions can be high, particularly in contexts with other urgent health priorities.
@@
 We also carry out a qualitative analysis of free-form comments provided by 61\% of respondents.
-Our results show that researchers are largely sceptical of the feasibility of near-term malaria eradication, with most believing that eradication will not be achieved for 50 years or more.
+Our results show that researchers are skeptical of the feasibility of near-term malaria eradication, with most believing that eradication will not be achieved for 50 years or more.
 \end{changemargin}
@@
         \begin{itemize}
-          \item Makes novel use of a "wisdom of crowds" approach
+          \item Employs a very large online survey of specialist researchers
           \item Assesses perceived time frame and likelihood of global malaria eradication among researchers
+          \item Results suggest that most malaria researchers believe short-term global malaria eradication to be unlikely
           \item Identifies challenges pertaining to eradication through qualitative analysis
-          \item Highlights the gap between researchers' collective pessimism and institutional optimism
         \end{itemize}
@@
 }
-m
 
@@
 The _Plasmodium falciparum_ species accounts for a large majority of the 200 million annual cases as well as the half million annual deaths worldwide [@White2014] [@World2016].
-Malaria "elimination", the "interruption of all local transmission of the infection in a country or region" [@Tanner2015] is actively being pursued by dozens of countries around the world, leading to a renewed push for "eradication" (the global elmination of malaria) [@Rabinovich_2017].
+Malaria "elimination", the "interruption of all local transmission of the infection in a country or region" [@Tanner2015] is actively being pursued by dozens of countries around the world, leading to a renewed push for "eradication" ("the worldwide interruption of transmission") [@Hopkins2013] [@Rabinovich_2017] [@TheLancet2011].
 
@@
 International programmes, such as the WHO Global Malaria Programme (GMP), have acknowledged the need "to take an official position on how and under what timeline malaria eradication could be achieved" [@WHO2015].
-Clarity on timeline and likelihood of eradication could inform policy, and plays a crucial role in the economic analysis of the expected value of malaria elimination initiatives.
+Clarity on timeline and likelihood of eradication could inform policy and forecasting models, and plays a crucial role in the economic analysis of the expected value of malaria elimination initiatives.
 But achieving clarity is difficult, given the many complex and interacting variables which affect malaria transmission, research funding, and technological development.
@@
 The general objective of eradication serves to inspire, rally funder support, motivate researchers, and focus the efforts of public health practitioners.
-Proponents of disease eradication point to the success of historical and current campaigns (smallpox and polio, respectively), and highlight the long term benefits in health and wealth to future generations (one often cited figure for smallpox was a cost-benefit ratio of more than 400 to 1 [@Barrett_2006]).
+Proponents of disease eradication point to the success of historical and current campaigns (smallpox and polio, respectively), and highlight the long term benefits in health and wealth to future generation.
+One often cited figure for smallpox was a cost-benefit ratio of more than 400 to 1 [@Barrett_2006]; a more recent analysis on River Blindness suggests that the costs of elimination (relative to staying in "control mode") in Africa would be far lower even in the short term, thanks to the improvements it would lead to in both treatment times and prevented surveillance costs [@Kim2017].
 However, the opportunity cost of investments in eradication-specific interventions is likely to be high, particularly in contexts of very low resources and many competing health problems.
-Additionally the impact of malaria on economic indicators is heterogeneous, with singificant impact in areas of Sub-Saharan Africa - where the endemicity is high - and little to no impact in areas of low endemicity [@Cutler_2010] [@Barofsky2015].
+Additionally the estimated impact of malaria on economic indicators is heterogeneous, with singificant impact in areas of Sub-Saharan Africa - where the endemicity is high - and little to no impact in areas of low endemicity [@Cutler_2010] [@Barofsky2015].
 Additionally, the “expected value” of an investment in a binary scenario (eradication or not) is a function of the probability of the scenario’s occurrence, the temporal lag of that occurrence, and the uncertainy around both probability of occurrence and temporal lag.
@@
 Therefore, estimating the likelihood and time frame of eradication of malaria is essential for making sound investments in health.
-But how can we quantify these values given the great deal of uncertainty surrounding eradication?
+But how can we prospectively quantify these values given the great deal of uncertainty surrounding eradication?
 
+Time to eradication, a crucial component in any hypothetical cost-benefit analysis that takes into account discounting, is difficult to assess and requires several layers of assumptions in order to generate even a range of possible scenarios; this can be done with a high degree of reliability for diseases closer to eradication such as Lympathic Filariasis [@Kastner2015], but the uncertainties regarding malaria's future treatment protocols and epidemiology are too great to allow for a robust analysis based on cascading assumptions.
 Many studies have shown value in expert elicitation as a means to reduce uncertainty and inform decision making [@Morgan_2014].
@@
 
-Participants were asked to quantify (as a percentage) the likelihood of eradication in the next 10, 20, 30, 40, and 50 years.
 Most participants saw eradication as extremely unlikely in the next 10-30 years, but increasingly likely thereafter.
 Figure 2 shows the distribution of year-specific likelihood perceptions (panels A-E), as well as an illustration of how both likelihood and uncertainty grow over time (panel F).
+At the 40 year mark, the distribution of perceived likelihood of eradication appears "normal", and by 50 years it is slightly shifted to the right (ie, consensus is towards eradication more probable than not).
 
-Participants were asked to provide the number of years they believe it will take until eradication can be achieved.
-`r length(which(is.na(df$years[df$responded])))` (`r round(length(which(is.na(df$years[df$responded]))) / nrow(df) * 100, digits = 1)`%) were either blank or uninteligible, whereas `r length(which(!is.na(df$years)))` participants responded.
+In regards to responses to perceived years until eradication, `r length(which(is.na(df$years[df$responded])))` (`r round(length(which(is.na(df$years[df$responded]))) / nrow(df) * 100, digits = 1)`%) were either blank or uninteligible, whereas `r length(which(!is.na(df$years)))` participants responded.
 Among respondants, `r length(which(df$years >= 50))` (`r round(length(which(df$years >= 50)) / length(which(!is.na(df$years))) * 100, digits = 1)` %) estimated that it would be 50 or more years until eradication.
@@
 Figure 3 shows both the aggregated perceived likelihood of eradication over time before and after adjusting for sample selection based on binned number of publications.
-Our adjusted and unadjusted estimates coincide in the long-term, but diverge sharply in the near-term.
+Our adjusted and unadjusted estimates coincide in the long-term, but diverge sharply in the near-term; adjustment suggests that had our pool of respondents been more representative, the average perceived likelihood of near-term eradcation would have been much lower.
 
@@
 
-Participants were heterogenous in their perceptions, with all of the 5 pre-determined cut-offs containing the whole range of likelihoods (0-100%), and the free-form time frame responses suggesting that eradication would be achieved in a time-frame ranging from less than a decade to never.
+```{r, fig.height = 3, fig.width = 4, fig.cap = 'Average perceived years to aggregation by discipline', eval = FALSE}
+
+# Participants were heterogenous in their perceptions, with all of the 5 pre-determined cut-offs containing the whole range of likelihoods (0-100%), and the free-form time frame responses suggesting that eradication would be achieved in a time-frame ranging from less than a decade to never.
 Heterogeneity can only be partly explained by area of expertise, as the differences in perception between disciplines were minor and insignificant (see Figure 4).
 
-```{r, fig.height = 3, fig.width = 4, fig.cap = 'Average perceived years to aggregation by discipline'}
 areas_df <- areas_df %>% arrange(desc(count))
@@
 
-There are several reasons to be skeptical that the combined opinions of malaria researchers is a reliable indicator.
+This paper has several limitations.
 First, academic researchers are specialists - their narrow, field-specific view of eradication's feasibility is of arguable reliability, given that they may be unfamiliar with the operational, cultural and "real-world" challenges of malaria eradication.
@@
 
-As with Keenan et al's survey of experts regarding the feasibility of eradication of neglected tropical diseases [@Keenan2013], our survey did not delve into whether researchers had clinical or operational experience, nor did it assess opinions of program workers, nor did it explore complexities pertaining to different types of or forms of existence of malaria.
+As with Keenan et al's survey of experts regarding the feasibility of eradication of neglected tropical diseases [@Keenan2013], our survey detected relatively high levels of eradication skepticism and did not delve into whether researchers had clinical or operational experience, nor did it assess opinions of program workers, nor did it explore complexities pertaining to different types of or forms of existence of malaria.
+Though our sample size was over twice Keenan's, this was largely due to having contacted more authors, as our response rate was only one fourth as large.
 

### 2018-04-10 paper.Rmd
major update

@@
 ---
-title: "Researchers' perceptions of malaria eradication: findings from a mixed-methods analysis of a large online survey"
-bibliography: library.bib
+title: 'Researchers'' perceptions of malaria eradication: findings from a mixed-methods
+  analysis of a large online survey'
+csl: elsevier-with-titles.csl
 output:
   pdf_document:
-    keep_tex: true
-    latex_engine: xelatex
     includes:
       in_header: preamble.sty
-csl: elsevier-with-titles.csl
+    keep_tex: yes
+    latex_engine: xelatex
+  word_document: default
+bibliography: library.bib
 ---
@@
 Quantifying an event's probability and time frame is essential for calculating its expected value.
-In the case of global malaria eradication, uncertainty regarding feasibility makes it difficult for policymakers and public health practitioners to forecast the expected value of future benefits.
-The opportunity cost of investments in eradication-specific interventions can be high, particularly in contexts with other urgent health priorities.
+Uuncertainty regarding feasibility makes it difficult for policymakers and public health practitioners to forecast the return on investment of malaria eradication.
+Since the opportunity cost of investments in eradication-specific interventions can be high - particularly in contexts with other urgent health priorities - understanding eradication's expected value is essential.
 In a large online survey of malaria researchers (n = 844), we query perceptions regarding the likelihood and time frame of eradication.
-We assess pessimism/optimism (via the proxy of years-to-eradication), broken down by area of expertise, and adjust for selection bias.
-We also carry out a qualitative analysis of free-form comments provided by 61\% of respondents.
+We assess pessimism/optimism (via the proxy of years-to-eradication), and adjust for selection bias.
+We also carry out a qualitative analysis of the free-form comments provided by 61\% of respondents.
 Our results show that researchers are skeptical of the feasibility of near-term malaria eradication, with most believing that eradication will not be achieved for 50 years or more.
@@
 Malaria is a parasitic disease transmitted among humans by mosquitoes.
-The _Plasmodium falciparum_ species accounts for a large majority of the 200 million annual cases as well as the half million annual deaths worldwide [@White2014] [@World2016].
+The _Plasmodium falciparum_ species accounts for a large majority of the 200 million annual cases as well as the half million annual deaths worldwide [@White2014] [@World2016] [@Ashley2018].
 Malaria "elimination", the "interruption of all local transmission of the infection in a country or region" [@Tanner2015] is actively being pursued by dozens of countries around the world, leading to a renewed push for "eradication" ("the worldwide interruption of transmission") [@Hopkins2013] [@Rabinovich_2017] [@TheLancet2011].
@@
 This is not the first time that eradication has been in the international spotlight.
-The scientific and public health communities have had eradication on their policy agenda since the WHO established the Global Malaria Eradication Program in the 1950s [@Njera2011].
+The scientific and public health communities have had eradication on their policy agenda since the World Health Organisation (WHO) established the Global Malaria Eradication Program in the 1950s [@Njera2011].
 In 1957, U.S.
@@
 In recent years, much of the discourse regarding malaria has shifted back to global eradication [@Roberts2007], with funders, researchers, and public health practitioners rallying to the cause [@Tanner2015].
-The Bill and Melinda Gates Foundation has begun actively promoting eradication as feasible "within a generation" [@Gates2014], and the World Health Organization (WHO) has set ambitious goals, stating the objective of eliminating malaria in 65 new endemic countries from 2015 through 2030 (Figure 1).
+The Bill and Melinda Gates Foundation has begun actively promoting eradication as feasible "within a generation" [@Gates2014], and the WHO has set ambitious goals, stating the objective of eliminating malaria in 65 new endemic countries from 2015 through 2030 (Figure 1).
 
@@
 International programmes, such as the WHO Global Malaria Programme (GMP), have acknowledged the need "to take an official position on how and under what timeline malaria eradication could be achieved" [@WHO2015].
-Clarity on timeline and likelihood of eradication could inform policy and forecasting models, and plays a crucial role in the economic analysis of the expected value of malaria elimination initiatives.
+Clarity on timeline and likelihood of eradication could inform forecasting of disease transmission, and plays a crucial role in the economic analysis of the expected value of malaria eradication initiatives, ultimately informing health policy decisions.
 But achieving clarity is difficult, given the many complex and interacting variables which affect malaria transmission, research funding, and technological development.
@@
 
+Proponents of disease eradication point to the success of historical and current campaigns (smallpox and polio, respectively), and highlight the long term benefits in health and wealth to future generations [@Barrett2013].
+One often cited figure is for smallpox eradication, in which the investment of each dollar led to a return of greater than 400 [@Barrett_2006]; unlike smallpox (for which analysis was able to be retrospectively constructed based on observed costs and benefits), in the case of a prevalent disease, forecasting models have to be used in order to prospectively estimate the value of an investment.
+\st{Additionally the estimated impact of malaria on economic indicators is heterogeneous, with singificant impact in areas of Sub-Saharan Africa - where the endemicity is high - and little to no impact in areas of low endemicity} [@Cutler_2010] [@Barofsky2015].
+
 The general objective of eradication serves to inspire, rally funder support, motivate researchers, and focus the efforts of public health practitioners.
-Proponents of disease eradication point to the success of historical and current campaigns (smallpox and polio, respectively), and highlight the long term benefits in health and wealth to future generation.
-One often cited figure for smallpox was a cost-benefit ratio of more than 400 to 1 [@Barrett_2006]; a more recent analysis on River Blindness suggests that the costs of elimination (relative to staying in "control mode") in Africa would be far lower even in the short term, thanks to the improvements it would lead to in both treatment times and prevented surveillance costs [@Kim2017].
-However, the opportunity cost of investments in eradication-specific interventions is likely to be high, particularly in contexts of very low resources and many competing health problems.
-Additionally the estimated impact of malaria on economic indicators is heterogeneous, with singificant impact in areas of Sub-Saharan Africa - where the endemicity is high - and little to no impact in areas of low endemicity [@Cutler_2010] [@Barofsky2015].
-Additionally, the “expected value” of an investment in a binary scenario (eradication or not) is a function of the probability of the scenario’s occurrence, the temporal lag of that occurrence, and the uncertainy around both probability of occurrence and temporal lag.
-This uncertainty makes the "risk" of investing in malaria elimination and eradication high.
-Therefore, estimating the likelihood and time frame of eradication of malaria is essential for making sound investments in health.
-But how can we prospectively quantify these values given the great deal of uncertainty surrounding eradication?
+But to the extent that malaria eradication (by definition) has never occurred, the parameters needed for a ex-post cost-benefit analysis are unknown.
+Nonetheless, prospectively estimating eradication's return on investment is crucial to deciding when and how to pursue the goal, especially in light of the high direct and opportunity costs of eradication-specific interventions.
+One approach to cost-benefit analysis is the use of mathematical and stochastic models.
+These have been applied to diseases which are closer to eradication than malaria, since the uncertainty around model input parameters is less, requiring fewer cascading assumptions in order to present possible comparative scenarios.
+For example, Kastner et al.
+were able to describe 4 relatively realistic pathways to Lympathic Filariasis eradication, as well as the pre-requisite role and magnitude of certain interventions [@Kastner2015].
+A similar modeling framework was then used to estimate the cost of eradication [@Kastner2017].
+A recent modeling analysis on onchocerciasis eradication, based on a disease transmission model, showed that the costs of elimination (relative to staying in "control mode") in Africa would be far lower even in the short term, thanks to the improvements it would lead to in both treatment times and prevented surveillance costs.
+Given the relative proximity of eradication, and the narrow geographic scope, the authors were also able to estimate the timeline to eradication [@Kim2017].
 
-Time to eradication, a crucial component in any hypothetical cost-benefit analysis that takes into account discounting, is difficult to assess and requires several layers of assumptions in order to generate even a range of possible scenarios; this can be done with a high degree of reliability for diseases closer to eradication such as Lympathic Filariasis [@Kastner2015], but the uncertainties regarding malaria's future treatment protocols and epidemiology are too great to allow for a robust analysis based on cascading assumptions.
+This level of detail and specificity in modeling the cost-benefit landscape of malaria eradication, unfortunately, is not possible (or at least not commonly undertaken), given its high prevalence and epidemiological complexity.
+In fact, there are no mathematical models (to the authors' knowledge) estimating the likelihood and time frame of eradication, or its derivative cost-benefit ratio.
+While a great deal of rigorous studies exist forecasting the effect of certain tools and strategies relative to alternatives [@Brady2017] or aimed at regional disease elimination [@Kim2015], these analyses do not endeavor to estimate the generalization of those tools or strategies to other areas.
+Globally, where mathematical modeling has been used for the purposes of forecasting the future epidemiology of malaria, the methods have generally been aimed at optimizing elimination methods [@Slater2015], determining whether a strategy is scalable [@Brady2017], guiding funding and drug development [@Patouillard2017] [@Slater2017], or comparing a range of hypothetical morbidity scenarios [@Winskill2017], rather than assessing the likelihood of or time until the occurrence of those scenarios.
+In other words, researchers are (rightfully) focused on the \emph{how} of eradication, rather than the forecasting of its timeframe or likelihood, the lack of attention paid to the latter likely being a reflection of its complexity, not lack of importance.
+
+To the extent that (i) estimating eradication's likelihood and timeframe is essential to forecasting the cost-benefit ratio of eradication interventions, and (ii) mathematical models generally do not venture into areas of such high uncertainty, alternative methods are needed.
+Just as the stock market aggregates perceptions to provide a fairly accurate assessment of something as complex as a company's value, aggregating perceptions may be a useful tool for tackling the complexity of malaria eradication.
 Many studies have shown value in expert elicitation as a means to reduce uncertainty and inform decision making [@Morgan_2014].
-But experts can sometimes be mistaken, a fact implicitly recognized when patients request a "second opinion" from another doctor when facing uncertainty.
-Additionally, relying on only a small panel of experts for a problem as complex as malaria exposes one to bias, just as an overly concentrated investment portfolio exposes one to more risk.
-As Sir Francis Galton demonstrated in his famous study in which he showed that the crowds' aggregated estimates of cow's weight formed a quasi-normal distribution centered around the true weight [@Wallis2014] [@Galton1907Voxpopuli], averaging the perceptions of many can be more accurate than taking the opinion of any single expert, since the biases of diverse viewpoints can be complementary and symbiotic.
+\st{But experts can sometimes be mistaken, a fact implicitly recognized when patients request a "second opinion" from another doctor when facing uncertainty.
+Additionally, relying on only a small panel of experts for a problem as complex as malaria exposes one to bias, just as an overly concentrated investment portfolio exposes one to more risk.} As Sir Francis Galton demonstrated in his famous study in which he showed that the crowds' aggregated estimates of cow's weight formed a quasi-normal distribution centered around the true weight [@Wallis2014] [@Galton1907Voxpopuli], averaging the perceptions of many can be more accurate than taking the opinion of any single expert, since the biases of diverse viewpoints can be complementary and symbiotic.
+Measuring consensus and discord among disease-specific researchers from a variety of disciplines can serve as a barometer of (informed) opinion, both guiding resources and identifying areas of concern [@Keenan2013].
 
-Assessing the likelihood and time frame of eradication, therefore, requires the combination of multiple points of view.
-Measuring consensus and discord among disease-specific researchers from a variety of disciplines can serve as a barometer of (informed) opinion, both guiding resources and identifying areas of concern [@Keenan2013].
-We propose that the aggregation of malaria researchers' perceptions regarding the time frame andlikelihood of eradication forms a probability distribution which can be used to estimate the expected value of eradication-specific investments.
+The optimal assignment of resources for malaria eradication campaigns hinges on the expected value of those campaigns, the latter being a direct function of the discount rate applied to future benefits and the probability of "success" (ie, eradication).
+Holding constant factors such as the cost of eradication and the benefits of achieving it, the return on investment of malaria eradication initiatives is a function of eradication's timeframe (assuming a > 0 discount rate) and probability (assuming a < 100% likelihood of success).
+Given this, estimating these parameters is crucial to evaluating if and when attempts at eradication should be undertaken.
 
-A great deal of previous research from serveral endemic areas already covers the cost per case prevented [@Sicuri2011] [@Silumbe2015] [@Btto2016] [@IlungaIlunga2014] [@Dalaba2015].
+We propose that the aggregation of malaria researchers' perceptions regarding the time frame and likelihood of eradication forms a probability distribution which can be used to estimate the expected value of eradication-specific investments.
+The objective of this study is to gauge (expert) opinion about, estimate the likelihood of, and quantify the potential time frame to malaria eradication through a systematic online survey of malaria research professionals from a wide array of academic disciplines.
+In doing so, we aim to help guide the optimal distribution of health resources by informing estimations of the expected value of malaria eradication efforts.
+
+\st{A great deal of previous research from serveral endemic areas already covers the cost per case prevented [@Sicuri2011] [@Silumbe2015] [@Btto2016] [@IlungaIlunga2014] [@Dalaba2015].
 Likewise, literature exists which could serve as a model for quantifying the location-specific opportunity costs associated with funneling funds towards malaria eradication [@Stuckey2014] [@White2011] [@Korenromp2012].
 The correct discount rate for estimating the value of future lives saved is more of a philosophical question than an economic one.
-This leaves only the probability and time-frame to eradication, questions which have been addressed anecdotally, but never answered quantitatively.
+This leaves only the probability and time-frame to eradication, questions which have been addressed anecdotally, but never answered quantitatively.}
 
-Though the case-specific marginal cost of eradication can be expected to be high (relative to a simple control approach), successful eradication would mean massive recurring savings in the long-term [@Barrett2013].
+\st{Though the case-specific marginal cost of eradication can be expected to be high (relative to a simple control approach), successful eradication would mean massive recurring savings in the long-term [@Barrett2013].
 However, to the extent that the case-specific marginal cost of prevention in an eradication campaign is high, estimating the likelihood of success is fundamental to the correct distribution of resources, particularly in low-income environments.
-
-In other words, the rational assignment of resources for malaria eradication campaigns hinges on the expected value of those campaigns, the latter being a direct function of the discount rate applied to future benefits (which this study does not aspire to assess) and the probability of "success" (ie, eradication).
-Holding constant factors such as the cost of eradication and the benefits of achieving it, the return on investment is a linear function of eradication's probability.
-Given this, estimating probability is crucial to evaluating if and when attempts at eradication should be undertaken.
-
-The objective of this study is to gauge (expert) opinion about, estimate the likelihood of, and quantify the potential time frame to malaria eradication through a systematic online survey of malaria research professionals from a wide array of academic disciplines.
-In doing so, we aim to help guide the optimal distribution of health resources by informing estimations of the expected value of malaria eradication efforts.
+}
 
@@
 The searching and retrieval of information pertaining to articles and citations from the PubMed database was carried out using the RISmed package [@Kovalchik2015].
+Information retrieved about authors was used to de-bias paramaters in an ordinary least squares regression, analyzing the association between number of publications and perceived years to eradication.
 
@@
 Quantitative analysis was carried out in R language [@R].
-Ordinary least squares regression was employed to estimate the effect of area of expertise on perceived years to eradication.
 All analysis code, as well as the code used for the identification and contacting of participants, is publicly available at [https://github.com/joebrew/malaria_survey](https://github.com/joebrew/malaria_survey).
@@
 One stated that the concept was "absurd" and that "I'm not even sure why people talk about it".
-Another questioned the utility of discussing "eradiction" as a concept:
+Another questioned the utility of discussing "eradication" as a concept:
 
@@
 
-Approximately three-quarters of respondents believe that malaria will not be eradicated in the next 50 years; in other words, given that our pool of respondents is of typical post-PhD age, most believe they will not live to see eradication.
-When adjusted for selection bias, the perceived likelihood of eradication 50 years from now remains similarly low, but estimates for shorter-term eradication are even lower.
-
-In regards to differences by academic discipline, it is important to note that diversity within disciplines was greater than diversity between them.
-That said, one might surmise as to why disciplines at the extremes differed.
-Chemists, on average, reported that eradication will be achieved in less than 40 years, whereas economists thought it would take a full ten years more.
-Speculatively, the collective optimism in the field of chemistry may be attributable to recent advances in drug development and insecticides, whereas economists may be more pessimistic due to concerns such as free-riding when it comes to global public goods [@barrett] [@Bodansky_2012].
-This study was not designed to generate inference regarding reasons why disciplines might differ in perception, but it does suggest further lines of research.
+Approximately three-quarters of respondents believe that malaria will not be eradicated in the next 50 years.
+When adjusted for selection bias, the perceived likelihood of eradication in 50 years remains similarly low, but estimates for shorter-term eradication are even lower.
 
@@
 This paper has several limitations.
-First, academic researchers are specialists - their narrow, field-specific view of eradication's feasibility is of arguable reliability, given that they may be unfamiliar with the operational, cultural and "real-world" challenges of malaria eradication.
+Conceptually, academic researchers are specialists - their narrow, field-specific view of eradication's feasibility is of arguable reliability, given that they may be unfamiliar with the operational, cultural and "real-world" challenges of malaria eradication.
 Though crowds have been found to be more "wise" than individuals in many cases, the application of an approach similar to the "wisdom of crowds" is not suitable to all classes of problems [@Mannes_2014].
@@
 
-As with Keenan et al's survey of experts regarding the feasibility of eradication of neglected tropical diseases [@Keenan2013], our survey detected relatively high levels of eradication skepticism and did not delve into whether researchers had clinical or operational experience, nor did it assess opinions of program workers, nor did it explore complexities pertaining to different types of or forms of existence of malaria.
-Though our sample size was over twice Keenan's, this was largely due to having contacted more authors, as our response rate was only one fourth as large.
+As with Keenan et al's survey of experts regarding the feasibility of eradication of neglected tropical diseases, our survey detected relatively high levels of eradication skepticism and did not delve into whether researchers had clinical or operational experience, nor did it assess opinions of program workers, nor did it explore complexities pertaining to different types of or forms of existence of malaria.
+Though our sample size was over twice Keenan's, this was largely due to having contacted more authors, as our response rate was only one fourth as large [@Keenan2013].
 
@@
 Our survey attempted to quantify the likelihood of, and time frame to, malaria eradication by gauging the collective opinion of malaria researchers.
-The findings of our survey show researchers expressing hesitance about the likelihood of eradication and suggesting a long time frame.
+The findings of our survey show researchers expressing hesitance about the likelihood of eradication and suggesting a long time frame until it is achieved.
 The causes for scepticism are diverse, but common themes were the need for innovation, systemic challenges, and the complexity of the disease and its transmission.
 
-The implication of these results are two-fold: (1) that those working or investing in eradication-specific campaigns, as well as those modelling these campaigns' hypothetical cost-effectiveness, should factor in researchers' perceived low likelihood and long time frame when calculating those campaigns' expected value; (2) that champions of near-term eradication may need to make a more compelling case to malaria researchers of eradication's feasibility, in order to better focus and inspire the latter.
+The implication of these results are two-fold: (1) that those working or investing in eradication-specific campaigns, as well as those modeling these campaigns' hypothetical cost-effectiveness, should factor in researchers' perceived low likelihood and long time frame when calculating those campaigns' expected value; (2) that champions of near-term eradication may need to make a more compelling case to malaria researchers of eradication's feasibility, in order to better focus and inspire the latter.
 

### 2018-04-10 paper.tex
major update

\documentclass[]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\hypersetup{unicode=true,
            pdftitle={Researchers' perceptions of malaria eradication: findings from a mixed-methods analysis of a large online survey},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{longtable,booktabs}
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

%%% Use protect on footnotes to avoid problems with footnotes in titles
\let\rmarkdownfootnote\footnote%
\def\footnote{\protect\rmarkdownfootnote}

%%% Change title format to be more compact
\usepackage{titling}

% Create subtitle command for use in maketitle
\newcommand{\subtitle}[1]{
  \posttitle{
    \begin{center}\large#1\end{center}
    }
}

\setlength{\droptitle}{-2em}
  \title{Researchers' perceptions of malaria eradication: findings from a
mixed-methods analysis of a large online survey}
  \pretitle{\vspace{\droptitle}\centering\huge}
  \posttitle{\par}
  \author{}
  \preauthor{}\postauthor{}
  \date{}
  \predate{}\postdate{}

\usepackage{multicol}
\usepackage{hyperref}
\usepackage{geometry}
\usepackage[utf8]{inputenc}
% \usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{etoolbox}
% \AtBeginEnvironment{quote}{\singlespacing\small}
% \usepackage{setspace} % for \onehalfspacing and \singlespacing macros
% \onehalfspacing

\usepackage{fancyhdr} % Headers and footers
\pagestyle{fancy} % All pages have headers and footers
\fancyhead{} % Blank out the default header
\fancyfoot[C]{\thepage} % Blank out the default footer
\fancyhead[C]{ $\bullet$ Manuscript submission to SSM $\bullet$ } 
\renewcommand{\thefootnote}{\fnsymbol{footnote}}

\newcommand{\footremember}[2]{%
    \footnote{#2}
    \newcounter{#1}
    \setcounter{#1}{\value{footnote}}%
}
\newcommand{\footrecall}[1]{%
    \footnotemark[\value{#1}]%
}

\def\changemargin#1#2{\list{}{\rightmargin#2\leftmargin#1}\item[]}
\let\endchangemargin=\endlist

\usepackage{soul}

\begin{document}
\maketitle

\begin{center}
\begin{large}

Joe Brew\footremember{isglobal}{Barcelona Institute for Global Health: c/ Rosselló, 132, 5è 2a. 08036, Barcelona, Spain}\footremember{cism}{Centro de Investigação em Saúde de Manhiça: Vila da Manhiça, Bairro Cambeve, Rua 12, Distrito da Manhiça, CP 1929, Maputo, Mozambique}\footremember{vu}{VU University Amsterdam: De Boelelaan 1105, 1081 HV Amsterdam, Netherlands}, Menno Pradhan\footrecall{vu}\footremember{uva}{University of Amsterdam: REC E, Roetersstraat 11, Amsterdam, Netherlands}, Jacqueline Broerse\footrecall{vu}, Elisa Sicuri\footrecall{isglobal}\footremember{icl}{Imperial College London: South Kensington Campus, London SW7 2AZ, U.K.}\footrecall{cism}

\end{large}
\end{center}

\vspace{5mm}

\begin{center}
\textbf{Abstract}  
\end{center}

\vspace{5mm}

\begin{center}
\begin{changemargin}{3cm}{3cm}

Quantifying an event's probability and time frame is essential for calculating its expected value. Uuncertainty regarding feasibility makes it difficult for policymakers and public health practitioners to forecast the return on investment of malaria eradication. Since the opportunity cost of investments in eradication-specific interventions can be high - particularly in contexts with other urgent health priorities - understanding eradication's expected value is essential. In a large online survey of malaria researchers (n = 844), we query perceptions regarding the likelihood and time frame of eradication. We assess pessimism/optimism (via the proxy of years-to-eradication), and adjust for selection bias. We also carry out a qualitative analysis of the free-form comments provided by 61\% of respondents. Our results show that researchers are skeptical of the feasibility of near-term malaria eradication, with most believing that eradication will not be achieved for 50 years or more.
\end{changemargin}
\end{center}

\noindent\fbox{%
    \parbox{\textwidth}{%
        \subsection*{Research Highlights}
        \begin{itemize}
          \item Employs a very large online survey of specialist researchers
          \item Assesses perceived time frame and likelihood of global malaria eradication among researchers
          \item Results suggest that most malaria researchers believe short-term global malaria eradication to be unlikely
          \item Identifies challenges pertaining to eradication through qualitative analysis
        \end{itemize}
      \subsection*{Keywords}
        Malaria, eradication, elimination, mixed methods, survey, crowdsourcing 
    }%
}

\section{Introduction}\label{introduction}

\subsection{Background}\label{background}

Malaria is a parasitic disease transmitted among humans by mosquitoes.
The \emph{Plasmodium falciparum} species accounts for a large majority
of the 200 million annual cases as well as the half million annual
deaths worldwide {[}1{]} {[}2{]} {[}3{]}. Malaria ``elimination'', the
``interruption of all local transmission of the infection in a country
or region'' {[}4{]} is actively being pursued by dozens of countries
around the world, leading to a renewed push for ``eradication'' (``the
worldwide interruption of transmission'') {[}5{]} {[}6{]} {[}7{]}.

This is not the first time that eradication has been in the
international spotlight. The scientific and public health communities
have had eradication on their policy agenda since the World Health
Organisation (WHO) established the Global Malaria Eradication Program in
the 1950s {[}8{]}. In 1957, U.S. President Dwight Eisenhower told
Congress that malaria could be expected to be eradicated in five years.
Following the failure of the WHO's first attempt, the focus shifted away
from global eradication towards local elimination and control
strategies. In recent years, much of the discourse regarding malaria has
shifted back to global eradication {[}9{]}, with funders, researchers,
and public health practitioners rallying to the cause {[}4{]}. The Bill
and Melinda Gates Foundation has begun actively promoting eradication as
feasible ``within a generation'' {[}10{]}, and the WHO has set ambitious
goals, stating the objective of eliminating malaria in 65 new endemic
countries from 2015 through 2030 (Figure 1).

\begin{figure}[h]

{\centering \includegraphics{paper_files/figure-latex/unnamed-chunk-4-1}

}

\caption{Countries with malaria: Observed and WHO objectives}\label{fig:unnamed-chunk-4}
\end{figure}

Even in areas of high endemicity, advances in immunology, parasitology,
modeling and vaccinology, along with rapid economic development, have
made eradication appear a more feasible goal, though not possible in the
short term {[}11{]} {[}12{]}. From both administrative {[}13{]} and
scientific {[}14{]} points of view, eradication has never before
received so much attention.

Most of the current research on expert opinion regarding the feasibility
of malaria eradication focuses on the \emph{how} rather than the
\emph{if} and the \emph{when} {[}4{]}. The participants in the Malaria
Eradication Research Agenda (MalERA) process, in particular, have guided
research goals and identified gaps in order for elmination to occur
{[}14{]} {[}6{]}. Though the MalERA authors firmly state that
eradication is \emph{not} feasible given the ``current tools and state
of knowledge'', mentions to the time frame are vague (``within the
lifetime of young scientists just embarking on their careers'' {[}14{]}
and ``in the longer term'' {[}6{]}) and no mention is made of the
perception of the overall probability of achieving eradication.
International programmes, such as the WHO Global Malaria Programme
(GMP), have acknowledged the need ``to take an official position on how
and under what timeline malaria eradication could be achieved''
{[}15{]}. Clarity on timeline and likelihood of eradication could inform
forecasting of disease transmission, and plays a crucial role in the
economic analysis of the expected value of malaria eradication
initiatives, ultimately informing health policy decisions. But achieving
clarity is difficult, given the many complex and interacting variables
which affect malaria transmission, research funding, and technological
development. The question of \emph{how} is complex enough, rendering
questions of \emph{if} and \emph{when} even more difficult to answer.

Proponents of disease eradication point to the success of historical and
current campaigns (smallpox and polio, respectively), and highlight the
long term benefits in health and wealth to future generations {[}16{]}.
One often cited figure is for smallpox eradication, in which the
investment of each dollar led to a return of greater than 400 {[}17{]};
unlike smallpox (for which analysis was able to be retrospectively
constructed based on observed costs and benefits), in the case of a
prevalent disease, forecasting models have to be used in order to
prospectively estimate the value of an investment.
\st{Additionally the estimated impact of malaria on economic indicators is heterogeneous, with singificant impact in areas of Sub-Saharan Africa - where the endemicity is high - and little to no impact in areas of low endemicity}
{[}18{]} {[}19{]}.

The general objective of eradication serves to inspire, rally funder
support, motivate researchers, and focus the efforts of public health
practitioners. But to the extent that malaria eradication (by
definition) has never occurred, the parameters needed for a ex-post
cost-benefit analysis are unknown. Nonetheless, prospectively estimating
eradication's return on investment is crucial to deciding when and how
to pursue the goal, especially in light of the high direct and
opportunity costs of eradication-specific interventions. One approach to
cost-benefit analysis is the use of mathematical and stochastic models.
These have been applied to diseases which are closer to eradication than
malaria, since the uncertainty around model input parameters is less,
requiring fewer cascading assumptions in order to present possible
comparative scenarios. For example, Kastner et al. were able to describe
4 relatively realistic pathways to Lympathic Filariasis eradication, as
well as the pre-requisite role and magnitude of certain interventions
{[}20{]}. A similar modeling framework was then used to estimate the
cost of eradication {[}21{]}. A recent modeling analysis on
onchocerciasis eradication, based on a disease transmission model,
showed that the costs of elimination (relative to staying in ``control
mode'') in Africa would be far lower even in the short term, thanks to
the improvements it would lead to in both treatment times and prevented
surveillance costs. Given the relative proximity of eradication, and the
narrow geographic scope, the authors were also able to estimate the
timeline to eradication {[}22{]}.

This level of detail and specificity in modeling the cost-benefit
landscape of malaria eradication, unfortunately, is not possible (or at
least not commonly undertaken), given its high prevalence and
epidemiological complexity. In fact, there are no mathematical models
(to the authors' knowledge) estimating the likelihood and time frame of
eradication, or its derivative cost-benefit ratio. While a great deal of
rigorous studies exist forecasting the effect of certain tools and
strategies relative to alternatives {[}23{]} or aimed at regional
disease elimination {[}24{]}, these analyses do not endeavor to estimate
the generalization of those tools or strategies to other areas.
Globally, where mathematical modeling has been used for the purposes of
forecasting the future epidemiology of malaria, the methods have
generally been aimed at optimizing elimination methods {[}25{]},
determining whether a strategy is scalable {[}23{]}, guiding funding and
drug development {[}26{]} {[}27{]}, or comparing a range of hypothetical
morbidity scenarios {[}28{]}, rather than assessing the likelihood of or
time until the occurrence of those scenarios. In other words,
researchers are (rightfully) focused on the \emph{how} of eradication,
rather than the forecasting of its timeframe or likelihood, the lack of
attention paid to the latter likely being a reflection of its
complexity, not lack of importance.

To the extent that (i) estimating eradication's likelihood and timeframe
is essential to forecasting the cost-benefit ratio of eradication
interventions, and (ii) mathematical models generally do not venture
into areas of such high uncertainty, alternative methods are needed.
Just as the stock market aggregates perceptions to provide a fairly
accurate assessment of something as complex as a company's value,
aggregating perceptions may be a useful tool for tackling the complexity
of malaria eradication. Many studies have shown value in expert
elicitation as a means to reduce uncertainty and inform decision making
{[}29{]}.
\st{But experts can sometimes be mistaken, a fact implicitly recognized when patients request a "second opinion" from another doctor when facing uncertainty. Additionally, relying on only a small panel of experts for a problem as complex as malaria exposes one to bias, just as an overly concentrated investment portfolio exposes one to more risk.}
As Sir Francis Galton demonstrated in his famous study in which he
showed that the crowds' aggregated estimates of cow's weight formed a
quasi-normal distribution centered around the true weight {[}30{]}
{[}31{]}, averaging the perceptions of many can be more accurate than
taking the opinion of any single expert, since the biases of diverse
viewpoints can be complementary and symbiotic. Measuring consensus and
discord among disease-specific researchers from a variety of disciplines
can serve as a barometer of (informed) opinion, both guiding resources
and identifying areas of concern {[}32{]}.

The optimal assignment of resources for malaria eradication campaigns
hinges on the expected value of those campaigns, the latter being a
direct function of the discount rate applied to future benefits and the
probability of ``success'' (ie, eradication). Holding constant factors
such as the cost of eradication and the benefits of achieving it, the
return on investment of malaria eradication initiatives is a function of
eradication's timeframe (assuming a \textgreater{} 0 discount rate) and
probability (assuming a \textless{} 100\% likelihood of success). Given
this, estimating these parameters is crucial to evaluating if and when
attempts at eradication should be undertaken.

We propose that the aggregation of malaria researchers' perceptions
regarding the time frame and likelihood of eradication forms a
probability distribution which can be used to estimate the expected
value of eradication-specific investments. The objective of this study
is to gauge (expert) opinion about, estimate the likelihood of, and
quantify the potential time frame to malaria eradication through a
systematic online survey of malaria research professionals from a wide
array of academic disciplines. In doing so, we aim to help guide the
optimal distribution of health resources by informing estimations of the
expected value of malaria eradication efforts.

\st{A great deal of previous research from serveral endemic areas already covers the cost per case prevented [@Sicuri2011] [@Silumbe2015] [@Btto2016] [@IlungaIlunga2014] [@Dalaba2015]. Likewise, literature exists which could serve as a model for quantifying the location-specific opportunity costs associated with funneling funds towards malaria eradication [@Stuckey2014] [@White2011] [@Korenromp2012]. The correct discount rate for estimating the value of future lives saved is more of a philosophical question than an economic one. This leaves only the probability and time-frame to eradication, questions which have been addressed anecdotally, but never answered quantitatively.}

\st{Though the case-specific marginal cost of eradication can be expected to be high (relative to a simple control approach), successful eradication would mean massive recurring savings in the long-term [@Barrett2013]. However, to the extent that the case-specific marginal cost of prevention in an eradication campaign is high, estimating the likelihood of success is fundamental to the correct distribution of resources, particularly in low-income environments. }

\section{Methods}\label{methods}

Our study population included all first authors (with available email
addresses) returned in a PubMed search for the term ``malaria'' from
January 1, 2010 through December 20, 2016. We used PubMed because it was
the most comprehensive publication database for malaria-releated
research, and also exposed enough metadata about articles and authors so
as to allow for relevant analysis. Personalized emails addressing the
author by name and mentioning the relevant paper were sent to each of
the 7680 authors during the period from December 20, 2016 through
January 2, 2017. Researchers were invited to participate by clicking a
link to the survey form. The survey was simple, consisting of only name,
email, and four content-related fields along with a ``general comments''
section. The survey was administered and data were collected through
Google Drive. The original survey is viewable at
\url{https://goo.gl/forms/IroAEooDuJ6KM5Ho2}.

Content-related survey fields consisted of:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Area of expertise.
\item
  Perceived probability (\%) of malaria eradication in 10, 20, 30, 40,
  and 50 years.
\item
  Free choice perceived number of years until malaria eradication.
\end{enumerate}

The survey was intentionally as short as possible, so as to appeal to
time-pressed participants. However, supplementary data on researchers is
of value for the assessing of selection bias and determinants of
perception. Accordingly, we estimated the likelihood of a participant
being of one of two genders (male or female) based on first name. In
order to do this, we used data from the North Atlantic Population
Project, and U.S. government {[}33{]}. We also calculated the total
number of citations which each author had received, as well as the total
number of articles authored. We binned total citations into three
categories: 0-5 (junior-level researchers, PhD students, etc.); 6-99
(most professional academics); and \textgreater{}99 (the most prolific
researchers). The searching and retrieval of information pertaining to
articles and citations from the PubMed database was carried out using
the RISmed package {[}34{]}. Information retrieved about authors was
used to de-bias paramaters in an ordinary least squares regression,
analyzing the association between number of publications and perceived
years to eradication.

Survey results were first analyzed descriptively. Following Francis
Galton's example, we naively take the average of all responses as the
likely point estimate for event probabilities, and the totality of the
responses to each numeric question as the likely confidence interval of
those likelihoods and time frames.

Quantitative analysis was carried out in R language {[}35{]}. All
analysis code, as well as the code used for the identification and
contacting of participants, is publicly available at
\url{https://github.com/joebrew/malaria_survey}.

Qualitative analysis of free text comments was carried out using
thematic content analysis, with inductive open coding {[}36{]}.
Participants were invited to provide ``any general comments on the
timeline and likelihood of global eradication''. Thematic content
analysis {[}37{]} was employed to code responses following the 6-phase
approach laid out by Braun and Clarke {[}38{]}. The approach was
inductive, used open-coding to identify latent themes, and underwent
several iterations in which codes were modified, discarded and created.
Using the RQDA software to assist in data management and theme coding
{[}39{]}, four subject themes were identified. Comments were
additionally coded as either descriptive (comments pertaining to the
``problem'' of malaria eradication) or presciptive (pertaining to
potential ``solutions'' for eradicating malaria). Finally, free-text
comments were scored for overall sentiment polarity {[}40{]}.

\section{Results}\label{results}

\begin{figure}[h]

{\centering \includegraphics{paper_files/figure-latex/unnamed-chunk-5-1}

}

\caption{Perceptions of likelihood of eradication}\label{fig:unnamed-chunk-5}
\end{figure}

A total of 884 researchers participated in the survey from the 7918
invitations sent (participation rate of 11.16\%). Areas of expertise
were non-exclusive and self-described, with participants having the
option to choose from up to 3 of 10 checkboxes, or to write in one or
more ``other'' areas of
expertise.\footnote{Response categories were Anthropology, Biochemistry, Bioinformatics, Biology, Chemistry, Clinical medicine, Drug discovery, Ecology, Economics, Entomology, Epidemiology, Geography, GIS, History, Immunology, Infectious disease, IT, Malaria, Medical entomology, Medicinal chemistry, Microbiology, Parasitology, Pharmacology, Pharmacy, Political science, Public health, Statistics, Vector biology, Vector control, and Virology.}
604 (68.3\%) participants declared three or fewer areas of expertise.

Participants had a total of 219 unique (self-described) areas of
expertise. The five most popular were Epidemiology (357), Information
Technology (344), Parasitology (319), Biology (277), Clinical medicine
(207).

\subsection*{Quantitative results}

Most participants saw eradication as extremely unlikely in the next
10-30 years, but increasingly likely thereafter. Figure 2 shows the
distribution of year-specific likelihood perceptions (panels A-E), as
well as an illustration of how both likelihood and uncertainty grow over
time (panel F). At the 40 year mark, the distribution of perceived
likelihood of eradication appears ``normal'', and by 50 years it is
slightly shifted to the right (ie, consensus is towards eradication more
probable than not).

In regards to responses to perceived years until eradication, 59 (0.7\%)
were either blank or uninteligible, whereas 825 participants responded.
Among respondants, 616 (74.7 \%) estimated that it would be 50 or more
years until eradication.

Respondents were qualitatively different from non-respondents.
Importantly, the average number of total author-specific citations was
40.91 among respondents, but 92.92 among non-respondents. This suggests
a tendency for more senior or impactful researchers not to respond. When
examining the number of average citations per article, the difference
between respondents remained: 4.75 among respondents, and 8.95 among
non-respondents, highlighting the greater impact of non-respondents
relative to respondents. Males responded at a greater rate (12.18) than
females (9.14).

\begin{longtable}[]{@{}llrrl@{}}
\caption{Response rate by author characteristics}\tabularnewline
\toprule
Variable & Characteristic & Responded & Invited & Response
rate\tabularnewline
\midrule
\endfirsthead
\toprule
Variable & Characteristic & Responded & Invited & Response
rate\tabularnewline
\midrule
\endhead
Sex & Female & 209 & 2287 & 9.14 \%\tabularnewline
& Male & 358 & 2939 & 12.18 \%\tabularnewline
& NA & 317 & 2692 & 11.78 \%\tabularnewline
Citations & 0-5 & 621 & 3299 & 18.82 \%\tabularnewline
& 6-99 & 179 & 3270 & 5.47 \%\tabularnewline
& \textgreater{} 99 & 84 & 1349 & 6.23 \%\tabularnewline
\bottomrule
\end{longtable}

Selection bias is not of concern in the case of differential response if
the groups for whom there are differences are not different in terms of
the outcome variable. This was the case for sex: males responded at a
significantly greater rate than females (p \textless{} 0.001), but were
not statistically significantly different in regards to
pessimism/optimism (ie, time frame or likelihood of eradication). In the
case of researcher impact (as measured by the total number of
citations), selection bias plays an important role: being highly-cited
was associated both with eradication ``pessimism'' as well as likelihood
of non-response. In other words, our pool of respondents was less
highly-cited than our pool of invitees, and among respondents, those who
were highly-cited tended to be more pessimistic.

In order to de-bias sample selection, we employed Heckman's two-step
correction method as well as simple binomial logistic regression model
to estimate the likelihood of response as a function of sex and (binned)
number of citations. To the extent that the two methods presented nearly
identical value, we present here the results of the latter. Having
estimated the odds of survey participation, we then used the inverse of
the selection model's predictions as weights in a simple linear model to
adjust our estimates. We run a separate weighted model to estimate the
likelihood of eradication at 10, 20, 30, 40, and 50 years. Figure 3
shows both the aggregated perceived likelihood of eradication over time
before and after adjusting for sample selection based on binned number
of publications. Our adjusted and unadjusted estimates coincide in the
long-term, but diverge sharply in the near-term; adjustment suggests
that had our pool of respondents been more representative, the average
perceived likelihood of near-term eradcation would have been much lower.

\begin{figure}[h]

{\centering \includegraphics{paper_files/figure-latex/unnamed-chunk-11-1}

}

\caption{Aggregated perceived likelihood of eradication over time, adjusted for sample selection and unadjusted.}\label{fig:unnamed-chunk-11}
\end{figure}

\subsection{Qualitative analysis of
comments}\label{qualitative-analysis-of-comments}

Of the 884 who responded to the survey, 540 (61.09\%) provided a
comment. Relative to non-commenters, commenters were more optimistic on
average, but also more polarized in opinion. The three subject themes
identified through iterative, open coding were:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  \emph{Solutions}: Comments pertaining to the innovations required to
  achieve eradication, priorities, and the desirability of certain
  approaches.
\item
  \emph{Systemic challenges}: comments pertaining to political, social,
  environmental or logistical issues related to eradication.
\item
  \emph{Complexity}: comments which focus on the multi-dimensional
  components of eradication.
\end{enumerate}

Comments were also classified as descriptive or prescriptive. A majority
(59.26\%) were descriptive. Descriptive commenters were more pessimistic
(in regards to perceived years until eradication) than prescriptive
commenters, though this difference did not reach the level of
statistical significance (p = 0.21). Descriptive comments also received
sentiment polarity scores which were more negative than prescriptive
comments, although again this difference did not reach the level of
statistical significance (p = 0.18).

In regards to \textbf{solutions}, comments largely pertained to the
necessity of further technological advances and innovations. One
participant wrote that ``currently available technology can't achieve
{[}eradication{]}, even if delivered optimally''; another argued that
eradication could not be achieved without a ``game-changing
innovation'', whereas multiple others referred to the need for
``transformative'' technologies:

\begin{quote}
We can't achieve eradication with our current tools. We'd need new medicines, a better vaccine, and maybe other vector control tools.
\end{quote}

Many noted the need to ``overcome the challenge of drug resistance''.
More than 10\% of commenters noted the need for an effective vaccine.
Genetic engineering was mentioned by several commenters as a promising
means to achieve eradication quickly. Most comments coded as
``solutions'' were presciptive in nature, often suggesting the nature of
the needed innovation, with a heavy slant towards pharmaceutical options
and vaccination.

\textbf{Systemic challenges} to malaria eradication were noted by the
majority of commenters. Comments in this category can be divided into
four sub-themes: (i) lack of coordination, (ii) lack of good
surveillance and health services delivery, (iii) lack of political will
and (iv) poverty. In direct contrast to the previous comments, many
emphasized that ``we already have the tools to achieve eradication'' and
that the only piece lacking was ``robust health systems''. Many
commenters noted problems of coordination, as illustrated in the below
quote.

\begin{quote}
It will be very difficult to eradicate malaria... not because we don't have the technologies, which we already have... the problem is politics. Malaria doesn't stop in (sic) borders of a country and it would take a joint effort of a lot of political leaders to get programs in place to fight malaria. Unfortunately I don't see this happening anytime soon.
\end{quote}

Others echoed the sentiment, with many comments focusing on the need of
strong surveillance and treatment delivery systems. Many commenters
focused on other reasons for stagnating progress, such as ``weak or
failing health systems\ldots{}due to political unwillingness or
conflict''. Many noted that malaria is a ``disease of poverty'', with
``social injustice'' as the root cause. Some made the sequential
argument that ``eradication of poverty'' must preceed disease
eradication. Along the same lines, one commenter wrote:

\begin{quote}
Eradication requires a full systems-wide approach, not a disease-specific approach. The eradication of smallpox was a triumph of management, not medicine or technology.
\end{quote}

Another noted that the survey ``left off the list the most important
factor - economic development''. Many echoed the sentiment, stating that
``with no economic development, you cannot have eradication'' and that
poverty is the ``cause'' of malaria. Comments coded as ``systemic''
tended to be descriptive and more pessimistic than others.

\textbf{Complexity} was a relatively rare category (\textless{}20\% of
all comments), those whose comments were coded as the ``complexity''
category were more pessimistic than average in regards to the timeline
and likelihood of eradication. Many commenters highlighted the inherent
challenges in the epidemiology of malaria, such as the changing dynamics
of malaria transmission, the resilience of the parasite and vector,
climate change, and the inability to aim interventions accurately with
an ``ever-moving target''. The potential for adaptation was highlighted
in reference both to the mosquito as well as the parasite itself. Many
comments addressed the fact that the conversation on eradication is
largely taking place within the public health community, whereas the
causes of malaria endemicity are largely orthogonal to public health
interventions, ``going beyond the health sector''. Several commenters
pointed out the multitude of prerequisite conditions for eradication to
even be considered feasible:

\begin{quote}
To my mind, this question is highly dependent on background context, e.g. global political and economic dynamics, as well as international conflict. Complete global eradication is an extremely singular goal that requires a vast array of necessary conditions - if any of these fail, eradication will not be achieved.  
\end{quote}

Many commenters thought that the terms ``eradication'' and ``malaria''
were so complex and nebulous that the public health practitioners should
avoid the them all together, so as to not repeat the mistakes of the WHO
GMP in the 1950s. For example, some highlighted that talking about
``malaria'' as one disease misses the mark, since the different species
of parasite and contexts in which they live make elimination in each
area very distinct from other areas. One commenter wrote that
eradication is a ``postwar'' idea that developed from the ``abandonment
of a broad sociopolitical understanding of the causes of disease, and
the emphasis on technological solutions.'' Many stated that global
malaria eradication was simply not possible, and two argued that it may
not be desirable or ethical. One stated that the concept was ``absurd''
and that ``I'm not even sure why people talk about it''. Another
questioned the utility of discussing ``eradication'' as a concept:

\begin{quote}
Eradication is a different objective than elimination. Elimination means that the disease is not endemic but could reappear even in a country like Norway if infrastructure breaks down. Elimination may be possible in poor endemic countries, following socioeconomic development. Eradication means that the parasite disapears from the planet, which is not realistic...
\end{quote}

Comments questioning the utility of eradication as a concept or goal
tended to be skeptical of its feasibility. Largely, they were
prescriptive, advocating for a re-framing of the conversation so that
the focus was not on an ``arbitrary'' goal like eradication, but rather
on scaling up control and making region-specific progress.

\section{Discussion}\label{discussion}

Approximately three-quarters of respondents believe that malaria will
not be eradicated in the next 50 years. When adjusted for selection
bias, the perceived likelihood of eradication in 50 years remains
similarly low, but estimates for shorter-term eradication are even
lower.

Eradication of a disease is a ``high stakes game'', exposed to multiple
competing - and at times contradictory - incentives from multiple
stakeholders {[}41{]}. Understanding these incentives, and the factors
which can alter them, is vital to understanding how eradication can
succeed, and where it is most vulnerable to failure. The return on
investment of eradication-specific interventions is affected by the fact
that most researchers agree that eradication will take a long time to
achieve. This, in turn, reduces the expected value of future benefits,
disincentivizing eradication-specific investment. Given this, it is
important to quantify the positive externalities of ``failed''
eradication; in areas of high endemicity, even if the goal of
elimination is not achieved, the reduction in burden or disease can
still make interventions cost-effective.

However, areas of high malaria endemicity are often also those with high
competing health costs. When estimating the return on investment of
malaria elimination initiatives, not only must one take into account the
potential benefits (even in the case of failure), but also the
opportunity costs (even in the case of success). After all, elimination
is not a binary success/failure proposition - an initiative should be
judged both on its epidemiological circumstances {[}42{]} as well as the
counterfactual improvements in health which could have been achieved via
other paths.

\subsection{Limitations}\label{limitations}

This paper has several limitations. Conceptually, academic researchers
are specialists - their narrow, field-specific view of eradication's
feasibility is of arguable reliability, given that they may be
unfamiliar with the operational, cultural and ``real-world'' challenges
of malaria eradication. Though crowds have been found to be more
``wise'' than individuals in many cases, the application of an approach
similar to the ``wisdom of crowds'' is not suitable to all classes of
problems {[}43{]}. Crowds can be susceptible to social biases {[}44{]}
(although this survey's anonimity largely protects against this issue),
and other biases may come in to play, especially given that our study
was of a crowd of ``specialists'', rather than the population as a
whole.

Four potential biases are worth mentioning specifically. (1)
``Conjunction fallacy'' suggests that the general goal of eradication
may seem less likely than the sum of the goals of country-specific
elimination. (2) A (reverse) variant of the ``hot hand fallacy'', in
which researchers may mistakenly base their assessment of current
chances of eradication on previous failures. (3) Parkinson's law of
triviality suggests that researchers may disproportionately see the
challenges of their own research (antimalarial drug resistance, etc.) as
larger or more relevant to the global eradication campaign than they
really are. (4) Finally, and ironically, ``optimism bias'' may play a
perverse role in researchers' responses; though eradication is certainly
a goal desired by all, one could argue that malaria research specialists
subconciously realize that they actually stand to lose out profesionally
in the case of eradication.

As with Keenan et al's survey of experts regarding the feasibility of
eradication of neglected tropical diseases, our survey detected
relatively high levels of eradication skepticism and did not delve into
whether researchers had clinical or operational experience, nor did it
assess opinions of program workers, nor did it explore complexities
pertaining to different types of or forms of existence of malaria.
Though our sample size was over twice Keenan's, this was largely due to
having contacted more authors, as our response rate was only one fourth
as large {[}32{]}.

This study included the first authors of indexed journals. Though
certainly a group with important knowledge related to malaria, this
misses malaria control program employees, health agency workers, and
other stakeholders. Their experiences and viewpoints may be different
from those of academics, and arguably more relevant. Additionally, in
public health journals, first authors are often more junior than their
collaborators. By focusing solely on first authors, we may have
unintentionally created a sample which is qualitatively different than
the true universe of malaria researchers; to the extent that in our
result pool researchers with less experience (as represented through
publications) tended to be more ``optimistic'' regarding eradication, it
is reasonable to assume that the restriction of first authors may have
lead to an overly optimistic sample, making the results of the survey
even more striking.

\subsection{Conclusion}\label{conclusion}

Our survey attempted to quantify the likelihood of, and time frame to,
malaria eradication by gauging the collective opinion of malaria
researchers. The findings of our survey show researchers expressing
hesitance about the likelihood of eradication and suggesting a long time
frame until it is achieved. The causes for scepticism are diverse, but
common themes were the need for innovation, systemic challenges, and the
complexity of the disease and its transmission.

The implication of these results are two-fold: (1) that those working or
investing in eradication-specific campaigns, as well as those modeling
these campaigns' hypothetical cost-effectiveness, should factor in
researchers' perceived low likelihood and long time frame when
calculating those campaigns' expected value; (2) that champions of
near-term eradication may need to make a more compelling case to malaria
researchers of eradication's feasibility, in order to better focus and
inspire the latter.

We have strived to present the results of our study without insinuation
regarding the ``true'' feasibility and timeframe of eradication, as only
time will tell whether the collective ``wisdom'' of researchers was
worth adhering to or not. The actual cost-effectiveness of eradication
interventions is not only a function of eradication's success, but also
of a number of other factors which are only knowable retrospectively.
This study's primary contribution is the provision of a snapshot of
perceptions of malaria researchers, whose opinions may be of value not
only to other researchers, but also to the malaria and public health
communities at large.

\section*{References}\label{references}
\addcontentsline{toc}{section}{References}

\hypertarget{refs}{}
\hypertarget{ref-White2014}{}
{[}1{]} N.J. White, S. Pukrittayakamee, T.T. Hien, M.A. Faiz, O.A.
Mokuolu, A.M. Dondorp, Malaria, The Lancet. 383 (2014) 723--735.
doi:\href{https://doi.org/10.1016/s0140-6736(13)60024-0}{10.1016/s0140-6736(13)60024-0}.

\hypertarget{ref-World2016}{}
{[}2{]} WHO, World Malaria Report, (2016).
\url{http://apps.who.int/iris/bitstream/10665/252038/1/9789241511711-eng.pdf?ua=1}.

\hypertarget{ref-Ashley2018}{}
{[}3{]} E.A. Ashley, A.P. Phyo, C.J. Woodrow, Malaria, The Lancet.
(2018).
doi:\href{https://doi.org/10.1016/s0140-6736(18)30324-6}{10.1016/s0140-6736(18)30324-6}.

\hypertarget{ref-Tanner2015}{}
{[}4{]} M. Tanner, B. Greenwood, C.J.M. Whitty, E.K. Ansah, R.N. Price,
A.M. Dondorp, L. von Seidlein, J.K. Baird, J.G. Beeson, F.J. Fowkes, J.
Hemingway, K. Marsh, F. Osier, Malaria eradication and elimination:
Views on how to translate a vision into reality, BMC Medicine. 13
(2015).
doi:\href{https://doi.org/10.1186/s12916-015-0384-6}{10.1186/s12916-015-0384-6}.

\hypertarget{ref-Hopkins2013}{}
{[}5{]} D.R. Hopkins, Disease eradication, New England Journal of
Medicine. 368 (2013) 54--63.
doi:\href{https://doi.org/10.1056/nejmra1200391}{10.1056/nejmra1200391}.

\hypertarget{ref-Rabinovich_2017}{}
{[}6{]} R.N. Rabinovich, C. Drakeley, A.A. Djimde, B.F. Hall, S.I. Hay,
J. Hemingway, D.C. Kaslow, A. Noor, F. Okumu, R. Steketee, et al.,
MalERA: An updated research agenda for malaria elimination and
eradication, PLOS Medicine. 14 (2017) e1002456.
doi:\href{https://doi.org/10.1371/journal.pmed.1002456}{10.1371/journal.pmed.1002456}.

\hypertarget{ref-TheLancet2011}{}
{[}7{]} T. Lancet, Malaria: Control vs elimination vs eradication, The
Lancet. 378 (2011) 1117.
doi:\href{https://doi.org/10.1016/s0140-6736(11)61489-x}{10.1016/s0140-6736(11)61489-x}.

\hypertarget{ref-Njera2011}{}
{[}8{]} J.A. Nájera, M. González-Silva, P.L. Alonso, Some lessons for
the future from the global malaria eradication programme (19551969),
PLoS Med. 8 (2011) e1000412.
doi:\href{https://doi.org/10.1371/journal.pmed.1000412}{10.1371/journal.pmed.1000412}.

\hypertarget{ref-Roberts2007}{}
{[}9{]} L. Roberts, M. Enserink, MALARIA: Did they really say ...
eradication?, Science. 318 (2007) 1544--1545.
doi:\href{https://doi.org/10.1126/science.318.5856.1544}{10.1126/science.318.5856.1544}.

\hypertarget{ref-Gates2014}{}
{[}10{]} B. Gates, We can eradicate malaria---Within a generation,
Breaking a Fever. (2014).
\url{https://www.gatesnotes.com/Health/Eradicating-Malaria-in-a-Generation}.

\hypertarget{ref-Snow2015}{}
{[}11{]} R.W. Snow, Global malaria eradication and the importance of
plasmodium falciparum epidemiology in africa, BMC Medicine. 13 (2015)
23.
doi:\href{https://doi.org/10.1186/s12916-014-0254-7}{10.1186/s12916-014-0254-7}.

\hypertarget{ref-Eckhoff2014}{}
{[}12{]} P.A. Eckhoff, C.A. Bever, J. Gerardin, E.A. Wenger, Fun with
maths: Exploring implications of mathematical models for malaria
eradication, Malar J. 13 (2014) 486.
doi:\href{https://doi.org/10.1186/1475-2875-13-486}{10.1186/1475-2875-13-486}.

\hypertarget{ref-Yamey2004}{}
{[}13{]} G. Yamey, Roll back malaria: A failing global health campaign,
BMJ. 328 (2004) 1086--1087.
doi:\href{https://doi.org/10.1136/bmj.328.7448.1086}{10.1136/bmj.328.7448.1086}.

\hypertarget{ref-Alonso2011}{}
{[}14{]} P.L. Alonso, G. Brown, M. Arevalo-Herrera, F. Binka, C.
Chitnis, F. Collins, O.K. Doumbo, B. Greenwood, B.F. Hall, M.M. Levine,
K. Mendis, R.D. Newman, C.V. Plowe, M.H. Rodríguez, R. Sinden, L.
Slutsker, M. Tanner, A research agenda to underpin malaria eradication,
PLoS Med. 8 (2011) e1000406.
doi:\href{https://doi.org/10.1371/journal.pmed.1000406}{10.1371/journal.pmed.1000406}.

\hypertarget{ref-WHO2015}{}
{[}15{]} Malaria policy advisory committee to the WHO: Conclusions and
recommendations of seventh biannual meeting, Malar J. 14 (2015).
doi:\href{https://doi.org/10.1186/s12936-015-0787-z}{10.1186/s12936-015-0787-z}.

\hypertarget{ref-Barrett2013}{}
{[}16{]} S. Barrett, Economic considerations for the eradication
endgame, Philosophical Transactions of the Royal Society B: Biological
Sciences. 368 (2013) 20120149--20120149.
doi:\href{https://doi.org/10.1098/rstb.2012.0149}{10.1098/rstb.2012.0149}.

\hypertarget{ref-Barrett_2006}{}
{[}17{]} S. Barrett, The smallpox eradication game, Public Choice. 130
(2006) 179--207.
doi:\href{https://doi.org/10.1007/s11127-006-9079-z}{10.1007/s11127-006-9079-z}.

\hypertarget{ref-Cutler_2010}{}
{[}18{]} D. Cutler, W. Fung, M. Kremer, M. Singhal, T. Vogl, Early-life
malaria exposure and adult outcomes: Evidence from malaria eradication
in india, American Economic Journal: Applied Economics. 2 (2010) 72--94.
doi:\href{https://doi.org/10.1257/app.2.2.72}{10.1257/app.2.2.72}.

\hypertarget{ref-Barofsky2015}{}
{[}19{]} J. Barofsky, T.D. Anekwe, C. Chase, Malaria eradication and
economic outcomes in sub-saharan africa: Evidence from uganda, Journal
of Health Economics. 44 (2015) 118--136.
doi:\href{https://doi.org/10.1016/j.jhealeco.2015.08.002}{10.1016/j.jhealeco.2015.08.002}.

\hypertarget{ref-Kastner2015}{}
{[}20{]} R.J. Kastner, C.M. Stone, P. Steinmann, M. Tanner, F. Tediosi,
What is needed to eradicate lymphatic filariasis? A model-based
assessment on the impact of scaling up mass drug administration
programs, PLOS Neglected Tropical Diseases. 9 (2015) e0004147.
doi:\href{https://doi.org/10.1371/journal.pntd.0004147}{10.1371/journal.pntd.0004147}.

\hypertarget{ref-Kastner2017}{}
{[}21{]} R.J. Kastner, E. Sicuri, C.M. Stone, G. Matwale, A. Onapa, F.
Tediosi, How much will it cost to eradicate lymphatic filariasis? An
analysis of the financial and economic costs of intensified efforts
against lymphatic filariasis, PLOS Neglected Tropical Diseases. 11
(2017) e0005934.
doi:\href{https://doi.org/10.1371/journal.pntd.0005934}{10.1371/journal.pntd.0005934}.

\hypertarget{ref-Kim2017}{}
{[}22{]} Y.E. Kim, W.A. Stolk, M. Tanner, F. Tediosi, Modelling the
health and economic impacts of the elimination of river blindness
(onchocerciasis) in africa, BMJ Global Health. 2 (2017) e000158.
doi:\href{https://doi.org/10.1136/bmjgh-2016-000158}{10.1136/bmjgh-2016-000158}.

\hypertarget{ref-Brady2017}{}
{[}23{]} O.J. Brady, H.C. Slater, P. Pemberton-Ross, E. Wenger, R.J.
Maude, A.C. Ghani, M.A. Penny, J. Gerardin, L.J. White, N. Chitnis, R.
Aguas, S.I. Hay, D.L. Smith, E.M. Stuckey, E.A. Okiro, T.A. Smith, L.C.
Okell, Role of mass drug administration in elimination of plasmodium
falciparum malaria: A consensus modelling study, The Lancet Global
Health. 5 (2017) e680--e687.
doi:\href{https://doi.org/10.1016/s2214-109x(17)30220-6}{10.1016/s2214-109x(17)30220-6}.

\hypertarget{ref-Kim2015}{}
{[}24{]} Y.E. Kim, E. Sicuri, F. Tediosi, Financial and economic costs
of the elimination and eradication of onchocerciasis (river blindness)
in africa, PLOS Neglected Tropical Diseases. 9 (2015) e0004056.
doi:\href{https://doi.org/10.1371/journal.pntd.0004056}{10.1371/journal.pntd.0004056}.

\hypertarget{ref-Slater2015}{}
{[}25{]} H.C. Slater, A. Ross, A.L. Ouédraogo, L.J. White, C. Nguon,
P.G. Walker, P. Ngor, R. Aguas, S.P. Silal, A.M. Dondorp, P.L. Barre, R.
Burton, R.W. Sauerwein, C. Drakeley, T.A. Smith, T. Bousema, A.C. Ghani,
Assessing the impact of next-generation rapid diagnostic tests on
plasmodium falciparum malaria elimination strategies, Nature. 528 (2015)
S94--S101.
doi:\href{https://doi.org/10.1038/nature16040}{10.1038/nature16040}.

\hypertarget{ref-Patouillard2017}{}
{[}26{]} E. Patouillard, J. Griffin, S. Bhatt, A. Ghani, R. Cibulskis,
Global investment targets for malaria control and elimination between
2016 and 2030, BMJ Global Health. 2 (2017) e000176.
doi:\href{https://doi.org/10.1136/bmjgh-2016-000176}{10.1136/bmjgh-2016-000176}.

\hypertarget{ref-Slater2017}{}
{[}27{]} H.C. Slater, L.C. Okell, A.C. Ghani, Mathematical modelling to
guide drug development for malaria elimination, Trends in Parasitology.
33 (2017) 175--184.
doi:\href{https://doi.org/10.1016/j.pt.2016.09.004}{10.1016/j.pt.2016.09.004}.

\hypertarget{ref-Winskill2017}{}
{[}28{]} P. Winskill, P.G. Walker, J.T. Griffin, A.C. Ghani, Modelling
the cost-effectiveness of introducing the RTS, s malaria vaccine
relative to scaling up other malaria interventions in sub-saharan
africa, BMJ Global Health. 2 (2017) e000090.
doi:\href{https://doi.org/10.1136/bmjgh-2016-000090}{10.1136/bmjgh-2016-000090}.

\hypertarget{ref-Morgan_2014}{}
{[}29{]} M.G. Morgan, Use (and abuse) of expert elicitation in support
of decision making for public policy, Proceedings of the National
Academy of Sciences. 111 (2014) 7176--7184.
doi:\href{https://doi.org/10.1073/pnas.1319946111}{10.1073/pnas.1319946111}.

\hypertarget{ref-Wallis2014}{}
{[}30{]} K.F. Wallis, Revisiting francis galton's forecasting
competition, Statistical Science. 29 (2014) 420--424.
doi:\href{https://doi.org/10.1214/14-sts468}{10.1214/14-sts468}.

\hypertarget{ref-Galton1907Voxpopuli}{}
{[}31{]} F. Galton, Vox populi, Nature. 75 (1907) 7.
doi:\href{https://doi.org/10.1038/075450a0}{10.1038/075450a0}.

\hypertarget{ref-Keenan2013}{}
{[}32{]} J.D. Keenan, P.J. Hotez, A. Amza, N.E. Stoller, B.D. Gaynor,
T.C. Porco, T.M. Lietman, Elimination and eradication of neglected
tropical diseases with mass drug administrations: A survey of experts,
PLoS Negl Trop Dis. 7 (2013) e2562.
doi:\href{https://doi.org/10.1371/journal.pntd.0002562}{10.1371/journal.pntd.0002562}.

\hypertarget{ref-Lincoln}{}
{[}33{]} L. Mullen, Gender: Predict gender from names using historical
data, 2015. \url{https://github.com/ropensci/gender}.

\hypertarget{ref-Kovalchik2015}{}
{[}34{]} S. Kovalchik, RISmed: Download content from ncbi databases,
2015. \url{https://CRAN.R-project.org/package=RISmed}.

\hypertarget{ref-R}{}
{[}35{]} R Core Team, R: A language and environment for statistical
computing, R Foundation for Statistical Computing, Vienna, Austria,
2015. \url{https://www.R-project.org/}.

\hypertarget{ref-Markey_2014}{}
{[}36{]} K. Markey, M. Tilki, G. Taylor, Reflecting on the challenges of
choosing and using a grounded theory approach, Nurse Researcher. 22
(2014) 16--22.
doi:\href{https://doi.org/10.7748/nr.22.2.16.e1272}{10.7748/nr.22.2.16.e1272}.

\hypertarget{ref-Vaismoradi_2016}{}
{[}37{]} M. Vaismoradi, J. Jones, H. Turunen, S. Snelgrove, Theme
development in qualitative content analysis and thematic analysis,
Journal of Nursing Education and Practice. 6 (2016).
doi:\href{https://doi.org/10.5430/jnep.v6n5p100}{10.5430/jnep.v6n5p100}.

\hypertarget{ref-Braun2006}{}
{[}38{]} V. Braun, V. Clarke, Using thematic analysis in psychology,
Qualitative Research in Psychology. 3 (2006) 77--101.
doi:\href{https://doi.org/10.1191/1478088706qp063oa}{10.1191/1478088706qp063oa}.

\hypertarget{ref-Ronggui2017}{}
{[}39{]} R. Huang, RQDA: R-based qualitative data analysis, 2017.
\url{http://rqda.r-forge.r-project.org}.

\hypertarget{ref-sentimentr2017}{}
{[}40{]} T.W. Rinker, sentimentr: Calculate text polarity sentiment,
University at Buffalo/SUNY, Buffalo, New York, 2017.
\url{http://github.com/trinker/sentimentr}.

\hypertarget{ref-barrett}{}
{[}41{]} S. Barrett, Why cooperate? The incentive to supply global
public goods, Oxford University Press, 2007.
\url{https://global.oup.com/academic/product/why-cooperate-9780199211890}.

\hypertarget{ref-Churcher_2014}{}
{[}42{]} T.S. Churcher, J.M. Cohen, J. Novotny, N. Ntshalintshali, S.
Kunene, S. Cauchemez, Measuring the path toward malaria elimination,
Science. 344 (2014) 1230--1232.
doi:\href{https://doi.org/10.1126/science.1251449}{10.1126/science.1251449}.

\hypertarget{ref-Mannes_2014}{}
{[}43{]} A.E. Mannes, J.B. Soll, R.P. Larrick, The wisdom of select
crowds., Journal of Personality and Social Psychology. 107 (2014)
276--299. doi:\href{https://doi.org/10.1037/a0036677}{10.1037/a0036677}.

\hypertarget{ref-Lorenz_2011}{}
{[}44{]} J. Lorenz, H. Rauhut, F. Schweitzer, D. Helbing, How social
influence can undermine the wisdom of crowd effect, Proceedings of the
National Academy of Sciences. 108 (2011) 9020--9025.
doi:\href{https://doi.org/10.1073/pnas.1008636108}{10.1073/pnas.1008636108}.

\end{document}

### 2018-04-23 paper.Rmd
format changes

@@
 ---
-title: 'Researchers'' perceptions of malaria eradication: findings from a mixed-methods
-  analysis of a large online survey'
-csl: elsevier-with-titles.csl
+title: "Researchers' perceptions of malaria eradication: findings from a mixed-methodsanalysis of a large online survey"
+csl: journal-of-health-economics.csl
 output:

### 2018-04-23 paper.tex
format changes

@@
 \hypersetup{unicode=true,
-            pdftitle={Researchers' perceptions of malaria eradication: findings from a mixed-methods analysis of a large online survey},
+            pdftitle={Researchers' perceptions of malaria eradication: findings from a mixed-methodsanalysis of a large online survey},
             pdfborder={0 0 0},
@@
   \title{Researchers' perceptions of malaria eradication: findings from a
-mixed-methods analysis of a large online survey}
+mixed-methodsanalysis of a large online survey}
   \pretitle{\vspace{\droptitle}\centering\huge}
@@
 of the 200 million annual cases as well as the half million annual
-deaths worldwide {[}1{]} {[}2{]} {[}3{]}. Malaria ``elimination'', the
-``interruption of all local transmission of the infection in a country
-or region'' {[}4{]} is actively being pursued by dozens of countries
-around the world, leading to a renewed push for ``eradication'' (``the
-worldwide interruption of transmission'') {[}5{]} {[}6{]} {[}7{]}.
+deaths worldwide (White et al., 2014) (WHO, 2016) (Ashley et al., 2018).
+Malaria ``elimination'', the ``interruption of all local transmission of
+the infection in a country or region'' (Tanner et al., 2015) is actively
+being pursued by dozens of countries around the world, leading to a
+renewed push for ``eradication'' (``the worldwide interruption of
+transmission'') (Hopkins, 2013) (Rabinovich et al., 2017) (Lancet,
+2011).
 
@@
 Organisation (WHO) established the Global Malaria Eradication Program in
-the 1950s {[}8{]}. In 1957, U.S. President Dwight Eisenhower told
-Congress that malaria could be expected to be eradicated in five years.
-Following the failure of the WHO's first attempt, the focus shifted away
-from global eradication towards local elimination and control
-strategies. In recent years, much of the discourse regarding malaria has
-shifted back to global eradication {[}9{]}, with funders, researchers,
-and public health practitioners rallying to the cause {[}4{]}. The Bill
-and Melinda Gates Foundation has begun actively promoting eradication as
-feasible ``within a generation'' {[}10{]}, and the WHO has set ambitious
-goals, stating the objective of eliminating malaria in 65 new endemic
-countries from 2015 through 2030 (Figure 1).
+the 1950s (Nájera et al., 2011). In 1957, U.S. President Dwight
+Eisenhower told Congress that malaria could be expected to be eradicated
+in five years. Following the failure of the WHO's first attempt, the
+focus shifted away from global eradication towards local elimination and
+control strategies. In recent years, much of the discourse regarding
+malaria has shifted back to global eradication (Roberts and Enserink,
+2007), with funders, researchers, and public health practitioners
+rallying to the cause (Tanner et al., 2015). The Bill and Melinda Gates
+Foundation has begun actively promoting eradication as feasible ``within
+a generation'' (Gates, 2014), and the WHO has set ambitious goals,
+stating the objective of eliminating malaria in 65 new endemic countries
+from 2015 through 2030 (Figure 1).
 
@@
 made eradication appear a more feasible goal, though not possible in the
-short term {[}11{]} {[}12{]}. From both administrative {[}13{]} and
-scientific {[}14{]} points of view, eradication has never before
-received so much attention.
+short term (Snow, 2015) (Eckhoff et al., 2014). From both administrative
+(Yamey, 2004) and scientific (Alonso et al., 2011) points of view,
+eradication has never before received so much attention.
 
@@
 of malaria eradication focuses on the \emph{how} rather than the
-\emph{if} and the \emph{when} {[}4{]}. The participants in the Malaria
-Eradication Research Agenda (MalERA) process, in particular, have guided
-research goals and identified gaps in order for elmination to occur
-{[}14{]} {[}6{]}. Though the MalERA authors firmly state that
-eradication is \emph{not} feasible given the ``current tools and state
-of knowledge'', mentions to the time frame are vague (``within the
-lifetime of young scientists just embarking on their careers'' {[}14{]}
-and ``in the longer term'' {[}6{]}) and no mention is made of the
+\emph{if} and the \emph{when} (Tanner et al., 2015). The participants in
+the Malaria Eradication Research Agenda (MalERA) process, in particular,
+have guided research goals and identified gaps in order for elmination
+to occur (Alonso et al., 2011) (Rabinovich et al., 2017). Though the
+MalERA authors firmly state that eradication is \emph{not} feasible
+given the ``current tools and state of knowledge'', mentions to the time
+frame are vague (``within the lifetime of young scientists just
+embarking on their careers'' (Alonso et al., 2011) and ``in the longer
+term'' (Rabinovich et al., 2017)) and no mention is made of the
 perception of the overall probability of achieving eradication.
@@
 and under what timeline malaria eradication could be achieved''
-{[}15{]}. Clarity on timeline and likelihood of eradication could inform
-forecasting of disease transmission, and plays a crucial role in the
-economic analysis of the expected value of malaria eradication
-initiatives, ultimately informing health policy decisions. But achieving
-clarity is difficult, given the many complex and interacting variables
-which affect malaria transmission, research funding, and technological
-development. The question of \emph{how} is complex enough, rendering
-questions of \emph{if} and \emph{when} even more difficult to answer.
+(``Malaria policy advisory committee to the WHO,'' 2015). Clarity on
+timeline and likelihood of eradication could inform forecasting of
+disease transmission, and plays a crucial role in the economic analysis
+of the expected value of malaria eradication initiatives, ultimately
+informing health policy decisions. But achieving clarity is difficult,
+given the many complex and interacting variables which affect malaria
+transmission, research funding, and technological development. The
+question of \emph{how} is complex enough, rendering questions of
+\emph{if} and \emph{when} even more difficult to answer.
 
@@
 current campaigns (smallpox and polio, respectively), and highlight the
-long term benefits in health and wealth to future generations {[}16{]}.
-One often cited figure is for smallpox eradication, in which the
-investment of each dollar led to a return of greater than 400 {[}17{]};
-unlike smallpox (for which analysis was able to be retrospectively
-constructed based on observed costs and benefits), in the case of a
-prevalent disease, forecasting models have to be used in order to
-prospectively estimate the value of an investment.
+long term benefits in health and wealth to future generations (Barrett,
+2013). One often cited figure is for smallpox eradication, in which the
+investment of each dollar led to a return of greater than 400 (Barrett,
+2006); unlike smallpox (for which analysis was able to be
+retrospectively constructed based on observed costs and benefits), in
+the case of a prevalent disease, forecasting models have to be used in
+order to prospectively estimate the value of an investment.
 \st{Additionally the estimated impact of malaria on economic indicators is heterogeneous, with singificant impact in areas of Sub-Saharan Africa - where the endemicity is high - and little to no impact in areas of low endemicity}
-{[}18{]} {[}19{]}.
+(Cutler et al., 2010) (Barofsky et al., 2015).
 
@@
 well as the pre-requisite role and magnitude of certain interventions
-{[}20{]}. A similar modeling framework was then used to estimate the
-cost of eradication {[}21{]}. A recent modeling analysis on
-onchocerciasis eradication, based on a disease transmission model,
-showed that the costs of elimination (relative to staying in ``control
-mode'') in Africa would be far lower even in the short term, thanks to
-the improvements it would lead to in both treatment times and prevented
-surveillance costs. Given the relative proximity of eradication, and the
-narrow geographic scope, the authors were also able to estimate the
-timeline to eradication {[}22{]}.
+(Kastner et al., 2015). A similar modeling framework was then used to
+estimate the cost of eradication (Kastner et al., 2017). A recent
+modeling analysis on onchocerciasis eradication, based on a disease
+transmission model, showed that the costs of elimination (relative to
+staying in ``control mode'') in Africa would be far lower even in the
+short term, thanks to the improvements it would lead to in both
+treatment times and prevented surveillance costs. Given the relative
+proximity of eradication, and the narrow geographic scope, the authors
+were also able to estimate the timeline to eradication (Kim et al.,
+2017).
 
@@
 rigorous studies exist forecasting the effect of certain tools and
-strategies relative to alternatives {[}23{]} or aimed at regional
-disease elimination {[}24{]}, these analyses do not endeavor to estimate
-the generalization of those tools or strategies to other areas.
-Globally, where mathematical modeling has been used for the purposes of
-forecasting the future epidemiology of malaria, the methods have
-generally been aimed at optimizing elimination methods {[}25{]},
-determining whether a strategy is scalable {[}23{]}, guiding funding and
-drug development {[}26{]} {[}27{]}, or comparing a range of hypothetical
-morbidity scenarios {[}28{]}, rather than assessing the likelihood of or
-time until the occurrence of those scenarios. In other words,
+strategies relative to alternatives (Brady et al., 2017) or aimed at
+regional disease elimination (Kim et al., 2015), these analyses do not
+endeavor to estimate the generalization of those tools or strategies to
+other areas. Globally, where mathematical modeling has been used for the
+purposes of forecasting the future epidemiology of malaria, the methods
+have generally been aimed at optimizing elimination methods (Slater et
+al., 2015), determining whether a strategy is scalable (Brady et al.,
+2017), guiding funding and drug development (Patouillard et al., 2017)
+(Slater et al., 2017), or comparing a range of hypothetical morbidity
+scenarios (Winskill et al., 2017), rather than assessing the likelihood
+of or time until the occurrence of those scenarios. In other words,
 researchers are (rightfully) focused on the \emph{how} of eradication,
@@
 elicitation as a means to reduce uncertainty and inform decision making
-{[}29{]}.
+(Morgan, 2014).
 \st{But experts can sometimes be mistaken, a fact implicitly recognized when patients request a "second opinion" from another doctor when facing uncertainty.
@@
 showed that the crowds' aggregated estimates of cow's weight formed a
-quasi-normal distribution centered around the true weight {[}30{]}
-{[}31{]}, averaging the perceptions of many can be more accurate than
-taking the opinion of any single expert, since the biases of diverse
-viewpoints can be complementary and symbiotic. Measuring consensus and
-discord among disease-specific researchers from a variety of disciplines
-can serve as a barometer of (informed) opinion, both guiding resources
-and identifying areas of concern {[}32{]}.
+quasi-normal distribution centered around the true weight (Wallis, 2014)
+(Galton, 1907), averaging the perceptions of many can be more accurate
+than taking the opinion of any single expert, since the biases of
+diverse viewpoints can be complementary and symbiotic. Measuring
+consensus and discord among disease-specific researchers from a variety
+of disciplines can serve as a barometer of (informed) opinion, both
+guiding resources and identifying areas of concern (Keenan et al.,
+2013).
 
@@
 order to do this, we used data from the North Atlantic Population
-Project, and U.S. government {[}33{]}. We also calculated the total
-number of citations which each author had received, as well as the total
-number of articles authored. We binned total citations into three
+Project, and U.S. government (Mullen, 2015). We also calculated the
+total number of citations which each author had received, as well as the
+total number of articles authored. We binned total citations into three
 categories: 0-5 (junior-level researchers, PhD students, etc.); 6-99
@@
 articles and citations from the PubMed database was carried out using
-the RISmed package {[}34{]}. Information retrieved about authors was
-used to de-bias paramaters in an ordinary least squares regression,
-analyzing the association between number of publications and perceived
-years to eradication.
+the RISmed package (Kovalchik, 2015). Information retrieved about
+authors was used to de-bias paramaters in an ordinary least squares
+regression, analyzing the association between number of publications and
+perceived years to eradication.
 
@@
 
-Quantitative analysis was carried out in R language {[}35{]}. All
-analysis code, as well as the code used for the identification and
+Quantitative analysis was carried out in R language (R Core Team, 2015).
+All analysis code, as well as the code used for the identification and
 contacting of participants, is publicly available at
@@
 Qualitative analysis of free text comments was carried out using
-thematic content analysis, with inductive open coding {[}36{]}.
-Participants were invited to provide ``any general comments on the
-timeline and likelihood of global eradication''. Thematic content
-analysis {[}37{]} was employed to code responses following the 6-phase
-approach laid out by Braun and Clarke {[}38{]}. The approach was
-inductive, used open-coding to identify latent themes, and underwent
-several iterations in which codes were modified, discarded and created.
-Using the RQDA software to assist in data management and theme coding
-{[}39{]}, four subject themes were identified. Comments were
-additionally coded as either descriptive (comments pertaining to the
-``problem'' of malaria eradication) or presciptive (pertaining to
-potential ``solutions'' for eradicating malaria). Finally, free-text
-comments were scored for overall sentiment polarity {[}40{]}.
+thematic content analysis, with inductive open coding (Markey et al.,
+2014). Participants were invited to provide ``any general comments on
+the timeline and likelihood of global eradication''. Thematic content
+analysis (Vaismoradi et al., 2016) was employed to code responses
+following the 6-phase approach laid out by Braun and Clarke (Braun and
+Clarke, 2006). The approach was inductive, used open-coding to identify
+latent themes, and underwent several iterations in which codes were
+modified, discarded and created. Using the RQDA software to assist in
+data management and theme coding (Huang, 2017), four subject themes were
+identified. Comments were additionally coded as either descriptive
+(comments pertaining to the ``problem'' of malaria eradication) or
+presciptive (pertaining to potential ``solutions'' for eradicating
+malaria). Finally, free-text comments were scored for overall sentiment
+polarity (Rinker, 2017).
 
@@
 competing - and at times contradictory - incentives from multiple
-stakeholders {[}41{]}. Understanding these incentives, and the factors
-which can alter them, is vital to understanding how eradication can
-succeed, and where it is most vulnerable to failure. The return on
+stakeholders (Barrett, 2007). Understanding these incentives, and the
+factors which can alter them, is vital to understanding how eradication
+can succeed, and where it is most vulnerable to failure. The return on
 investment of eradication-specific interventions is affected by the fact
@@
 is not a binary success/failure proposition - an initiative should be
-judged both on its epidemiological circumstances {[}42{]} as well as the
-counterfactual improvements in health which could have been achieved via
-other paths.
+judged both on its epidemiological circumstances (Churcher et al., 2014)
+as well as the counterfactual improvements in health which could have
+been achieved via other paths.
 
@@
 similar to the ``wisdom of crowds'' is not suitable to all classes of
-problems {[}43{]}. Crowds can be susceptible to social biases {[}44{]}
-(although this survey's anonimity largely protects against this issue),
-and other biases may come in to play, especially given that our study
-was of a crowd of ``specialists'', rather than the population as a
-whole.
+problems (Mannes et al., 2014). Crowds can be susceptible to social
+biases (Lorenz et al., 2011) (although this survey's anonimity largely
+protects against this issue), and other biases may come in to play,
+especially given that our study was of a crowd of ``specialists'',
+rather than the population as a whole.
 
@@
 having contacted more authors, as our response rate was only one fourth
-as large {[}32{]}.
+as large (Keenan et al., 2013).
 
@@
 \hypertarget{refs}{}
+\hypertarget{ref-Alonso2011}{}
+Alonso, P.L., Brown, G., Arevalo-Herrera, M., Binka, F., Chitnis, C.,
+Collins, F., Doumbo, O.K., Greenwood, B., Hall, B.F., Levine, M.M.,
+Mendis, K., Newman, R.D., Plowe, C.V., Rodríguez, M.H., Sinden, R.,
+Slutsker, L., Tanner, M., 2011. A research agenda to underpin malaria
+eradication. PLoS Med 8, e1000406.
+\url{https://doi.org/10.1371/journal.pmed.1000406}
+
+\hypertarget{ref-Ashley2018}{}
+Ashley, E.A., Phyo, A.P., Woodrow, C.J., 2018. Malaria. The Lancet.
+\url{https://doi.org/10.1016/s0140-6736(18)30324-6}
+
+\hypertarget{ref-Barofsky2015}{}
+Barofsky, J., Anekwe, T.D., Chase, C., 2015. Malaria eradication and
+economic outcomes in sub-saharan africa: Evidence from uganda. Journal
+of Health Economics 44, 118--136.
+\url{https://doi.org/10.1016/j.jhealeco.2015.08.002}
+
+\hypertarget{ref-Barrett2013}{}
+Barrett, S., 2013. Economic considerations for the eradication endgame.
+Philosophical Transactions of the Royal Society B: Biological Sciences
+368, 20120149--20120149. \url{https://doi.org/10.1098/rstb.2012.0149}
+
+\hypertarget{ref-barrett}{}
+Barrett, S., 2007. Why cooperate? The incentive to supply global public
+goods. Oxford University Press.
+
+\hypertarget{ref-Barrett_2006}{}
+Barrett, S., 2006. The smallpox eradication game. Public Choice 130,
+179--207. \url{https://doi.org/10.1007/s11127-006-9079-z}
+
+\hypertarget{ref-Brady2017}{}
+Brady, O.J., Slater, H.C., Pemberton-Ross, P., Wenger, E., Maude, R.J.,
+Ghani, A.C., Penny, M.A., Gerardin, J., White, L.J., Chitnis, N., Aguas,
+R., Hay, S.I., Smith, D.L., Stuckey, E.M., Okiro, E.A., Smith, T.A.,
+Okell, L.C., 2017. Role of mass drug administration in elimination of
+plasmodium falciparum malaria: A consensus modelling study. The Lancet
+Global Health 5, e680--e687.
+\url{https://doi.org/10.1016/s2214-109x(17)30220-6}
+
+\hypertarget{ref-Braun2006}{}
+Braun, V., Clarke, V., 2006. Using thematic analysis in psychology.
+Qualitative Research in Psychology 3, 77--101.
+\url{https://doi.org/10.1191/1478088706qp063oa}
+
+\hypertarget{ref-Churcher_2014}{}
+Churcher, T.S., Cohen, J.M., Novotny, J., Ntshalintshali, N., Kunene,
+S., Cauchemez, S., 2014. Measuring the path toward malaria elimination.
+Science 344, 1230--1232. \url{https://doi.org/10.1126/science.1251449}
+
+\hypertarget{ref-Cutler_2010}{}
+Cutler, D., Fung, W., Kremer, M., Singhal, M., Vogl, T., 2010.
+Early-life malaria exposure and adult outcomes: Evidence from malaria
+eradication in india. American Economic Journal: Applied Economics 2,
+72--94. \url{https://doi.org/10.1257/app.2.2.72}
+
+\hypertarget{ref-Eckhoff2014}{}
+Eckhoff, P.A., Bever, C.A., Gerardin, J., Wenger, E.A., 2014. Fun with
+maths: Exploring implications of mathematical models for malaria
+eradication. Malar J 13, 486.
+\url{https://doi.org/10.1186/1475-2875-13-486}
+
+\hypertarget{ref-Galton1907Voxpopuli}{}
+Galton, F., 1907. Vox populi. Nature 75, 7.
+\url{https://doi.org/10.1038/075450a0}
+
+\hypertarget{ref-Gates2014}{}
+Gates, B., 2014. We can eradicate malaria---Within a generation.
+Breaking a Fever.
+
+\hypertarget{ref-Hopkins2013}{}
+Hopkins, D.R., 2013. Disease eradication. New England Journal of
+Medicine 368, 54--63. \url{https://doi.org/10.1056/nejmra1200391}
+
+\hypertarget{ref-Ronggui2017}{}
+Huang, R., 2017. RQDA: R-based qualitative data analysis.
+
+\hypertarget{ref-Kastner2017}{}
+Kastner, R.J., Sicuri, E., Stone, C.M., Matwale, G., Onapa, A., Tediosi,
+F., 2017. How much will it cost to eradicate lymphatic filariasis? An
+analysis of the financial and economic costs of intensified efforts
+against lymphatic filariasis. PLOS Neglected Tropical Diseases 11,
+e0005934. \url{https://doi.org/10.1371/journal.pntd.0005934}
+
+\hypertarget{ref-Kastner2015}{}
+Kastner, R.J., Stone, C.M., Steinmann, P., Tanner, M., Tediosi, F.,
+2015. What is needed to eradicate lymphatic filariasis? A model-based
+assessment on the impact of scaling up mass drug administration
+programs. PLOS Neglected Tropical Diseases 9, e0004147.
+\url{https://doi.org/10.1371/journal.pntd.0004147}
+
+\hypertarget{ref-Keenan2013}{}
+Keenan, J.D., Hotez, P.J., Amza, A., Stoller, N.E., Gaynor, B.D., Porco,
+T.C., Lietman, T.M., 2013. Elimination and eradication of neglected
+tropical diseases with mass drug administrations: A survey of experts.
+PLoS Negl Trop Dis 7, e2562.
+\url{https://doi.org/10.1371/journal.pntd.0002562}
+
+\hypertarget{ref-Kim2015}{}
+Kim, Y.E., Sicuri, E., Tediosi, F., 2015. Financial and economic costs
+of the elimination and eradication of onchocerciasis (river blindness)
+in africa. PLOS Neglected Tropical Diseases 9, e0004056.
+\url{https://doi.org/10.1371/journal.pntd.0004056}
+
+\hypertarget{ref-Kim2017}{}
+Kim, Y.E., Stolk, W.A., Tanner, M., Tediosi, F., 2017. Modelling the
+health and economic impacts of the elimination of river blindness
+(onchocerciasis) in africa. BMJ Global Health 2, e000158.
+\url{https://doi.org/10.1136/bmjgh-2016-000158}
+
+\hypertarget{ref-Kovalchik2015}{}
+Kovalchik, S., 2015. RISmed: Download content from ncbi databases.
+
+\hypertarget{ref-TheLancet2011}{}
+Lancet, T., 2011. Malaria: Control vs elimination vs eradication. The
+Lancet 378, 1117. \url{https://doi.org/10.1016/s0140-6736(11)61489-x}
+
+\hypertarget{ref-Lorenz_2011}{}
+Lorenz, J., Rauhut, H., Schweitzer, F., Helbing, D., 2011. How social
+influence can undermine the wisdom of crowd effect. Proceedings of the
+National Academy of Sciences 108, 9020--9025.
+\url{https://doi.org/10.1073/pnas.1008636108}
+
+\hypertarget{ref-WHO2015}{}
+Malaria policy advisory committee to the WHO: Conclusions and
+recommendations of seventh biannual meeting, 2015.. Malar J 14.
+\url{https://doi.org/10.1186/s12936-015-0787-z}
+
+\hypertarget{ref-Mannes_2014}{}
+Mannes, A.E., Soll, J.B., Larrick, R.P., 2014. The wisdom of select
+crowds. Journal of Personality and Social Psychology 107, 276--299.
+\url{https://doi.org/10.1037/a0036677}
+
+\hypertarget{ref-Markey_2014}{}
+Markey, K., Tilki, M., Taylor, G., 2014. Reflecting on the challenges of
+choosing and using a grounded theory approach. Nurse Researcher 22,
+16--22. \url{https://doi.org/10.7748/nr.22.2.16.e1272}
+
+\hypertarget{ref-Morgan_2014}{}
+Morgan, M.G., 2014. Use (and abuse) of expert elicitation in support of
+decision making for public policy. Proceedings of the National Academy
+of Sciences 111, 7176--7184.
+\url{https://doi.org/10.1073/pnas.1319946111}
+
+\hypertarget{ref-Lincoln}{}
+Mullen, L., 2015. Gender: Predict gender from names using historical
+data.
+
+\hypertarget{ref-Njera2011}{}
+Nájera, J.A., González-Silva, M., Alonso, P.L., 2011. Some lessons for
+the future from the global malaria eradication programme (19551969).
+PLoS Med 8, e1000412. \url{https://doi.org/10.1371/journal.pmed.1000412}
+
+\hypertarget{ref-Patouillard2017}{}
+Patouillard, E., Griffin, J., Bhatt, S., Ghani, A., Cibulskis, R., 2017.
+Global investment targets for malaria control and elimination between
+2016 and 2030. BMJ Global Health 2, e000176.
+\url{https://doi.org/10.1136/bmjgh-2016-000176}
+
+\hypertarget{ref-R}{}
+R Core Team, 2015. R: A language and environment for statistical
+computing. R Foundation for Statistical Computing, Vienna, Austria.
+
+\hypertarget{ref-Rabinovich_2017}{}
+Rabinovich, R.N., Drakeley, C., Djimde, A.A., Hall, B.F., Hay, S.I.,
+Hemingway, J., Kaslow, D.C., Noor, A., Okumu, F., Steketee, R., al.,
+2017. MalERA: An updated research agenda for malaria elimination and
+eradication. PLOS Medicine 14, e1002456.
+\url{https://doi.org/10.1371/journal.pmed.1002456}
+
+\hypertarget{ref-sentimentr2017}{}
+Rinker, T.W., 2017. sentimentr: Calculate text polarity sentiment.
+University at Buffalo/SUNY, Buffalo, New York.
+
+\hypertarget{ref-Roberts2007}{}
+Roberts, L., Enserink, M., 2007. MALARIA: Did they really say ...
+eradication? Science 318, 1544--1545.
+\url{https://doi.org/10.1126/science.318.5856.1544}
+
+\hypertarget{ref-Slater2017}{}
+Slater, H.C., Okell, L.C., Ghani, A.C., 2017. Mathematical modelling to
+guide drug development for malaria elimination. Trends in Parasitology
+33, 175--184. \url{https://doi.org/10.1016/j.pt.2016.09.004}
+
+\hypertarget{ref-Slater2015}{}
+Slater, H.C., Ross, A., Ouédraogo, A.L., White, L.J., Nguon, C., Walker,
+P.G., Ngor, P., Aguas, R., Silal, S.P., Dondorp, A.M., Barre, P.L.,
+Burton, R., Sauerwein, R.W., Drakeley, C., Smith, T.A., Bousema, T.,
+Ghani, A.C., 2015. Assessing the impact of next-generation rapid
+diagnostic tests on plasmodium falciparum malaria elimination
+strategies. Nature 528, S94--S101.
+\url{https://doi.org/10.1038/nature16040}
+
+\hypertarget{ref-Snow2015}{}
+Snow, R.W., 2015. Global malaria eradication and the importance of
+plasmodium falciparum epidemiology in africa. BMC Medicine 13, 23.
+\url{https://doi.org/10.1186/s12916-014-0254-7}
+
+\hypertarget{ref-Tanner2015}{}
+Tanner, M., Greenwood, B., Whitty, C.J.M., Ansah, E.K., Price, R.N.,
+Dondorp, A.M., Seidlein, L. von, Baird, J.K., Beeson, J.G., Fowkes,
+F.J., Hemingway, J., Marsh, K., Osier, F., 2015. Malaria eradication and
+elimination: Views on how to translate a vision into reality. BMC
+Medicine 13. \url{https://doi.org/10.1186/s12916-015-0384-6}
+
+\hypertarget{ref-Vaismoradi_2016}{}
+Vaismoradi, M., Jones, J., Turunen, H., Snelgrove, S., 2016. Theme
+development in qualitative content analysis and thematic analysis.
+Journal of Nursing Education and Practice 6.
+\url{https://doi.org/10.5430/jnep.v6n5p100}
+
+\hypertarget{ref-Wallis2014}{}
+Wallis, K.F., 2014. Revisiting francis galton's forecasting competition.
+Statistical Science 29, 420--424.
+\url{https://doi.org/10.1214/14-sts468}
+
 \hypertarget{ref-White2014}{}
-{[}1{]} N.J. White, S. Pukrittayakamee, T.T. Hien, M.A. Faiz, O.A.
-Mokuolu, A.M. Dondorp, Malaria, The Lancet. 383 (2014) 723--735.
-doi:\href{https://doi.org/10.1016/s0140-6736(13)60024-0}{10.1016/s0140-6736(13)60024-0}.
+White, N.J., Pukrittayakamee, S., Hien, T.T., Faiz, M.A., Mokuolu, O.A.,
+Dondorp, A.M., 2014. Malaria. The Lancet 383, 723--735.
+\url{https://doi.org/10.1016/s0140-6736(13)60024-0}
 
 \hypertarget{ref-World2016}{}
-{[}2{]} WHO, World Malaria Report, (2016).
-\url{http://apps.who.int/iris/bitstream/10665/252038/1/9789241511711-eng.pdf?ua=1}.
-
-\hypertarget{ref-Ashley2018}{}
-{[}3{]} E.A. Ashley, A.P. Phyo, C.J. Woodrow, Malaria, The Lancet.
-(2018).
-doi:\href{https://doi.org/10.1016/s0140-6736(18)30324-6}{10.1016/s0140-6736(18)30324-6}.
-
-\hypertarget{ref-Tanner2015}{}
-{[}4{]} M. Tanner, B. Greenwood, C.J.M. Whitty, E.K. Ansah, R.N. Price,
-A.M. Dondorp, L. von Seidlein, J.K. Baird, J.G. Beeson, F.J. Fowkes, J.
-Hemingway, K. Marsh, F. Osier, Malaria eradication and elimination:
-Views on how to translate a vision into reality, BMC Medicine. 13
-(2015).
-doi:\href{https://doi.org/10.1186/s12916-015-0384-6}{10.1186/s12916-015-0384-6}.
-
-\hypertarget{ref-Hopkins2013}{}
-{[}5{]} D.R. Hopkins, Disease eradication, New England Journal of
-Medicine. 368 (2013) 54--63.
-doi:\href{https://doi.org/10.1056/nejmra1200391}{10.1056/nejmra1200391}.
-
-\hypertarget{ref-Rabinovich_2017}{}
-{[}6{]} R.N. Rabinovich, C. Drakeley, A.A. Djimde, B.F. Hall, S.I. Hay,
-J. Hemingway, D.C. Kaslow, A. Noor, F. Okumu, R. Steketee, et al.,
-MalERA: An updated research agenda for malaria elimination and
-eradication, PLOS Medicine. 14 (2017) e1002456.
-doi:\href{https://doi.org/10.1371/journal.pmed.1002456}{10.1371/journal.pmed.1002456}.
-
-\hypertarget{ref-TheLancet2011}{}
-{[}7{]} T. Lancet, Malaria: Control vs elimination vs eradication, The
-Lancet. 378 (2011) 1117.
-doi:\href{https://doi.org/10.1016/s0140-6736(11)61489-x}{10.1016/s0140-6736(11)61489-x}.
-
-\hypertarget{ref-Njera2011}{}
-{[}8{]} J.A. Nájera, M. González-Silva, P.L. Alonso, Some lessons for
-the future from the global malaria eradication programme (19551969),
-PLoS Med. 8 (2011) e1000412.
-doi:\href{https://doi.org/10.1371/journal.pmed.1000412}{10.1371/journal.pmed.1000412}.
-
-\hypertarget{ref-Roberts2007}{}
-{[}9{]} L. Roberts, M. Enserink, MALARIA: Did they really say ...
-eradication?, Science. 318 (2007) 1544--1545.
-doi:\href{https://doi.org/10.1126/science.318.5856.1544}{10.1126/science.318.5856.1544}.
-
-\hypertarget{ref-Gates2014}{}
-{[}10{]} B. Gates, We can eradicate malaria---Within a generation,
-Breaking a Fever. (2014).
-\url{https://www.gatesnotes.com/Health/Eradicating-Malaria-in-a-Generation}.
-
-\hypertarget{ref-Snow2015}{}
-{[}11{]} R.W. Snow, Global malaria eradication and the importance of
-plasmodium falciparum epidemiology in africa, BMC Medicine. 13 (2015)
-23.
-doi:\href{https://doi.org/10.1186/s12916-014-0254-7}{10.1186/s12916-014-0254-7}.
-
-\hypertarget{ref-Eckhoff2014}{}
-{[}12{]} P.A. Eckhoff, C.A. Bever, J. Gerardin, E.A. Wenger, Fun with
-maths: Exploring implications of mathematical models for malaria
-eradication, Malar J. 13 (2014) 486.
-doi:\href{https://doi.org/10.1186/1475-2875-13-486}{10.1186/1475-2875-13-486}.
-
-\hypertarget{ref-Yamey2004}{}
-{[}13{]} G. Yamey, Roll back malaria: A failing global health campaign,
-BMJ. 328 (2004) 1086--1087.
-doi:\href{https://doi.org/10.1136/bmj.328.7448.1086}{10.1136/bmj.328.7448.1086}.
-
-\hypertarget{ref-Alonso2011}{}
-{[}14{]} P.L. Alonso, G. Brown, M. Arevalo-Herrera, F. Binka, C.
-Chitnis, F. Collins, O.K. Doumbo, B. Greenwood, B.F. Hall, M.M. Levine,
-K. Mendis, R.D. Newman, C.V. Plowe, M.H. Rodríguez, R. Sinden, L.
-Slutsker, M. Tanner, A research agenda to underpin malaria eradication,
-PLoS Med. 8 (2011) e1000406.
-doi:\href{https://doi.org/10.1371/journal.pmed.1000406}{10.1371/journal.pmed.1000406}.
-
-\hypertarget{ref-WHO2015}{}
-{[}15{]} Malaria policy advisory committee to the WHO: Conclusions and
-recommendations of seventh biannual meeting, Malar J. 14 (2015).
-doi:\href{https://doi.org/10.1186/s12936-015-0787-z}{10.1186/s12936-015-0787-z}.
-
-\hypertarget{ref-Barrett2013}{}
-{[}16{]} S. Barrett, Economic considerations for the eradication
-endgame, Philosophical Transactions of the Royal Society B: Biological
-Sciences. 368 (2013) 20120149--20120149.
-doi:\href{https://doi.org/10.1098/rstb.2012.0149}{10.1098/rstb.2012.0149}.
-
-\hypertarget{ref-Barrett_2006}{}
-{[}17{]} S. Barrett, The smallpox eradication game, Public Choice. 130
-(2006) 179--207.
-doi:\href{https://doi.org/10.1007/s11127-006-9079-z}{10.1007/s11127-006-9079-z}.
-
-\hypertarget{ref-Cutler_2010}{}
-{[}18{]} D. Cutler, W. Fung, M. Kremer, M. Singhal, T. Vogl, Early-life
-malaria exposure and adult outcomes: Evidence from malaria eradication
-in india, American Economic Journal: Applied Economics. 2 (2010) 72--94.
-doi:\href{https://doi.org/10.1257/app.2.2.72}{10.1257/app.2.2.72}.
-
-\hypertarget{ref-Barofsky2015}{}
-{[}19{]} J. Barofsky, T.D. Anekwe, C. Chase, Malaria eradication and
-economic outcomes in sub-saharan africa: Evidence from uganda, Journal
-of Health Economics. 44 (2015) 118--136.
-doi:\href{https://doi.org/10.1016/j.jhealeco.2015.08.002}{10.1016/j.jhealeco.2015.08.002}.
-
-\hypertarget{ref-Kastner2015}{}
-{[}20{]} R.J. Kastner, C.M. Stone, P. Steinmann, M. Tanner, F. Tediosi,
-What is needed to eradicate lymphatic filariasis? A model-based
-assessment on the impact of scaling up mass drug administration
-programs, PLOS Neglected Tropical Diseases. 9 (2015) e0004147.
-doi:\href{https://doi.org/10.1371/journal.pntd.0004147}{10.1371/journal.pntd.0004147}.
-
-\hypertarget{ref-Kastner2017}{}
-{[}21{]} R.J. Kastner, E. Sicuri, C.M. Stone, G. Matwale, A. Onapa, F.
-Tediosi, How much will it cost to eradicate lymphatic filariasis? An
-analysis of the financial and economic costs of intensified efforts
-against lymphatic filariasis, PLOS Neglected Tropical Diseases. 11
-(2017) e0005934.
-doi:\href{https://doi.org/10.1371/journal.pntd.0005934}{10.1371/journal.pntd.0005934}.
-
-\hypertarget{ref-Kim2017}{}
-{[}22{]} Y.E. Kim, W.A. Stolk, M. Tanner, F. Tediosi, Modelling the
-health and economic impacts of the elimination of river blindness
-(onchocerciasis) in africa, BMJ Global Health. 2 (2017) e000158.
-doi:\href{https://doi.org/10.1136/bmjgh-2016-000158}{10.1136/bmjgh-2016-000158}.
-
-\hypertarget{ref-Brady2017}{}
-{[}23{]} O.J. Brady, H.C. Slater, P. Pemberton-Ross, E. Wenger, R.J.
-Maude, A.C. Ghani, M.A. Penny, J. Gerardin, L.J. White, N. Chitnis, R.
-Aguas, S.I. Hay, D.L. Smith, E.M. Stuckey, E.A. Okiro, T.A. Smith, L.C.
-Okell, Role of mass drug administration in elimination of plasmodium
-falciparum malaria: A consensus modelling study, The Lancet Global
-Health. 5 (2017) e680--e687.
-doi:\href{https://doi.org/10.1016/s2214-109x(17)30220-6}{10.1016/s2214-109x(17)30220-6}.
-
-\hypertarget{ref-Kim2015}{}
-{[}24{]} Y.E. Kim, E. Sicuri, F. Tediosi, Financial and economic costs
-of the elimination and eradication of onchocerciasis (river blindness)
-in africa, PLOS Neglected Tropical Diseases. 9 (2015) e0004056.
-doi:\href{https://doi.org/10.1371/journal.pntd.0004056}{10.1371/journal.pntd.0004056}.
-
-\hypertarget{ref-Slater2015}{}
-{[}25{]} H.C. Slater, A. Ross, A.L. Ouédraogo, L.J. White, C. Nguon,
-P.G. Walker, P. Ngor, R. Aguas, S.P. Silal, A.M. Dondorp, P.L. Barre, R.
-Burton, R.W. Sauerwein, C. Drakeley, T.A. Smith, T. Bousema, A.C. Ghani,
-Assessing the impact of next-generation rapid diagnostic tests on
-plasmodium falciparum malaria elimination strategies, Nature. 528 (2015)
-S94--S101.
-doi:\href{https://doi.org/10.1038/nature16040}{10.1038/nature16040}.
-
-\hypertarget{ref-Patouillard2017}{}
-{[}26{]} E. Patouillard, J. Griffin, S. Bhatt, A. Ghani, R. Cibulskis,
-Global investment targets for malaria control and elimination between
-2016 and 2030, BMJ Global Health. 2 (2017) e000176.
-doi:\href{https://doi.org/10.1136/bmjgh-2016-000176}{10.1136/bmjgh-2016-000176}.
-
-\hypertarget{ref-Slater2017}{}
-{[}27{]} H.C. Slater, L.C. Okell, A.C. Ghani, Mathematical modelling to
-guide drug development for malaria elimination, Trends in Parasitology.
-33 (2017) 175--184.
-doi:\href{https://doi.org/10.1016/j.pt.2016.09.004}{10.1016/j.pt.2016.09.004}.
+WHO, 2016. World Malaria Report.
 
 \hypertarget{ref-Winskill2017}{}
-{[}28{]} P. Winskill, P.G. Walker, J.T. Griffin, A.C. Ghani, Modelling
+Winskill, P., Walker, P.G., Griffin, J.T., Ghani, A.C., 2017. Modelling
 the cost-effectiveness of introducing the RTS, s malaria vaccine
 relative to scaling up other malaria interventions in sub-saharan
-africa, BMJ Global Health. 2 (2017) e000090.
-doi:\href{https://doi.org/10.1136/bmjgh-2016-000090}{10.1136/bmjgh-2016-000090}.
-
-\hypertarget{ref-Morgan_2014}{}
-{[}29{]} M.G. Morgan, Use (and abuse) of expert elicitation in support
-of decision making for public policy, Proceedings of the National
-Academy of Sciences. 111 (2014) 7176--7184.
-doi:\href{https://doi.org/10.1073/pnas.1319946111}{10.1073/pnas.1319946111}.
-
-\hypertarget{ref-Wallis2014}{}
-{[}30{]} K.F. Wallis, Revisiting francis galton's forecasting
-competition, Statistical Science. 29 (2014) 420--424.
-doi:\href{https://doi.org/10.1214/14-sts468}{10.1214/14-sts468}.
-
-\hypertarget{ref-Galton1907Voxpopuli}{}
-{[}31{]} F. Galton, Vox populi, Nature. 75 (1907) 7.
-doi:\href{https://doi.org/10.1038/075450a0}{10.1038/075450a0}.
-
-\hypertarget{ref-Keenan2013}{}
-{[}32{]} J.D. Keenan, P.J. Hotez, A. Amza, N.E. Stoller, B.D. Gaynor,
-T.C. Porco, T.M. Lietman, Elimination and eradication of neglected
-tropical diseases with mass drug administrations: A survey of experts,
-PLoS Negl Trop Dis. 7 (2013) e2562.
-doi:\href{https://doi.org/10.1371/journal.pntd.0002562}{10.1371/journal.pntd.0002562}.
-
-\hypertarget{ref-Lincoln}{}
-{[}33{]} L. Mullen, Gender: Predict gender from names using historical
-data, 2015. \url{https://github.com/ropensci/gender}.
-
-\hypertarget{ref-Kovalchik2015}{}
-{[}34{]} S. Kovalchik, RISmed: Download content from ncbi databases,
-2015. \url{https://CRAN.R-project.org/package=RISmed}.
-
-\hypertarget{ref-R}{}
-{[}35{]} R Core Team, R: A language and environment for statistical
-computing, R Foundation for Statistical Computing, Vienna, Austria,
-2015. \url{https://www.R-project.org/}.
-
-\hypertarget{ref-Markey_2014}{}
-{[}36{]} K. Markey, M. Tilki, G. Taylor, Reflecting on the challenges of
-choosing and using a grounded theory approach, Nurse Researcher. 22
-(2014) 16--22.
-doi:\href{https://doi.org/10.7748/nr.22.2.16.e1272}{10.7748/nr.22.2.16.e1272}.
-
-\hypertarget{ref-Vaismoradi_2016}{}
-{[}37{]} M. Vaismoradi, J. Jones, H. Turunen, S. Snelgrove, Theme
-development in qualitative content analysis and thematic analysis,
-Journal of Nursing Education and Practice. 6 (2016).
-doi:\href{https://doi.org/10.5430/jnep.v6n5p100}{10.5430/jnep.v6n5p100}.
-
-\hypertarget{ref-Braun2006}{}
-{[}38{]} V. Braun, V. Clarke, Using thematic analysis in psychology,
-Qualitative Research in Psychology. 3 (2006) 77--101.
-doi:\href{https://doi.org/10.1191/1478088706qp063oa}{10.1191/1478088706qp063oa}.
-
-\hypertarget{ref-Ronggui2017}{}
-{[}39{]} R. Huang, RQDA: R-based qualitative data analysis, 2017.
-\url{http://rqda.r-forge.r-project.org}.
-
-\hypertarget{ref-sentimentr2017}{}
-{[}40{]} T.W. Rinker, sentimentr: Calculate text polarity sentiment,
-University at Buffalo/SUNY, Buffalo, New York, 2017.
-\url{http://github.com/trinker/sentimentr}.
-
-\hypertarget{ref-barrett}{}
-{[}41{]} S. Barrett, Why cooperate? The incentive to supply global
-public goods, Oxford University Press, 2007.
-\url{https://global.oup.com/academic/product/why-cooperate-9780199211890}.
-
-\hypertarget{ref-Churcher_2014}{}
-{[}42{]} T.S. Churcher, J.M. Cohen, J. Novotny, N. Ntshalintshali, S.
-Kunene, S. Cauchemez, Measuring the path toward malaria elimination,
-Science. 344 (2014) 1230--1232.
-doi:\href{https://doi.org/10.1126/science.1251449}{10.1126/science.1251449}.
-
-\hypertarget{ref-Mannes_2014}{}
-{[}43{]} A.E. Mannes, J.B. Soll, R.P. Larrick, The wisdom of select
-crowds., Journal of Personality and Social Psychology. 107 (2014)
-276--299. doi:\href{https://doi.org/10.1037/a0036677}{10.1037/a0036677}.
-
-\hypertarget{ref-Lorenz_2011}{}
-{[}44{]} J. Lorenz, H. Rauhut, F. Schweitzer, D. Helbing, How social
-influence can undermine the wisdom of crowd effect, Proceedings of the
-National Academy of Sciences. 108 (2011) 9020--9025.
-doi:\href{https://doi.org/10.1073/pnas.1008636108}{10.1073/pnas.1008636108}.
+africa. BMJ Global Health 2, e000090.
+\url{https://doi.org/10.1136/bmjgh-2016-000090}
+
+\hypertarget{ref-Yamey2004}{}
+Yamey, G., 2004. Roll back malaria: A failing global health campaign.
+BMJ 328, 1086--1087. \url{https://doi.org/10.1136/bmj.328.7448.1086}
 

### 2018-04-24 paper.tex
final for submission

@@
 \hypersetup{unicode=true,
-            pdftitle={Researchers' perceptions of malaria eradication: findings from a mixed-methodsanalysis of a large online survey},
+            pdftitle={Researchers' perceptions of malaria eradication: findings from a mixed-methods analysis of a large online survey},
             pdfborder={0 0 0},
@@
   \title{Researchers' perceptions of malaria eradication: findings from a
-mixed-methodsanalysis of a large online survey}
+mixed-methods analysis of a large online survey}
   \pretitle{\vspace{\droptitle}\centering\huge}
@@
 
+\usepackage{setspace}
+\doublespacing
+
+\usepackage[right, modulo]{lineno}
+\linenumbers
+
 \begin{document}
 \maketitle
-
-\begin{center}
-\begin{large}
-
-Joe Brew\footremember{isglobal}{Barcelona Institute for Global Health: c/ Rosselló, 132, 5è 2a.
-08036, Barcelona, Spain}\footremember{cism}{Centro de Investigação em Saúde de Manhiça: Vila da Manhiça, Bairro Cambeve, Rua 12, Distrito da Manhiça, CP 1929, Maputo, Mozambique}\footremember{vu}{VU University Amsterdam: De Boelelaan 1105, 1081 HV Amsterdam, Netherlands}, Menno Pradhan\footrecall{vu}\footremember{uva}{University of Amsterdam: REC E, Roetersstraat 11, Amsterdam, Netherlands}, Jacqueline Broerse\footrecall{vu}, Elisa Sicuri\footrecall{isglobal}\footremember{icl}{Imperial College London: South Kensington Campus, London SW7 2AZ, U.K.}\footrecall{cism}
-
-\end{large}
-\end{center}
-
-\vspace{5mm}
 
@@
 Quantifying an event's probability and time frame is essential for calculating its expected value.
-Uuncertainty regarding feasibility makes it difficult for policymakers and public health practitioners to forecast the return on investment of malaria eradication.
+Uncertainty regarding feasibility makes it difficult for policymakers and public health practitioners to forecast the return on investment of malaria eradication.
 Since the opportunity cost of investments in eradication-specific interventions can be high - particularly in contexts with other urgent health priorities - understanding eradication's expected value is essential.
 In a large online survey of malaria researchers (n = 844), we query perceptions regarding the likelihood and time frame of eradication.
-We assess pessimism/optimism (via the proxy of years-to-eradication), and adjust for selection bias.
+We assess perceived years to and likelihood of eradication, and adjust for selection bias.
 We also carry out a qualitative analysis of the free-form comments provided by 61\% of respondents.
@@
 \end{center}
+
+\vspace{10mm}
 
@@
       \subsection*{Keywords}
-        Malaria, eradication, elimination, mixed methods, survey, crowdsourcing 
+        Malaria; eradication; elimination; mixed methods; survey; crowdsourcing 
     }%
 }
+
+\newpage
 
@@
 
-{\centering \includegraphics{paper_files/figure-latex/unnamed-chunk-4-1}
+{\centering \includegraphics{paper_files/figure-latex/unnamed-chunk-3-1}
 
@@
 
-\caption{Countries with malaria: Observed and WHO objectives}\label{fig:unnamed-chunk-4}
+\caption{Countries with malaria: Observed and WHO objectives}\label{fig:unnamed-chunk-3}
 \end{figure}
@@
 the case of a prevalent disease, forecasting models have to be used in
-order to prospectively estimate the value of an investment.
-\st{Additionally the estimated impact of malaria on economic indicators is heterogeneous, with singificant impact in areas of Sub-Saharan Africa - where the endemicity is high - and little to no impact in areas of low endemicity}
+order to prospectively estimate the value of an investment. Additionally
+the estimated impact of malaria on economic indicators is heterogeneous,
+with singificant impact in areas of Sub-Saharan Africa - where the
+endemicity is high - and little to no impact in areas of low endemicity
 (Cutler et al., 2010) (Barofsky et al., 2015).
@@
 support, motivate researchers, and focus the efforts of public health
-practitioners. But to the extent that malaria eradication (by
-definition) has never occurred, the parameters needed for a ex-post
-cost-benefit analysis are unknown. Nonetheless, prospectively estimating
-eradication's return on investment is crucial to deciding when and how
-to pursue the goal, especially in light of the high direct and
-opportunity costs of eradication-specific interventions. One approach to
-cost-benefit analysis is the use of mathematical and stochastic models.
-These have been applied to diseases which are closer to eradication than
-malaria, since the uncertainty around model input parameters is less,
-requiring fewer cascading assumptions in order to present possible
-comparative scenarios. For example, Kastner et al. were able to describe
-4 relatively realistic pathways to Lympathic Filariasis eradication, as
-well as the pre-requisite role and magnitude of certain interventions
-(Kastner et al., 2015). A similar modeling framework was then used to
-estimate the cost of eradication (Kastner et al., 2017). A recent
-modeling analysis on onchocerciasis eradication, based on a disease
-transmission model, showed that the costs of elimination (relative to
-staying in ``control mode'') in Africa would be far lower even in the
-short term, thanks to the improvements it would lead to in both
-treatment times and prevented surveillance costs. Given the relative
-proximity of eradication, and the narrow geographic scope, the authors
-were also able to estimate the timeline to eradication (Kim et al.,
-2017).
-
-This level of detail and specificity in modeling the cost-benefit
+practitioners. The recently established Lancet Commission on malaria
+eradication states that ``eradication is the only acceptable end goal''
+(while acknowledging that there exists ``scepticism about {[}its{]}
+technical feasibility'') (Chen et al., 2018). To the extent that malaria
+eradication (by definition) has never occurred, the parameters needed
+for a ex-post cost-benefit analysis are unknown. Nonetheless,
+prospectively estimating eradication's return on investment is crucial
+to deciding when and how to pursue the goal, especially in light of the
+high direct and opportunity costs of eradication-specific interventions.
+One approach to economic evaluation is the use of mathematical and
+stochastic models. These have been applied to diseases which are closer
+to eradication than malaria, since the uncertainty around model input
+parameters is less, requiring fewer cascading assumptions in order to
+present possible comparative scenarios. For example, Kastner et al. were
+able to describe 4 relatively realistic pathways to Lympathic Filariasis
+eradication, as well as the pre-requisite role and magnitude of certain
+interventions (Kastner et al., 2015). A similar modeling framework was
+then used to estimate the cost of eradication (Kastner et al., 2017). A
+recent modeling analysis on onchocerciasis eradication, based on a
+disease transmission model, showed that the costs of elimination
+(relative to staying in ``control mode'') in Africa would be far lower
+even in the short term, thanks to the improvements it would lead to in
+both treatment times and prevented surveillance costs. Given the
+relative proximity of eradication, and the narrow geographic scope, the
+authors were also able to estimate the timeline to eradication (Kim et
+al., 2017).
+
+This level of detail and specificity in the economic evaluation
 landscape of malaria eradication, unfortunately, is not possible (or at
@@
 (to the authors' knowledge) estimating the likelihood and time frame of
-eradication, or its derivative cost-benefit ratio. While a great deal of
-rigorous studies exist forecasting the effect of certain tools and
-strategies relative to alternatives (Brady et al., 2017) or aimed at
-regional disease elimination (Kim et al., 2015), these analyses do not
-endeavor to estimate the generalization of those tools or strategies to
-other areas. Globally, where mathematical modeling has been used for the
-purposes of forecasting the future epidemiology of malaria, the methods
-have generally been aimed at optimizing elimination methods (Slater et
-al., 2015), determining whether a strategy is scalable (Brady et al.,
-2017), guiding funding and drug development (Patouillard et al., 2017)
-(Slater et al., 2017), or comparing a range of hypothetical morbidity
-scenarios (Winskill et al., 2017), rather than assessing the likelihood
-of or time until the occurrence of those scenarios. In other words,
-researchers are (rightfully) focused on the \emph{how} of eradication,
-rather than the forecasting of its timeframe or likelihood, the lack of
-attention paid to the latter likely being a reflection of its
-complexity, not lack of importance.
+eradication, or its derivative cost-benefit ratio. Globally, where
+mathematical modeling has been used for the purposes of forecasting the
+future epidemiology of malaria, the methods have generally been aimed at
+optimizing elimination methods (Slater et al., 2015), determining
+whether a strategy is scalable (Brady et al., 2017), guiding funding and
+drug development (Patouillard et al., 2017) (Slater et al., 2017), or
+comparing a range of hypothetical morbidity scenarios (Winskill et al.,
+2017), rather than assessing the likelihood of or time until the
+occurrence of those scenarios.
 
@@
 elicitation as a means to reduce uncertainty and inform decision making
-(Morgan, 2014).
-\st{But experts can sometimes be mistaken, a fact implicitly recognized when patients request a "second opinion" from another doctor when facing uncertainty.
-Additionally, relying on only a small panel of experts for a problem as complex as malaria exposes one to bias, just as an overly concentrated investment portfolio exposes one to more risk.}
-As Sir Francis Galton demonstrated in his famous study in which he
-showed that the crowds' aggregated estimates of cow's weight formed a
-quasi-normal distribution centered around the true weight (Wallis, 2014)
-(Galton, 1907), averaging the perceptions of many can be more accurate
-than taking the opinion of any single expert, since the biases of
-diverse viewpoints can be complementary and symbiotic. Measuring
-consensus and discord among disease-specific researchers from a variety
-of disciplines can serve as a barometer of (informed) opinion, both
-guiding resources and identifying areas of concern (Keenan et al.,
+(Morgan, 2014). As Francis Galton demonstrated in his famous study in
+which he showed that the crowds' aggregated estimates of cow's weight
+formed a quasi-normal distribution centered around the true weight
+(Wallis, 2014) (Galton, 1907), averaging the perceptions of many can be
+more accurate than taking the opinion of any single expert, since the
+biases of diverse viewpoints can be complementary and symbiotic.
+Measuring consensus and discord among disease-specific researchers from
+a variety of disciplines can serve as a barometer of (informed) opinion,
+both guiding resources and identifying areas of concern (Keenan et al.,
 2013).
@@
 
+Though the case-specific marginal cost of eradication can be expected to
+be high (relative to a simple control approach), successful eradication
+would mean massive recurring savings in the long-term (Barrett, 2013).
+However, to the extent that the case-specific marginal cost of
+prevention in an eradication campaign is high, estimating the likelihood
+of success is fundamental to the correct distribution of resources,
+particularly in low-income environments.
+
 We propose that the aggregation of malaria researchers' perceptions
@@
 expected value of malaria eradication efforts.
-
-\st{A great deal of previous research from serveral endemic areas already covers the cost per case prevented [@Sicuri2011] [@Silumbe2015] [@Btto2016] [@IlungaIlunga2014] [@Dalaba2015].
-Likewise, literature exists which could serve as a model for quantifying the location-specific opportunity costs associated with funneling funds towards malaria eradication [@Stuckey2014] [@White2011] [@Korenromp2012].
-The correct discount rate for estimating the value of future lives saved is more of a philosophical question than an economic one.
-This leaves only the probability and time-frame to eradication, questions which have been addressed anecdotally, but never answered quantitatively.}
-
-\st{Though the case-specific marginal cost of eradication can be expected to be high (relative to a simple control approach), successful eradication would mean massive recurring savings in the long-term [@Barrett2013].
-However, to the extent that the case-specific marginal cost of prevention in an eradication campaign is high, estimating the likelihood of success is fundamental to the correct distribution of resources, particularly in low-income environments.
-}
 
@@
 
-{\centering \includegraphics{paper_files/figure-latex/unnamed-chunk-5-1}
+{\centering \includegraphics{paper_files/figure-latex/unnamed-chunk-4-1}
 
@@
 
-\caption{Perceptions of likelihood of eradication}\label{fig:unnamed-chunk-5}
+\caption{Perceptions of likelihood of eradication}\label{fig:unnamed-chunk-4}
 \end{figure}
@@
 
-{\centering \includegraphics{paper_files/figure-latex/unnamed-chunk-11-1}
+{\centering \includegraphics{paper_files/figure-latex/unnamed-chunk-10-1}
 
@@
 
-\caption{Aggregated perceived likelihood of eradication over time, adjusted for sample selection and unadjusted.}\label{fig:unnamed-chunk-11}
+\caption{Aggregated perceived likelihood of eradication over time, adjusted for sample selection and unadjusted.}\label{fig:unnamed-chunk-10}
 \end{figure}
@@
 commenters, though this difference did not reach the level of
-statistical significance (p = 0.21). Descriptive comments also received
-sentiment polarity scores which were more negative than prescriptive
-comments, although again this difference did not reach the level of
-statistical significance (p = 0.18).
+statistical significance (p = 0.21 using Pearson's Chi-squared test).
+Descriptive comments also received sentiment polarity scores which were
+more negative than prescriptive comments, although again this difference
+did not reach the level of statistical significance (p = 0.18).
 
@@
 other stakeholders. Their experiences and viewpoints may be different
-from those of academics, and arguably more relevant. Additionally, in
-public health journals, first authors are often more junior than their
-collaborators. By focusing solely on first authors, we may have
-unintentionally created a sample which is qualitatively different than
-the true universe of malaria researchers; to the extent that in our
-result pool researchers with less experience (as represented through
-publications) tended to be more ``optimistic'' regarding eradication, it
-is reasonable to assume that the restriction of first authors may have
-lead to an overly optimistic sample, making the results of the survey
-even more striking.
+from those of academics, and arguably more relevant. Our de-biasing
+method accounts for different response rates of ``senior'' vs.
+``junior'' researchers, but does not take into account the fact that
+first authors are generally more junior than senior authors (ie, the
+pool from which we sampled may have been biased itself). To the extent
+that in our results suggests that those with less experience (as
+represented through publications) tended to be more ``optimistic''
+regarding eradication, it is reasonable to assume that the restriction
+of first authors may have lead to an overly optimistic sample, making
+the results of the survey even more striking.
 
@@
 
-Our survey attempted to quantify the likelihood of, and time frame to,
-malaria eradication by gauging the collective opinion of malaria
-researchers. The findings of our survey show researchers expressing
-hesitance about the likelihood of eradication and suggesting a long time
-frame until it is achieved. The causes for scepticism are diverse, but
-common themes were the need for innovation, systemic challenges, and the
-complexity of the disease and its transmission.
+The findings of our survey show researchers expressing hesitance about
+the likelihood of eradication and suggesting a long time frame until it
+is achieved. The causes for scepticism are diverse, but common themes
+were the need for innovation, systemic challenges, and the complexity of
+the disease and its transmission.
 
@@
 
+\hypertarget{ref-Chen2018}{}
+Chen, I., Cooney, R., Feachem, R.G.A., Lal, A., Mpanju-Shumbusho, W.,
+2018. The lancet commission on malaria eradication. The Lancet 391,
+1556--1558. \url{https://doi.org/10.1016/s0140-6736(18)30911-5}
+
 \hypertarget{ref-Churcher_2014}{}
@@
 \url{https://doi.org/10.1371/journal.pntd.0002562}
-
-\hypertarget{ref-Kim2015}{}
-Kim, Y.E., Sicuri, E., Tediosi, F., 2015. Financial and economic costs
-of the elimination and eradication of onchocerciasis (river blindness)
-in africa. PLOS Neglected Tropical Diseases 9, e0004056.
-\url{https://doi.org/10.1371/journal.pntd.0004056}
 

### 2020-04-15 legacy/paper.Rmd
updated

--- 2018-04-10 paper.Rmd
@@
 ---
-title: 'Researchers'' perceptions of malaria eradication: findings from a mixed-methods
-  analysis of a large online survey'
-csl: elsevier-with-titles.csl
+title: "Researchers' perceptions of malaria eradication: findings from a mixed-methods analysis of a large online survey"
+csl: journal-of-health-economics.csl
 output:
@@
                                     'uva'),
-                           institution = c('Barcelona Institute for Global Health',
-                                           'Imperial College London',
+                           institution = c('Barcelona Institute for Global Health, Hospital Clinic',
+                                           'Health Economics Group, Department of Infectious Disease Epidemiology, School of Public Health, Imperial College London',
                                            'Centro de Investigação em Saúde de Manhiça',
@@
 
-\begin{center}
-\begin{large}
+<!-- \begin{center} -->
+<!-- \begin{large} -->
 
-```{r, results = 'asis', eval = TRUE}
-make_author(authors = authors,
-            institutions = institutions)
-```
+<!-- ```{r, results = 'asis', eval = TRUE} -->
+<!-- make_author(authors = authors, -->
+<!--             institutions = institutions) -->
+<!-- ``` -->
 
-\end{large}
-\end{center}
+<!-- \end{large} -->
+<!-- \end{center} -->
 
-\vspace{5mm}
+<!-- \vspace{5mm} -->
 
@@
       \subsection*{Keywords}
-        Malaria, eradication, elimination, mixed methods, survey, crowdsourcing 
+        Malaria; eradication; elimination; mixed methods; survey; crowdsourcing 
     }%
 }
+
+<!-- ## Acknowledgements -->
+
+<!-- This research would not have been possible without the participation of the 844 malaria researchers who gave their time and insights.
+We are grateful for their willingness to contribute to this study.
+-->
+
+\newpage
 
@@
 One often cited figure is for smallpox eradication, in which the investment of each dollar led to a return of greater than 400 [@Barrett_2006]; unlike smallpox (for which analysis was able to be retrospectively constructed based on observed costs and benefits), in the case of a prevalent disease, forecasting models have to be used in order to prospectively estimate the value of an investment.
-\st{Additionally the estimated impact of malaria on economic indicators is heterogeneous, with singificant impact in areas of Sub-Saharan Africa - where the endemicity is high - and little to no impact in areas of low endemicity} [@Cutler_2010] [@Barofsky2015].
+Additionally the estimated impact of malaria on economic indicators is heterogeneous, with singificant impact in areas of Sub-Saharan Africa - where the endemicity is high - and little to no impact in areas of low endemicity [@Cutler_2010] [@Barofsky2015].
 
 The general objective of eradication serves to inspire, rally funder support, motivate researchers, and focus the efforts of public health practitioners.
-But to the extent that malaria eradication (by definition) has never occurred, the parameters needed for a ex-post cost-benefit analysis are unknown.
+The recently established Lancet Commission on malaria eradication states that "eradication is the only acceptable end goal" (while acknowledging that there exists "scepticism about [its] technical feasibility") [@Chen2018].
+To the extent that malaria eradication (by definition) has never occurred, the parameters needed for a ex-post cost-benefit analysis are unknown.
 Nonetheless, prospectively estimating eradication's return on investment is crucial to deciding when and how to pursue the goal, especially in light of the high direct and opportunity costs of eradication-specific interventions.
-One approach to cost-benefit analysis is the use of mathematical and stochastic models.
+One approach to economic evaluation is the use of mathematical and stochastic models.
 These have been applied to diseases which are closer to eradication than malaria, since the uncertainty around model input parameters is less, requiring fewer cascading assumptions in order to present possible comparative scenarios.
@@
 
-This level of detail and specificity in modeling the cost-benefit landscape of malaria eradication, unfortunately, is not possible (or at least not commonly undertaken), given its high prevalence and epidemiological complexity.
+This level of detail and specificity in the economic evaluation landscape of malaria eradication, unfortunately, is not possible (or at least not commonly undertaken), given its high prevalence and epidemiological complexity.
 In fact, there are no mathematical models (to the authors' knowledge) estimating the likelihood and time frame of eradication, or its derivative cost-benefit ratio.
-While a great deal of rigorous studies exist forecasting the effect of certain tools and strategies relative to alternatives [@Brady2017] or aimed at regional disease elimination [@Kim2015], these analyses do not endeavor to estimate the generalization of those tools or strategies to other areas.
 Globally, where mathematical modeling has been used for the purposes of forecasting the future epidemiology of malaria, the methods have generally been aimed at optimizing elimination methods [@Slater2015], determining whether a strategy is scalable [@Brady2017], guiding funding and drug development [@Patouillard2017] [@Slater2017], or comparing a range of hypothetical morbidity scenarios [@Winskill2017], rather than assessing the likelihood of or time until the occurrence of those scenarios.
-In other words, researchers are (rightfully) focused on the \emph{how} of eradication, rather than the forecasting of its timeframe or likelihood, the lack of attention paid to the latter likely being a reflection of its complexity, not lack of importance.
 
@@
 Many studies have shown value in expert elicitation as a means to reduce uncertainty and inform decision making [@Morgan_2014].
-\st{But experts can sometimes be mistaken, a fact implicitly recognized when patients request a "second opinion" from another doctor when facing uncertainty.
-Additionally, relying on only a small panel of experts for a problem as complex as malaria exposes one to bias, just as an overly concentrated investment portfolio exposes one to more risk.} As Sir Francis Galton demonstrated in his famous study in which he showed that the crowds' aggregated estimates of cow's weight formed a quasi-normal distribution centered around the true weight [@Wallis2014] [@Galton1907Voxpopuli], averaging the perceptions of many can be more accurate than taking the opinion of any single expert, since the biases of diverse viewpoints can be complementary and symbiotic.
+As Francis Galton demonstrated in his famous study in which he showed that the crowds' aggregated estimates of cow's weight formed a quasi-normal distribution centered around the true weight [@Wallis2014] [@Galton1907Voxpopuli], averaging the perceptions of many can be more accurate than taking the opinion of any single expert, since the biases of diverse viewpoints can be complementary and symbiotic.
 Measuring consensus and discord among disease-specific researchers from a variety of disciplines can serve as a barometer of (informed) opinion, both guiding resources and identifying areas of concern [@Keenan2013].
@@
 
+Though the case-specific marginal cost of eradication can be expected to be high (relative to a simple control approach), successful eradication would mean massive recurring savings in the long-term [@Barrett2013].
+However, to the extent that the case-specific marginal cost of prevention in an eradication campaign is high, estimating the likelihood of success is fundamental to the correct distribution of resources, particularly in low-income environments.
+
 We propose that the aggregation of malaria researchers' perceptions regarding the time frame and likelihood of eradication forms a probability distribution which can be used to estimate the expected value of eradication-specific investments.
@@
 In doing so, we aim to help guide the optimal distribution of health resources by informing estimations of the expected value of malaria eradication efforts.
-
-\st{A great deal of previous research from serveral endemic areas already covers the cost per case prevented [@Sicuri2011] [@Silumbe2015] [@Btto2016] [@IlungaIlunga2014] [@Dalaba2015].
-Likewise, literature exists which could serve as a model for quantifying the location-specific opportunity costs associated with funneling funds towards malaria eradication [@Stuckey2014] [@White2011] [@Korenromp2012].
-The correct discount rate for estimating the value of future lives saved is more of a philosophical question than an economic one.
-This leaves only the probability and time-frame to eradication, questions which have been addressed anecdotally, but never answered quantitatively.}
-
-\st{Though the case-specific marginal cost of eradication can be expected to be high (relative to a simple control approach), successful eradication would mean massive recurring savings in the long-term [@Barrett2013].
-However, to the extent that the case-specific marginal cost of prevention in an eradication campaign is high, estimating the likelihood of success is fundamental to the correct distribution of resources, particularly in low-income environments.
-}
 
@@
 A majority (`r round(320 / 540 * 100, digits = 2)`%) were descriptive.
-Descriptive commenters were more pessimistic (in regards to perceived years until eradication) than prescriptive commenters, though this difference did not reach the level of statistical significance (p = 0.21).
+Descriptive commenters were more pessimistic (in regards to perceived years until eradication) than prescriptive commenters, though this difference did not reach the level of statistical significance (p = 0.21 using Pearson's Chi-squared test).
 Descriptive comments also received sentiment polarity scores which were more negative than prescriptive comments, although again this difference did not reach the level of statistical significance (p = 0.18).
@@
 Their experiences and viewpoints may be different from those of academics, and arguably more relevant.
-Additionally, in public health journals, first authors are often more junior than their collaborators.
-By focusing solely on first authors, we may have unintentionally created a sample which is qualitatively different than the true universe of malaria researchers; to the extent that in our result pool researchers with less experience (as represented through publications) tended to be more "optimistic" regarding eradication, it is reasonable to assume that the restriction of first authors may have lead to an overly optimistic sample, making the results of the survey even more striking.
+Our de-biasing method accounts for different response rates of "senior" vs.
+"junior" researchers, but does not take into account the fact that first authors are generally more junior than senior authors (ie, the pool from which we sampled may have been biased itself).
+To the extent that in our results suggests that those with less experience (as represented through publications) tended to be more "optimistic" regarding eradication, it is reasonable to assume that the restriction of first authors may have lead to an overly optimistic sample, making the results of the survey even more striking.
 
@@
 
-Our survey attempted to quantify the likelihood of, and time frame to, malaria eradication by gauging the collective opinion of malaria researchers.
 The findings of our survey show researchers expressing hesitance about the likelihood of eradication and suggesting a long time frame until it is achieved.

### 2020-04-15 code/prepare_data.R

@@ -1,0 +1,592 @@
+get_new_data <- FALSE
+library(dplyr)
+library(ggplot2)
+library(tidyr)
+library(broom)
+library(RColorBrewer)
+# library(Hmisc)
+# library(Rmisc)
+# install.packages(c("gender", "genderdata"),
+#                  repos = "http://packages.ropensci.org",
+#                  type = "source")
+library(gender)
+library(wru)
+library(sampleSelection)
+library(stargazer)
+library(nnet)
+
+if('prepared_data.RData' %in% dir()){
+  load('prepared_data.RData')
+} else {
+  
+  # Send emails
+  source('code/recruit.R', chdir = TRUE)
+  
+  # Get number of citations of each article (sept 2017)
+  citations_df <- data_frame(id = as.character(sort(unique(final_authors$id))),
+                             n_citations = NA)
+  if(!'citations.RData' %in% dir('data')){
+    for (i in 1:nrow(citations_df)){
+      message(paste0(i, ' of ', nrow(citations_df)))
+      try({
+        res <- EUtilsSummary(paste0(citations_df$id[i],
+                                    '[uid]'))
+        citations_df$n_citations[i] <- Cited(res)
+      })
+    }
+    
+    citations_df <- 
+      citations_df %>%
+      arrange(desc(n_citations))
+    save(citations_df, 
+         file = 'data/citations.RData')
+  } else {
+    load('data/citations.RData')
+  }
+  
+  
+  # Get average and total number of citations per author
+  citations_metrics <-
+    final_authors %>%
+    left_join(citations_df) %>%
+    group_by(author) %>%
+    summarise(n_citations_total = sum(n_citations, na.rm = TRUE),
+              n_citations_average = mean(n_citations, na.rm = TRUE))
+  
+  # Join that data to our author data
+  final_authors_aggregated <-
+    left_join(final_authors_aggregated,
+              citations_metrics,
+              by = 'author')
+  
+  if(get_new_data){
+    file_name <- paste0('snapshot_', Sys.Date(), '.RData')
+  } else {
+    snaps <- dir('snapshots')
+    dates <- as.Date(substr(snaps, 10, 19))
+    file_name <- snaps[which.max(dates)]
+  }
+  if(!file_name %in% dir('snapshots')){
+    # Fetch data
+    library(gsheet)
[…]

### 2020-04-15 code/theme_publication.R

@@ -1,0 +1,94 @@
+# https://rpubs.com/Koundy/71792
+
+theme_publication <- function(base_size=9) {
+  library(grid)
+  library(ggthemes)
+  (theme_foundation(base_size=base_size)
+    + theme(plot.title = element_text(#face = "bold",
+                                      size = rel(1.2), hjust = 0.5),
+            text = element_text(),
+            panel.background = element_rect(colour = NA),
+            plot.background = element_rect(colour = NA),
+            panel.border = element_rect(colour = NA),
+            axis.title = element_text(#face = "bold",
+                                      size = rel(1)),
+            axis.title.y = element_text(angle=90,vjust =2),
+            axis.title.x = element_text(vjust = -0.2),
+            axis.text = element_text(), 
+            axis.line = element_line(colour="black"),
+            axis.ticks = element_line(),
+            panel.grid.major = element_line(colour="#f0f0f0"),
+            panel.grid.minor = element_blank(),
+            legend.key = element_rect(colour = NA),
+            legend.position = "bottom",
+            legend.direction = "horizontal",
+            legend.key.size= unit(0.2, "cm"),
+            # legend.margin = unit(0, "cm"),
+            legend.title = element_text(face="italic"),
+            plot.margin=unit(c(10,5,5,5),"mm"),
+            strip.background=element_rect(colour="#f0f0f0",fill="#f0f0f0"),
+            strip.text = element_text(face="bold")
+    ))
+  
+}
+
+scale_fill_publication <- function(...){
+  library(scales)
+  discrete_scale("fill","publication",manual_pal(values = c("#386cb0","#fdb462","#7fc97f","#ef3b2c","#662506","#a6cee3","#fb9a99","#984ea3","#ffff33")), ...)
+  
+}
+
+scale_colour_publication <- function(...){
+  library(scales)
+  discrete_scale("colour","publication",manual_pal(values = c("#386cb0","#fdb462","#7fc97f","#ef3b2c","#662506","#a6cee3","#fb9a99","#984ea3","#ffff33")), ...)
+  
+}
+
+library(ggplot2)
+library(gridExtra)
+
+theme_black = function(base_size = 12, base_family = "") {
+  
+  theme_grey(base_size = base_size, base_family = base_family) %+replace%
+    
+    theme(
+      # Specify axis options
+      axis.line = element_blank(),  
+      axis.text.x = element_text(size = base_size*0.8, color = "white", lineheight = 0.9),  
[…]

### 2020-04-15 extra_visualizations.R

@@ -1,137 +1,0 @@
-
-
-g1 <- ggplot(data = df %>%
-               mutate(responded = ifelse(responded, 'Respondents', 'Non-respondents')), 
-             aes(x = n_citations_total)) +
-  geom_density(aes(group = responded,
-                   fill = responded),
-               alpha = 0.6) +
-  scale_x_log10() +
-  theme_paper() +
-  scale_fill_manual(name = '',
-                    values = c('darkorange', 'lightblue')) +
-  labs(x = 'Citations (log scale)',
-       y = 'Density',
-       title = 'Total lifetime citations')
-
-
-Again, the distribution is shown below (b). 
-
-
-g2 <- ggplot(data = df %>%
-               mutate(responded = ifelse(responded, 'Respondents', 'Non-respondents')), 
-             aes(x = n_citations_average)) +
-  geom_density(aes(group = responded,
-                   fill = responded),
-               alpha = 0.6,
-               n = 10) +
-  scale_x_log10() +
-  theme_paper() +
-  scale_fill_manual(name = '',
-                    values = c('darkorange', 'lightblue')) +
-  labs(x = 'Citations (log scale)',
-       y = 'Density',
-       title = 'Average citations per article')
-# Rmisc::multiplot(g1, g2, cols = 2)
-g1
-g2
-
-
-{r, fig.height = 4.5, fig.width = 4.5}
-# Get averages per area
-results_list <- list()
-dist_list <- list()
-year_list <- list()
-areas_df <- areas_df %>% arrange(desc(count))
-small_areas <- areas_df$area[1:12]
-for (i in 1:length(small_areas)){
-  this_area <- small_areas[i]
-  sub_data <- df[df[,paste0('area_', gsub(' ', '_', this_area))],]
-  this_df <- data_frame(area = this_area,
-                        avg = mean(sub_data$years, na.rm = TRUE),
-                        med = median(sub_data$years, na.rm = TRUE))
-  dist_df <- data_frame(area = this_area,
-                        val = sub_data$years)
-  numberfy <- function(x){
-    ifelse(x == '0%', 0,
-           ifelse(x == '1-20%', 10,
-                  ifelse(x == '21-40%', 30,
-                         ifelse(x == '41-60%', 50,
-                                ifelse(x == '61-80%', 70,
-                                       ifelse(x == '81-99%', 90,
-                                              ifelse(x == '100%', 100, NA)))))))
-    
-  }
[…]

### 2020-04-15 legacy/extra_visualizations.R

@@ -1,0 +1,137 @@
+
+
+g1 <- ggplot(data = df %>%
+               mutate(responded = ifelse(responded, 'Respondents', 'Non-respondents')), 
+             aes(x = n_citations_total)) +
+  geom_density(aes(group = responded,
+                   fill = responded),
+               alpha = 0.6) +
+  scale_x_log10() +
+  theme_paper() +
+  scale_fill_manual(name = '',
+                    values = c('darkorange', 'lightblue')) +
+  labs(x = 'Citations (log scale)',
+       y = 'Density',
+       title = 'Total lifetime citations')
+
+
+Again, the distribution is shown below (b). 
+
+
+g2 <- ggplot(data = df %>%
+               mutate(responded = ifelse(responded, 'Respondents', 'Non-respondents')), 
+             aes(x = n_citations_average)) +
+  geom_density(aes(group = responded,
+                   fill = responded),
+               alpha = 0.6,
+               n = 10) +
+  scale_x_log10() +
+  theme_paper() +
+  scale_fill_manual(name = '',
+                    values = c('darkorange', 'lightblue')) +
+  labs(x = 'Citations (log scale)',
+       y = 'Density',
+       title = 'Average citations per article')
+# Rmisc::multiplot(g1, g2, cols = 2)
+g1
+g2
+
+
+{r, fig.height = 4.5, fig.width = 4.5}
+# Get averages per area
+results_list <- list()
+dist_list <- list()
+year_list <- list()
+areas_df <- areas_df %>% arrange(desc(count))
+small_areas <- areas_df$area[1:12]
+for (i in 1:length(small_areas)){
+  this_area <- small_areas[i]
+  sub_data <- df[df[,paste0('area_', gsub(' ', '_', this_area))],]
+  this_df <- data_frame(area = this_area,
+                        avg = mean(sub_data$years, na.rm = TRUE),
+                        med = median(sub_data$years, na.rm = TRUE))
+  dist_df <- data_frame(area = this_area,
+                        val = sub_data$years)
+  numberfy <- function(x){
+    ifelse(x == '0%', 0,
+           ifelse(x == '1-20%', 10,
+                  ifelse(x == '21-40%', 30,
+                         ifelse(x == '41-60%', 50,
+                                ifelse(x == '61-80%', 70,
+                                       ifelse(x == '81-99%', 90,
+                                              ifelse(x == '100%', 100, NA)))))))
+    
+  }
[…]

### 2020-04-15 prepare_data.R

@@ -1,592 +1,0 @@
-get_new_data <- FALSE
-library(dplyr)
-library(ggplot2)
-library(tidyr)
-library(broom)
-library(RColorBrewer)
-# library(Hmisc)
-# library(Rmisc)
-# install.packages(c("gender", "genderdata"),
-#                  repos = "http://packages.ropensci.org",
-#                  type = "source")
-library(gender)
-library(wru)
-library(sampleSelection)
-library(stargazer)
-library(nnet)
-
-if('prepared_data.RData' %in% dir()){
-  load('prepared_data.RData')
-} else {
-  
-  # Send emails
-  source('code/recruit.R', chdir = TRUE)
-  
-  # Get number of citations of each article (sept 2017)
-  citations_df <- data_frame(id = as.character(sort(unique(final_authors$id))),
-                             n_citations = NA)
-  if(!'citations.RData' %in% dir('data')){
-    for (i in 1:nrow(citations_df)){
-      message(paste0(i, ' of ', nrow(citations_df)))
-      try({
-        res <- EUtilsSummary(paste0(citations_df$id[i],
-                                    '[uid]'))
-        citations_df$n_citations[i] <- Cited(res)
-      })
-    }
-    
-    citations_df <- 
-      citations_df %>%
-      arrange(desc(n_citations))
-    save(citations_df, 
-         file = 'data/citations.RData')
-  } else {
-    load('data/citations.RData')
-  }
-  
-  
-  # Get average and total number of citations per author
-  citations_metrics <-
-    final_authors %>%
-    left_join(citations_df) %>%
-    group_by(author) %>%
-    summarise(n_citations_total = sum(n_citations, na.rm = TRUE),
-              n_citations_average = mean(n_citations, na.rm = TRUE))
-  
-  # Join that data to our author data
-  final_authors_aggregated <-
-    left_join(final_authors_aggregated,
-              citations_metrics,
-              by = 'author')
-  
-  if(get_new_data){
-    file_name <- paste0('snapshot_', Sys.Date(), '.RData')
-  } else {
-    snaps <- dir('snapshots')
-    dates <- as.Date(substr(snaps, 10, 19))
-    file_name <- snaps[which.max(dates)]
-  }
-  if(!file_name %in% dir('snapshots')){
-    # Fetch data
-    library(gsheet)
[…]

### 2020-04-15 theme_publication.R

@@ -1,94 +1,0 @@
-# https://rpubs.com/Koundy/71792
-
-theme_publication <- function(base_size=9) {
-  library(grid)
-  library(ggthemes)
-  (theme_foundation(base_size=base_size)
-    + theme(plot.title = element_text(#face = "bold",
-                                      size = rel(1.2), hjust = 0.5),
-            text = element_text(),
-            panel.background = element_rect(colour = NA),
-            plot.background = element_rect(colour = NA),
-            panel.border = element_rect(colour = NA),
-            axis.title = element_text(#face = "bold",
-                                      size = rel(1)),
-            axis.title.y = element_text(angle=90,vjust =2),
-            axis.title.x = element_text(vjust = -0.2),
-            axis.text = element_text(), 
-            axis.line = element_line(colour="black"),
-            axis.ticks = element_line(),
-            panel.grid.major = element_line(colour="#f0f0f0"),
-            panel.grid.minor = element_blank(),
-            legend.key = element_rect(colour = NA),
-            legend.position = "bottom",
-            legend.direction = "horizontal",
-            legend.key.size= unit(0.2, "cm"),
-            # legend.margin = unit(0, "cm"),
-            legend.title = element_text(face="italic"),
-            plot.margin=unit(c(10,5,5,5),"mm"),
-            strip.background=element_rect(colour="#f0f0f0",fill="#f0f0f0"),
-            strip.text = element_text(face="bold")
-    ))
-  
-}
-
-scale_fill_publication <- function(...){
-  library(scales)
-  discrete_scale("fill","publication",manual_pal(values = c("#386cb0","#fdb462","#7fc97f","#ef3b2c","#662506","#a6cee3","#fb9a99","#984ea3","#ffff33")), ...)
-  
-}
-
-scale_colour_publication <- function(...){
-  library(scales)
-  discrete_scale("colour","publication",manual_pal(values = c("#386cb0","#fdb462","#7fc97f","#ef3b2c","#662506","#a6cee3","#fb9a99","#984ea3","#ffff33")), ...)
-  
-}
-
-library(ggplot2)
-library(gridExtra)
-
-theme_black = function(base_size = 12, base_family = "") {
-  
-  theme_grey(base_size = base_size, base_family = base_family) %+replace%
-    
-    theme(
-      # Specify axis options
-      axis.line = element_blank(),  
-      axis.text.x = element_text(size = base_size*0.8, color = "white", lineheight = 0.9),  
[…]
